### 2018-06-26 Chapters/Chapter1.tex
Initial commit

\chapter{Chapter Title Here} % Main chapter title

Here we will do stuff.

### 2018-06-26 main.tex
Initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis 
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{multicol}

\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3.8cm, % Outer margin
	bindingoffset=.5cm, % Binding offset
	top=1.5cm, % Top margin
	bottom=1.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Doctor of Philosophy} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Juan Manuel Losada} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Biological Sciences} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{NTNU} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://department.university.com}{Department or School Name}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{http://researchgroup.university.com}{Research Group Name}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

\begin{document}

\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Master Thesis}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Juan Manuel Losada
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright}
\emph{Supervisor:} \\
Arne Brataas

\emph{Co-supervisor:}\\
Alireza Qaiumzadeh
\end{flushright}

\end{minipage}\\[3cm]

\end{center}
\end{titlepage}

\tableofcontents % Prints the main table of contents

\mainmatter % Begin numeric (1,2,3...) page numbering
\pagestyle{thesis} % Return the page headers back to the "thesis" style

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2018-07-01 Chapters/Chapter1.tex
Bloch Theorem and apendix1

@@
 Here we will do stuff.
+
+The one particle part of the Hamiltonian can be written as:
+
+\begin{equation}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar}{2m}\Delta^2_{\textbf{r}} + U(\textbf{r})
+\end{equation}
+
+Where $U(\textbf{r})$ has the symmetry of the lattice, i.e.
+$U(\textbf{r} + \textbf{R}) = U(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
+The group of translation symmetries $T_{\textbf{R}}\phi(\textbf{r}) = \phi(\textbf{r} + \textbf{R})$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong: $T_{\textbf{R}}\phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{R}) \phi_{n, \textbf{k}}(\textbf{r})$.
+Now, imposing periodic boundary conditions, $\phi_{n, \textbf{k}}(\textbf{r} + L_\mu \textbf{a}_\mu) = \Gamma^{\textbf{k}}(L_\mu \textbf{a}_\mu) \phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} \phi_{n, \textbf{k}}(\textbf{r}) = \phi_{n, \textbf{k}}(\textbf{r})$, so that, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, this can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
+Therefore, for a wavefunction in a periodic lattice we have:
+
+\begin{equation}
+\phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
+\end{equation}
+
+\begin{subappendices}
+\begin{section}{Crystal structure and reciprocal lattice}
+\label{AP1A}
+
+Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\textbf{a}_\mu$:
+
+\begin{equation}
+\textbf{R} = \sum_{\mu=1}^3 m_\mu \textbf{a}_\mu
+\end{equation}
+
+Where $m_\mu$ are integers.
+The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
+The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
+With this notation the first Brillouin zone is:
+
+\begin{equation}
+\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
+\end{equation}
+
+Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
+We will only consider cubic lattices where $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
+
+\end{section}
+\end{subappendices}

### 2018-07-02 Chapters/Chapter1.tex
Added Wannier

@@
 
-Here we will do stuff.
+\begin{section}{Free particle in a periodic potential}
 
@@
 \begin{equation}
+\label{Bloch1}
 \phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
 \end{equation}
+
+Which is the well-known Bloch function form.
+Here, $n$ is called the band index, and $\textbf{k}$ is the quasimomentum.
+The energy of this wavefunction is $\epsilon_{n \textbf{k}}$.
+Notice that both $\phi_{n,\textbf{k}}$ and $\epsilon_{n \textbf{k}}$ are periodic functions of $\textbf{k}$ in the reciprocal lattice.
+
+The Bloch function is extended over the whole crystal volume $V$.
+We would like to work with a localized basis.
+An alternative orthonormal basis are the Wannier functions, defined in terms of the Bloch functions as:
+
+\begin{equation}
+\psi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
+\end{equation}
+
+Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
+Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+
+\end{section}
+
+\begin{section}{Derivation of the single-band Hubbard model}
+
+The Hamiltonian for a system of $N_e$ electrons has the form:
+
+\begin{equation}
+\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
+\end{equation}
+
+Where $v$ represents the electron-electron interaction.
+
+\end{section}
 
@@
 The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
+The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
 The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.

### 2018-07-04 Chapters/Chapter1.tex
Derive Hubbard

@@
 \begin{equation}
+\label{Ham1}
 \hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
@@
 
-Where $v$ represents the electron-electron interaction.
+Where $v$ represents the electron-electron interaction and $\hat{H}^{(1)}$ is the free particle Hamiltonian.
+We use the Wannier functions $\Phi_j$ as a basis and restrict ourselves to a fixed band so we don't write the band index.
+Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\Phi_j$ and spin $\sigma$.
+In this basis, the second quantized form of \ref{Ham1} is:
+
+\begin{equation}
+\hat{H} = -\sum_{i,j,\sigma} t_{i,j} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\end{equation}
+
+Where $t_{ij} = \bra{i} \hat{H}^{(1)} \ket{j} = t_{ji}^*$.
+And where we assume $\hat{H}^{(1)}$ and $\hat{v}$ to be spin independent.
+Also we assume that $t_{ii} = t(0) = 0$.
+For a system of strongly correlated electrons we can assume that:
+
+\begin{itemize}
+\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
+In an isotropic system we can approximate:
+
+\begin{equation}
+t_{ij} = \begin{cases}
+             t,  & \text{for } (i,j) \text{ nearest neighbous} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
+\end{equation}
+
+\item The dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$ since the Coulomb interaction will be screened for further electrons. Therefore we approximate:
+
+\begin{equation}
+\bra{ij} \hat{v} \ket{kl} =
+	\begin{cases}
+		U, & \text{if } i=j=k=l \\
+		0, & \text{otherwise}
+	\end{cases}						
+\end{equation}
+
+Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$.
+
+\end{itemize}
+
+Taking these approximations we obtain the single band Hubbard model:
+
+\begin{equation}
+\hat{H} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.) + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
 

### 2018-07-08 Chapters/Chapter1.tex
Heisenber model

@@
 
-Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$.
+Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$
 
@@
 \begin{equation}
+\label{Hubbard}
 \hat{H} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.) + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
+
+\end{section}
+
+\begin{section}{Heisenberg antiferromagnet from Hubbard model}
+
+At half filling, in the $t << U$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
+There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
+The ground state energy is $0$.
+The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
+The energy of one of these states is $U$.
+Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
+Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
+
+Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.)$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be state from the ground state, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
+In second order we have:
+
+\begin{equation}
+\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
+\end{equation}
+
+The sum being over all excited states.
+Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
+These states have energy $E_s = U$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{U}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi}$.
+These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{U}$.
+Now,
+
+\begin{align*}
+	\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} =
+	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma} \sum_{\langle i',j' \rangle, \sigma'} \hat{c}_{i \sigma}^\dagger 			\hat{c}_{j \sigma} \hat{c}_{i' \sigma'}^\dagger \hat{c}_{j' \sigma'} \ket{\phi} =
+	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \ket{\phi} &= \\
+	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \ket{\phi} &
+\end{align*}
+
+Where we imposed $i=j'$ and $j=i'$ because that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
+Let us now introduce the on-site spin operators:
+
+\begin{equation}
+\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
+\end{equation}
+
+Which satisfy:
+
+\begin{align*}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \\ 
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} 
+\end{align*}
+
+Introducing these relations into $H_{eff}$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
+
+\begin{align*}
+H_{eff} = -\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i				\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}				_{\sigma \sigma'}\right) = \\
+-\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 							\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b =
+-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} &= \\
+-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+\end{align*}
+
+The constant term can be neglected leaving:
+
+\begin{equation}
+H_{eff} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\end{equation}
+
+Which is the Heisenberg model for antiferromagnets.
 

### 2018-07-22 Chapters/Chapter1.tex
Include SO

@@
 \begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar}{2m}\Delta^2_{\textbf{r}} + U(\textbf{r})
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r})
 \end{equation}
@@
 
-The Hamiltonian for a system of $N_e$ electrons has the form:
+The single particle Hamiltonian including spin orbit interaction is $\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}$, where $\lambda = \frac{\hbar^2}{4m^2c^2}$.
+Including interaction, the Hamiltonian for a system of $N_e$ electrons has the form:
 
@@
 
-Where $v$ represents the electron-electron interaction and $\hat{H}^{(1)}$ is the free particle Hamiltonian.
+Where $v$ represents the electron-electron interaction.
 We use the Wannier functions $\Phi_j$ as a basis and restrict ourselves to a fixed band so we don't write the band index.
@@
 \begin{equation}
-\hat{H} = -\sum_{i,j,\sigma} t_{i,j} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
 \end{equation}
 
-Where $t_{ij} = \bra{i} \hat{H}^{(1)} \ket{j} = t_{ji}^*$.
+Where $t_{ij} = \bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = \bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
 And where we assume $\hat{H}^{(1)}$ and $\hat{v}$ to be spin independent.
-Also we assume that $t_{ii} = t(0) = 0$.
+Also we can impose that $t_{ii} = t(0) = 0$.
 For a system of strongly correlated electrons we can assume that:
@@
 \begin{itemize}
-\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
+\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\boldsymbol{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
 In an isotropic system we can approximate:
@@
 \end{equation}
+
+and
+
+\begin{equation}
+\boldsymbol{\Delta}_{ij} = \begin{cases}
+             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbous} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
+\end{equation}
+
+(What about i=j for $\Delta$?)
 
@@
 \label{Hubbard}
-\hat{H} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.) + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 
-Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.)$.
+Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
 Let $\ket{\phi}$ and $\ket{\phi'}$ be state from the ground state, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
@@
 \begin{align*}
-	\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} =
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma} \sum_{\langle i',j' \rangle, \sigma'} \hat{c}_{i \sigma}^\dagger 			\hat{c}_{j \sigma} \hat{c}_{i' \sigma'}^\dagger \hat{c}_{j' \sigma'} \ket{\phi} =
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \ket{\phi} &= \\
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \ket{\phi} &
+&\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} (t^2 \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t(\delta_{\sigma_1 \sigma_2}		\boldsymbol{\Delta}_{i'j'}\boldsymbol{\sigma}_{\sigma_3 \sigma_4} + \delta_{\sigma_3 \sigma_4}						\boldsymbol{\Delta}_{ij}\boldsymbol{\sigma}_{\sigma_1 \sigma_2}) + \mathcal{O}(\boldsymbol{\Delta}^2)) 				\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4}					\ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 					\sigma_4}) + \mathcal{O}(\boldsymbol{\Delta}^2)) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \hat{H}_J + \hat{H}_D + \mathcal{O}(\boldsymbol{\Delta}^2))\ket{\phi}
 \end{align*}
 
-Where we imposed $i=j'$ and $j=i'$ because that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
+In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
+We will neglect the $\mathcal{O}(\boldsymbol{\Delta}^2)$ term since $t$ is dominant.
+
 Let us now introduce the on-site spin operators:
@@
 
-Introducing these relations into $H_{eff}$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
+Introducing these relations into $H_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
 
 \begin{align*}
-H_{eff} = -\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i				\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}				_{\sigma \sigma'}\right) = \\
--\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 							\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b =
--\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} &= \\
--\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+\hat{H}_{J} = &-\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b = 
+-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \\
+&-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
 \end{align*}
@@
 \begin{equation}
-H_{eff} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\hat{H}_{J} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
 \end{equation}
 
-Which is the Heisenberg model for antiferromagnets.
+Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{U}$. Likewise, for $\hat{H}_D$:
+
+\begin{align*}
+\hat{H}_D = &-\frac{t}{U} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&-\frac{2t}{U}\sum_{\langle i,j \rangle} \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) = \\
+&-\frac{4it}{U} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{align*}
+
+Where $\boldsymbol{D}_{ij} = -\frac{4it}{U}\boldsymbol{\Delta}_{ij}$.
 

### 2018-07-22 Chapters/Chapter1.tex
style changes

@@
 
-\begin{section}{Free particle in a periodic potential}
+In this chapter we will start with a Hamiltonian
 
-The one particle part of the Hamiltonian can be written as:
+\begin{equation}
+\label{Ham1}
+\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
+\end{equation}
+
+where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian.
+
+\begin{equation}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}
+\end{equation}
+
+Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ and $U(\bs{r})$ is a periodic potential. In this Chapter we will derive an effective Hamiltonian using time independent perturbation theory.
+
+\begin{section}{Single particle in a periodic potential}
+
+First we will define a suitable basis for the single particle wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
 
@@
 \begin{equation}
-\psi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
+\phi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
 \end{equation}
@@
 Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
-Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+Using \ref{Bloch1} we see that $\phi_{in}(\textbf{r}) = \phi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \phi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+We will restrict ourselves to a fixed band, so we will drop the band index and write $\phi_i(\bs{r})$ or $\ket{i}$.
 
@@
 
-The single particle Hamiltonian including spin orbit interaction is $\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}$, where $\lambda = \frac{\hbar^2}{4m^2c^2}$.
-Including interaction, the Hamiltonian for a system of $N_e$ electrons has the form:
-
-\begin{equation}
-\label{Ham1}
-\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
-\end{equation}
-
-Where $v$ represents the electron-electron interaction.
-We use the Wannier functions $\Phi_j$ as a basis and restrict ourselves to a fixed band so we don't write the band index.
-Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\Phi_j$ and spin $\sigma$.
+In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
+Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\phi_j$ and spin $\sigma$.
 In this basis, the second quantized form of \ref{Ham1} is:
@@
 Where $t_{ij} = \bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = \bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
-And where we assume $\hat{H}^{(1)}$ and $\hat{v}$ to be spin independent.
+Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
+We assumed $\hat{v}$ to be spin independent.
 Also we can impose that $t_{ii} = t(0) = 0$.
@@
 
-\begin{section}{Heisenberg antiferromagnet from Hubbard model}
+\begin{section}{Effective Hamiltonian for half-filling system}
 
@@
 
-Where $\boldsymbol{D}_{ij} = -\frac{4it}{U}\boldsymbol{\Delta}_{ij}$.
+Where $\boldsymbol{D}_{ij} = -\frac{4it}{U}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
+
+\begin{equation}
+\hat{H}_{eff} = \sum_{\langle i,j \rangle} J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{equation}
 

### 2018-09-03 Chapters/Chapter2.tex
chap 2
chap 2

\chapter{Perturbing the lattice}

In this chapter we will study how introducing an electromagnetic perturbation in \ref{Ham1} can affect the parameters $J$ and $\boldsymbol{D}_{ij}$ of the effective Hamiltonian.

\section{Modified exchange interaction}

We start by considering only the exchange interaction part. Consider the Hamiltonian:

\begin{equation}
\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$. The electric field has the form $\bs{E}(t) = E_0 (\sin (\omega t) \hat{e}_x + \lambda \cos (\omega t)\hat{e}_y)$ where $\lambda = 0, \pm 1$ representing planar or circular polarized field. We can therefore take $A_{ij} = \frac{E_0}{\omega} (-\cos(\omega t)\hat{e}_x +  \lambda \sin(\omega t)\hat{e}_y)\hat{e}_{ij}$, where $\hat{e}_{ij}$ is a unit vector pointing from site $i$ to site $j$.

The Hamiltonan with the new $t_{ij}(t)$ is periodic in time with period $T=\frac{2\pi}{\omega}$. According to Floquet's theorem there exist solutions that have the form $\ket{\psi(t)} = e^{-i \epsilon_\alpha t} \ket{\psi_\alpha (t)}$ where $\ket{\psi_\alpha(t)}$ has also period $T$, and so it can be expanded in Fourier series $\ket{\psi_\alpha(t)} = \sum_m e^{i\omega mt} \ket{\psi_{\alpha,m}}$

### 2018-09-04 Chapters/Chapter1.tex
introchap

--- 2018-07-08 Chapters/Chapter1.tex
@@
-\chapter{Chapter Title Here} % Main chapter title
+\chapter{AFM spinotronics}
 
-\begin{section}{Free particle in a periodic potential}
+https://arxiv.org/ftp/arxiv/papers/1506/1506.07507.pdf
 
-The one particle part of the Hamiltonian can be written as:
+Exploiting both spin and charge of the electron in electronic microdevices has lead to a tremendous progress in both basic
+condensed-matter research and microelectronic applications, resulting in the modern field of spintronics. Current spintronics
+relies primarily on ferromagnets while antiferromagnets have traditionally played only a supporting role. Recently,
+antiferromagnets have been revisited as potential candidates for the key active elements in spintronic devices.
 
-\begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar}{2m}\Delta^2_{\textbf{r}} + U(\textbf{r})
-\end{equation}
+\section{History and background}
 
-Where $U(\textbf{r})$ has the symmetry of the lattice, i.e.
-$U(\textbf{r} + \textbf{R}) = U(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
-The group of translation symmetries $T_{\textbf{R}}\phi(\textbf{r}) = \phi(\textbf{r} + \textbf{R})$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong: $T_{\textbf{R}}\phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{R}) \phi_{n, \textbf{k}}(\textbf{r})$.
-Now, imposing periodic boundary conditions, $\phi_{n, \textbf{k}}(\textbf{r} + L_\mu \textbf{a}_\mu) = \Gamma^{\textbf{k}}(L_\mu \textbf{a}_\mu) \phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} \phi_{n, \textbf{k}}(\textbf{r}) = \phi_{n, \textbf{k}}(\textbf{r})$, so that, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, this can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
-Therefore, for a wavefunction in a periodic lattice we have:
-
-\begin{equation}
-\label{Bloch1}
-\phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
-\end{equation}
-
-Which is the well-known Bloch function form.
-Here, $n$ is called the band index, and $\textbf{k}$ is the quasimomentum.
-The energy of this wavefunction is $\epsilon_{n \textbf{k}}$.
-Notice that both $\phi_{n,\textbf{k}}$ and $\epsilon_{n \textbf{k}}$ are periodic functions of $\textbf{k}$ in the reciprocal lattice.
-
-The Bloch function is extended over the whole crystal volume $V$.
-We would like to work with a localized basis.
-An alternative orthonormal basis are the Wannier functions, defined in terms of the Bloch functions as:
-
-\begin{equation}
-\psi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
-\end{equation}
-
-Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
-Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
-
-\end{section}
-
-\begin{section}{Derivation of the single-band Hubbard model}
-
-The Hamiltonian for a system of $N_e$ electrons has the form:
-
-\begin{equation}
-\label{Ham1}
-\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
-\end{equation}
-
-Where $v$ represents the electron-electron interaction and $\hat{H}^{(1)}$ is the free particle Hamiltonian.
-We use the Wannier functions $\Phi_j$ as a basis and restrict ourselves to a fixed band so we don't write the band index.
-Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\Phi_j$ and spin $\sigma$.
-In this basis, the second quantized form of \ref{Ham1} is:
-
-\begin{equation}
-\hat{H} = -\sum_{i,j,\sigma} t_{i,j} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
-\end{equation}
-
-Where $t_{ij} = \bra{i} \hat{H}^{(1)} \ket{j} = t_{ji}^*$.
-And where we assume $\hat{H}^{(1)}$ and $\hat{v}$ to be spin independent.
-Also we assume that $t_{ii} = t(0) = 0$.
-For a system of strongly correlated electrons we can assume that:
-
-\begin{itemize}
-\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
-In an isotropic system we can approximate:
-
-\begin{equation}
-t_{ij} = \begin{cases}
-             t,  & \text{for } (i,j) \text{ nearest neighbous} \\
-             0,  & \text{otherwise}
-       \end{cases} \quad
-\end{equation}
-
-\item The dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$ since the Coulomb interaction will be screened for further electrons. Therefore we approximate:
-
-\begin{equation}
-\bra{ij} \hat{v} \ket{kl} =
-	\begin{cases}
-		U, & \text{if } i=j=k=l \\
-		0, & \text{otherwise}
-	\end{cases}						
-\end{equation}
-
-Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$
-
-\end{itemize}
-
-Taking these approximations we obtain the single band Hubbard model:
-
-\begin{equation}
-\label{Hubbard}
-\hat{H} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.) + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation}
-
-\end{section}
-
-\begin{section}{Heisenberg antiferromagnet from Hubbard model}
-
-At half filling, in the $t << U$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
-First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
-There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
-The ground state energy is $0$.
-The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
-The energy of one of these states is $U$.
-Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
-Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
-
-Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -t\sum_{\langle i,j \rangle, \sigma}(\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + h.c.)$.
-Let $\ket{\phi}$ and $\ket{\phi'}$ be state from the ground state, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
-In second order we have:
-
-\begin{equation}
-\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
-\end{equation}
-
-The sum being over all excited states.
-Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
-These states have energy $E_s = U$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{U}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi}$.
-These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{U}$.
-Now,
-
-\begin{align*}
-	\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} =
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma} \sum_{\langle i',j' \rangle, \sigma'} \hat{c}_{i \sigma}^\dagger 			\hat{c}_{j \sigma} \hat{c}_{i' \sigma'}^\dagger \hat{c}_{j' \sigma'} \ket{\phi} =
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \ket{\phi} &= \\
-	\bra{\phi'} -\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \ket{\phi} &
-\end{align*}
-
-Where we imposed $i=j'$ and $j=i'$ because that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
-Let us now introduce the on-site spin operators:
-
-\begin{equation}
-\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
-\end{equation}
-
-Which satisfy:
-
-\begin{align*}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \\ 
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} 
-\end{align*}
-
-Introducing these relations into $H_{eff}$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
-
-\begin{align*}
-H_{eff} = -\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i				\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}				_{\sigma \sigma'}\right) = \\
--\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 							\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b =
--\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} &= \\
--\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
-\end{align*}
-
-The constant term can be neglected leaving:
-
-\begin{equation}
-H_{eff} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
-\end{equation}
-
-Which is the Heisenberg model for antiferromagnets.
-
-\end{section}
-
-\begin{subappendices}
-\begin{section}{Crystal structure and reciprocal lattice}
-\label{AP1A}
-
-Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\textbf{a}_\mu$:
-
-\begin{equation}
-\textbf{R} = \sum_{\mu=1}^3 m_\mu \textbf{a}_\mu
-\end{equation}
-
-Where $m_\mu$ are integers.
-The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
-The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
-The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
-With this notation the first Brillouin zone is:
-
-\begin{equation}
-\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
-\end{equation}
-
-Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
-We will only consider cubic lattices where $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
-
-\end{section}
-\end{subappendices}
+\section{AFM dynamics}

### 2018-09-04 Chapters/Chapter2.tex
introchap

@@
-\chapter{Perturbing the lattice}
+\chapter{Chapter Title Here} % Main chapter title
 
-In this chapter we will study how introducing an electromagnetic perturbation in \ref{Ham1} can affect the parameters $J$ and $\boldsymbol{D}_{ij}$ of the effective Hamiltonian.
-
-\section{Modified exchange interaction}
-
-We start by considering only the exchange interaction part. Consider the Hamiltonian:
+In this chapter we will start with a Hamiltonian
 
 \begin{equation}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\label{Ham1}
+\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
 \end{equation}
 
-Which is the Hamiltonian \ref{Hubbard} without DMI interaction.
-We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$.
-The electric field has the form $\bs{E}(t) = E_0 (\sin (\omega t) \hat{e}_x + \lambda \cos (\omega t)\hat{e}_y)$ where $\lambda = 0, \pm 1$ representing planar or circular polarized field.
-We can therefore take $A_{ij} = \frac{E_0}{\omega} (-\cos(\omega t)\hat{e}_x +  \lambda \sin(\omega t)\hat{e}_y)\hat{e}_{ij}$, where $\hat{e}_{ij}$ is a unit vector pointing from site $i$ to site $j$.
+where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian.
 
-The Hamiltonan with the new $t_{ij}(t)$ is periodic in time with period $T=\frac{2\pi}{\omega}$.
-According to Floquet's theorem there exist solutions that have the form $\ket{\psi(t)} = e^{-i \epsilon_\alpha t} \ket{\psi_\alpha (t)}$ where $\ket{\psi_\alpha(t)}$ has also period $T$, and so it can be expanded in Fourier series $\ket{\psi_\alpha(t)} = \sum_m e^{i\omega mt} \ket{\psi_{\alpha,m}}$
+\begin{equation}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}
+\end{equation}
+
+Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $U(\bs{r})$ is a periodic potential.
+The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
+Then, for a half filled system we will derive an effective Hamiltonian using time independent perturbation theory.
+
+\begin{section}{Single particle in a periodic potential}
+
+First we will define a suitable basis for the single particle wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
+
+\begin{equation}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r})
+\end{equation}
+
+Where $U(\textbf{r})$ has the symmetry of the lattice, i.e.
+$U(\textbf{r} + \textbf{R}) = U(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
+The group of translation symmetries $T_{\textbf{R}}\phi(\textbf{r}) = \phi(\textbf{r} + \textbf{R})$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong: $T_{\textbf{R}}\phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{R}) \phi_{n, \textbf{k}}(\textbf{r})$.
+Now, imposing periodic boundary conditions, $\phi_{n, \textbf{k}}(\textbf{r} + L_\mu \textbf{a}_\mu) = \Gamma^{\textbf{k}}(L_\mu \textbf{a}_\mu) \phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} \phi_{n, \textbf{k}}(\textbf{r}) = \phi_{n, \textbf{k}}(\textbf{r})$, so that, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, this can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
+Therefore, for a wavefunction in a periodic lattice we have:
+
+\begin{equation}
+\label{Bloch1}
+\phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
+\end{equation}
+
+Which is the well-known Bloch function form.
+Here, $n$ is called the band index, and $\textbf{k}$ is the quasimomentum.
+The energy of this wavefunction is $\epsilon_{n \textbf{k}}$.
+Notice that both $\phi_{n,\textbf{k}}$ and $\epsilon_{n \textbf{k}}$ are periodic functions of $\textbf{k}$ in the reciprocal lattice.
+
+The Bloch function is extended over the whole crystal volume $V$.
+We would like to work with a localized basis.
+An alternative orthonormal basis are the Wannier functions, defined in terms of the Bloch functions as:
+
+\begin{equation}
+\phi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
+\end{equation}
+
+Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
+Using \ref{Bloch1} we see that $\phi_{in}(\textbf{r}) = \phi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \phi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+We will restrict ourselves to a fixed band, so we will drop the band index and write $\phi_i(\bs{r})$ or $\ket{i}$.
+
+\end{section}
+
+\begin{section}{Derivation of the single-band Hubbard model}
+
+In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
+Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\phi_j$ and spin $\sigma$.
+In this basis, the second quantized form of \ref{Ham1} is:
+
+\begin{equation}
+\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\end{equation}
+
+Where $t_{ij} = \bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = \bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
+Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$ (why?), and therefore $\bs{\Delta}_{ii} = 0$.
+We assumed $\hat{v}$ to be spin independent.
+Also we can impose that $t_{ii} = t(0) = 0$.
+For a system of strongly correlated electrons we can assume that:
+
+\begin{itemize}
+\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\boldsymbol{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
+In an isotropic system we can approximate:
+
+\begin{equation}
+t_{ij} = \begin{cases}
+             t,  & \text{for } (i,j) \text{ nearest neighbous} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
+\end{equation}
+
+and
+
+\begin{equation}
+\boldsymbol{\Delta}_{ij} = \begin{cases}
+             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbous} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
+\end{equation}
+
+\item The dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$ since the Coulomb interaction will be screened for further electrons. Therefore we approximate:
+
+\begin{equation}
+\bra{ij} \hat{v} \ket{kl} =
+	\begin{cases}
+		U, & \text{if } i=j=k=l \\
+		0, & \text{otherwise}
+	\end{cases}						
+\end{equation}
+
+Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$
+
+\end{itemize}
+
+Taking these approximations we obtain the single band Hubbard model:
+
+\begin{equation}
+\label{Hubbard}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+\end{section}
+
+\begin{section}{Effective Hamiltonian for half-filling system}
+
+At half filling, in the $t << U$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
+There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
+The ground state energy is $0$.
+The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
+The energy of one of these states is $U$.
+Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
+Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
+
+Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be state from the ground state, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
+In second order we have:
+
+\begin{equation}
+\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
+\end{equation}
+
+The sum being over all excited states.
+Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
+These states have energy $E_s = U$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{U}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi}$.
+These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{U}$.
+Now,
+
+\begin{align*}
+&\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} (t^2 \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t(\delta_{\sigma_1 \sigma_2}		\boldsymbol{\Delta}_{i'j'}\boldsymbol{\sigma}_{\sigma_3 \sigma_4} + \delta_{\sigma_3 \sigma_4}						\boldsymbol{\Delta}_{ij}\boldsymbol{\sigma}_{\sigma_1 \sigma_2}) + \mathcal{O}(\boldsymbol{\Delta}^2)) 				\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4}					\ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 					\sigma_4}) + \mathcal{O}(\boldsymbol{\Delta}^2)) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \\
+&-\frac{1}{U} \bra{\phi'} \hat{H}_J + \hat{H}_D + \mathcal{O}(\boldsymbol{\Delta}^2))\ket{\phi}
+\end{align*}
+
+In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
+We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
+We will neglect the $\mathcal{O}(\boldsymbol{\Delta}^2)$ term since $t$ is dominant.
+
+Let us now introduce the on-site spin operators:
+
+\begin{equation}
+\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
+\end{equation}
+
+Which satisfy:
+
+\begin{align*}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \\ 
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} 
+\end{align*}
+
+Introducing these relations into $H_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
+
+\begin{align*}
+\hat{H}_{J} = &-\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b = 
+-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \\
+&-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+\end{align*}
+
+The constant term can be neglected leaving:
+
+\begin{equation}
+\hat{H}_{J} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\end{equation}
+
+Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{U}$. Likewise, for $\hat{H}_D$:
+
+\begin{align*}
+\hat{H}_D = &-\frac{t}{U} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&-\frac{2t}{U}\sum_{\langle i,j \rangle} \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) = \\
+&-\frac{4it}{U} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{align*}
+
+Where $\boldsymbol{D}_{ij} = -\frac{4it}{U}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
+
+\begin{equation}
+\hat{H}_{eff} = \sum_{\langle i,j \rangle} J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{equation}
+
+\end{section}
+
+\begin{subappendices}
+\begin{section}{Crystal structure and reciprocal lattice}
+\label{AP1A}
+
+Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\textbf{a}_\mu$:
+
+\begin{equation}
+\textbf{R} = \sum_{\mu=1}^3 m_\mu \textbf{a}_\mu
+\end{equation}
+
+Where $m_\mu$ are integers.
+The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
+The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
+The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
+With this notation the first Brillouin zone is:
+
+\begin{equation}
+\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
+\end{equation}
+
+Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
+We will only consider cubic lattices where $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
+
+\end{section}
+\end{subappendices}

### 2018-09-04 Chapters/Chapter3.tex
introchap

\chapter{Perturbing the lattice}

In this chapter we will study how introducing an electromagnetic perturbation in \ref{Ham1} can affect the parameters $J$ and $\boldsymbol{D}_{ij}$ of the effective Hamiltonian.

\section{Modified exchange interaction}

We start by considering only the exchange interaction part. Consider the Hamiltonian:

\begin{equation}
\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$. The electric field has the form $\bs{E}(t) = E_0 (\sin (\omega t) \hat{e}_x + \lambda \cos (\omega t)\hat{e}_y)$ where $\lambda = 0, \pm 1$ representing planar or circular polarized field. We can therefore take $A_{ij} = \frac{E_0}{\omega} (-\cos(\omega t)\hat{e}_x +  \lambda \sin(\omega t)\hat{e}_y)\hat{e}_{ij}$, where $\hat{e}_{ij}$ is a unit vector pointing from site $i$ to site $j$.

The Hamiltonan with the new $t_{ij}(t)$ is periodic in time with period $T=\frac{2\pi}{\omega}$. According to Floquet's theorem there exist solutions that have the form $\ket{\psi(t)} = e^{-i \epsilon_\alpha t} \ket{\psi_\alpha (t)}$ where $\ket{\psi_\alpha(t)}$ has also period $T$, and so it can be expanded in Fourier series $\ket{\psi_\alpha(t)} = \sum_m e^{i\omega mt} \ket{\psi_{\alpha,m}}$ introducing this ansatz in the Scrodinger equation and projecting into the m'th mode we obtain:

\begin{equation}
(\epsilon_\alpha-\omega m) \ket{\psi_{\alpha, m}} = \sum_{m'} = H_{m'-m} \ket{\psi_{\alpha,m'}}
\end{equation}

Where $H_m = \frac{1}{T}\int_0^T dt e^{i\omega mt} H(t)$. The hopping term with the Peierls phase has Fourier components:

\begin{equation}
H_{m,ij} = \begin{cases}
	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\mp iea\frac{E_0}{\omega}\cos(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{x} \\
	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\pm iea\lambda\frac{E_0}{\omega}\sin(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{y} \\
\end{cases} \quad
\end{equation}

### 2018-09-05 Chapters/Chapter1.tex
Add Melendley and some text

@@
 \chapter{AFM spinotronics}
+Historically ferromagnets have been widely studied as spintronic elements.
+However, today, the development of information technology demands devices with high storage density, high energy efficiency and high write/read speeds.
+Therefore, controlling magnetically ordered systems on subpicosecond timescales is currently a widely studied area.
+It has been shown that circularly polarized femtosecond laser pulses can be used to control the spin dynamics in magnets \cite{Kimel2005}.
+Antiferromagnetic metals have become an interesting alternative due to their rigidity to external magnetic field, and the abscence of stray field.
+
+Antiferromagnetism materials exhibits no net magnetization since the spins in the material align antiparallel to each other.
+Historiacally, ferromagnetic materials have been more interesting for practical applications, however recent researches show that antiferromagnetism has promising application in next generation spintronic devices.
+Controlling magnetically ordered systems on subpicosecond timescales.
 

### 2018-09-05 main.tex
Bloch Theorem and apendix1
Added Wannier
Derive Hubbard
Heisenber model
style changes
Add title
chap 2
chap 2
introchap
Add Melendley and some text

@@
 \usepackage{mathpazo} % Use the Palatino font by default
+\usepackage{appendix}
+\usepackage{chngcntr}
+\usepackage{etoolbox}
+\usepackage{amsmath}
+\usepackage{bm}
+\usepackage{braket}
 
@@
 
-\addbibresource{example.bib} % The filename of the bibliography
+\addbibresource{MT.bib} % The filename of the bibliography
 
@@
 
-\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{Ultrafast manipulation of exchange DMI in antiferromagnetic insulators} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
@@
 }
+
+% Start of subappendices environment
+\AtBeginEnvironment{subappendices}{%
+\chapter*{Appendices}
+\addcontentsline{toc}{chapter}{Appendices}
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+}
+
+% End of subappendices environment
+\AtEndEnvironment{subappendices}{%
+\counterwithout{figure}{section}
+\counterwithout{table}{section}
+}
+
+\newcommand{\bs}[1] {\boldsymbol{#1}}
 
@@
 \include{Chapters/Chapter1}
-%\include{Chapters/Chapter2} 
-%\include{Chapters/Chapter3}
+\include{Chapters/Chapter2} 
+\include{Chapters/Chapter3}
 %\include{Chapters/Chapter4} 

### 2018-09-11 Chapters/Chapter3.tex
commit

@@
 
-We start by considering only the exchange interaction part. Consider the Hamiltonian:
+We start by considering only the exchange interaction part in a one-dimensional lattice. Consider the Hamiltonian:
 
@@
 We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$.
-The electric field has the form $\bs{E}(t) = E_0 (\sin (\omega t) \hat{e}_x + \lambda \cos (\omega t)\hat{e}_y)$ where $\lambda = 0, \pm 1$ representing planar or circular polarized field.
-We can therefore take $A_{ij} = \frac{E_0}{\omega} (-\cos(\omega t)\hat{e}_x +  \lambda \sin(\omega t)\hat{e}_y)\hat{e}_{ij}$, where $\hat{e}_{ij}$ is a unit vector pointing from site $i$ to site $j$.
+The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)$ (one-dimensional lattice).
+We can therefore take $A_{ij} = -\frac{E_0}{\omega}\cos(\omega t)(i-j)$.
 
@@
 \begin{equation}
-H_{m,ij} = \begin{cases}
-	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\mp iea\frac{E_0}{\omega}\cos(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{x} \\
-	\frac{t_0}{T} \int_0^T dt e^{i\omega mt} e^{\pm iea\lambda\frac{E_0}{\omega}\sin(\omega t)}, & \text{for } \hat{e}_{ij} = \pm \hat{y} \\
-\end{cases} \quad
+H_{m} = \frac{t_0}{T} \sum_{\langle i,j \rangle, \sigma} \int_0^T dt e^{i\omega mt} e^{-iea\frac{E_0}{\omega}\cos(\omega t)(i-j)}\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma} = -t_0 \sum_{\langle i,j \rangle, \sigma} (-1)^mJ_m((i-j)ea\frac{E_0}{\omega})\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma}
 \end{equation}
+
+Where $J_m(x)$ is the \textit{m}th Bessel function.

### 2018-09-11 Chapters/Chapter1.tex

--- 2018-09-04 Chapters/Chapter1.tex
@@
 \chapter{AFM spinotronics}
-
-https://arxiv.org/ftp/arxiv/papers/1506/1506.07507.pdf
-
-Exploiting both spin and charge of the electron in electronic microdevices has lead to a tremendous progress in both basic
-condensed-matter research and microelectronic applications, resulting in the modern field of spintronics. Current spintronics
-relies primarily on ferromagnets while antiferromagnets have traditionally played only a supporting role. Recently,
-antiferromagnets have been revisited as potential candidates for the key active elements in spintronic devices.
 
@@
 
+Antiferromagnetism was first studied by L.
+Neel who introduced a thermodinamic theory that made it possible to explain the antiferromagnetic order and it pretict the existance of a temperature above which this order vanishes.
+This temperature is known as Neel temperature.
+In the next section we will present a semiclassical model for antiferromagnetic materials.
+
+During several decades after the discovery of antiferromagnetics, these materials were percived as useless from a practical point of view.On contrast, ferromagnets have been widely studied historically for its technical applications.
+However, in the frame of spinotronic devices, the development of information technology demands devices with high storage density, high energy efficiency and high write-read speeds.
+Therefore, controlling magnetically ordered systems on subpicosecond timescales is currently a widely studied area.
+Some progress has been done using ferromagnetic materials, for example, it has been shown that circularly polarized femtosecond laser pulses can be used to control the spin dynamics in magnets \cite{Kimel2005}.
+However, antiferromagnets aim to complement or even replace ferromagnets due to their rigidity to external magnetic field, and the abscence of stray field.
+
+It has been shown that spin-transfer torques and giant magnetoresistance effects can occur in circuits containing only normal and antiferromagnetic materials \cite{MacDonald2011}.
+Additionally, spin axis reorientation by a lateral electrical current can be used to offer ultra-fast electrical writing and reading in AFM devices \cite{Zelezny2014}.
+
 \section{AFM dynamics}

### 2018-09-16 Chapters/Chapter1.tex
Transformation

@@
 \section{AFM dynamics}
+
+In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics.
+We write the Heisenberg Hamiltonian as $\hat{H} = J \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j - K \sum_i S_{iz}^2$ with $J>0$ and $K$ is the anisotropy energy.
+Let the lattice be a one dimensional chain with $2N$ sites, such lattice can be described by the repetition of $N$ unit cells consisting of two sites $\alpha$ and $\beta$ for the left and right site respectively.
+Then the ground state of this Hamiltonian is double degenerated and is obtained by aligning the spins in the $\alpha$ sites in the $\hat{z}$ direction and the $\beta$ spins in the $-\hat{z}$ direction or vice versa.
+Let us introduce the parameters:
+
+\begin{align}
+\bs{m}_i &= \frac{\bs{S}_{\alpha}^i + \bs{S}_{\beta}^i}{2S} \\
+\bs{l}_i &= \frac{\bs{S}_{\alpha}^i - \bs{S}_{\beta}^i}{2S}
+\end{align}
+
+Where $S$ is the spin angular momentum in units of $\hbar$. Inverting these relations, introducing them into the Hamiltonian and neglecting edge terms we obtain:
+
+\begin{align}
+\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
+& 2JS^2\sum_i^{N} (\bs{m}_i^2-\bs{l}_i^2)+\frac{JS^2}{2}\sum_i^{N-1}\left[(\bs{l}_{i+1}-\bs{l}_i)^2-(\bs{m}_{i+1}-\bs{m}_i)^2 \right] \nonumber \\
+& + JS^2\sum_i^{N-1} \left[ \bs{m}_i(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
+\end{align}

### 2018-09-16 Chapters/Chapter3.tex
Transformation

@@
 Which is the Hamiltonian \ref{Hubbard} without DMI interaction.
-We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ieaA_{ij}(t)}$, where $A_{ij}$ is the projection of the vector potential into the vector from site $i$ to $j$.
-The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)$ (one-dimensional lattice).
-We can therefore take $A_{ij} = -\frac{E_0}{\omega}\cos(\omega t)(i-j)$.
-
-The Hamiltonan with the new $t_{ij}(t)$ is periodic in time with period $T=\frac{2\pi}{\omega}$.
-According to Floquet's theorem there exist solutions that have the form $\ket{\psi(t)} = e^{-i \epsilon_\alpha t} \ket{\psi_\alpha (t)}$ where $\ket{\psi_\alpha(t)}$ has also period $T$, and so it can be expanded in Fourier series $\ket{\psi_\alpha(t)} = \sum_m e^{i\omega mt} \ket{\psi_{\alpha,m}}$ introducing this ansatz in the Scrodinger equation and projecting into the m'th mode we obtain:
+We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)}$, where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$.
+The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)\bs{\hat{x}}$ (one-dimensional lattice).
+We can therefore take $\bs{A}(t) = -\frac{E_0}{\omega}\cos(\omega t)\bs{\hat{x}} = -\bs{A}\cos(\omega t)$.
+Therefore the time dependent Hamiltonian is:
 
 \begin{equation}
-(\epsilon_\alpha-\omega m) \ket{\psi_{\alpha, m}} = \sum_{m'} = H_{m'-m} \ket{\psi_{\alpha,m'}}
+\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + U\hat{D}
 \end{equation}
 
-Where $H_m = \frac{1}{T}\int_0^T dt e^{i\omega mt} H(t)$. The hopping term with the Peierls phase has Fourier components:
+Where $\hat{D}$ is the double occupancy number operator and $\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ is the hopping operator.
+Since the time dependence in periodic we can expand $t_{ij}(t) = \sum_m t_{ij,m} e^{im \omega t}$, where
 
 \begin{equation}
-H_{m} = \frac{t_0}{T} \sum_{\langle i,j \rangle, \sigma} \int_0^T dt e^{i\omega mt} e^{-iea\frac{E_0}{\omega}\cos(\omega t)(i-j)}\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma} = -t_0 \sum_{\langle i,j \rangle, \sigma} (-1)^mJ_m((i-j)ea\frac{E_0}{\omega})\hat{c}_{i\sigma}^\dagger \hat{c}_{j\sigma}
+t_{ij,m} = t_0(-1)^mJ_m(\alpha_{ij})
 \end{equation}
 
-Where $J_m(x)$ is the \textit{m}th Bessel function.
+Where $\alpha_{ij} = e\bs{R}_{ij}\bs{A}$ and $J_m(x)$ is the \textit{m}th Bessel function, and correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
+
+In order to derive the form of the effective Hamiltonian in the half filling system with $\frac{t}{U} << 1$ let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
+The transformed Hamiltonian is:
+
+\begin{equation}
+\hat{H}'(t) = \hat{U}^\dagger (t) \hat{H}(t) \hat{U}(t) - i\hat{U}^\dagger(t) d_t \hat{U}(t)
+\end{equation}
+
+We perform the unitary transformation perturbatively in the hopping parameter $t_0$.
+We expand $\hat{S}(t) = \sum_\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \hat{H}'^{(\nu)}(t)$.
+In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
+With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e.
+we can write:
+
+\begin{equation}
+\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
+\end{equation}
+
+where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$. We also decompose the hopping operator as:
+
+\begin{equation}
+\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
+\end{equation}
+
+Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. We can write the transformed Hamiltonian as:
+
+\begin{equation}
+\label{Perturbation}
+\hat{H}'(t) = \hat{H}(t) + \sum_{n=1}^\infty \frac{1}{n!} \left[i\hat{S}(t), \dots, \left[ i\hat{S}(t), \hat{H}(t) \right]\dots \right] - d_t \hat{S}(t)
+\end{equation}
+
+To zeroth order we have $\hat{H}'^{(0)}= U\hat{D}$ and $i\hat{S}^{(0)}(t)=0$. In first order we obtain:
+
+\begin{equation}
+\hat{H}'^{(1)}(t)=-\hat{T}(t)-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(1)}_{dm} e^{im\omega t}
+\end{equation}
+
+Therefore:
+
+\begin{align*}
+i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \\
+\hat{H}'^{(1)}(t) &= -\hat{T}_0(t)
+\end{align*}
+
+To second order we find:
+
+\begin{equation}
+\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] - d_t\hat{S}^{(2)}(t)
+\end{equation}
+
+Where the middle term is:
+
+\begin{align*}
+\left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] &= -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} +\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
+&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
+&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
+\end{align*}
+
+We obtain:
+
+\begin{align*}
+i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \\
+\hat{H}'^{(2)}(t) &= \sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t}
+\end{align*}
+
+Now the effective Hamiltonian acts on the subspace of $\hat{P}_0$, therefore we are only interested on $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$).
+In this subspace we can write:
+
+\begin{align*}
+\hat{T}_{1n} \hat{T}_{-1(m-n)} &= 0 \\
+\hat{T}_{-1(m-n)} \hat{T}_{1n} &= \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,(m-n)} t_{ij,n} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
+\end{align*}
+
+So that,
+
+\begin{equation}
+\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
+\end{equation}
+
+Comparing with \ref{PertNoEMF} we can see that this will lead to a spin Hamiltonian
+
+\begin{equation}
+\hat{H}_{eff}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j
+\end{equation}
+
+With
+
+\begin{align}
+J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
+&= \sum_{mn} (-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
+\end{align}
+
+In the case $\omega >> U$ we can limit to $m=0$ (time independent part) and $n=0$ or $n=\pm1$ (small denominators), additionally, if the electric field is small we can use $J_n(x) \aprox x^n$.
+With these approximations:
+
+\begin{equation}
+J_{ij} = 2 t_0^2 \alpha_{ij}^2 \left( \frac{1}{U-\omega} - \frac{1}{U} + \frac{1}{U+\omega} \right)
+\end{equation}

### 2018-09-17 Chapters/Chapter3.tex
add apendix 3a\
commit

@@
 We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)}$, where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$.
+This is known as Peierls substitution and it is derived in \ref{AP3A}.
 The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)\bs{\hat{x}}$ (one-dimensional lattice).
@@
 \end{equation}
+
+\end{section}
+
+\begin{subappendices}
+\begin{section}{Peierls Substitution}
+\label{AP3A}
+
+In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the latice \ref{LaticeHam} to:
+
+\begin{equation}
+  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
+\end{equation}
+
+Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian. We will show that the functions:
+
+\begin{equation}
+
+\end{equation}
+
+\end{section}
+\end{subappendices}

### 2018-09-17 Chapters/Chapter3.tex
Peierls substitution

@@
 
-\section{Modified exchange interaction}
+\begin{section}{Modified exchange interaction}
 
@@
 
-In the case $\omega >> U$ we can limit to $m=0$ (time independent part) and $n=0$ or $n=\pm1$ (small denominators), additionally, if the electric field is small we can use $J_n(x) \aprox x^n$.
+In the case $\omega >> U$ we can limit to $m=0$ (time independent part) and $n=0$ or $n=\pm1$ (small denominators), additionally, if the electric field is small we can use $J_n(x) \approx x^n$.
 With these approximations:
@@
 \begin{equation}
+\label{HamEMF}
   \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
@@
 
-Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian. We will show that the functions:
+Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian.
+We define a new set of Wannier functions in terms of those defined in \ref{Wannier2}, and obtain the new Bloch functions.
+
+\begin{align}
+\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
+\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
+\end{align}
+
+Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:
+
+\begin{align*}
+\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
+&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
+\end{align*}
+
+And so, the matrix elements as in the case without field except for a phase:
 
 \begin{equation}
+t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
+\end{equation}
 
-\end{equation}
+When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.
 

### 2018-09-18 Chapters/Chapter3.tex
Correction
commit with cancer

@@
 \begin{align}
-J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
-&= \sum_{mn} (-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
+J_{ij}(t) &= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
+&= \sum_{mn} 2(-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
 \end{align}
@@
 \begin{equation}
-J_{ij} = 2 t_0^2 \alpha_{ij}^2 \left( \frac{1}{U-\omega} - \frac{1}{U} + \frac{1}{U+\omega} \right)
+J_{ij} = 4 t_0^2 \left( \frac{\alpha_{ij}^2}{U-\omega} + \frac{1}{U} + \frac{\alpha_{ij}^2}{U+\omega} \right)
 \end{equation}
@@
 
+Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
+
+\begin{equation}
+  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} = \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} \psi_{\bs{R}}}=  e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}} \alpha_R \hat{z}(\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
+\end{equation}
+
 \end{section}

### 2018-09-26 Chapters/Chapter1.tex
minor changes

--- 2018-09-11 Chapters/Chapter1.tex
@@
 Antiferromagnetism was first studied by L.
-Neel who introduced a thermodinamic theory that made it possible to explain the antiferromagnetic order and it pretict the existance of a temperature above which this order vanishes.
-This temperature is known as Neel temperature.
+N\'eel who introduced a thermodinamic theory that made it possible to explain the antiferromagnetic order and it pretict the existance of a temperature above which this order vanishes.
+This temperature is known as N\'eel temperature.
 In the next section we will present a semiclassical model for antiferromagnetic materials.
@@
 Additionally, spin axis reorientation by a lateral electrical current can be used to offer ultra-fast electrical writing and reading in AFM devices \cite{Zelezny2014}.
-
-\section{AFM dynamics}

### 2018-09-26 Chapters/Chapter2.tex
Transformation
commit
Peierls substitution
minor changes

@@
-\chapter{Chapter Title Here} % Main chapter title
+\chapter{Effective Hamiltonian } % Main chapter title
 
@@
 \begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}
 \end{equation}
 
-Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $U(\bs{r})$ is a periodic potential.
+Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $\text{U}(\bs{r})$ is a periodic potential.
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
@@
 \begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r})
+\label{LaticeHam}
+\hat{H}^{(1)}_{\text{NSOI}}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r})
 \end{equation}
 
-Where $U(\textbf{r})$ has the symmetry of the lattice, i.e.
-$U(\textbf{r} + \textbf{R}) = U(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
-The group of translation symmetries $T_{\textbf{R}}\phi(\textbf{r}) = \phi(\textbf{r} + \textbf{R})$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong: $T_{\textbf{R}}\phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{R}) \phi_{n, \textbf{k}}(\textbf{r})$.
-Now, imposing periodic boundary conditions, $\phi_{n, \textbf{k}}(\textbf{r} + L_\mu \textbf{a}_\mu) = \Gamma^{\textbf{k}}(L_\mu \textbf{a}_\mu) \phi_{n, \textbf{k}}(\textbf{r}) = \Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} \phi_{n, \textbf{k}}(\textbf{r}) = \phi_{n, \textbf{k}}(\textbf{r})$, so that, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, this can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
+Where $\text{U}(\textbf{r})$ has the symmetry of the lattice, i.e.
+$\text{U}(\textbf{r} + \textbf{R}) = \text{U}(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
+Let $\hat{H}^{(1)}_{\text{NSOI}}$ act on a Hilbert space $\mathcal{H}$ and let $\ket{\phi} \in \mathcal{H}$, then, the group of translation symmetries defined by $\bra{\bs{r}} T_{\textbf{R}} \ket{\phi} = \bra{\bs{r} + \bs{R}} \ket{\phi}$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong.
+If $\Gamma^{\textbf{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\textbf{R}}\ket{\phi_{n, \textbf{k}}} = \Gamma^{\textbf{k}}(\textbf{R}) \ket{\phi_{n, \textbf{k}}}$.
+Now, imposing periodic boundary conditions, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
+This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
 Therefore, for a wavefunction in a periodic lattice we have:
@@
 \label{Bloch1}
-\phi_{n, \textbf{k}}(\textbf{r}+\textbf{R}) = e^{i\textbf{k}\textbf{R}}\phi_{n, \textbf{k}} (\textbf{r})
+\bra{\bs{r}+\bs{R}} \ket{\phi_{n, \textbf{k}}} = e^{i\textbf{k}\textbf{R}}\bra{\bs{r}} \ket{\phi_{n, \textbf{k}}}
 \end{equation}
@@
 We would like to work with a localized basis.
-An alternative orthonormal basis are the Wannier functions, defined in terms of the Bloch functions as:
+An alternative orthonormal basis are the Wannier functions $\ket{\psi_{n\bs{k}}}$, defined in terms of the Bloch functions as:
 
-\begin{equation}
-\phi_{in}(\textbf{r}) = \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \psi_{n\textbf{k}}(\textbf{r})
-\end{equation}
+\begin{align}
+\bra{\bs{r}}\ket{\phi_{in}} &= \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \bra{\bs{r}}\ket{\psi_{n\textbf{k}}} \label{Wannier1} \\
+\bra{\bs{r}}\ket{\psi_{n\bs{k}}} &= \frac{1}{\sqrt{M}} \sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\phi_{\bs{R}n}} \label{Wannier2}
+\end{align}
 
@@
 Using \ref{Bloch1} we see that $\phi_{in}(\textbf{r}) = \phi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \phi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
-We will restrict ourselves to a fixed band, so we will drop the band index and write $\phi_i(\bs{r})$ or $\ket{i}$.
+From now on we will restrict ourselves to a fixed band, so we will drop the band index.
+Additionally, we will include the spin state, therefore the basis states will have two quantum numbers one for the site and one for the spin state.
+We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant.
+Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
 
@@
 In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
-Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\phi_j$ and spin $\sigma$.
+Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\ket{j\sigma}$.
 In this basis, the second quantized form of \ref{Ham1} is:
+
+\begin{equation}
+\hat{H} = \sum_{i,j,\sigma, \sigma'} \bra{i\sigma} \hat{H}^{(1)} \ket{j\sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\end{equation}
+
+Where we assumed $\hat{v}$ to be spin independent. This can be rewritten as:
 
@@
 
-Where $t_{ij} = \bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + U(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = \bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
-Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$ (why?), and therefore $\bs{\Delta}_{ii} = 0$.
-We assumed $\hat{v}$ to be spin independent.
-Also we can impose that $t_{ii} = t(0) = 0$.
-For a system of strongly correlated electrons we can assume that:
+Where $t_{ij} = -\bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = -\bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
+Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$, for example, in the $x$ component:
+
+\begin{align*}
+\Delta_{ij,x} &= -\bra{i} \lambda (\partial_y V(\bs{r}) p_z - \partial_z V(\bs{r}) p_y) \ket{j} = i \hbar \lambda \int d \bs{r} \phi_i(\bs{r})^* (\partial_y V(\bs{r}) \partial_z - \partial_z V(\bs{r}) \partial_y) \phi_j(\bs{r}) = \\
+&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z(\phi_i(\bs{r})^*\partial_y V(\bs{r}) - \partial_y(\phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
+&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z \phi_i(\bs{r})^* \partial_y V(\bs{r}) - \partial_y \phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
+&= \int d\bs{r} \phi_j(\bs{r}) \lambda (\bs{\nabla}V(\bs{r}) \times \bs{p})_x \phi_i(\bs{r})^* = - \Delta_{ji,x}
+\end{align*}
+
+Therefore $\bs{\Delta}_{ii} = 0$. Also we can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
 
@@
 	\begin{cases}
-		U, & \text{if } i=j=k=l \\
+		\text{U}, & \text{if } i=j=k=l \\
 		0, & \text{otherwise}
@@
 \label{Hubbard}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 
-At half filling, in the $t << U$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+At half filling, in the $t << \text{U}$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
 First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
@@
 The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
-The energy of one of these states is $U$.
+The energy of one of these states is $\text{U}$.
 Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
@@
 Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
-These states have energy $E_s = U$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{U}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi}$.
-These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{U}$.
+These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
+These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{\text{U}}$.
 Now,
 
-\begin{align*}
-&\bra{\phi'} -\frac{\hat{H_t^2}}{U} \ket{\phi} = \\
-&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} (t^2 \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t(\delta_{\sigma_1 \sigma_2}		\boldsymbol{\Delta}_{i'j'}\boldsymbol{\sigma}_{\sigma_3 \sigma_4} + \delta_{\sigma_3 \sigma_4}						\boldsymbol{\Delta}_{ij}\boldsymbol{\sigma}_{\sigma_1 \sigma_2}) + \mathcal{O}(\boldsymbol{\Delta}^2)) 				\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4}					\ket{\phi} = \\
-&-\frac{1}{U} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 					\sigma_4}) + \mathcal{O}(\boldsymbol{\Delta}^2)) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \\
-&-\frac{1}{U} \bra{\phi'} \hat{H}_J + \hat{H}_D + \mathcal{O}(\boldsymbol{\Delta}^2))\ket{\phi}
-\end{align*}
+\begin{align}
+\label{PertNoEMF}
+&\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} (t^2 \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t(\delta_{\sigma_1 \sigma_2}		\boldsymbol{\Delta}_{i'j'}\boldsymbol{\sigma}_{\sigma_3 \sigma_4} + \delta_{\sigma_3 \sigma_4}						\boldsymbol{\Delta}_{ij}\boldsymbol{\sigma}_{\sigma_1 \sigma_2}) + \mathcal{O}(\boldsymbol{\Delta}^2)) 				\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4}					\ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 					\sigma_4}) + \mathcal{O}(\boldsymbol{\Delta}^2)) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \hat{H}_J + \hat{H}_D + \mathcal{O}(\boldsymbol{\Delta}^2))\ket{\phi}
+\end{align}
 
@@
 \begin{align*}
-\hat{H}_{J} = &-\frac{t^2}{U} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
-&-\frac{t^2}{U}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b = 
--\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \\
-&-\frac{t^2}{U}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b =
+-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
 \end{align*}
@@
 \begin{equation}
-\hat{H}_{J} = \frac{2t^2}{U} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
 \end{equation}
 
-Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{U}$. Likewise, for $\hat{H}_D$:
+Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}}$. Likewise, for $\hat{H}_D$:
 
 \begin{align*}
-\hat{H}_D = &-\frac{t}{U} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&-\frac{2t}{U}\sum_{\langle i,j \rangle} \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) = \\
-&-\frac{4it}{U} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&-\frac{2t}{\text{U}}\sum_{\langle i,j \rangle} \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) = \\
+&-\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
 \end{align*}
 
-Where $\boldsymbol{D}_{ij} = -\frac{4it}{U}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
+Where $\boldsymbol{D}_{ij} = -\frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
 
@@
 \end{equation}
+
+\end{section}
+
+\begin{section}{AFM dynamics}
+
+In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics.
+We write the Heisenberg Hamiltonian as $\hat{H} = J \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j - K \sum_i S_{iz}^2$ with $J>0$ and $K$ is the anisotropy energy.
+Let the lattice be a one dimensional chain with $2N$ sites, such lattice can be described by the repetition of $N$ unit cells consisting of two sites $\alpha$ and $\beta$ for the left and right site respectively.
+Then the ground state of this Hamiltonian is double degenerated and is obtained by aligning the spins in the $\alpha$ sites in the $\hat{z}$ direction and the $\beta$ spins in the $-\hat{z}$ direction or vice versa.
+Let us introduce the parameters:
+
+\begin{align}
+\bs{m}_i &= \frac{\bs{S}_{\alpha}^i + \bs{S}_{\beta}^i}{2S} \\
+\bs{l}_i &= \frac{\bs{S}_{\alpha}^i - \bs{S}_{\beta}^i}{2S}
+\end{align}
+
+Where $S$ is the spin angular momentum in units of $\hbar$. Inverting these relations, introducing them into the Hamiltonian and neglecting edge terms we obtain:
+
+\begin{align}
+\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
+& 2JS^2\sum_i^{N} (\bs{m}_i^2-\bs{l}_i^2)+\frac{JS^2}{2}\sum_i^{N-1}\left[(\bs{l}_{i+1}-\bs{l}_i)^2-(\bs{m}_{i+1}-\bs{m}_i)^2 \right] \nonumber \\
+& + JS^2\sum_i^{N-1} \left[ \bs{m}_i(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
+\end{align}
 

### 2018-09-26 main.tex
minor changes

@@
 \usepackage{bm}
-\usepackage{braket}
+\usepackage{physics}
 
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=bibtex,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 
@@
 
-\thesistitle{Ultrafast manipulation of exchange DMI in antiferromagnetic insulators} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
+\thesistitle{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–Moriya interactions in antiferromagnetic insulators} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
 \supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname

### 2018-09-27 Chapters/Chapter2.tex
Squres lattice

@@
 
-Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$
+i.e.
+$\text{U} = \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}')^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}') \phi(\bs{r})$, where $\phi(\bs{r})$ is the Wannier function centered at the origin.
+Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$.
 
@@
 
-At half filling, in the $t << \text{U}$ limit we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+At half filling, in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
 First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
@@
 
-Let us write $\hat{H} = \hat{H_0} + \hat{H_t}$, $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-Let $\ket{\phi}$ and $\ket{\phi'}$ be state from the ground state, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
+Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
+$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
 In second order we have:
@@
 
-Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}}$. Likewise, for $\hat{H}_D$:
+Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$:
 

### 2018-09-27 Chapters/Chapter3.tex
minor changes
Squres lattice

--- 2018-09-17 Chapters/Chapter3.tex
@@
 \begin{equation}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 This is known as Peierls substitution and it is derived in \ref{AP3A}.
-The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)\bs{\hat{x}}$ (one-dimensional lattice).
-We can therefore take $\bs{A}(t) = -\frac{E_0}{\omega}\cos(\omega t)\bs{\hat{x}} = -\bs{A}\cos(\omega t)$.
-Therefore the time dependent Hamiltonian is:
+We write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, where $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
+The vector potential takes the form $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
+The time dependent Hamiltonian is:
 
 \begin{equation}
-\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + U \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + U\hat{D}
+\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
 \end{equation}
@@
 Where $\hat{D}$ is the double occupancy number operator and $\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ is the hopping operator.
-Since the time dependence in periodic we can expand $t_{ij}(t) = \sum_m t_{ij,m} e^{im \omega t}$, where
+Let $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij}$ a real number, then we can apply the Jacobi–Anger expansion:
 
-\begin{equation}
-t_{ij,m} = t_0(-1)^mJ_m(\alpha_{ij})
-\end{equation}
+\begin{align*}
+t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
+\end{align*}
 
-Where $\alpha_{ij} = e\bs{R}_{ij}\bs{A}$ and $J_m(x)$ is the \textit{m}th Bessel function, and correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
+Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
 
-In order to derive the form of the effective Hamiltonian in the half filling system with $\frac{t}{U} << 1$ let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
+In order to derive the form of the effective Hamiltonian in the half filling system with $t << \text{U}$ let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
 The transformed Hamiltonian is:
@@
 
-We perform the unitary transformation perturbatively in the hopping parameter $t_0$.
-We expand $\hat{S}(t) = \sum_\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \hat{H}'^{(\nu)}(t)$.
+We perform the unitary transformation perturbatively in the hopping parameter $t_0$, to that end let us write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion.
+We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
 In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
@@
 \begin{equation}
-\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
+\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
 \end{equation}
@@
 \begin{equation}
-\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
+\hat{T}(t) = \eta \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
 \end{equation}
 
-Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. We can write the transformed Hamiltonian as:
+Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$.
+Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:
 
@@
 
-To zeroth order we have $\hat{H}'^{(0)}= U\hat{D}$ and $i\hat{S}^{(0)}(t)=0$. In first order we obtain:
+Now, starting from order zero and for each order we will determine $i\hat{S}^{(\nu)}(t)$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+To zeroth order in $\eta$ we have $\hat{H}'^{(0)}= U\hat{D}$ and $i\hat{S}^{(0)}(t)=0$.
+In first order we obtain:
 
@@
 \begin{align}
-J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
-&= \sum_{mn} (-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
+J_{ij}(t) &= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
+&= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
 \end{align}
 
-In the case $\omega >> U$ we can limit to $m=0$ (time independent part) and $n=0$ or $n=\pm1$ (small denominators), additionally, if the electric field is small we can use $J_n(x) \approx x^n$.
-With these approximations:
+Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $J_{-m}(x) = (-1)^mJ_m(x)$ and $J_m(-x) = (-1)^mJ_m(x)$ we can write \ref{Jij1} as:
 
 \begin{equation}
-J_{ij} = 2 t_0^2 \alpha_{ij}^2 \left( \frac{1}{U-\omega} - \frac{1}{U} + \frac{1}{U+\omega} \right)
+J_{ij}(t) = \sum_{mn} 2t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{J_{n-m}(\alpha_{ij})J_{n}(\alpha_{ij})+J_{n}(\alpha_{ij})J_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
+\end{equation}
+
+After time average this reduces to the $m=0$ term:
+
+\begin{equation}
+\label{Jij2}
+J_{ij}(t) = \sum_{n} 4t_0^2 \frac{J_n(\alpha_{ij})^2}{U+n\omega}
+\end{equation}
+
+Now, $\alpha_{ij} = \text{Re}(e\bs{R}_{ij}\vec{A})$.
+For a square lattices aligned with the coordinate system so that $\vec{a}_1=\hat{e}_x$ and $\vec{a}_2=\hat{e}_y$, we will have $\bs{R}_{ij} = \pm a\hat{e}_x,\pm a\hat{e}_y$, where $a$ is the lattice constant.
+Using $\vec{A}=\frac{iE_0}{\omega\sqrt{1+\lambda^2}}(\hat{e}_x+i\lambda\hat{e}_y)$ we have:
+
+\begin{equation}
+\alpha_{ij} = \begin{cases}
+             \pm \frac{eaE_0}{\omega \sqrt{1+\lambda^2}} = \pm \frac{\mathcal{E}}{\sqrt{1+\lambda^2}},  & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
+             \pm \lambda\frac{eaE_0}{\omega \sqrt{1+\lambda^2}} = \pm \frac{\lambda \mathcal{E}}{\sqrt{1+\lambda^2}},  & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
+       \end{cases} \quad
+\end{equation}
+
+Where $\mathcal{E} = \frac{eaE_0}{\omega}$.
+For $\omega>>U$ we can take only the three smallest values of $n$, i.e.
+$n=0, \pm 1$ in \ref{Jij2} as an approximation.
+We can also use that $\alpha_{ij} << 1$ since $\omega$ appears in the denominator and so $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$:
+
+\begin{equation}
+J_{ij} = 4t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 4t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
+\end{equation}
+
+For plane polarized light ($\lambda = 0$) the exchange interaction only changes in the direction of the polarization, that is:
+
+\begin{equation}
+J_{ij}^{PP} = \begin{cases}
+		J_{ij}^0 + 4t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
+J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
+\end{cases} \quad 
+\end{equation}
+
+For circular polarized light ($\lambda=\pm1$) in this approximation the exchange interaction changes in the same way in all the directions:
+
+\begin{equation}
+J_{ij}^{CP} = J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
 \end{equation}
@@
 \begin{equation}
+\label{PeierlsMtxElem}
 t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
@@
 
+Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
+
+\begin{align*}
+  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
+  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
+\end{align*}
+
+Therefore relation \ref{PeierlsMtxElem} still holds.
+
 \end{section}

### 2018-09-30 Chapters/Chapter2.tex
detalied anysotropic derivation

@@
 We will neglect the $\mathcal{O}(\boldsymbol{\Delta}^2)$ term since $t$ is dominant.
+We defined:
+
+\begin{align}
+\hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \\
+\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
+\end{align}
 
@@
 
-Introducing these relations into $H_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
+Introducing these relations into $\hat{H}_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
 
@@
 \hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle, \sigma \sigma'} \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b =
--\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle, \sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\} =
+-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left\{ \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} \right\} = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
 \end{align*}
@@
 \hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&-\frac{2t}{\text{U}}\sum_{\langle i,j \rangle} \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) = \\
-&-\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+ &= -\frac{t}{\text{U}} \sum_{\langle i,j \rangle} \left\{ \right.
+	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
+	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
+	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
+	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
+	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
+	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
+	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
+	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
+\left. \right\} = \\
+&= -\frac{2t}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
+&= +\frac{2ti}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = \\
+&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
 \end{align*}
 
-Where $\boldsymbol{D}_{ij} = -\frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
+In the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
+We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$.
+Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
+Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
 

### 2018-10-01 Chapters/Chapter2.tex
Contituum ham

@@
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
-Then, for a half filled system we will derive an effective Hamiltonian using time independent perturbation theory.
+We will consider a half filled system in the strong coupling limit.
+Ignoring electron hopping and spin orbit interaction, the ground state of this system is massively degenerated.
+We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
+This effective Hamiltonian will be the sum of a spin exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$ plus an anisotropic interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ \cite{Moriya1960}.
 
@@
 
+Now we can take the continuum limit with:
+
+\begin{align*}
+\bs{m}_i &\rightarrow \bs{m}(x) \\
+\bs{l}_i &\rightarrow \bs{l}(x) \\
+2d \sum_i &\rightarrow \int dx \\
+\hat{H} &\rightarrow \int \frac{dx}{2d} \mathcal{H}(\bs{l},\bs{m})
+\end{align*}
+
+This, together with $\bs{m}_i-\bs{l}_i = 2\bs{m}_i-1$ and $\bs{m}_{i+1} \rightarrow \bs{m}(x) + 2d \partial_x\bs{m}(x)$ gives:
+
+\begin{equation}
+\mathcal{H}(\bs{l},\bs{m}) = JS^2\left\{ 4|\bs{m}|^2 + |\partial_x\bs{l}'|^2 -  |\partial_x\bs{m}'|^2 +(\bs{m}\partial_x\bs{l} -\bs{l}\partial_x\bs{m}) \right\} -KS^2\left\{ (\bs{l}\hat{z})^2 + (\bs{m}\hat{z})^2 \right\}
+\end{equation}
+
 \end{section}

### 2018-10-01 Chapters/Chapter1.tex
Added some references

@@
 
-During several decades after the discovery of antiferromagnetics, these materials were percived as useless from a practical point of view.On contrast, ferromagnets have been widely studied historically for its technical applications.
-However, in the frame of spinotronic devices, the development of information technology demands devices with high storage density, high energy efficiency and high write-read speeds.
+The discovery of the giant magnetoresistance effect by P.
+Grünberg \cite{Binasch1989} and A.
+Fert \cite{Baibich1988} in the 80s opened the gate for a new field of study known as spinotronics, in which electron spin is exploited in improved electronic devices.
+Magnetoresistive random-access memory (MRAM) is an example of a new type of memory in which data is stored in magnetic elements \citep{Akerman2005}.
+Newer techniques include thermal assisted switching (TA-MRAM) \citep{Bandiera2015} and spin transfer torque (SPRAM) \citep{Kawahara2012}.
+
+However, so far, in most current spinotronic devices antiferromagnets play only a minor role.
+During several decades after the discovery of antiferromagnetics, these materials were percived as useless from a practical point of view.
+On contrast, ferromagnets have been widely studied historically for its technical applications.
+However, the development of information technology demands devices with high storage density, high energy efficiency and high write-read speeds.
 Therefore, controlling magnetically ordered systems on subpicosecond timescales is currently a widely studied area.
-Some progress has been done using ferromagnetic materials, for example, it has been shown that circularly polarized femtosecond laser pulses can be used to control the spin dynamics in magnets \cite{Kimel2005}.
-However, antiferromagnets aim to complement or even replace ferromagnets due to their rigidity to external magnetic field, and the abscence of stray field.
+Antiferromagnets aim to complement or even replace ferromagnets due to their rigidity to external magnetic field, and the abscence of stray field.
 

### 2018-10-01 Chapters/Chapter2.tex
Added some references

@@
 We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
-This effective Hamiltonian will be the sum of a spin exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$ plus an anisotropic interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ \cite{Moriya1960}.
+This effective Hamiltonian will be the sum of a spin exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$ plus an anisotropic interaction of the form $\bs{D}\bs{S}_i\times\bs{S}_j$ \cite{Moriya1960}.
 
@@
 
-In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics.
+In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics \cite{Tveten2016}.
 We write the Heisenberg Hamiltonian as $\hat{H} = J \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j - K \sum_i S_{iz}^2$ with $J>0$ and $K$ is the anisotropy energy.

### 2018-10-06 Chapters/Chapter2.tex
order

@@
 \begin{equation}
+\label{SpinOperators}
 \boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
@@
 
+\begin{align}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\end{align}
+
+In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:
+
 \begin{align*}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \\ 
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} 
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\}= \\
+&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
 \end{align*}
 
-Introducing these relations into $\hat{H}_J$ and using $n_{i \uparrow} + n_{i \downarrow} = 1$ we obtain:
+Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
+We also used the well known property $tr(\bs{\sigma}^a\bs{\sigma}^b)=2\delta_{a,b}$.
+And second:
 
 \begin{align*}
-\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle, \sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\} =
--\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left\{ \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} \right\} = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
-\end{align*}
-
-The constant term can be neglected leaving:
-
-\begin{equation}
-\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
-\end{equation}
-
-Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$:
-
-\begin{align*}
-\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
- &= -\frac{t}{\text{U}} \sum_{\langle i,j \rangle} \left\{ \right.
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+ &= \left\{ \right.
 	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
@@
 \left. \right\} = \\
-&= -\frac{2t}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
-&= +\frac{2ti}{\text{U}}\sum_{\langle i,j \rangle}\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = \\
+&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
+&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{align*}
+
+Where in the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
+We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$.
+Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
+
+These two relations are important and will be used in the next chapter:
+
+\begin{align}
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2}
+\end{align}
+
+Now introducing the spin operators into  $\hat{H}_J$ with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
+
+\begin{align*}
+\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
+\end{align*}
+
+The constant term can be neglected leaving:
+
+\begin{equation}
+\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\end{equation}
+
+Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
+
+\begin{align*}
+\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
@@
 
-In the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
-We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$.
-Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
 Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
@@
 \begin{equation}
-\hat{H}_{eff} = \sum_{\langle i,j \rangle} J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\hat{H}_{eff} = \sum_{\langle i,j \rangle} \left( J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \right)
 \end{equation}

### 2018-10-06 Chapters/Chapter3.tex
Contituum ham
order

@@
 
-\begin{section}{Modified exchange interaction}
+\begin{section}{Hubbard model without SOI}
 
@@
 
-Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
+Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
+Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
 
@@
 
+\begin{section}{Hubbard model with SOI}
+
+Now, let's investigate the effect of the electric field for the Hubbard model with SOI. As seen in \ref{AP3A} we can use the Peierls substitution to obtain the Hamiltonian:
+
+\begin{equation}
+\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma, \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 + \bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
+\end{equation}
+
+In this case the hopping operator $\hat{T}(t)$ includes the spin orbit interaction, but the time dependence is the same as before, we can use $e^{ie\bs{R}_{ij}\bs{A}(t)} =  \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij}) e^{im\omega t}$ where as before $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$ to write:
+
+\begin{equation}
+\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma, \sigma'} \sum_m \Gamma_{ij,m}^{\sigma\sigma'} e^{im \omega t} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
+\end{equation}
+
+Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar.
+Now we can follow the same procedure as in the previous section to obtain:
+
+\begin{equation}
+\hat{H}'^{(2)}(t) = \sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{equation}
+
+As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:
+
+\begin{equation}
+\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{equation}
+
+Where,
+
+\begin{equation}
+\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
+\end{equation}
+
+For any integers $a,b$. Therefore:
+
+\begin{equation}
+\hat{H}_{eff}(t) = -\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
+\end{equation}
+
+We can rewrite:
+
+\begin{align*}
+\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})m}J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
+\end{align*}
+
+Where we used $\theta_{ji} = \theta_{ij}$, $\alpha_{ji} = - \alpha_{ij}$ and $\bs{\Delta}_{ji} = -\bs{\Delta}_{ij}$.
+We neglect the $\mathcal{O}(\bs{\Delta}_{ij}^2)$ term.
+The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
+The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
+Define:
+
+\begin{equation}
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
+    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
+    \right\}e^{im\omega t}
+\end{equation}
+
+Now, introducing the spin operators \ref{SpinOperators}, using relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and taking into account that in this subspace $n_{i\uparrow}+n_{i\downarrow}=1$ we obtain:
+
+\begin{align*}
+\hat{H}_{eff}(t) &\approx -\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
+&= -t_0^2 \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
+&- t_0 \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+&\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= \hat{H}_J'(t)+\hat{H}_D'(t)
+\end{align*}
+
+Now, for $\hat{H}_J'(t)$ we know from the previous chapter that:
+
+\begin{equation}
+\sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right) = -2\sum_{\langle i,j \rangle}\bs{S}_i\bs{S}_j
+\end{equation}
+
+Up to a constant. Therefore:
+
+\begin{align}
+\hat{H}_J'(t) &= 2t_0^2 \sum_{mn} \bs{S}_i\bs{S}_j e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
+    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
+    \right\}e^{im\omega t} = \nonumber \\
+&= \sum_{mn} \bs{S}_i\bs{S}_j J_{ij}(t)
+\end{align}
+
+With the same expression for $J_{ij}(t)$ as in the previous section. For $\hat{H}_D'(t)$ we use the relation:
+
+\begin{align}
+&\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right)\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) = \nonumber \\
+&= \sum_{\langle i,j \rangle} 4i\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j
+\end{align}
+
+To obtain:
+
+\begin{equation}
+\hat{H}_D'(t) = -\sum_{\langle i,j \rangle} 4it_0 \bs{\Delta}_{ij}\mathcal{M}(\alpha_{ij},t) \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j
+\end{equation}
+
+With
+
+\begin{equation}
+\bs{D}_{ij} = -4it_0\bs{\Delta}_{ij}\mathcal{M}(\alpha_{ij},t) = -4it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+    \frac{J_{m-n}(\alpha_{ij})J_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
+    \frac{J_n(\alpha_{ij})J_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
+    \right\}e^{im\omega t}
+\end{equation}
+
+\end{section}
+
 \begin{subappendices}

### 2018-10-07 Chapters/Chapter3.tex
Fixes

--- 2018-09-27 Chapters/Chapter3.tex
@@
 \begin{align*}
-t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
+t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
 \end{align*}
 
-Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$ and $J_m(x)$ is the \textit{m}th Bessel function. Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
+Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$ and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
+Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
 
@@
 \begin{equation}
+\label{1stO}
+\hat{H}'^{(1)}(t) = -\hat{T}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] - d_t\hat{S}^{(1)}(t)
+\end{equation}
+
+Now we expanding in $m,d$ and use $\left[ \hat{D}, \hat{S}^{(\nu)}_{dm} \right] = d\hat{S}^{(\nu)}_{dm}$ because $\hat{S}^{(\nu)}_{dm}$ changes the doublon number by $d$:
+
+\begin{equation}
 \hat{H}'^{(1)}(t)=-\hat{T}(t)-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(1)}_{dm} e^{im\omega t}
@@
 
-\begin{align*}
-i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \\
-\hat{H}'^{(1)}(t) &= -\hat{T}_0(t)
-\end{align*}
+\begin{align}
+i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \label{1stOSpin}\\
+\hat{H}'^{(1)}(t) &= -\hat{T}_0(t) \label{1stOH}
+\end{align}
 
@@
 \begin{equation}
-\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] - d_t\hat{S}^{(2)}(t)
+\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
 \end{equation}
 
-Where the middle term is:
+Using \ref{1stO} and using $\left[ i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t)\right] = 0$ due to different Fourier modes of the hopping operator being equal up to a constant, we can rewrite:
+
+\begin{equation}
+\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] - d_t\hat{S}^{(2)}(t)
+\end{equation}
+
+Using \ref{1stOSpin} and \ref{1stOH}, the middle term is:
 
 \begin{align*}
-\left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] &= -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} +\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
-&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
-&= -\sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
+&\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] = -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} + 2\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
+&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{2\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
+&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{2\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
+\end{align*}
+
+Altogether:
+
+\begin{align*}
+\hat{H}'^{(2)}(t) &= \sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{2(U+n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{2(U-n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t} \\
+&-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(2)}_{dm} e^{im\omega t}
 \end{align*}
@@
 
-\begin{align*}
-i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \\
-\hat{H}'^{(2)}(t) &= \sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t}
-\end{align*}
+\begin{align}
+i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \label{2ndOSpin}\\
+\hat{H}'^{(2)}(t) &= \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t} \label{2ndOH}
+\end{align}
 
@@
 \begin{equation}
-\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
+\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
 \end{equation}
@@
 \begin{align}
-J_{ij}(t) &= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
-&= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
+J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
+&= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
 \end{align}
 
-Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} J_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $J_{-m}(x) = (-1)^mJ_m(x)$ and $J_m(-x) = (-1)^mJ_m(x)$ we can write \ref{Jij1} as:
+Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $\mathcal{J}_{-m}(x) = (-1)^m\mathcal{J}_m(x)$ and $\mathcal{J}_m(-x) = (-1)^m\mathcal{J}_m(x)$ we can write \ref{Jij1} as:
 
 \begin{equation}
-J_{ij}(t) = \sum_{mn} 2t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{J_{n-m}(\alpha_{ij})J_{n}(\alpha_{ij})+J_{n}(\alpha_{ij})J_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
+J_{ij}(t) = \sum_{mn} t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
 \end{equation}
@@
 \label{Jij2}
-J_{ij}(t) = \sum_{n} 4t_0^2 \frac{J_n(\alpha_{ij})^2}{U+n\omega}
+J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{U+n\omega}
 \end{equation}
@@
 \begin{equation}
-J_{ij} = 4t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 4t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
+J_{ij} = 2t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
 \end{equation}
@@
 J_{ij}^{PP} = \begin{cases}
-		J_{ij}^0 + 4t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
+		J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
 J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
@@
 \begin{equation}
-J_{ij}^{CP} = J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
+J_{ij}^{CP} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
+\end{equation}
+
+\end{section}
+
+\begin{section}{Hubbard model with SOI}
+
+Now, let's investigate the effect of the electric field for the Hubbard model with SOI. As seen in \ref{AP3A} we can use the Peierls substitution to obtain the Hamiltonian:
+
+\begin{equation}
+\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma, \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 + \bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
+\end{equation}
+
+In this case the hopping operator $\hat{T}(t)$ includes the spin orbit interaction, but the time dependence is the same as before, we can use $e^{ie\bs{R}_{ij}\bs{A}(t)} =  \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t}$ where as before $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$ to write:
+
+\begin{equation}
+\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma, \sigma'} \sum_m \Gamma_{ij,m}^{\sigma\sigma'} e^{im \omega t} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
+\end{equation}
+
+Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar.
+Now we can follow the same procedure as in the previous section to obtain \ref{2ndOH}
+
+\begin{equation}
+\hat{H}'^{(2)}(t) = \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{equation}
+
+As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:
+
+\begin{equation}
+\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{equation}
+
+Where,
+
+\begin{equation}
+\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
+\end{equation}
+
+For any integers $a,b$. Therefore:
+
+\begin{equation}
+\hat{H}_{eff}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
+\end{equation}
+
+We can rewrite:
+
+\begin{align*}
+\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
+\end{align*}
+
+Where we used $\theta_{ji} = \theta_{ij}$, $\alpha_{ji} = - \alpha_{ij}$ and $\bs{\Delta}_{ji} = -\bs{\Delta}_{ij}$.
+We neglect the $\mathcal{O}(\bs{\Delta}_{ij}^2)$ term.
+The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
+The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
+Define:
+
+\begin{equation}
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
+    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
+    \right\}e^{im\omega t}
+\end{equation}
+
+Now, introducing the spin operators \ref{SpinOperators}, using relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and taking into account that in this subspace $n_{i\uparrow}+n_{i\downarrow}=1$ we obtain:
+
+\begin{align*}
+\hat{H}_{eff}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
+&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
+&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
+&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
+&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
+&= \hat{H}_J'(t)+\hat{H}_D'(t)
+\end{align*}
+
+Where we also used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:
+
+\begin{align}
+J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\end{align}
+
+For $\bs{D}_{ij}(t)$ this is:
+
+\begin{equation}
+\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
+    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
+    \right\}e^{im\omega t}
 \end{equation}

### 2018-10-10 Chapters/Chapter1.tex
commit before fix

@@
 Antiferromagnetism was first studied by L.
-N\'eel who introduced a thermodinamic theory that made it possible to explain the antiferromagnetic order and it pretict the existance of a temperature above which this order vanishes.
+N\'eel who introduced a thermodynamic theory following the Weiss's model of a local molecular field.
+This made it possible to explain the antiferromagnetic order and it predicted the existence of a temperature above which this order vanishes.
 This temperature is known as N\'eel temperature.
-In the next section we will present a semiclassical model for antiferromagnetic materials.
+Later N\'eel proposed the picture of a magnetic order where two sublattices were magnetised in opposite directions.
+During the same period, Lev Landau developed a phenomenological model using a combination of two antiferromagnetically coupled ferromagnetic layers.
 

### 2018-10-10 Chapters/Chapter2.tex
Fixes
commit before fix

@@
 We would like to work with a localized basis.
-An alternative orthonormal basis are the Wannier functions $\ket{\psi_{n\bs{k}}}$, defined in terms of the Bloch functions as:
+An alternative orthonormal basis are the Wannier functions $\ket{\psi_{in}}$, defined in terms of the Bloch functions as:
 
 \begin{align}
-\bra{\bs{r}}\ket{\phi_{in}} &= \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \bra{\bs{r}}\ket{\psi_{n\textbf{k}}} \label{Wannier1} \\
-\bra{\bs{r}}\ket{\psi_{n\bs{k}}} &= \frac{1}{\sqrt{M}} \sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\phi_{\bs{R}n}} \label{Wannier2}
+\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
+\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\textbf{k}\textbf{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
 \end{align}
@@
 Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
-Using \ref{Bloch1} we see that $\phi_{in}(\textbf{r}) = \phi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \phi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
 From now on we will restrict ourselves to a fixed band, so we will drop the band index.
@@
 
+Compare with \cite{Stepanov2017}.
+
 \end{section}

### 2018-10-10 Chapters/Chapter3.tex
commit before fix

@@
 \end{section}
+
+\begin{section}{Identities}
+
+Let $Z(t)$ be an operator dependent on the parameter $t$. Then:
+
+\begin{align*}
+d_t e^{Z} &= d_t \sum_{n=0}^\infty \frac{1}{n!} Z^n = \sum_{n=0}^\infty \sum_{m=0}^{n-1} \frac{1}{n!} Z^m \frac{\partial Z}{\partial t} Z^{n-m-1} = \\
+&= \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{1}{(m+p+1)!}Z^m \frac{\partial Z}{\partial t} Z^p = \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{m!p!}{(m+p+1)!} \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} =\\
+&= \sum_{m=0}^\infty \sum_{p=0}^\infty \int_0^1 dx x^m (1-x)^p \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} = \int_0^1 dx e^{Zx} \frac{\partial Z}{\partial t} e^{Z(1-x)} = \\
+&= \int_0^1 dx \sum_{n=0}^\infty \frac{1}{n!} \left[xZ, \dots, \left[xZ, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
+\end{align*}
+
+Where we used the Beta function $\int_0^1 dx x^m (1-x)^p = \frac{m!p!}{(m+p+1)!}$ and we also used the Baker–Campbell–Hausdorff expansion for $e^{xZ}\frac{\partial Z}{\partial t}e^{-xZ}$ and $\int_0^1 x^n = \frac{1}{n+1}$.
+Therefore we proved:
+
+\begin{equation}
+d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
+\end{equation}
+
+\end{section}
+
 \end{subappendices}

### 2018-10-10 Chapters/Chapter3.tex
Fix

@@
 \begin{equation}
-\hat{H}'(t) = \hat{U}^\dagger (t) \hat{H}(t) \hat{U}(t) - i\hat{U}^\dagger(t) d_t \hat{U}(t)
+\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
 \end{equation}
@@
 
-Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$.
+Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. Now we can use the identity:
+
+\begin{equation}
+id_t e^{-i\hat{S}(t)} = \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))e^{-i\hat{S}(t)}
+\end{equation}
+
+Derived in appendix \ref{AP3B}, where $\text{ad}_A(B) = [A,B]$. To rewrite the transformed Hamiltonian as:
+
+\begin{equation}
+\hat{H}'(t) = e^{i\hat{S}(t)} \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right) e^{-i\hat{S}(t)}
+\end{equation}
+
 Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:
@@
 \begin{equation}
-\label{Perturbation}
-\hat{H}'(t) = \hat{H}(t) + \sum_{n=1}^\infty \frac{1}{n!} \left[i\hat{S}(t), \dots, \left[ i\hat{S}(t), \hat{H}(t) \right]\dots \right] - d_t \hat{S}(t)
+\label{PertFull}
+\hat{H}'(t) = \sum_m \frac{1}{m!} \text{ad}_{i\hat{S}(t)}^m \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right)
 \end{equation}
 
-Now, starting from order zero and for each order we will determine $i\hat{S}^{(\nu)}(t)$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
-To zeroth order in $\eta$ we have $\hat{H}'^{(0)}= U\hat{D}$ and $i\hat{S}^{(0)}(t)=0$.
-In first order we obtain:
+Now, in this expression we have to expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+Notice that we do not expand $\hat{H}(t)$ as an infinite series since $\hat{H}(t) = -\eta \hat{T}(t) + U\hat{D}$.
+Now, notice also that if we take $i\hat{S}^{(0)}(t)=0$ in \ref{PertFull}, then, to zeroth order in $\eta$ only terms in $m=0$ and $n=0$ contribute obtaining:
+
+\begin{equation}
+\hat{H}'^{(0)}(t) = U\hat{D}
+\end{equation}
+
+Which is indeed diagonal in the doublon number, and therefore we can take $i\hat{S}^{(0)}(t)=0$.
+With this equating terms of the same order in \ref{PertFull} is greatly simplified, since terms with high $m,n$ will correspond to terms with high $\eta$.
+Since we are only interested in orders up to second order, we can truncate \ref{PertFull} up to $m=2$:
+
+\begin{align}
+\label{PertTrunc}
+\hat{H}'(t) &=  \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) + [i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))] + \nonumber \\
+&+ \frac{1}{2} [i\hat{S}(t),[i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) ]]
+\end{align}
+
+This equation holds up to order $\eta^2$. In first order we obtain:
 
@@
 \label{1stO}
-\hat{H}'^{(1)}(t) = -\hat{T}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] - d_t\hat{S}^{(1)}(t)
+\hat{H}'^{(1)}(t) = -\hat{T}(t) - d_t\hat{S}^{(1)}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right]
 \end{equation}
@@
 
-\begin{equation}
-\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
-\end{equation}
+\begin{align}
+\hat{H}'^{(2)}(t) &= - d_t\hat{S}^{(2)}(t) - \frac{1}{2}\left[-i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t) \right] + \left[i\hat{S}^{(1)}(t), -\hat{T}(t)-\frac{1}{2}d_t\hat{S}^{(1)}(t) \right] +\nonumber \\
+&+ \left[i\hat{S}^{(2)}(t), U\hat{D} \right] + \frac{1}{2} \left[i\hat{S}^{(1)}(t), \left[i\hat{S}^{(1)}(t), U\hat{D} \right] \right] = \nonumber \\
+&= \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
+\end{align}
 
@@
 
+Kinetic hopping and the Rashba spin orbit are both NN hopping processes, so they are both renormalized in the same way by the laser field \cite{Stepanov2017}.
 For $\bs{D}_{ij}(t)$ this is:
@@
 \begin{section}{Identities}
-
+\label{AP3B}
 Let $Z(t)$ be an operator dependent on the parameter $t$. Then:
@@
 \begin{equation}
-d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
+\label{SneidersID}
+d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \text{ad}_Z ^n \left(\frac{\partial Z}{\partial t}\right) e^Z
 \end{equation}
+
+Where $\text{ad}_A(B) = [A,B]$.
 

### 2018-10-15 Chapters/Chapter2.tex
com

@@
 &\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} (t^2 \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t(\delta_{\sigma_1 \sigma_2}		\boldsymbol{\Delta}_{i'j'}\boldsymbol{\sigma}_{\sigma_3 \sigma_4} + \delta_{\sigma_3 \sigma_4}						\boldsymbol{\Delta}_{ij}\boldsymbol{\sigma}_{\sigma_1 \sigma_2}) + \mathcal{O}(\boldsymbol{\Delta}^2)) 				\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4}					\ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 					\sigma_4}) + \mathcal{O}(\boldsymbol{\Delta}^2)) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \hat{H}_J + \hat{H}_D + \mathcal{O}(\boldsymbol{\Delta}^2))\ket{\phi}
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
+& \bra{\phi'} \hat{H}_J + \hat{H}_D + \hat{H}_P \ket{\phi}
 \end{align}
@@
 We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
-We will neglect the $\mathcal{O}(\boldsymbol{\Delta}^2)$ term since $t$ is dominant.
 We defined:
@@
 \hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \\
-\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
+\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \\
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
 \end{align}
@@
 
-These two relations are important and will be used in the next chapter:
+Also:
+
+\begin{align*}
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= \dots = \\
+&= \begin{pmatrix}
+S_i^x & S_i^y & S_i^z
+\end{pmatrix}
+\\
+&\begin{pmatrix}
+-2(\Delta_{ij}^z)^2 - 2(\Delta_{ij}^y)^2 + 2(\Delta_{ij}^x)^2 & 4\Delta_{ij}^x\Delta_{ij}^y & 4\Delta_{ij}^x\Delta_{ij}^z \\ 4\Delta_{ij}^y\Delta_{ij}^x & -2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 -2(\Delta_{ij}^z)^2 & 4\Delta_{ij}^y\Delta_{ij}^z \\ 4\Delta_{ij}^z\Delta_{ij}^x & 4\Delta_{ij}^z\Delta_{ij}^y & -2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^z)^2
+\end{pmatrix}
+\\
+&\begin{pmatrix}
+S_j^x \\ S_j^y \\ S_j^z
+\end{pmatrix} = \\
+&\sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta
+\end{align*}
+
+These three relations are important and will be used in the next chapter:
 
@@
 &\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2}
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2} \\
+& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
 \end{align}
@@
 
-Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. The total effective Hamiltonian is:
+Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ gives:
+
+\begin{align*}
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&\frac{1}{\text{U}} \sum_{\langle i,j \rangle} \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta = \sum_{\langle i,j \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j
+\end{align*}
+
+With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
+
+The total effective Hamiltonian is:
 

### 2018-10-15 Chapters/Chapter3.tex
com

@@
 Where $\hat{D}$ is the double occupancy number operator and $\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ is the hopping operator.
-Let $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij}$ a real number, then we can apply the Jacobi–Anger expansion:
+Let $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
+
+\begin{align}
+\alpha_{ij} &= -\alpha_{ji} \label{alphaSym} \\
+\theta_{ij} &= \theta_{ji} \label{thetaSym} \\
+\end{align}
+
+and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
 
@@
 
-Now, $\alpha_{ij} = \text{Re}(e\bs{R}_{ij}\vec{A})$.
+Now, $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$.
 For a square lattices aligned with the coordinate system so that $\vec{a}_1=\hat{e}_x$ and $\vec{a}_2=\hat{e}_y$, we will have $\bs{R}_{ij} = \pm a\hat{e}_x,\pm a\hat{e}_y$, where $a$ is the lattice constant.
@@
 \end{equation}
+
+\begin{subsection}{Honeycomb lattice}
+
+Now, in \ref{Jij2}, consider that the $\alpha_{ij}$ values are given by $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ where $\bs{R}_{ij}$ are the displacement vectors in a honeycomb lattice.
+There are six such vectors:
+
+\begin{align}
+\bs{R}_1^\pm &= \pm a\hat{e}_x \\
+\bs{R}_2^\pm &= \pm a\frac{1}{2}(\hat{e}_x + \sqrt{3}\hat{e}_y) \\
+\bs{R}_3^\pm &= \pm a\frac{1}{2}(\hat{e}_x - \sqrt{3}\hat{e}_y)
+\end{align}
+
+These six possible directions will lead to $\alpha_a^\pm = \pm |e\bs{R}_a\vec{A}|$ where $\vec{A}=\frac{iE_0}{\omega\sqrt{1+\lambda^2}}(\hat{e}_x+i\lambda\hat{e}_y)$:
+
+\begin{align}
+\alpha_1^\pm &= \pm \frac{eaE_0}{\omega\sqrt{1+\lambda^2}} \\
+\alpha_2^\pm &= \alpha_3^\pm = \pm \frac{eaE_0}{2\omega} \sqrt{\frac{1+3\lambda^2}{1+\lambda^2}} = \pm\frac{eaE_0}{2\omega}\sqrt{1+\frac{2\lambda^2}{1+\lambda^2}}
+\end{align}
+
+We see that again, this result will not depend on the helicity of the applied electric field.
+
+\end{subsection}
 
@@
 \hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
+&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
 &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})

### 2018-10-16 Chapters/Chapter2.tex
commit

@@
 \begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
  &= \left\{ \right.
@@
 \begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&= \dots = \\
-&= \begin{pmatrix}
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= \overbrace{\Delta_{ij}^z\Delta_{ij}^z(\frac{1}{2}+S_i^z)(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^z\Delta_{ij}^+S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^z\Delta_{ij}^-(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^z(-\Delta_{ij}^z) S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^+\Delta_{ij}^z (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^+\Delta_{ij}^+S_i^-(-S_j^-)}^{\uparrow \downarrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^+\Delta_{ij}^-(\frac{1}{2}+S_i^z)(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^+(-\Delta_{ij}^z) S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^-\Delta_{ij}^z S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^-\Delta_{ij}^+(\frac{1}{2}-S_i^z)(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^-\Delta_{ij}^-S_i^+(-S_j^+)}^{\downarrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^-(-\Delta_{ij}^z) (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
+	& \overbrace{(-\Delta_{ij}^z)\Delta_{ij}^z S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^+ (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^- S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} + \\
+	&+\overbrace{(-\Delta_{ij}^z)(-\Delta_{ij}^z)(\frac{1}{2}-S_i^z)(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \downarrow} = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z (-2(\Delta_{ij}^z)^2 + 2\Delta_{ij}^+\Delta_{ij}^-) + S_i^zS_j^+(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^zS_j^-(-2\Delta_{ij}^z\Delta_{ij}^+) +\\
+&+ S_i^+S_j^z(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^+S_j^+(-\Delta_{ij}^-\Delta_{ij}^-) + S_i^+S_j^-(\Delta_{ij}^z)^2 +\\
+&+ S_i^-S_j^z(-2\Delta_{ij}^z\Delta_{ij}^+) + S_i^-S_j^+(\Delta_{ij}^z)^2 + S_i^-S_j^-(-(\Delta_{ij}^+)^2) = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z(-2(\Delta_{ij}^z)^2+2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 + S_i^zS_j^y(-4\Delta_{ij}^z\Delta_{ij}^y)+S_i^zS_j^x(-4\Delta_{ij}^z\Delta_{ij}^x) + \\
+&+S_i^yS_j^z(-4\Delta_{ij}^y\Delta_{ij}^z)+S_i^yS_j^y(2(\Delta_{ij}^z)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^x)^2)+S_i^yS_j^x(-4\Delta_{ij}^y\Delta_{ij}^x) + \\
+&+ S_i^xS_j^z(-4\Delta_{ij}^x\Delta_{ij}^z) + S_i^xS_j^y(-4\Delta_{ij}^x\Delta_{ij}^y) + S_i^xS_j^x(2(\Delta_{ij}^z)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^x)^2) = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \begin{pmatrix}
 S_i^x & S_i^y & S_i^z
@@
 &\begin{pmatrix}
--2(\Delta_{ij}^z)^2 - 2(\Delta_{ij}^y)^2 + 2(\Delta_{ij}^x)^2 & 4\Delta_{ij}^x\Delta_{ij}^y & 4\Delta_{ij}^x\Delta_{ij}^z \\ 4\Delta_{ij}^y\Delta_{ij}^x & -2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 -2(\Delta_{ij}^z)^2 & 4\Delta_{ij}^y\Delta_{ij}^z \\ 4\Delta_{ij}^z\Delta_{ij}^x & 4\Delta_{ij}^z\Delta_{ij}^y & -2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^z)^2
+2(\Delta_{ij}^z)^2 + 2(\Delta_{ij}^y)^2 - 2(\Delta_{ij}^x)^2 & -4\Delta_{ij}^x\Delta_{ij}^y & -4\Delta_{ij}^x\Delta_{ij}^z \\ -4\Delta_{ij}^y\Delta_{ij}^x & +2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2 +2(\Delta_{ij}^z)^2 & -4\Delta_{ij}^y\Delta_{ij}^z \\ -4\Delta_{ij}^z\Delta_{ij}^x & -4\Delta_{ij}^z\Delta_{ij}^y & 2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^z)^2
 \end{pmatrix}
-\\
-&\begin{pmatrix}
+\begin{pmatrix}
 S_j^x \\ S_j^y \\ S_j^z
 \end{pmatrix} = \\
-&\sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta
+&\frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \sum_{\alpha, \beta} S_i^\alpha (4\Delta_{ij}^\alpha\Delta_{ij}^\beta - \delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2) S_j^\beta
 \end{align*}

### 2018-10-21 Chapters/Chapter3.tex
graphene

@@
 
+\begin{align}
+\hat{H}_{\text{eff}}(t) &= \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = -\frac{1}{2}\sum_{mn} \left( \frac{\hat{P}_0  \hat{T}_{-1(m-n)}\hat{T}_{1n}\hat{P}_0}{U+n\omega} + \frac{\hat{P}_0 \hat{T}_{-1n} \hat{T}_{1(m-n)} \hat{P}_0}{U-n\omega} \right) e^{im\omega t} \nonumber \\
+&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \label{HeffSimplified}
+\end{align}
+
+Now, since the hopping operators act on the subspace $d=0$ and must remain within that subspace, thus we can write:
+
 \begin{align*}
-\hat{T}_{1n} \hat{T}_{-1(m-n)} &= 0 \\
-\hat{T}_{-1(m-n)} \hat{T}_{1n} &= \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,(m-n)} t_{ij,n} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
+\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,a} t_{ij,b} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
 \end{align*}
 
-So that,
+Where $a$ and $b$ are any two Fourier modes. Inserting this into \ref{HeffSimplified}:
 
 \begin{equation}
-\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
+\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,(-n)} t_{ij,(m+n)}}{U+n\omega} e^{im\omega t}
 \end{equation}
@@
 
-\begin{align}
-J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
-&= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
-\end{align}
+\begin{equation}
+J_{ij}(t) = \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
+\end{equation}
 
@@
 \begin{align}
-J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
+\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI}
 \end{align}
@@
 \end{section}
+
+\input{Chapters/SGraphene}
 

### 2018-10-21 Chapters/SGraphene.tex
graphene

\begin{section}{Graphene}

In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. However, if inversion symmetry is broken, a Rashba spin orbit interaction term is allowed between nearest neighbors. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:

\begin{align}
\hat{H}_{KMH} &= -t\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \nonumber \\
&+ i\Delta_R \sum_{\langle i j \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}) \hat{c}_{j\sigma'} + U\hat{D}
\end{align}

Where sum over next-nearest neighbors is denotes by $\langle \langle i j \rangle \rangle$ and $\Delta$ is the intrinsic spin orbit coupling and $\Delta_R$ is the Rashba spin orbit coupling. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from i to j makes a right ($+1$) or a left turn ($-1$).
We can apply Peierls substitution in presence of a vector potential $\vec{\bs{A}}(t)$ to obtain the time dependent Hamiltonian:

\begin{align}
\hat{H}_{KMH}(t) &= -\sum_{\langle i j \rangle \sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} \nonumber \\
&+ i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  e^{ie\bs{R}_{ij}\bs{A}(t)} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + U\hat{D}
\end{align}

We can write the hopping operator as a sum of two terms $\hat{T}(t) = \hat{T}^1(t) + \hat{T}^2(t)$, the first corresponding to the hopping between nearest neighbors and the second corresponding to the hopping between next-nearest neighbors. $\hat{T}^1(t)$ is the same as the hopping in the previous section specialized for the case of Rashba interaction:

\begin{align*}
\hat{T}^1(t) &= -\sum_{\langle i j \rangle \sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'} \nonumber \\
&= -\sum_{\langle i j \rangle \sigma \sigma'} \left( \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} \right) (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'} \nonumber \\
&= \sum_{\langle i j \rangle \sigma \sigma'} \sum_m  \Xi_{ij,m}^{\sigma \sigma'} e^{im\omega t}\hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'}
\end{align*}

Where we defined:

\begin{equation}
 \Xi_{ij,m}^{\sigma \sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}))
\end{equation}

Similarly, for $\hat{T}^2(t)$:

\begin{align*}
\hat{T}^2(t) &= i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  e^{ie\bs{R}_{ij}\bs{A}(t)} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \\
&= i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  \left( \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} \right) \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \\
&= \sum_{\langle i j \rangle \sigma \sigma'} \sum_m  \Pi_{ij,m}^{\sigma \sigma'} e^{im\omega t}\hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'}
\end{align*}

Where

\begin{equation}
\Pi_{ij,m}^{\sigma \sigma'} = i \Delta e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) \nu_{ij} \sigma_{\sigma \sigma'}^z
\end{equation}

We write $\hat{H}_{KMH}(t) = \hat{T}^1(t) + \hat{T}^2(t) + U\hat{D}$ and apply \ref{HeffSimplified} to obtain $\hat{H}_{\text{eff}}(t)$. In order to find an expression for $\hat{H}_{\text{eff}}(t)$, we need to find how the terms $\hat{T}_{-1a}\hat{T}_{1b}$ ($a$ and $b$ being subscripts for the Fourier mode) act on the $d=0$ subspace when $\hat{T}(t) = \hat{T}^1(t) + \hat{T}^2(t)$. Now, $\hat{T}_1(t)$ represents the hopping between nearest neighbors whereas $\hat{T}_2(t)$ represents the hopping between next-nearest neighbors, the only way to avoid double occupancies would be to apply $\hat{T}^1(t)$ twice between the same nearest neighbors sites, or $\hat{T}^2(t)$ between the same next-nearest neighbors sites, that is, any cross term between $\hat{T}^1(t)$ and $\hat{T}^2(t)$ will lead to double occupancies. This means that $\hat{P}_0\hat{T}_{-1a}\hat{T}_{1b}\hat{P}_0 = \hat{P}_0\hat{T}_{-1a}^1\hat{T}_{1b}^1\hat{P}_0+\hat{P}_0\hat{T}_{-1a}^2\hat{T}_{1b}^2\hat{P}_0$, for the nearest neighbors hopping operator we obtain the same expression as in the previous section:

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}^1\hat{T}_{1b}^1 \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Xi_{ji,a}^{\sigma_1\sigma_2}\Xi_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
\end{equation}

Whereas for the next-neighbors hopping operator:

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}^2\hat{T}_{1b}^2 \hat{P}_0 = \sum_{\langle \langle i,j \rangle \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Pi_{ji,a}^{\sigma_1\sigma_2}\Pi_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
\end{equation}

Therefore for the effective Hamiltonian:

\begin{align*}
\hat{H}_{\text{eff}}(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}^1(t) + \hat{H}_{\text{eff}}^2(t)
\end{align*}

For $\hat{H}_{\text{eff}}^1(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}. For $\hat{H}_{\text{eff}}^2(t)$ the interaction will be between next-nearest neighbors:

\begin{align*}
\hat{H}_{\text{eff}}^2(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \sum_{\langle \langle i,j \rangle \rangle \sigma_1 \sigma_2 \sigma_3 \sigma_4} \left\{ \frac{\hat{P}_0 (\Pi_{ji,(m-n)}^{\sigma_1\sigma_2}\Pi_{ij,n}^{\sigma_3\sigma_4} + \Pi_{ji,(-n)}^{\sigma_1\sigma_2}\Pi_{ij,(m+n)}^{\sigma_3\sigma_4}) \hat{P}_0}{U+n\omega} \right\}\hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} e^{im\omega t} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \sum_{mn} \frac{e^{i(\frac{\pi}{2}-\theta_{ij})m}}{\text{U}+n\omega} \left\{ \mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij}) \right\} e^{im \omega t} \\
& \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\}
\end{align*}

As expected, the time dependence is the same as in the nearest neighbor interaction. For the spin sum we use \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} taking into account that in the $d=0$ subspace $\hat{n}_{i\uparrow}+\hat{n}_{i\downarrow} = 1$:

\begin{align*}
&\sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} = \sum_{\sigma \sigma'} \sigma_{\sigma \sigma}^z\sigma_{\sigma' \sigma'}^z \hat{c}_{i\sigma}^\dagger\hat{c}_{j\sigma}\hat{c}_{j\sigma'}^\dagger\hat{c}_{i\sigma'} \\
&= \sum_{\sigma \sigma'} \sigma_{\sigma \sigma}^z\sigma_{\sigma' \sigma'}^z \left( \frac{\delta_{\sigma\sigma'}}{2} + \bs{S}_i\bs{\sigma}_{\sigma'\sigma}\right)\left( \frac{\delta_{\sigma\sigma'}}{2} - \bs{S}_j\bs{\sigma}_{\sigma\sigma'}\right) \\
&= \left( \frac{1}{2}+S_i^z \right) \left( \frac{1}{2}-S_j^z \right) - S_i^-(-S_j^+)-S_i^+(-S_j^-) + \left( \frac{1}{2}-S_i^z \right) \left( \frac{1}{2}+S_j^z \right) \\
&= 1-2S_i^zS_j^z+2(S_i^xS_j^x+S_i^yS_j^y)
\end{align*}

Neglecting the constant term, the effective next-nearest neighbors interaction reads:

\begin{equation}
\hat{H}_{\text{eff}}^2(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
\end{equation}

With:

\begin{equation}
H_{ij}(t) = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{equation}

\end{section}

### 2018-10-24 Chapters/Chapter3.tex
asdf

@@
 Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar.
-Now we can follow the same procedure as in the previous section to obtain \ref{2ndOH}
+Now we can follow the same procedure as in the previous section that lead to \ref{HeffSimplified}:
 
 \begin{equation}
-\hat{H}'^{(2)}(t) = \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\hat{H}_{\text{eff}}(t) = \hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0 = -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0 \left(\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)} \right) \hat{P}_0 }{\text{U}+n\omega} \right\} e^{im\omega t}
 \end{equation}
 
-As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:
+The product of hopping operators restricted on this subspace can be written as:
 
 \begin{equation}
-\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
+\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4}
 \end{equation}
 
-Where,
+For any integers $a,b$ labeling any Fourier modes. Therefore:
 
 \begin{equation}
-\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
+\hat{H}_{\text{eff}}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4} \left\{ \frac{\Gamma_{ji,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ij,n}^{\sigma_3\sigma_4} + \Gamma_{ji,-n}^{\sigma_1\sigma_2}\Gamma_{ij,(m+n)}^{\sigma_3\sigma_4} }{\text{U}+n\omega}  \right\} e^{im\omega t}
 \end{equation}
 
-For any integers $a,b$. Therefore:
-
-\begin{equation}
-\hat{H}_{eff}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
-\end{equation}
-
-We can rewrite:
+We can write:
 
 \begin{align*}
-\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
-&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
-&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
+\Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{a}(\alpha_{ji})\mathcal{J}_b(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
+&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
 \end{align*}
@@
 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
-    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
-    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
-    \right\}e^{im\omega t}
+    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
 \end{equation}
@@
 \begin{align*}
-\hat{H}_{eff}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+\hat{H}_{\text{eff}}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
 &\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
@@
 \bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
-    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
-    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
-    \right\}e^{im\omega t}
+    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
 \end{equation}

### 2018-10-24 Chapters/SGraphene.tex
asdf

@@
 In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
-However, if inversion symmetry is broken, a Rashba spin orbit interaction term is allowed between nearest neighbors.
+However, if inversion symmetry is broken by i.e.
+an external electric field in the $\hat{z}$ direction, a Rashba spin orbit interaction term is allowed between nearest neighbors.
 In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:
@@
 &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
-&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}^1(t) + \hat{H}_{\text{eff}}^2(t)
+&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t)
 \end{align*}
 
-For $\hat{H}_{\text{eff}}^1(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}.
-For $\hat{H}_{\text{eff}}^2(t)$ the interaction will be between next-nearest neighbors:
+For $\hat{H}_{\text{eff}}'(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}.
+For $\hat{H}_{\text{eff}}''(t)$ the interaction will be between next-nearest neighbors:
 
 \begin{align*}
-\hat{H}_{\text{eff}}^2(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
+\hat{H}_{\text{eff}}''(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
 &= -\frac{1}{2}\sum_{mn} \sum_{\langle \langle i,j \rangle \rangle \sigma_1 \sigma_2 \sigma_3 \sigma_4} \left\{ \frac{\hat{P}_0 (\Pi_{ji,(m-n)}^{\sigma_1\sigma_2}\Pi_{ij,n}^{\sigma_3\sigma_4} + \Pi_{ji,(-n)}^{\sigma_1\sigma_2}\Pi_{ij,(m+n)}^{\sigma_3\sigma_4}) \hat{P}_0}{U+n\omega} \right\}\hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} e^{im\omega t} \\
@@
 \begin{equation}
-\hat{H}_{\text{eff}}^2(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
 \end{equation}
@@
 
+This describes a type of anisotropic exchange interaction.
+Notice that the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}.
+
+Together with exchange and DMI interaction obtained in the previous section the total effective Hamiltonian in this system is:
+
+\begin{align}
+\hat{H}_{\text{eff}}(t) = &\hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t) = \sum_{\langle i,j \rangle} \left( J_{ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j \right) \nonumber \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+\end{align}
+
+Where $J_{ij}(t)$ and $\bs{D}_{ij}(t)$ have been obtained in \ref{JijHSOI} and \ref{DijHSOI} and we take $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ to obtain:
+
+\begin{align*}
+J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{ij}(t) &= -2t_0\Delta_R (R_{ij}^y, - R_{ij}^x, 0) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\end{align*}
+
+Where $J_{ij}(t)$ and $\bs{D}_{ij}(t)$ have been defined in \ref{JijHSOI} and \ref{DijHSOI}.
+
 \end{section}

### 2018-10-29 Chapters/Chapter3.tex
Refactor done

@@
 
-In this chapter we will study how introducing an electromagnetic perturbation in \ref{Ham1} can affect the parameters $J$ and $\boldsymbol{D}_{ij}$ of the effective Hamiltonian.
+In this chapter we will derive an effective Hamiltonian for different types of Hubbard-like models in the presence of a high frequency electromagnetic perturbation.
+The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
+
+\begin{section}{Time dependent effective Hamiltonian}
+
+\input{Chapters/TDHeff}
+
+\end{section}
 
@@
 
-We start by considering only the exchange interaction part in a one-dimensional lattice. Consider the Hamiltonian:
+We start by considering the simplest hopping operator, as in the Hubbard model:
 
@@
 Which is the Hamiltonian \ref{Hubbard} without DMI interaction.
-We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)}$, where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$.
-This is known as Peierls substitution and it is derived in \ref{AP3A}.
-We write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, where $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
-The vector potential takes the form $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
-The time dependent Hamiltonian is:
+We see that the hopping amplitudes introduced in the previous section take the form $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'} t_0$ for $i,j$ being nearest neighbors, and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
+With this we can directly apply \ref{HeffSimplified} to obtain:
 
 \begin{equation}
-\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
+\hat{H}_{\text{eff}}(t) = -\frac{t_0^2}{2} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{equation}
 
-Where $\hat{D}$ is the double occupancy number operator and $\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma} t_{ij}(t)\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ is the hopping operator.
-Let $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
-
-\begin{align}
-\alpha_{ij} &= -\alpha_{ji} \label{alphaSym} \\
-\theta_{ij} &= \theta_{ji} \label{thetaSym} \\
-\end{align}
-
-and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
+Now, introducing the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and summing over the spin states as in \ref{SpinRel1}:
 
 \begin{align*}
-t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)} = t_0e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_0 \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m} e^{im\omega t}
+\sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} = \sum_{\sigma, \sigma'} \left( \frac{\delta_{\sigma \sigma'}}{2} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma} \right) \left( \frac{\delta_{\sigma \sigma'}}{2} - \bs{S}_j\bs{\sigma}_{\sigma \sigma'} \right) = -2\bs{S}_i \bs{S}_j
 \end{align*}
 
-Where $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$ and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
-Correspondingly $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$.
-
-In order to derive the form of the effective Hamiltonian in the half filling system with $t << \text{U}$ let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
-The transformed Hamiltonian is:
+Where we neglected the constant term. The effective spin Hamiltonian is thus:
 
 \begin{equation}
-\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
-\end{equation}
-
-We perform the unitary transformation perturbatively in the hopping parameter $t_0$, to that end let us write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion.
-We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
-In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
-Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
-With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e.
-we can write:
-
-\begin{equation}
-\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
-\end{equation}
-
-where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$. We also decompose the hopping operator as:
-
-\begin{equation}
-\hat{T}(t) = \eta \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
-\end{equation}
-
-Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. Now we can use the identity:
-
-\begin{equation}
-id_t e^{-i\hat{S}(t)} = \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))e^{-i\hat{S}(t)}
-\end{equation}
-
-Derived in appendix \ref{AP3B}, where $\text{ad}_A(B) = [A,B]$. To rewrite the transformed Hamiltonian as:
-
-\begin{equation}
-\hat{H}'(t) = e^{i\hat{S}(t)} \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right) e^{-i\hat{S}(t)}
-\end{equation}
-
-Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:
-
-\begin{equation}
-\label{PertFull}
-\hat{H}'(t) = \sum_m \frac{1}{m!} \text{ad}_{i\hat{S}(t)}^m \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right)
-\end{equation}
-
-Now, in this expression we have to expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
-Notice that we do not expand $\hat{H}(t)$ as an infinite series since $\hat{H}(t) = -\eta \hat{T}(t) + U\hat{D}$.
-Now, notice also that if we take $i\hat{S}^{(0)}(t)=0$ in \ref{PertFull}, then, to zeroth order in $\eta$ only terms in $m=0$ and $n=0$ contribute obtaining:
-
-\begin{equation}
-\hat{H}'^{(0)}(t) = U\hat{D}
-\end{equation}
-
-Which is indeed diagonal in the doublon number, and therefore we can take $i\hat{S}^{(0)}(t)=0$.
-With this equating terms of the same order in \ref{PertFull} is greatly simplified, since terms with high $m,n$ will correspond to terms with high $\eta$.
-Since we are only interested in orders up to second order, we can truncate \ref{PertFull} up to $m=2$:
-
-\begin{align}
-\label{PertTrunc}
-\hat{H}'(t) &=  \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) + [i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))] + \nonumber \\
-&+ \frac{1}{2} [i\hat{S}(t),[i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) ]]
-\end{align}
-
-This equation holds up to order $\eta^2$. In first order we obtain:
-
-\begin{equation}
-\label{1stO}
-\hat{H}'^{(1)}(t) = -\hat{T}(t) - d_t\hat{S}^{(1)}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right]
-\end{equation}
-
-Now we expanding in $m,d$ and use $\left[ \hat{D}, \hat{S}^{(\nu)}_{dm} \right] = d\hat{S}^{(\nu)}_{dm}$ because $\hat{S}^{(\nu)}_{dm}$ changes the doublon number by $d$:
-
-\begin{equation}
-\hat{H}'^{(1)}(t)=-\hat{T}(t)-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(1)}_{dm} e^{im\omega t}
-\end{equation}
-
-Therefore:
-
-\begin{align}
-i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{Ud+m\omega}e^{im\omega t} \label{1stOSpin}\\
-\hat{H}'^{(1)}(t) &= -\hat{T}_0(t) \label{1stOH}
-\end{align}
-
-To second order we find:
-
-\begin{align}
-\hat{H}'^{(2)}(t) &= - d_t\hat{S}^{(2)}(t) - \frac{1}{2}\left[-i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t) \right] + \left[i\hat{S}^{(1)}(t), -\hat{T}(t)-\frac{1}{2}d_t\hat{S}^{(1)}(t) \right] +\nonumber \\
-&+ \left[i\hat{S}^{(2)}(t), U\hat{D} \right] + \frac{1}{2} \left[i\hat{S}^{(1)}(t), \left[i\hat{S}^{(1)}(t), U\hat{D} \right] \right] = \nonumber \\
-&= \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
-\end{align}
-
-Using \ref{1stO} and using $\left[ i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t)\right] = 0$ due to different Fourier modes of the hopping operator being equal up to a constant, we can rewrite:
-
-\begin{equation}
-\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] - d_t\hat{S}^{(2)}(t)
-\end{equation}
-
-Using \ref{1stOSpin} and \ref{1stOH}, the middle term is:
-
-\begin{align*}
-&\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] = -\left[\sum_m \left( \frac{\hat{T}_{1m}}{U+m\omega} - \frac{\hat{T}_{-1m}}{U-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} + 2\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
-&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{U+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{U+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{U-m\omega} - \frac{2\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{U-m\omega} \right\} e^{i(m+n)\omega t} \\
-&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} - \frac{2\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t}
-\end{align*}
-
-Altogether:
-
-\begin{align*}
-\hat{H}'^{(2)}(t) &= \sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{U+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{2(U+n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{2(U-n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{U-n\omega} \right\} e^{im\omega t} \\
-&-\sum_{d\neq 0}\sum_m (Ud+m\omega) i\hat{S}^{(2)}_{dm} e^{im\omega t}
-\end{align*}
-
-We obtain:
-
-\begin{align}
-i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(Ud+n\omega)(Ud+m\omega)} \label{2ndOSpin}\\
-\hat{H}'^{(2)}(t) &= \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{U-n\omega} \right) e^{im\omega t} \label{2ndOH}
-\end{align}
-
-Now the effective Hamiltonian acts on the subspace of $\hat{P}_0$, therefore we are only interested on $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$).
-In this subspace we can write:
-
-\begin{align}
-\hat{H}_{\text{eff}}(t) &= \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = -\frac{1}{2}\sum_{mn} \left( \frac{\hat{P}_0  \hat{T}_{-1(m-n)}\hat{T}_{1n}\hat{P}_0}{U+n\omega} + \frac{\hat{P}_0 \hat{T}_{-1n} \hat{T}_{1(m-n)} \hat{P}_0}{U-n\omega} \right) e^{im\omega t} \nonumber \\
-&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \label{HeffSimplified}
-\end{align}
-
-Now, since the hopping operators act on the subspace $d=0$ and must remain within that subspace, thus we can write:
-
-\begin{align*}
-\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,a} t_{ij,b} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
-\end{align*}
-
-Where $a$ and $b$ are any two Fourier modes. Inserting this into \ref{HeffSimplified}:
-
-\begin{equation}
-\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,(-n)} t_{ij,(m+n)}}{U+n\omega} e^{im\omega t}
-\end{equation}
-
-Comparing with \ref{PertNoEMF} we can see that this will lead to a spin Hamiltonian
-
-\begin{equation}
-\hat{H}_{eff}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j
 \end{equation}
@@
 
-\begin{equation}
-J_{ij}(t) = \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
-\end{equation}
-
-Now, $t_{ij,m} = t_0 e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$, using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $\mathcal{J}_{-m}(x) = (-1)^m\mathcal{J}_m(x)$ and $\mathcal{J}_m(-x) = (-1)^m\mathcal{J}_m(x)$ we can write \ref{Jij1} as:
-
-\begin{equation}
-J_{ij}(t) = \sum_{mn} t_0^2 e^{i(\frac{\pi}{2}-\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{U+n\omega} \right) e^{im\omega t}
-\end{equation}
+\begin{align}
+J_{ij}(t) &= t_0^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
+&=\sum_{mn} t_0^2 e^{-i(\frac{\pi}{2}+\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{\text{U}+n\omega} \right) e^{im\omega t} \label{Jij1}
+\end{align}
 
@@
 \label{Jij2}
-J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{U+n\omega}
+J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
 \end{equation}
 
-Now, $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$.
+For $\omega>>U$ we can truncate \ref{Jij2} to the three smallest values of $n$, i.e.
+$n=0, \pm 1$.
+We can also use that $\alpha_{ij} << 1$ because $\alpha_{ij}$ is proportional to $\vec{A}$ which is proportional to $\omega^{-1}$.
+Therefore we can use $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:
+
+\begin{equation}
+\label{Jij3}
+J_{ij} \approx 2t_0^2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\end{equation}
+
+The lattice structure is contained in $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$.
 For a square lattices aligned with the coordinate system so that $\vec{a}_1=\hat{e}_x$ and $\vec{a}_2=\hat{e}_y$, we will have $\bs{R}_{ij} = \pm a\hat{e}_x,\pm a\hat{e}_y$, where $a$ is the lattice constant.
@@
 Where $\mathcal{E} = \frac{eaE_0}{\omega}$.
-For $\omega>>U$ we can take only the three smallest values of $n$, i.e.
-$n=0, \pm 1$ in \ref{Jij2} as an approximation.
-We can also use that $\alpha_{ij} << 1$ since $\omega$ appears in the denominator and so $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$:
-
-\begin{equation}
-J_{ij} = 2t_0^2 \left(\frac{\alpha_{ij}^2}{U+\omega} +\frac{1}{U} +\frac{\alpha_{ij}^2}{U-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
-\end{equation}
 
@@
 J_{ij}^{PP} = \begin{cases}
-		J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
+		J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
 J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
@@
 \begin{equation}
-J_{ij}^{CP} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{U+\omega} + \frac{1}{U-\omega} \right)
+\label{JijCPSQUARE}
+J_{ij}^{CP} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
 \end{equation}
@@
 
-Now, in \ref{Jij2}, consider that the $\alpha_{ij}$ values are given by $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ where $\bs{R}_{ij}$ are the displacement vectors in a honeycomb lattice.
+Now consider a honeycomb lattice structure, so that the $\alpha_{ij}$ values are given by $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ where $\bs{R}_{ij}$ are the displacement vectors in a honeycomb lattice.
 There are six such vectors:
@@
 
-We see that again, this result will not depend on the helicity of the applied electric field.
+From here we can see that if we take the same approximation as in \ref{Jij3} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.
 
@@
 
-Now, let's investigate the effect of the electric field for the Hubbard model with SOI. As seen in \ref{AP3A} we can use the Peierls substitution to obtain the Hamiltonian:
+Now, let's investigate the effect of the electric field for the Hubbard model with SOI, i.e. \ref{Hubbard}, in this case the hopping operator gets an extra spin-dependent term:
 
 \begin{equation}
-\hat{H}(t) = -\sum_{\langle i,j \rangle, \sigma, \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 + \bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} = -\hat{T}(t) + \text{U}\hat{D}
+\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
 \end{equation}
 
-In this case the hopping operator $\hat{T}(t)$ includes the spin orbit interaction, but the time dependence is the same as before, we can use $e^{ie\bs{R}_{ij}\bs{A}(t)} =  \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t}$ where as before $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$ to write:
+In this case the hopping amplitudes are:
 
 \begin{equation}
-\hat{T}(t) = \sum_{\langle i,j \rangle, \sigma, \sigma'} \sum_m \Gamma_{ij,m}^{\sigma\sigma'} e^{im \omega t} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
+\label{HoppHubbSOI}
+t_{ij}^{\sigma \sigma'} = \begin{cases}
+	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
+	0 & \text{ otherwise}
+\end{cases} \quad
 \end{equation}
 
-Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar.
-Now we can follow the same procedure as in the previous section that lead to \ref{HeffSimplified}:
+And as before $\hat{H} = -\hat{T} + \text{U}\hat{D}$.
+In the presence of an electromagnetic field we can apply the Peierls substitution as we did before, and the effective Hamiltonian will be given by \ref{HeffSimplified}.
+inserting the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} we get:
+
+\begin{align}
+\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
+&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
+\end{align}
+
+Now, since the spin orbit interaction is weaker than the kinetic term, we can neglect the term proportional to $\bs{\Delta}_{ij}^2$ and write:
 
 \begin{equation}
-\hat{H}_{\text{eff}}(t) = \hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0 = -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0 \left(\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)} \right) \hat{P}_0 }{\text{U}+n\omega} \right\} e^{im\omega t}
+(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \approx \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4})
 \end{equation}
 
-The product of hopping operators restricted on this subspace can be written as:
+Where we used $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$.
+The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
+The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
 
-\begin{equation}
-\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4}
-\end{equation}
-
-For any integers $a,b$ labeling any Fourier modes. Therefore:
-
-\begin{equation}
-\hat{H}_{\text{eff}}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4} \left\{ \frac{\Gamma_{ji,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ij,n}^{\sigma_3\sigma_4} + \Gamma_{ji,-n}^{\sigma_1\sigma_2}\Gamma_{ij,(m+n)}^{\sigma_3\sigma_4} }{\text{U}+n\omega}  \right\} e^{im\omega t}
-\end{equation}
-
-We can write:
+Now we can rewrite \ref{HeffHubbSOI1} as:
 
 \begin{align*}
-\Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{a}(\alpha_{ji})\mathcal{J}_b(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
-&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
-&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
-\end{align*}
-
-Where we used $\theta_{ji} = \theta_{ij}$, $\alpha_{ji} = - \alpha_{ij}$ and $\bs{\Delta}_{ji} = -\bs{\Delta}_{ij}$.
-We neglect the $\mathcal{O}(\bs{\Delta}_{ij}^2)$ term.
-The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
-The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
-Define:
-
-\begin{equation}
-\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
-    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
-\end{equation}
-
-Now, introducing the spin operators \ref{SpinOperators}, using relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and taking into account that in this subspace $n_{i\uparrow}+n_{i\downarrow}=1$ we obtain:
-
-\begin{align*}
-\hat{H}_{\text{eff}}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
-&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
+\hat{H}_{\text{eff}}(t) &\approx - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
 &= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
@@
 
-Where we also used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:
+Where we used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:
 
@@
 \begin{equation}
-\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
+\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{-i(\frac{\pi}{2}+\theta_{ij})m} \left\{ 
     \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}

### 2018-10-29 Chapters/SGraphene.tex
Refactor done

@@
 \begin{align}
-\hat{H}_{KMH} &= -t\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \nonumber \\
+\hat{H}_{KMH} &= -t_0\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \nonumber \\
 &+ i\Delta_R \sum_{\langle i j \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}) \hat{c}_{j\sigma'} + U\hat{D}
@@
 
-Where sum over next-nearest neighbors is denotes by $\langle \langle i j \rangle \rangle$ and $\Delta$ is the intrinsic spin orbit coupling and $\Delta_R$ is the Rashba spin orbit coupling.
+Where sum over next-nearest neighbors is denotes by $\langle \langle i j \rangle \rangle$ and $\Delta$ is the intrinsic spin orbit coupling and $\Delta_R$ is the Rashba spin orbit coupling, which is the same as in the previous section if we choose $\bs{\Delta}_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$.
 $\nu_{ij}=\pm 1$ depending on whether the electron traversing from i to j makes a right ($+1$) or a left turn ($-1$).
-We can apply Peierls substitution in presence of a vector potential $\vec{\bs{A}}(t)$ to obtain the time dependent Hamiltonian:
+In this case the hopping amplitudes can be written as:
 
-\begin{align}
-\hat{H}_{KMH}(t) &= -\sum_{\langle i j \rangle \sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} \nonumber \\
-&+ i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  e^{ie\bs{R}_{ij}\bs{A}(t)} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + U\hat{D}
-\end{align}
+\begin{equation}
+\label{HoppHubbSOI}
+t_{ij}^{\sigma \sigma'} = \begin{cases}
+	\delta_{\sigma \sigma'}t_0- i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}) & \text{for } i, j \text{ nearest neighbors} \\
+	-i\Delta \nu_{ij} \sigma_{\sigma \sigma'}^z & \text{for } i, j \text{ next-nearest neighbors} \\
+	0 & \text{ otherwise}
+\end{cases} \quad
+\end{equation}
 
-We can write the hopping operator as a sum of two terms $\hat{T}(t) = \hat{T}^1(t) + \hat{T}^2(t)$, the first corresponding to the hopping between nearest neighbors and the second corresponding to the hopping between next-nearest neighbors.
-$\hat{T}^1(t)$ is the same as the hopping in the previous section specialized for the case of Rashba interaction:
+We can apply \ref{HeffSimplified} with this hopping amplitudes to obtain:
 
 \begin{align*}
-\hat{T}^1(t) &= -\sum_{\langle i j \rangle \sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)} (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'} \nonumber \\
-&= -\sum_{\langle i j \rangle \sigma \sigma'} \left( \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} \right) (\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij})) \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'} \nonumber \\
-&= \sum_{\langle i j \rangle \sigma \sigma'} \sum_m  \Xi_{ij,m}^{\sigma \sigma'} e^{im\omega t}\hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'}
+\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+& - \frac{1}{2} \sum_{\langle \langle i,j \rangle \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+&= \hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t)
 \end{align*}
 
-Where we defined:
-
-\begin{equation}
- \Xi_{ij,m}^{\sigma \sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma \sigma'}t_0 - i\Delta_R \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}))
-\end{equation}
-
-Similarly, for $\hat{T}^2(t)$:
+$\hat{H}_{\text{eff}}'(t)$ is the same effective Hamiltonian as in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ and it will lead to the same spin Hamiltonian after introducing spin operators $\hat{H}_{\text{eff}}'(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}.
+Now we will find the spin Hamiltonian for $\hat{H}_{\text{eff}}''(t)$.
+Using $\nu_{ij}\nu_{ji} = -1$:
 
 \begin{align*}
-\hat{T}^2(t) &= i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  e^{ie\bs{R}_{ij}\bs{A}(t)} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \\
-&= i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'}  \left( \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} \right) \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \\
-&= \sum_{\langle i j \rangle \sigma \sigma'} \sum_m  \Pi_{ij,m}^{\sigma \sigma'} e^{im\omega t}\hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma'}
+\hat{H}_{\text{eff}}''(t) &= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{align*}
 
-Where
-
-\begin{equation}
-\Pi_{ij,m}^{\sigma \sigma'} = i \Delta e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) \nu_{ij} \sigma_{\sigma \sigma'}^z
-\end{equation}
-
-We write $\hat{H}_{KMH}(t) = \hat{T}^1(t) + \hat{T}^2(t) + U\hat{D}$ and apply \ref{HeffSimplified} to obtain $\hat{H}_{\text{eff}}(t)$.
-In order to find an expression for $\hat{H}_{\text{eff}}(t)$, we need to find how the terms $\hat{T}_{-1a}\hat{T}_{1b}$ ($a$ and $b$ being subscripts for the Fourier mode) act on the $d=0$ subspace when $\hat{T}(t) = \hat{T}^1(t) + \hat{T}^2(t)$.
-Now, $\hat{T}_1(t)$ represents the hopping between nearest neighbors whereas $\hat{T}_2(t)$ represents the hopping between next-nearest neighbors, the only way to avoid double occupancies would be to apply $\hat{T}^1(t)$ twice between the same nearest neighbors sites, or $\hat{T}^2(t)$ between the same next-nearest neighbors sites, that is, any cross term between $\hat{T}^1(t)$ and $\hat{T}^2(t)$ will lead to double occupancies.
-This means that $\hat{P}_0\hat{T}_{-1a}\hat{T}_{1b}\hat{P}_0 = \hat{P}_0\hat{T}_{-1a}^1\hat{T}_{1b}^1\hat{P}_0+\hat{P}_0\hat{T}_{-1a}^2\hat{T}_{1b}^2\hat{P}_0$, for the nearest neighbors hopping operator we obtain the same expression as in the previous section:
-
-\begin{equation}
-\hat{P}_0 \hat{T}_{-1a}^1\hat{T}_{1b}^1 \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Xi_{ji,a}^{\sigma_1\sigma_2}\Xi_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
-\end{equation}
-
-Whereas for the next-neighbors hopping operator:
-
-\begin{equation}
-\hat{P}_0 \hat{T}_{-1a}^2\hat{T}_{1b}^2 \hat{P}_0 = \sum_{\langle \langle i,j \rangle \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Pi_{ji,a}^{\sigma_1\sigma_2}\Pi_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
-\end{equation}
-
-Therefore for the effective Hamiltonian:
-
-\begin{align*}
-\hat{H}_{\text{eff}}(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
-&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
-&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t)
-\end{align*}
-
-For $\hat{H}_{\text{eff}}'(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}.
-For $\hat{H}_{\text{eff}}''(t)$ the interaction will be between next-nearest neighbors:
-
-\begin{align*}
-\hat{H}_{\text{eff}}''(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
-&= -\frac{1}{2}\sum_{mn} \sum_{\langle \langle i,j \rangle \rangle \sigma_1 \sigma_2 \sigma_3 \sigma_4} \left\{ \frac{\hat{P}_0 (\Pi_{ji,(m-n)}^{\sigma_1\sigma_2}\Pi_{ij,n}^{\sigma_3\sigma_4} + \Pi_{ji,(-n)}^{\sigma_1\sigma_2}\Pi_{ij,(m+n)}^{\sigma_3\sigma_4}) \hat{P}_0}{U+n\omega} \right\}\hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} e^{im\omega t} \\
-&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \sum_{mn} \frac{e^{i(\frac{\pi}{2}-\theta_{ij})m}}{\text{U}+n\omega} \left\{ \mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij}) \right\} e^{im \omega t} \\
-& \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\} \\
-&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\}
-\end{align*}
-
-As expected, the time dependence is the same as in the nearest neighbor interaction.
 For the spin sum we use \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} taking into account that in the $d=0$ subspace $\hat{n}_{i\uparrow}+\hat{n}_{i\downarrow} = 1$:
@@
 This describes a type of anisotropic exchange interaction.
-Notice that the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}.
+Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the time dependence will not be the same, since the structure terms $\alpha_{ij}$ will change for next-nearest neighbors $i$ and $j$.
 
-Together with exchange and DMI interaction obtained in the previous section the total effective Hamiltonian in this system is:
+Altogether, the total effective Hamiltonian in this system is:
 
@@
 
-Where $J_{ij}(t)$ and $\bs{D}_{ij}(t)$ have been defined in \ref{JijHSOI} and \ref{DijHSOI}.
-
 \end{section}

### 2018-10-29 Chapters/TDHeff.tex
Refactor done

First we will start we a general Hamiltonian of the type:

\begin{equation}
\hat{H} = -\hat{T} + \text{U}\hat{D}
\end{equation}

Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\hat{T}$ is any hopping operator. The only assumption we will make about $\hat{T}$ is that it is proportional to any power of $\hat{p}$ in which case we can apply the Peierls substitution (\ref{AP3A}) to introduce to take into account the effect of the electromagnetic perturbation in the lattice. The strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.

In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$. In the simplest case, for example, the sum would be restricted to nearest neighbors and the hopping amplitude would be diagonal in the spin state. With this notation, in presence of a vector potential $\vec{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:

\begin{equation}
t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)}
\end{equation}

Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$. We write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, where $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively. The vector potential takes the form $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.

Let us define $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:

\begin{align}
\alpha_{ij} &= -\alpha_{ji} \label{alphaSym} \\
\theta_{ij} &= \theta_{ji} \label{thetaSym}
\end{align}

and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:

\begin{align*}
t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
\end{align*}

Where we defined

\begin{equation}
\label{HoppAmpFourier}
t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})
\end{equation}

Which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}. Correspondingly we can write $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$ where $\hat{T}_m$ is the sum of all the \textit{m}th Fourier mode of the hopping terms. We can further decompose the hopping operator into:

\begin{equation}
\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
\end{equation}

Where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.

In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$. The transformed Hamiltonian is:

\begin{equation}
\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
\end{equation}

We perform the unitary transformation perturbatively in the hopping operator, we can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion. We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$. In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$. Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$. With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e. we can write:

\begin{equation}
\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
\end{equation}

where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.

Now we can use the identity:

\begin{equation}
id_t e^{-i\hat{S}(t)} = \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))e^{-i\hat{S}(t)}
\end{equation}

Derived in appendix \ref{AP3B}, where $\text{ad}_A(B) = [A,B]$ to rewrite the transformed Hamiltonian as:

\begin{equation}
\hat{H}'(t) = e^{i\hat{S}(t)} \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right) e^{-i\hat{S}(t)}
\end{equation}

Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:

\begin{equation}
\label{PertFull}
\hat{H}'(t) = \sum_m \frac{1}{m!} \text{ad}_{i\hat{S}(t)}^m \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right)
\end{equation}

Now, in this expression we have to expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number. Notice that we do not expand $\hat{H}(t)$ as an infinite series since $\hat{H}(t) = -\eta \hat{T}(t) + \text{U}\hat{D}$. Now, notice also that if we take $i\hat{S}^{(0)}(t)=0$ in \ref{PertFull}, then, to zeroth order in $\eta$ only terms in $m=0$ and $n=0$ contribute obtaining:

\begin{equation}
\hat{H}'^{(0)}(t) = \text{U}\hat{D}
\end{equation}

Which is indeed diagonal in the doublon number, and therefore we can take $i\hat{S}^{(0)}(t)=0$. With this equating terms of the same order in \ref{PertFull} is greatly simplified, since terms with high $m,n$ will correspond to terms with high $\eta$. Since we are only interested in orders up to second order, we can truncate \ref{PertFull} up to $m=2$:

\begin{align}
\label{PertTrunc}
\hat{H}'(t) &=  \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) + [i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))] + \nonumber \\
&+ \frac{1}{2} [i\hat{S}(t),[i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) ]]
\end{align}

This equation holds up to order $\eta^2$. In first order we obtain:

\begin{equation}
\label{1stO}
\hat{H}'^{(1)}(t) = -\hat{T}(t) - d_t\hat{S}^{(1)}(t) + \left[ i\hat{S}^{(1)}(t), \text{U}\hat{D} \right]
\end{equation}

Now we expanding in $m,d$ and use $\left[ \hat{D}, \hat{S}^{(\nu)}_{dm} \right] = d\hat{S}^{(\nu)}_{dm}$ because $\hat{S}^{(\nu)}_{dm}$ changes the doublon number by $d$:

\begin{equation}
\hat{H}'^{(1)}(t)=-\hat{T}(t)-\sum_{d\neq 0}\sum_m (\text{U}d+m\omega) i\hat{S}^{(1)}_{dm} e^{im\omega t}
\end{equation}

Therefore:

\begin{align}
i\hat{S}^{(1)}_d(t) &= -\sum_m \frac{\hat{T}_{d,m}}{\text{U}d+m\omega}e^{im\omega t} \label{1stOSpin}\\
\hat{H}'^{(1)}(t) &= -\sum_m \hat{T}_{0,m}(t)e^{im\omega t} \label{1stOH}
\end{align}

To second order we find:

\begin{align}
\hat{H}'^{(2)}(t) &= - d_t\hat{S}^{(2)}(t) - \frac{1}{2}\left[-i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t) \right] + \left[i\hat{S}^{(1)}(t), -\hat{T}(t)-\frac{1}{2}d_t\hat{S}^{(1)}(t) \right] +\nonumber \\
&+ \left[i\hat{S}^{(2)}(t), \text{U}\hat{D} \right] + \frac{1}{2} \left[i\hat{S}^{(1)}(t), \left[i\hat{S}^{(1)}(t), \text{U}\hat{D} \right] \right] = \nonumber \\
&= \left[i\hat{S}^{(2)}(t), \text{U} \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), \text{U}\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
\end{align}

Using \ref{1stO} and using $\left[ i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t)\right] = 0$ due to different Fourier modes of the hopping operator being equal up to a constant (explain better), we can rewrite:

\begin{equation}
\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), \text{U} \hat{D} \right] - \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] - d_t\hat{S}^{(2)}(t)
\end{equation}

Using \ref{1stOSpin} and \ref{1stOH}, the middle term is:

\begin{align*}
&\left[ i\hat{S}^{(1)}(t), \hat{T}(t) - \hat{H}'^{(1)}(t)\right] = -\left[\sum_m \left( \frac{\hat{T}_{1m}}{\text{U}+m\omega} - \frac{\hat{T}_{-1m}}{\text{U}-m\omega} \right)e^{im \omega t}, \sum_n \left( \hat{T}_{-1n} + 2\hat{T}_{0n} + \hat{T}_{1n} \right) e^{in\omega t} \right] \\
&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1m}, \hat{T}_{0n} \right]}{\text{U}+m\omega} + \frac{\left[\hat{T}_{1m}, \hat{T}_{-1n} \right]}{\text{U}+m\omega} - \frac{\left[\hat{T}_{-1m}, \hat{T}_{1n} \right]}{\text{U}-m\omega} - \frac{2\left[\hat{T}_{-1m}, \hat{T}_{0n} \right]}{\text{U}-m\omega} \right\} e^{i(m+n)\omega t} \\
&= -\sum_{mn} \left\{ \frac{2\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{\text{U}+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} - \frac{2\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{\text{U}-n\omega} \right\} e^{im\omega t}
\end{align*}

Altogether:

\begin{align*}
\hat{H}'^{(2)}(t) &= \sum_{mn} \left\{ \frac{\left[\hat{T}_{1n}, \hat{T}_{0(m-n)} \right]}{\text{U}+n\omega} + \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{2(\text{U}+n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{2(\text{U}-n\omega)} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{0(m-n)} \right]}{\text{U}-n\omega} \right\} e^{im\omega t} \\
&-\sum_{d\neq 0}\sum_m (\text{U}d+m\omega) i\hat{S}^{(2)}_{dm} e^{im\omega t}
\end{align*}

We obtain:

\begin{align}
i\hat{S}^{(2)}_{dm} &= \sum_n \frac{\left[ \hat{T}_{dn}, \hat{T}_{0(m-n)} \right]}{(\text{U}d+n\omega)(\text{U}d+m\omega)} \label{2ndOSpin}\\
\hat{H}'^{(2)}(t) &= \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t} \label{2ndOH}
\end{align}

Now the effective Hamiltonian acts on the subspace of $\hat{P}_0$, therefore we are only interested on $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$). In this subspace we can write:

\begin{align}
\hat{H}_{\text{eff}}(t) &= \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = -\frac{1}{2}\sum_{mn} \left( \frac{\hat{P}_0  \hat{T}_{-1(m-n)}\hat{T}_{1n}\hat{P}_0}{\text{U}+n\omega} + \frac{\hat{P}_0 \hat{T}_{-1n} \hat{T}_{1(m-n)} \hat{P}_0}{\text{U}-n\omega} \right) e^{im\omega t} \nonumber \\
&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{\text{U}+n\omega} \right\} e^{im\omega t}
\end{align}

Now, since the hopping operators act on the subspace $d=0$ and must remain within that subspace, therefore $\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0$ will be a sum of all possible hoppings between two different sites:

\begin{align*}
\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0 = \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} t_{ij,a}^{\sigma_1 \sigma_2} t_{ji,b}^{\sigma_3 \sigma_4} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4}
\end{align*}

Where $a$ and $b$ are any two Fourier modes. Inserting this into \ref{HeffSimplified} and using the definition of $t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$ and using that $\theta_{ji} = \theta_{ij}$ and $\alpha_{ji} = -\alpha_{ij}$ and the properties $\mathcal{J}_{-m}(x) = (-1)^m\mathcal{J}_m(x)$ and $\mathcal{J}_m(-x) = (-1)^m\mathcal{J}_m(x)$ we can write \ref{HeffSimplified} as:

\begin{align}
&\hat{H}_{\text{eff}}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} \frac{t_{ij,m-n}^{\sigma_1 \sigma_2} t_{ji,n}^{\sigma_3 \sigma_4} + t_{ij,-n}^{\sigma_1 \sigma_2} t_{ji,m+n}^{\sigma_3 \sigma_4}}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} \frac{ \mathcal{J}_{m-n}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ji}) + \mathcal{J}_{-n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ji})}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} (-1)^m \frac{ \mathcal{J}_{n-m}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
&= - \frac{1}{2} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffSimplified}
\end{align}

Where we defined:

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{-i(\frac{\pi}{2}+\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
\end{equation}

In the following sections we will apply what we have derived here for different models of the hopping operator.

### 2018-10-30 Chapters/Chapter3.tex
change title

@@
 \begin{equation}
-\label{Jij2}
-J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
 \end{equation}
 
-For $\omega>>U$ we can truncate \ref{Jij2} to the three smallest values of $n$, i.e.
+For $\omega>>U$ we can truncate this to the three smallest values of $n$, i.e.
 $n=0, \pm 1$.
@@
 \begin{equation}
-\label{Jij3}
-J_{ij} \approx 2t_0^2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\label{MFactorApprox}
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx 2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right)
+\end{equation}
+
+And the exchange interaction coupling becomes:
+
+\begin{equation}
+\label{Jij2}
+J_{ij} \approx J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
 \end{equation}
@@
 
-From here we can see that if we take the same approximation as in \ref{Jij3} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.
+From here we can see that if we take the same approximation as in \ref{Jij2} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.
 

### 2018-10-30 Chapters/SGraphene.tex
change title

@@
 an external electric field in the $\hat{z}$ direction, a Rashba spin orbit interaction term is allowed between nearest neighbors.
-In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:
+In these circumstances the system can be modeled by the Kane-Mele-Hubbard model \cite{Laubach2014}:
 
@@
 This describes a type of anisotropic exchange interaction.
-Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the time dependence will not be the same, since the structure terms $\alpha_{ij}$ will change for next-nearest neighbors $i$ and $j$.
+Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the renormalization will not be the same, since the structure terms $\alpha_{ij}$ will differ from those in a nearest neighbor interaction.
+For example, if we take the time independent approximation \ref{MFactorApprox}, then the exchange interaction will be:
+
+\begin{align*}
+J_{ij} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\end{align*}
+
+Where $\mathcal{E} = \frac{eaE_0}{\omega}$. Whereas the anisotropic exchange coupling will be:
+
+\begin{align*}
+H_{ij} = H_{ij}^0 + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\end{align*}
+
+Where $H_{ij}^0 = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
 

### 2018-10-31 Chapters/Chapter2.tex
a
Refactor done
Stuffs

@@
 \begin{equation}
-\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j = J\sum_{\langle i,j \rangle} \boldsymbol{S}_i\boldsymbol{S}_j
+\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i\bs{S}_j
 \end{equation}
 
-Which is the Heisenberg model for antiferromagnets with $J = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
+Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
 
 \begin{align*}
-\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j = \sum_{\langle i,j \rangle} \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j
 \end{align*}
 
-Where $\boldsymbol{D}_{ij} = \frac{4it}{\text{U}}\boldsymbol{\Delta}_{ij}$. Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ gives:
+Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$. Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ gives:
 
@@
 With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
+This term is known as pseudodipolar interaction \citep{Moriya1960} and it will be neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
 
@@
 \begin{equation}
-\hat{H}_{eff} = \sum_{\langle i,j \rangle} \left( J\boldsymbol{S}_i\boldsymbol{S}_j + \boldsymbol{D}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \right)
+\hat{H}_{\text{eff}} \approx \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j \right) \label{HeffNOEMF}
 \end{equation}
+
+With:
+
+\begin{align}
+J_{ij}^0 &= \frac{2t^2}{\text{U}} \label{Jij0} \\
+\bs{D}_{ij}^0 &= \frac{4it}{\text{U}}\bs{\Delta}_{ij} \label{Dij0}
+\end{align}
 

### 2018-10-31 Chapters/KaneMele.tex
Stuffs

--- 2018-10-30 Chapters/SGraphene.tex
@@
-\begin{section}{Graphene}
+\begin{section}{Kane Mele Hubbard model}
 
-In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
+The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene.
+In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
 However, if inversion symmetry is broken by i.e.
@@
 \begin{equation}
-\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} \tilde{J}_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
 \end{equation}
@@
 \begin{equation}
-H_{ij}(t) = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\tilde{J}_{ij}(t) = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{equation}
 
-This describes a type of anisotropic exchange interaction.
+This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
+If the laser field is not too strong $\tilde{J}_{ij}(t) > 0$, and, in the $\hat{e}_z$ direction this interaction will compete against the exchange interaction $J_{ij}(t)$.
+The reason for this is that being $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned.
+The effect of $\tilde{J}_{ij}(t)$ will be the opposite, forcing the next nearest neighbor spins to be in opposite directions.
+In general the strength of the exchange interaction will be larger and the net effect of $\tilde{J}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
+
 Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the renormalization will not be the same, since the structure terms $\alpha_{ij}$ will differ from those in a nearest neighbor interaction.
-For example, if we take the time independent approximation \ref{MFactorApprox}, then the exchange interaction will be:
+For example, if we take the time independent approximation \ref{MFactorApprox}, and use $\lambda = \pm 1$ for circular polarized light, then the exchange interaction will be:
 
 \begin{align*}
-J_{ij} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+J_{ij} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = J_{ij}^0 + J_{ij}^0 \text{U}\frac{1}{2} \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
 \end{align*}
 
-Where $\mathcal{E} = \frac{eaE_0}{\omega}$. Whereas the anisotropic exchange coupling will be:
+Where $\mathcal{E} = \frac{eaE_0}{\omega}$. And the DMI coupling will be approximated by:
 
 \begin{align*}
-H_{ij} = H_{ij}^0 + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\bs{D}_{ij} = \bs{D}_{ij}^0 + 2it_0\bs{\Delta}_{ij}  \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = \bs{D}_{ij}^0 + \bs{D}_{ij}^0 \text{U}\frac{1}{2} \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
 \end{align*}
 
-Where $H_{ij}^0 = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
+$J_{ij}^0$ and $\bs{D}_{ij}^0$ have been defined in \ref{Jij0} and \ref{Dij0}, the factor $\frac{1}{2}$ is due to the light being circularly polarized.
+In contrast, the anisotropic exchange coupling will be:
+
+\begin{align*}
+\tilde{J}_{ij} = \tilde{J}_{ij}^0 + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = \tilde{J}_{ij}^0 + \tilde{J}_{ij}^0 \text{U} \frac{3}{2} \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\end{align*}
+
+Where $\tilde{J}_{ij}^0 = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
+If we define $\Delta J_{ij} = J_{ij} - J_{ij}^0$ and $\Delta \tilde{J}_{ij} = \tilde{J}_{ij} - \tilde{J}_{ij}^0$ we can see that, in this approximation $\frac{\Delta J_{ij}}{\Delta \tilde{J}_{ij}} = \frac{1}{3}\frac{J_{ij}^0}{\tilde{J}_{ij}^0}$ whereas $\frac{\Delta J_{ij}}{\Delta |\bs{D}_{ij}|} = \frac{J_{ij}^0}{|\bs{D}_{ij}^0|}$.
 
@@
 \hat{H}_{\text{eff}}(t) = &\hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t) = \sum_{\langle i,j \rangle} \left( J_{ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j \right) \nonumber \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+&+ \sum_{\langle \langle i,j \rangle \rangle} \tilde{J}_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
 \end{align}
@@
 J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{ij}(t) &= -2t_0\Delta_R (R_{ij}^y, - R_{ij}^x, 0) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\bs{D}_{ij}(t) &= -2t_0\Delta_R (R_{ij}^y, - R_{ij}^x, 0) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\tilde{J}_{ij}(t) &= \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{align*}

### 2018-11-21 Chapters/Chapter3.tex
Stuffs
uni changes

@@
 The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
+This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}), in which only the exchange interaction $J$ plays a role.We reproduce the result, and extend the analysis to different systems with spin orbit interaction, thereby modulating $\bs{D}_{ij}$ or other spin interactions.
 
@@
 
+The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI.
 In this case the hopping amplitudes are:
@@
 
-\input{Chapters/SGraphene}
+\input{Chapters/KaneMele}
 

### 2018-11-22 Chapters/Chapter3.tex
minor

--- 2018-10-30 Chapters/Chapter3.tex
@@
 We can also use that $\alpha_{ij} << 1$ because $\alpha_{ij}$ is proportional to $\vec{A}$ which is proportional to $\omega^{-1}$.
-Therefore we can use $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:
+Therefore we can use $\mathcal{J}_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:
 

### 2018-11-22 Chapters/KaneMele.tex
minor

@@
 This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
+The same spin model is obtain in \cite{Rachel2010} without the laser perturbation.
 If the laser field is not too strong $\tilde{J}_{ij}(t) > 0$, and, in the $\hat{e}_z$ direction this interaction will compete against the exchange interaction $J_{ij}(t)$.
-The reason for this is that being $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned.
+The reason for this is that since $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned.
 The effect of $\tilde{J}_{ij}(t)$ will be the opposite, forcing the next nearest neighbor spins to be in opposite directions.
+In the $\hat{e}_x-\hat{e}_y$ plane, $\tilde{J}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$.
 In general the strength of the exchange interaction will be larger and the net effect of $\tilde{J}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.

### 2018-11-22 Chapters/Chapter2.tex
Moar text

@@
-\chapter{Effective Hamiltonian } % Main chapter title
+\chapter{Effective Hamiltonian}
 
@@
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
+The Hubbard model, was developed to describe the single-band magnetism \cite{Hubbard1963}, it also describes the transition between conducting and insulating systems, predicting the existence of Mott insulators, materials which should be conducting according to band theory, but they are insulating due to electron-electron interactions.
+
 We will consider a half filled system in the strong coupling limit.

### 2018-11-22 Chapters/Chapter3.tex
Moar text

@@
 
-In this chapter we will derive an effective Hamiltonian for different types of Hubbard-like models in the presence of a high frequency electromagnetic perturbation.
+In this chapter we will derive an effective spin Hamiltonian for different models in the presence of a high frequency electromagnetic perturbation.
 The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
+This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:
+
+\begin{equation*}
+\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation*}
+
+In this model only the exchange interaction $J$ plays a role.
+The electromagnetic perturbation is then introduced via the Peierls substitution.
+We reproduce the result in section \ref{Section3Hubbard}.
+In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions.
+The simplest model with spin orbit interaction is \ref{Hubbard}:
+
+\begin{equation*}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation*}
+
+In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
+In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}.
+For this case we examine the Kane Mele Hubbard model.
+The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
+This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.
+
+Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
 
 \begin{section}{Time dependent effective Hamiltonian}
-
+\label{SectionTDHeff}
 \input{Chapters/TDHeff}
@@
 \begin{section}{Hubbard model without SOI}
-
+\label{Section3Hubbard}
 We start by considering the simplest hopping operator, as in the Hubbard model:
@@
 \begin{section}{Hubbard model with SOI}
-
+\label{Section3HubbardSOI}
 Now, let's investigate the effect of the electric field for the Hubbard model with SOI, i.e. \ref{Hubbard}, in this case the hopping operator gets an extra spin-dependent term:

### 2018-11-22 Chapters/KaneMele.tex
Moar text

@@
 The same spin model is obtain in \cite{Rachel2010} without the laser perturbation.
-If the laser field is not too strong $\tilde{J}_{ij}(t) > 0$, and, in the $\hat{e}_z$ direction this interaction will compete against the exchange interaction $J_{ij}(t)$.
-The reason for this is that since $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned.
-The effect of $\tilde{J}_{ij}(t)$ will be the opposite, forcing the next nearest neighbor spins to be in opposite directions.
+If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\tilde{J}_{ij}(t) > 0$.
+Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane.
+The exchange interaction $J_{ij}(t)$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned.
+Therefore, $\tilde{J}_{ij}(t)$ will compete against $J_{ij}(t)$ in the $\hat{e}_z$ direction.
 In the $\hat{e}_x-\hat{e}_y$ plane, $\tilde{J}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$.

### 2018-11-26 Chapters/Chapter1.tex
changes

@@
 Additionally, spin axis reorientation by a lateral electrical current can be used to offer ultra-fast electrical writing and reading in AFM devices \cite{Zelezny2014}.
+
+Our goal in this project is to investigate the techniques to manipulate the magnetic state in an antiferromagnetic insulator, which could potantially lead to applications for ultra-fast writing devices.
+For ferromagnetic materials it has already been shown that short laser pulses can induce an effective magnetic field that can reach an amplitude of a few Tesla (\cite{Qaiumzadeh2016}, \cite{Qaiumzadeh2013}).

### 2018-11-26 Chapters/Chapter2.tex
changes

--- 2018-10-31 Chapters/Chapter2.tex
@@
-\chapter{Effective Hamiltonian } % Main chapter title
+\chapter{Effective Spin Hamiltonian}
 
@@
 
-where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian.
+where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian:
 
 \begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\boldsymbol{\sigma}\boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\bs{\sigma}\bs{\nabla}V(\textbf{r}) \times \textbf{p}
 \end{equation}
@@
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
+The original Hubbard model, was developed to describe the single-band magnetism \cite{Hubbard1963}, it also describes the transition between conducting and insulating systems, predicting the existence of Mott insulators, materials which should be conducting according to band theory, but they are insulating due to electron-electron interactions.
+
 We will consider a half filled system in the strong coupling limit.

### 2018-11-26 Chapters/Chapter3.tex
minor
changes

@@
 
-In this model only the exchange interaction $J$ plays a role.
+In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role.
 The electromagnetic perturbation is then introduced via the Peierls substitution.
@@
 \begin{equation*}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation*}
 
+Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.
 In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
-In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}.
+
+In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator.
 For this case we examine the Kane Mele Hubbard model.

### 2018-11-28 Chapters/OtherHams.tex
NNN ham

Next we will consider a Hamiltonian:

\begin{equation}
\hat{H} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij}^{(0)} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{ij}^{(1)} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
	\text{U}\hat{D}
\end{equation}

Which is the same we studied in section \ref{Section3HubbardSOI} plus a NNN hopping and SOI term. As before, $\bs{\Delta}_{ij}^{(n)}$ describes Rashba SOI when $\bs{\Delta}_{ij}^{(n)} = i\Delta_R^{(n)}(R_{ij}^y, -R_{ij}^x, 0)$.
The hopping amplitudes thus are:

\begin{equation}
\label{HoppHubbSOI}
t_{ij}^{\sigma \sigma'} = \begin{cases}
	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{0,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
	0 & \text{ otherwise}
\end{cases} \quad
\end{equation}

The effective Hamiltonian will be the same as in section \ref{Section3HubbardSOI}, with the corresponding NNN terms. This is because in second order perturbation NN hopping terms do not mix with NNN hopping terms. Thus, the effective spin Hamiltonian will be:

\begin{align}
\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{0,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{0,ij}(t) \bs{S}_i \times \bs{S}_j \right\} + \nonumber \\
&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
\end{align}

Where:

\begin{align*}
J_{0,ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{0,ij}(t) &= 2it_0 \bs{\Delta}_{0,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{1,ij}(t) &= 2it_1 \bs{\Delta}_{1,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}

### 2018-12-03 Chapters/Chapter3.tex
NNN ham
moar

@@
 In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator.
-For this case we examine the Kane Mele Hubbard model.
+For this case we examine the Kane-Mele-Hubbard model.
 The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
@@
 
+\begin{section}{Other general Hamiltonians}
+\label{SectionOtherHams}
+\input{Chapters/OtherHams}
+
+\end{section}
+
 \begin{subappendices}
@@
 
-In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the latice \ref{LaticeHam} to:
+In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the lattice \ref{LaticeHam} to:
 

### 2018-12-03 Chapters/KaneMele.tex
NNN ham
moar

@@
-\begin{section}{Kane Mele Hubbard model}
+\begin{section}{Kane-Mele-Hubbard model}
 
@@
 \hat{H}_{KMH} &= -t_0\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} \nonumber \\
-&+ i\Delta_R \sum_{\langle i j \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}) \hat{c}_{j\sigma'} + U\hat{D}
+&+ i\Delta_R \sum_{\langle i j \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \hat{z}(\bs{\sigma}_{\sigma \sigma'} \times \bs{R}_{ij}) \hat{c}_{j\sigma'} + \text{U}\hat{D}
 \end{align}
 
-Where sum over next-nearest neighbors is denotes by $\langle \langle i j \rangle \rangle$ and $\Delta$ is the intrinsic spin orbit coupling and $\Delta_R$ is the Rashba spin orbit coupling, which is the same as in the previous section if we choose $\bs{\Delta}_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$.
+Where sum over next-nearest neighbors is denoted by $\langle \langle i j \rangle \rangle$ and $\Delta$ is the intrinsic spin orbit coupling and $\Delta_R$ is the Rashba spin orbit coupling, which is the same as in the previous section if we choose $\bs{\Delta}_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$.
 $\nu_{ij}=\pm 1$ depending on whether the electron traversing from i to j makes a right ($+1$) or a left turn ($-1$).
@@
 \begin{equation}
-\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} \tilde{J}_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j 
 \end{equation}
@@
 \begin{equation}
-\tilde{J}_{ij}(t) = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\bs{\Gamma}_{ij}(t) = \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
 \end{equation}
 
-This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
+This is the same pseudodipolar interaction derived in the previous Chapter with no laser interaction.
+In this case it describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
 The same spin model is obtain in \cite{Rachel2010} without the laser perturbation.
-If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\tilde{J}_{ij}(t) > 0$.
+If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij}(t) > 0$.
 Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane.
 The exchange interaction $J_{ij}(t)$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned.
-Therefore, $\tilde{J}_{ij}(t)$ will compete against $J_{ij}(t)$ in the $\hat{e}_z$ direction.
-In the $\hat{e}_x-\hat{e}_y$ plane, $\tilde{J}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$.
-In general the strength of the exchange interaction will be larger and the net effect of $\tilde{J}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
+Therefore, $\Gamma^{zz}_{ij}(t)$ will compete against $J_{ij}(t)$ in the $\hat{e}_z$ direction.
+In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$.
+In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
 
@@
 \begin{align*}
-\tilde{J}_{ij} = \tilde{J}_{ij}^0 + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = \tilde{J}_{ij}^0 + \tilde{J}_{ij}^0 \text{U} \frac{3}{2} \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
+\Gamma^{zz}_{ij} = \Gamma^{0,zz}_{ij} + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = \tilde{J}_{ij}^0 + \tilde{J}_{ij}^0 \text{U} \frac{3}{2} \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
 \end{align*}
 
-Where $\tilde{J}_{ij}^0 = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
-If we define $\Delta J_{ij} = J_{ij} - J_{ij}^0$ and $\Delta \tilde{J}_{ij} = \tilde{J}_{ij} - \tilde{J}_{ij}^0$ we can see that, in this approximation $\frac{\Delta J_{ij}}{\Delta \tilde{J}_{ij}} = \frac{1}{3}\frac{J_{ij}^0}{\tilde{J}_{ij}^0}$ whereas $\frac{\Delta J_{ij}}{\Delta |\bs{D}_{ij}|} = \frac{J_{ij}^0}{|\bs{D}_{ij}^0|}$.
+Where $\Gamma^{0,zz}_{ij}(t) = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
 
@@
 \hat{H}_{\text{eff}}(t) = &\hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t) = \sum_{\langle i,j \rangle} \left( J_{ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j \right) \nonumber \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \tilde{J}_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
+&+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j 
 \end{align}
@@
 \bs{D}_{ij}(t) &= -2t_0\Delta_R (R_{ij}^y, - R_{ij}^x, 0) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\tilde{J}_{ij}(t) &= \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\bs{\Gamma}_{ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
 \end{align*}

### 2018-12-03 Chapters/OtherHams.tex
moar

@@
-Next we will consider a Hamiltonian:
+In the previous sections we have seen that the second order perturbation effective Hamiltonian will contain the following terms:
+
+\begin{itemize}
+	\item Exchange interaction $J_{ij} \bs{S}_i \bs{S}_j$, arising from the kinetic hopping - kinetic hopping terms.
+	\item DMI $\bs{D}_{ij} \bs{S}_i \times \bs{S}_j$, arising from the kinetic hopping - SOI hopping terms.
+	\item Anisotropic or pseudodipolar interaction $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$, arising from the SOI hopping - SOI hopping terms.
+\end{itemize}
+
+And all these coupling factors will be renormalized by the laser field.
+In the cases that we obtained both exchange interaction and DMI we ignored the anisotropic interaction since it is second order in the SOI coupling constant.
+However, if no kinetic hopping term is allowed only the anisotropic interaction will remain (for example, the NNN interaction considered in the Kane-Mele-Hubbard model).
+Additionally, the symmetries of the lattice will constrain the direction the the $\bs{D}_{ij}$ vector of the DMI \cite{Moriya1960}.
+
+In order to summarise, we will consider the following Hamiltonian:
 
 \begin{equation}
-\hat{H} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij}^{(0)} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{ij}^{(1)} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} - 
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_2 + \bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
 	\text{U}\hat{D}
@@
 t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{0,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
-	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
+	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
+	(\delta_{\sigma \sigma'}t_2+\bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
 	0 & \text{ otherwise}
@@
 \begin{align}
-\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{0,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{0,ij}(t) \bs{S}_i \times \bs{S}_j \right\} + \nonumber \\
-&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
+\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j \right\} + \nonumber \\
+&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
 \end{align}
@@
 \begin{align*}
-J_{0,ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{0,ij}(t) &= 2it_0 \bs{\Delta}_{0,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
 J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{1,ij}(t) &= 2it_1 \bs{\Delta}_{1,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\bs{D}_{1,ij}(t) &= 2it_1 \bs{\Delta}_{1,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{2,ij}(t) &= 2it_2 \bs{\Delta}_{2,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{align*}
+
+In the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$, i.e.:
+
+\begin{equation}
+\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\text{U}\hat{D}
+\end{equation}
+
+We recover the original Kane-Mele model with only intrinsic SOI and an additional NNN kinetic hopping term proportional to $t_1$. With this, the effective Hamiltonian will be:
+
+\begin{equation}
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
+\end{equation}
+
+Where we neglected the pseudodipolar interaction in favor of the DMI and where:
+
+\begin{align*}
+J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\end{align*}
+
+Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
+However, in the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.

### 2018-12-04 Chapters/OtherHams.tex
may be crashing

@@
 \begin{equation}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
+\label{OtherHamsSpinModel}
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j \right\}
 \end{equation}
 
-Where we neglected the pseudodipolar interaction in favor of the DMI and where:
+Where:
 
@@
 J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{\Gamma}_{2,ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
 \end{align*}
@@
 However, in the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
+In general SDW will appear in the ground state of \ref{OtherHamsSpinModel} and the SDW wavevector will be determined by a function of the parameters of this model.
+Next we will show numerically that the ratio between the NN and NNN parameters can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
+
+We will use the time average approximation \ref{MFactorApprox0} so that we can write:
+
+\begin{align}
+J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}} \\
+D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}}
+\end{align}
+
+Where $J_{1,ij}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = \frac{4t_2\Delta}{\text{U}}$.
+Now, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$:
+
+\begin{align}
+J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
+D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{\frac{3}{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
+\end{align}
+
+Therefore, $|\alpha_{ij}|$ will be $\sqrt{3}$ times bigger for NNN than for NN, and, in each case the absolute vale is independent of $i,j$.
+Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
+Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6$ we obtain (ref fig).
+The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in (figure)
+
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.4\linewidth]{Chapters/NNvsNNN.jpg}
+  \caption{A subfigure}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.4\linewidth]{Chapters/ratio.jpg}
+  \caption{A subfigure}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{A figure with two subfigures}
+\label{fig:test}
+\end{figure}

### 2018-12-04 Code/Chap3.R

@@ -1,0 +1,43 @@
+#units: hbar=1 (Energy*Time)  t1=1(Energy),
+#electric field is measured in units of t1/ea
+
+library(latex2exp)
+t1 <- 1 #NN hopping integral
+t2 <- 0.1 #NNN hoping integral
+delta <- 0.5 #NNN intrinsic SOI coupling
+
+U <- 10 #Interaction energy
+w <- 6 #Laser frecuency
+bessel_trunc_order <- 10
+lattice_cte <- 1
+field_energies <- seq(from=0, by=0.01, to=20)
+
+#J1 = 2*t1^2/U*J1_factor
+J1_factor <- vector(mode="numeric", length=length(field_energies))
+
+for (n in -bessel_trunc_order:bessel_trunc_order) {
+  J1_factor <- J1_factor + besselJ(field_energies/sqrt(2), nu = n)^2 / (1 + n * w / U)
+}
+
+#D2 = 4*t2*delta/U*D2_factor
+D2_factor <- vector(mode="numeric", length=length(field_energies))
+
+for (n in -bessel_trunc_order:bessel_trunc_order) {
+  D2_factor <- D2_factor + besselJ(sqrt(3)*field_energies/sqrt(2), nu = n)^2 / (1 + n * w / U)
+}
+
+ratioJD0 <- t1^2 / ( 2 * t2 * delta)
+ratioJD <-  ratioJD0*J1_factor/D2_factor
+
+jpeg('rplot.jpg')
+plot(x,y)
+
+
+plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = TeX('$E$'), ylab = '')
+lines(x=field_energies, y = D2_factor, type = 'l', col = "red")
+legend("topright", legend = c(TeX('$J_1/J_1^0$'), TeX('$D_2/D_2^0$')), fill = c("green", "red"))
+
+dev.off()
+jpeg('rplot.jpg')
+plot(x=field_energies, y = ratioJD, ylim = c(-2*ratioJD0,2*ratioJD0), type = 'l', col = "blue", xlab = TeX('$E$'), ylab = TeX('$J/D$'))
+dev.off()

### 2018-12-07 Chapters/OtherHams.tex
changes

@@
 In general SDW will appear in the ground state of \ref{OtherHamsSpinModel} and the SDW wavevector will be determined by a function of the parameters of this model.
+In many cases NNN DMI cannot be neglected in favour of NNN exchange interaction, it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
 Next we will show numerically that the ratio between the NN and NNN parameters can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
@@
 
-Where $J_{1,ij}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = \frac{4t_2\Delta}{\text{U}}$.
-Now, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$:
+Where $\bs{D}_{2,ij} = \hat{e}_z D_{2,ij}$ and where $J_{1,ij}^0 = J_{1}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = -\frac{4t_2\Delta\nu_{ij}}{\text{U}}$.
+Since $\mathcal{J}_n(-x) = (-1)^n\mathcal{J}_n(x)$ the dependance is on $|\alpha_{ij}|$ only.
+Now, using \ref{Def_alpha}, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$, where $a$ is the lattice constant and $\mathcal{E} = \frac{eaE_0}{\omega}$.
+Now, for $J_{1,ij}$, $i$ and $j$ are NN and so we can write $|\vec{R}_{ij}|=a$, whereas for $D_{2,ij}$, $i$ and $j$ are NNN and so $|\vec{R}_{ij}|=\sqrt{3}a$.
+Thus:
 
 \begin{align}
-J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
+J_{1,ij} &= J_{1} = J_{1}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
 D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{\frac{3}{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
@@
 
-Therefore, $|\alpha_{ij}|$ will be $\sqrt{3}$ times bigger for NNN than for NN, and, in each case the absolute vale is independent of $i,j$.
+In each case the absolute vale is independent of $i,j$.
 Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
-Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6$ we obtain (ref fig).
-The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in (figure)
+Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6$ we obtain \ref{Fig1:NNvsNNN}.
+The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in \ref{Fig1:ratio}.
 
@@
   \centering
-  \includegraphics[width=.4\linewidth]{Chapters/NNvsNNN.jpg}
-  \caption{A subfigure}
-  \label{fig:sub1}
+  \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.jpg}
+  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$.}
+  \label{Fig1:NNvsNNN}
 \end{subfigure}%
@@
   \centering
-  \includegraphics[width=.4\linewidth]{Chapters/ratio.jpg}
-  \caption{A subfigure}
-  \label{fig:sub2}
+  \includegraphics[width=1\linewidth]{Chapters/ratio.jpg}
+  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign.}
+  \label{Fig1:ratio}
 \end{subfigure}
-\caption{A figure with two subfigures}
-\label{fig:test}
+%\caption{A figure with two subfigures}
+\label{Fig1}
 \end{figure}

### 2018-12-07 Code/Chap3.R

@@ -2,12 +2,26 @@
 #electric field is measured in units of t1/ea
 
 library(latex2exp)
+
+plot_disconnect <- function(x, y, ylim, ...) {
+  Y_DISC <- 10
+  plot(x = range(x), y = ylim, type = 'n', ...)
+  discontinuities <- which(abs(diff(y)) > Y_DISC)
+  last_point <- 1
+  for (current_point in discontinuities) {
+    if (current_point > last_point + 1) {
+      lines(x = x[last_point:current_point], y = y[last_point:current_point], type = 'l', ...)
+    }
+    last_point <- current_point + 1
+  }
+}
+
 t1 <- 1 #NN hopping integral
 t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-w <- 6 #Laser frecuency
+w <- 16 #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
 field_energies <- seq(from=0, by=0.01, to=20)
@@ -30,14 +44,16 @@ ratioJD0 <- t1^2 / ( 2 * t2 * delta)
 ratioJD <-  ratioJD0*J1_factor/D2_factor
 
 jpeg('rplot.jpg')
-plot(x,y)
 
-
-plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = TeX('$E$'), ylab = '')
-lines(x=field_energies, y = D2_factor, type = 'l', col = "red")
+plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = TeX('$E$'), ylab = '', lwd = 2)
+lines(x=field_energies, y = D2_factor, type = 'l', col = "red", lwd = 2)
 legend("topright", legend = c(TeX('$J_1/J_1^0$'), TeX('$D_2/D_2^0$')), fill = c("green", "red"))
 
 dev.off()
+
 jpeg('rplot.jpg')
-plot(x=field_energies, y = ratioJD, ylim = c(-2*ratioJD0,2*ratioJD0), type = 'l', col = "blue", xlab = TeX('$E$'), ylab = TeX('$J/D$'))
+
+plot_disconnect(x=field_energies, y = ratioJD, ylim = c(-2*ratioJD0,2*ratioJD0), col = "blue", lwd = 2, xlab = TeX('$E$'), ylab = '')
+legend("topright", legend=TeX('$J/D$'), fill = c("blue"))
+
 dev.off()

### 2018-12-07 Chapters/OtherHams.tex
moar

@@
 Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
-However, in the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
-In general SDW will appear in the ground state of \ref{OtherHamsSpinModel} and the SDW wavevector will be determined by a function of the parameters of this model.
-In many cases NNN DMI cannot be neglected in favour of NNN exchange interaction, it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
-Next we will show numerically that the ratio between the NN and NNN parameters can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
+In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
+In the most general Hamiltonian \ref{OtherHamsSpinModel} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
+
+As an example, we will show this for the one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i\bs{S}_j$.
+In this case we can write generally $\bs{S}(r) = S(\cos(kr), \sin(kr), 0)$, where the real number $k$ plays the role of the wavevector, and $\theta = ka-\pi$ is the deviation from the N\'eel state.
+Then the classical energy per site is given by:
+
+\begin{equation}
+\frac{E(\theta)}{2S^2} = -|J_1|\cos(\theta) + |D_2|\sin(2 \theta)
+\end{equation}
+
+and the energy is minimized for $\theta^* = \arcsin(\frac{\frac{J1}{D2} - \sqrt{(\frac{J1}{D2})^2+32}}{8})$, i.e.
+$\theta^* = \theta^*(\frac{J1}{D2})$.
+This approximated Hamiltonian with no NNN exchange interaction is very simple, but it can describe some systems where it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
+Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J1}{D2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
 

### 2018-12-07 Chapters/SDW.r

@@ -1,0 +1,18 @@
+#E = sum J_1S_i S_j + sum D_2 S_i times S_j
+
+library(latex2exp)
+
+J1 <- 1
+D2 <- 0.01
+
+theta <- seq(from = -pi, by = 0.01, to = pi)
+E <- -J1*cos(theta) + D2*sin(2*theta)
+
+solp <- asin((J1/D2 + sqrt((J1/D2)^2+32))/8)
+Ep <- -J1*cos(solp) + D2*sin(2*solp)
+soln <- asin((J1/D2 - sqrt((J1/D2)^2+32))/8)
+En <- -J1*cos(soln) + D2*sin(2*soln)
+
+plot(x = theta, y = E, type = 'l')
+lines(x = solp, y = Ep, lwd = 5, type = 'p', col = 'green')
+lines(x = soln, y = En, lwd = 5, type = 'p', col = 'green')

### 2018-12-09 Chapters/Chap3/HNoSoi.tex
Big refactor

--- 2018-11-22 Chapters/Chapter3.tex
@@
-\chapter{Perturbing the lattice}
-
-In this chapter we will derive an effective spin Hamiltonian for different models in the presence of a high frequency electromagnetic perturbation.
-The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
-This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:
-
-\begin{equation*}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-In this model only the exchange interaction $J$ plays a role.
-The electromagnetic perturbation is then introduced via the Peierls substitution.
-We reproduce the result in section \ref{Section3Hubbard}.
-In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions.
-The simplest model with spin orbit interaction is \ref{Hubbard}:
-
-\begin{equation*}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
-In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}.
-For this case we examine the Kane Mele Hubbard model.
-The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
-This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.
-
-Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
-
-\begin{section}{Time dependent effective Hamiltonian}
-\label{SectionTDHeff}
-\input{Chapters/TDHeff}
-
-\end{section}
-
 \begin{section}{Hubbard model without SOI}
@@
 \begin{equation}
+\label{MFactorApprox0}
 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
@@
 \end{section}
-
-\begin{section}{Hubbard model with SOI}
-\label{Section3HubbardSOI}
-Now, let's investigate the effect of the electric field for the Hubbard model with SOI, i.e. \ref{Hubbard}, in this case the hopping operator gets an extra spin-dependent term:
-
-\begin{equation}
-\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
-\end{equation}
-
-The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI.
-In this case the hopping amplitudes are:
-
-\begin{equation}
-\label{HoppHubbSOI}
-t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
-	0 & \text{ otherwise}
-\end{cases} \quad
-\end{equation}
-
-And as before $\hat{H} = -\hat{T} + \text{U}\hat{D}$.
-In the presence of an electromagnetic field we can apply the Peierls substitution as we did before, and the effective Hamiltonian will be given by \ref{HeffSimplified}.
-inserting the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} we get:
-
-\begin{align}
-\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
-&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
-\end{align}
-
-Now, since the spin orbit interaction is weaker than the kinetic term, we can neglect the term proportional to $\bs{\Delta}_{ij}^2$ and write:
-
-\begin{equation}
-(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \approx \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4})
-\end{equation}
-
-Where we used $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$.
-The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
-The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
-
-Now we can rewrite \ref{HeffHubbSOI1} as:
-
-\begin{align*}
-\hat{H}_{\text{eff}}(t) &\approx - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
-&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
-&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
-&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
-&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
-&= \hat{H}_J'(t)+\hat{H}_D'(t)
-\end{align*}
-
-Where we used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:
-
-\begin{align}
-J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
-\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI}
-\end{align}
-
-Kinetic hopping and the Rashba spin orbit are both NN hopping processes, so they are both renormalized in the same way by the laser field \cite{Stepanov2017}.
-For $\bs{D}_{ij}(t)$ this is:
-
-\begin{equation}
-\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{-i(\frac{\pi}{2}+\theta_{ij})m} \left\{ 
-    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
-\end{equation}
-
-\end{section}
-
-\input{Chapters/KaneMele}
-
-\begin{subappendices}
-\begin{section}{Peierls Substitution}
-\label{AP3A}
-
-In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the latice \ref{LaticeHam} to:
-
-\begin{equation}
-\label{HamEMF}
-  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
-\end{equation}
-
-Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian.
-We define a new set of Wannier functions in terms of those defined in \ref{Wannier2}, and obtain the new Bloch functions.
-
-\begin{align}
-\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
-\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
-\end{align}
-
-Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:
-
-\begin{align*}
-\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
-&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
-&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
-\end{align*}
-
-And so, the matrix elements as in the case without field except for a phase:
-
-\begin{equation}
-\label{PeierlsMtxElem}
-t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
-\end{equation}
-
-When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.
-
-Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
-
-\begin{align*}
-  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
-  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
-\end{align*}
-
-Therefore relation \ref{PeierlsMtxElem} still holds.
-
-\end{section}
-
-\begin{section}{Identities}
-\label{AP3B}
-Let $Z(t)$ be an operator dependent on the parameter $t$. Then:
-
-\begin{align*}
-d_t e^{Z} &= d_t \sum_{n=0}^\infty \frac{1}{n!} Z^n = \sum_{n=0}^\infty \sum_{m=0}^{n-1} \frac{1}{n!} Z^m \frac{\partial Z}{\partial t} Z^{n-m-1} = \\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{1}{(m+p+1)!}Z^m \frac{\partial Z}{\partial t} Z^p = \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{m!p!}{(m+p+1)!} \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} =\\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \int_0^1 dx x^m (1-x)^p \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} = \int_0^1 dx e^{Zx} \frac{\partial Z}{\partial t} e^{Z(1-x)} = \\
-&= \int_0^1 dx \sum_{n=0}^\infty \frac{1}{n!} \left[xZ, \dots, \left[xZ, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
-\end{align*}
-
-Where we used the Beta function $\int_0^1 dx x^m (1-x)^p = \frac{m!p!}{(m+p+1)!}$ and we also used the Baker–Campbell–Hausdorff expansion for $e^{xZ}\frac{\partial Z}{\partial t}e^{-xZ}$ and $\int_0^1 x^n = \frac{1}{n+1}$.
-Therefore we proved:
-
-\begin{equation}
-\label{SneidersID}
-d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \text{ad}_Z ^n \left(\frac{\partial Z}{\partial t}\right) e^Z
-\end{equation}
-
-Where $\text{ad}_A(B) = [A,B]$.
-
-\end{section}
-
-\end{subappendices}

### 2018-12-09 Chapters/Chap3/HWithSoi.tex
Big refactor

\begin{section}{Hubbard model with SOI}
\label{Section3HubbardSOI}
Now, let's investigate the effect of the electric field for the Hubbard model with SOI, i.e. \ref{Hubbard}, in this case the hopping operator gets an extra spin-dependent term:

\begin{equation}
\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
\end{equation}

The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI. 
In this case the hopping amplitudes are:

\begin{equation}
\label{HoppHubbSOI}
t_{ij}^{\sigma \sigma'} = \begin{cases}
	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
	0 & \text{ otherwise}
\end{cases} \quad
\end{equation}

And as before $\hat{H} = -\hat{T} + \text{U}\hat{D}$. In the presence of an electromagnetic field we can apply the Peierls substitution as we did before, and the effective Hamiltonian will be given by \ref{HeffSimplified}.  inserting the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} we get:

\begin{align}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
\end{align}

Using $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$:

\begin{align*}
&(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) = \\ 
&\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3, \sigma_4})
\end{align*}

The term proportional to $t_0^2$ will lead to the modified exchange interaction, as in the previous section. The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction and the term proportional to $\bs{\Delta}_{ij}^2$ will lead to the pseudodipolar interaction.

Now we can rewrite \ref{HeffHubbSOI1} as:

\begin{align*}
\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3, \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) + \\
&+\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \\
&(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3, \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} \left\{ J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}(t)\bs{S}_j \right\}
\end{align*}

Where we used relations \ref{SpinRel1}, \ref{SpinRel2} and \ref{SpinRel3}. We have:

\begin{align}
J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI} \\
\Gamma_{ij}^{\alpha \beta}(t) &= (\delta_{\alpha \beta} \bs{\Delta}_{ij}^2 - 2\Delta_{ij}^\alpha\Delta_{ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align}

We can see that since we only considered NN hopping processes, all the terms in the spin Hamiltonian are renormalized in the same way by the laser field (as in \cite{Stepanov2017}). In order to obtain different dependencies with the field we should consider NNN hopping processes.

\end{section}

### 2018-12-09 Chapters/Chap3/ModelsNNN.tex
Big refactor

\begin{section}{Including next nearest neighbor hopping}

In the previous sections we have seen that the second order perturbation effective Hamiltonian will contain the following terms:

\begin{itemize}
	\item Exchange interaction $J_{ij} \bs{S}_i \bs{S}_j$, arising from the kinetic hopping - kinetic hopping terms.
	\item DMI $\bs{D}_{ij} \bs{S}_i \times \bs{S}_j$, arising from the kinetic hopping - SOI hopping terms.
	\item Anisotropic or pseudodipolar interaction $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$, arising from the SOI hopping - SOI hopping terms.
\end{itemize}

And all these coupling factors will be renormalized by the laser field. This renormalization depends only on the field and the sites $i$, $j$, it does not depend on the nature of the interaction. With this in mind we will introduce a model with additional NNN hopping terms:

\begin{equation}
\label{BigHam}
\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} - 
	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_2 + \bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
	\text{U}\hat{D}
\end{equation}

Where sum over next-nearest neighbors is denoted by $\langle \langle i j \rangle \rangle$. This Hamiltonian is the same we studied in section \ref{Section3HubbardSOI} plus a NNN hopping and SOI term. The hopping amplitudes thus are:

\begin{equation}
t_{ij}^{\sigma \sigma'} = \begin{cases}
	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
	(\delta_{\sigma \sigma'}t_2+\bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
	0 & \text{ otherwise}
\end{cases} \quad
\end{equation}

The effective Hamiltonian will be the same as in section \ref{Section3HubbardSOI}, with the corresponding NNN terms. This is because in second order perturbation NN hopping terms do not mix with NNN hopping terms. Thus, the effective spin Hamiltonian will be:

\begin{align}
\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}(t)\bs{S}_j\right\} + \nonumber \\
&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}(t)\bs{S}_j\right\}
\end{align}

Where:

\begin{align}
J_{n,ij}(t) &= t_n^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JGeneral} \\
\bs{D}_{n,ij}(t) &= 2it_n \bs{\Delta}_{n,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DGeneral} \\
\Gamma_{n,ij}^{\alpha \beta}(t) &= (\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{GammaGeneral}
\end{align}

NNN interaction coupling factors will be normalized according to $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$, where $i$, $j$ are NNN sites, whereas NN interaction coupling factors will be normalized according to $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ where $i$, $j$ are NN sites. Therefore the dependence on the field will differ. For example, if we take the time independent approximation \ref{MFactorApprox}, and use $\lambda = \pm 1$ for circular polarized light, and $\alpha_{ij} = \pm\frac{\mathcal{E}|\bs{R}_{ij}|}{a\sqrt{2}}$, where $\mathcal{E} = \frac{eaE_0}{\omega}$. Then the exchange interaction will be:

\begin{align*}
J_{1,ij} &= J_1^0 + t_1^2 \frac{\mathcal{E}^2}{2} \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = J_1^0 + J_1^0 \frac{\mathcal{E}^2}{2} \left( \frac{1}{1+\frac{\omega}{\text{U}}} + \frac{1}{1-\frac{\omega}{\text{U}}} \right) \\
J_{2,ij} &= J_2^0 + t_2^2 \frac{3\mathcal{E}^2}{2} \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) = J_2^0 + J_2^0 \frac{3\mathcal{E}^2}{2} \left( \frac{1}{1+\frac{\omega}{\text{U}}} + \frac{1}{1-\frac{\omega}{\text{U}}} \right) \\
\end{align*}

Where $J_n^0 = \frac{t_n^2}{\text{U}}$ and where we used that $|\bs{R}_{ij}| = a$ for NN and $|\bs{R}_{ij}| = \sqrt{3}a$ for NNN in a honeycomb lattice. The other coupling factors in \ref{DGeneral} and \ref{GammaGeneral} can be approximated in the same way.

In subsection (add reference!!!!!!!!!!!) we will investigate this numerically. The reason for this is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ (assuming flat field approximation). This phase will be larger for NNN hopping than for NN hopping and this will therefore translate in the corresponding spin interactions.

Next we will show several well-known models which are described by \ref{BigHam}.

\begin{subsection}{Kane-Mele-Hubbard model}

The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene. In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:

\begin{align}
\hat{H}_{\text{KMH}} &= -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}
\end{align}

Where $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). This Hamiltonian is described by \ref{BigHam} if we set $\bs{\Delta}_{1,ij} = 0$, $t_2 = 0$ and $\bs{\Delta}_{2,ij} = -i\Delta \nu_{ij} \hat{e}_z$. Then, the effective spin model will be:

\begin{equation}
\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j 
\end{equation}

With and:

\begin{align*}
J_{ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{ij}(t) &= \Delta^2 \text{diag}(-1,-1,1)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}

according to \ref{JGeneral} and \ref{GammaGeneral}. Notice that:

\begin{equation*}
\bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left(S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y\right)
\end{equation*}

This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors. The same spin model is obtain in \cite{Rachel2010} without the laser perturbation. If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij}(t) > 0$. Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane. The exchange interaction $J_{ij}(t)$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned. Therefore, $\Gamma^{zz}_{ij}(t)$ will compete against $J_{ij}(t)$ in the $\hat{e}_z$ direction. In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$. In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.

\end{subsection}

\end{section}

### 2018-12-09 Chapters/Chap3/OtherHams.tex
Big refactor

--- 2018-12-07 Chapters/OtherHams.tex
@@
-In the previous sections we have seen that the second order perturbation effective Hamiltonian will contain the following terms:
-
-\begin{itemize}
-	\item Exchange interaction $J_{ij} \bs{S}_i \bs{S}_j$, arising from the kinetic hopping - kinetic hopping terms.
-	\item DMI $\bs{D}_{ij} \bs{S}_i \times \bs{S}_j$, arising from the kinetic hopping - SOI hopping terms.
-	\item Anisotropic or pseudodipolar interaction $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$, arising from the SOI hopping - SOI hopping terms.
-\end{itemize}
-
-And all these coupling factors will be renormalized by the laser field.
-In the cases that we obtained both exchange interaction and DMI we ignored the anisotropic interaction since it is second order in the SOI coupling constant.
-However, if no kinetic hopping term is allowed only the anisotropic interaction will remain (for example, the NNN interaction considered in the Kane-Mele-Hubbard model).
-Additionally, the symmetries of the lattice will constrain the direction the the $\bs{D}_{ij}$ vector of the DMI \cite{Moriya1960}.
-
-In order to summarise, we will consider the following Hamiltonian:
-
-\begin{equation}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} - 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_2 + \bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
-	\text{U}\hat{D}
-\end{equation}
-
-Which is the same we studied in section \ref{Section3HubbardSOI} plus a NNN hopping and SOI term.
-As before, $\bs{\Delta}_{ij}^{(n)}$ describes Rashba SOI when $\bs{\Delta}_{ij}^{(n)} = i\Delta_R^{(n)}(R_{ij}^y, -R_{ij}^x, 0)$.
-The hopping amplitudes thus are:
-
-\begin{equation}
-\label{HoppHubbSOI}
-t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
-	(\delta_{\sigma \sigma'}t_2+\bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
-	0 & \text{ otherwise}
-\end{cases} \quad
-\end{equation}
-
-The effective Hamiltonian will be the same as in section \ref{Section3HubbardSOI}, with the corresponding NNN terms.
-This is because in second order perturbation NN hopping terms do not mix with NNN hopping terms.
-Thus, the effective spin Hamiltonian will be:
-
-\begin{align}
-\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j \right\} + \nonumber \\
-&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
-\end{align}
-
-Where:
-
-\begin{align*}
-J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{1,ij}(t) &= 2it_1 \bs{\Delta}_{1,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{2,ij}(t) &= 2it_2 \bs{\Delta}_{2,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
-\end{align*}
+\begin{section}{Other general Hamiltonians}
+\label{SectionOtherHams}
 
@@
 \end{figure}
+
+\end{section}

### 2018-12-09 Chapters/Chapter2.tex
Big refactor

@@
 
-Therefore $\bs{\Delta}_{ii} = 0$. Also we can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
+Therefore $\bs{\Delta}_{ii} = 0$. Notice also that $\bs{\Delta}_{ij}$ is purely imaginary.
+We can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
 
@@
 These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
-These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{eff} = -\frac{\hat{H_t^2}}{\text{U}}$.
+These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
 Now,
@@
 
-Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$. Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ gives:
+Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$, notice that being $\bs{\Delta}_{ij}$ purely imaginary, $\bs{D}_{ij}^0$ is a real vector. 
+Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ leads to:
 
@@
 With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
-This term is known as pseudodipolar interaction \citep{Moriya1960} and it will be neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
-
 The total effective Hamiltonian is:
@@
 \begin{equation}
-\hat{H}_{\text{eff}} \approx \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j \right) \label{HeffNOEMF}
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right) \label{HeffNOEMF}
 \end{equation}
@@
 J_{ij}^0 &= \frac{2t^2}{\text{U}} \label{Jij0} \\
-\bs{D}_{ij}^0 &= \frac{4it}{\text{U}}\bs{\Delta}_{ij} \label{Dij0}
+\bs{D}_{ij}^0 &= \frac{4it}{\text{U}}\bs{\Delta}_{ij} \label{Dij0} \\ 
+\bs{\Gamma_{ij}}^{\alpha \beta} &= \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta) \label{Gij0}
 \end{align}
 
-Compare with \cite{Stepanov2017}.
+The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
+Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
+$\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
+interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}.
+In the next chapter we will examine this further.
+Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
 

### 2018-12-09 Chapters/Chapter3.tex
may be crashing
Big refactor

@@
 
-\begin{section}{Time dependent effective Hamiltonian}
-\label{SectionTDHeff}
-\input{Chapters/TDHeff}
+\input{Chapters/Chap3/TDHeff}
 
-\end{section}
+\input{Chapters/Chap3/HNoSoi}
 
-\begin{section}{Hubbard model without SOI}
-\label{Section3Hubbard}
-We start by considering the simplest hopping operator, as in the Hubbard model:
+\input{Chapters/Chap3/HWithSoi}
 
-\begin{equation}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation}
+\input{Chapters/Chap3/ModelsNNN}
 
-Which is the Hamiltonian \ref{Hubbard} without DMI interaction.
-We see that the hopping amplitudes introduced in the previous section take the form $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'} t_0$ for $i,j$ being nearest neighbors, and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
-With this we can directly apply \ref{HeffSimplified} to obtain:
-
-\begin{equation}
-\hat{H}_{\text{eff}}(t) = -\frac{t_0^2}{2} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
-\end{equation}
-
-Now, introducing the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} and summing over the spin states as in \ref{SpinRel1}:
-
-\begin{align*}
-\sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} = \sum_{\sigma, \sigma'} \left( \frac{\delta_{\sigma \sigma'}}{2} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma} \right) \left( \frac{\delta_{\sigma \sigma'}}{2} - \bs{S}_j\bs{\sigma}_{\sigma \sigma'} \right) = -2\bs{S}_i \bs{S}_j
-\end{align*}
-
-Where we neglected the constant term. The effective spin Hamiltonian is thus:
-
-\begin{equation}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j
-\end{equation}
-
-With
-
-\begin{align}
-J_{ij}(t) &= t_0^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
-&=\sum_{mn} t_0^2 e^{-i(\frac{\pi}{2}+\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{\text{U}+n\omega} \right) e^{im\omega t} \label{Jij1}
-\end{align}
-
-After time average this reduces to the $m=0$ term:
-
-\begin{equation}
-\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
-\end{equation}
-
-For $\omega>>U$ we can truncate this to the three smallest values of $n$, i.e.
-$n=0, \pm 1$.
-We can also use that $\alpha_{ij} << 1$ because $\alpha_{ij}$ is proportional to $\vec{A}$ which is proportional to $\omega^{-1}$.
-Therefore we can use $\mathcal{J}_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:
-
-\begin{equation}
-\label{MFactorApprox}
-\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx 2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right)
-\end{equation}
-
-And the exchange interaction coupling becomes:
-
-\begin{equation}
-\label{Jij2}
-J_{ij} \approx J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
-\end{equation}
-
-The lattice structure is contained in $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$.
-For a square lattices aligned with the coordinate system so that $\vec{a}_1=\hat{e}_x$ and $\vec{a}_2=\hat{e}_y$, we will have $\bs{R}_{ij} = \pm a\hat{e}_x,\pm a\hat{e}_y$, where $a$ is the lattice constant.
-Using $\vec{A}=\frac{iE_0}{\omega\sqrt{1+\lambda^2}}(\hat{e}_x+i\lambda\hat{e}_y)$ we have:
-
-\begin{equation}
-\alpha_{ij} = \begin{cases}
-             \pm \frac{eaE_0}{\omega \sqrt{1+\lambda^2}} = \pm \frac{\mathcal{E}}{\sqrt{1+\lambda^2}},  & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
-             \pm \lambda\frac{eaE_0}{\omega \sqrt{1+\lambda^2}} = \pm \frac{\lambda \mathcal{E}}{\sqrt{1+\lambda^2}},  & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
-       \end{cases} \quad
-\end{equation}
-
-Where $\mathcal{E} = \frac{eaE_0}{\omega}$.
-
-For plane polarized light ($\lambda = 0$) the exchange interaction only changes in the direction of the polarization, that is:
-
-\begin{equation}
-J_{ij}^{PP} = \begin{cases}
-		J_{ij}^0 + 2t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right) & \text{for } \bs{R}_{ij} = \pm \hat{e}_x \\
-J_{ij}^0 & \text{for } \bs{R}_{ij} = \pm \hat{e}_y
-\end{cases} \quad 
-\end{equation}
-
-For circular polarized light ($\lambda=\pm1$) in this approximation the exchange interaction changes in the same way in all the directions:
-
-\begin{equation}
-\label{JijCPSQUARE}
-J_{ij}^{CP} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
-\end{equation}
-
-\begin{subsection}{Honeycomb lattice}
-
-Now consider a honeycomb lattice structure, so that the $\alpha_{ij}$ values are given by $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ where $\bs{R}_{ij}$ are the displacement vectors in a honeycomb lattice.
-There are six such vectors:
-
-\begin{align}
-\bs{R}_1^\pm &= \pm a\hat{e}_x \\
-\bs{R}_2^\pm &= \pm a\frac{1}{2}(\hat{e}_x + \sqrt{3}\hat{e}_y) \\
-\bs{R}_3^\pm &= \pm a\frac{1}{2}(\hat{e}_x - \sqrt{3}\hat{e}_y)
-\end{align}
-
-These six possible directions will lead to $\alpha_a^\pm = \pm |e\bs{R}_a\vec{A}|$ where $\vec{A}=\frac{iE_0}{\omega\sqrt{1+\lambda^2}}(\hat{e}_x+i\lambda\hat{e}_y)$:
-
-\begin{align}
-\alpha_1^\pm &= \pm \frac{eaE_0}{\omega\sqrt{1+\lambda^2}} \\
-\alpha_2^\pm &= \alpha_3^\pm = \pm \frac{eaE_0}{2\omega} \sqrt{\frac{1+3\lambda^2}{1+\lambda^2}} = \pm\frac{eaE_0}{2\omega}\sqrt{1+\frac{2\lambda^2}{1+\lambda^2}}
-\end{align}
-
-From here we can see that if we take the same approximation as in \ref{Jij2} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.
-
-\end{subsection}
-
-\end{section}
-
-\begin{section}{Hubbard model with SOI}
-\label{Section3HubbardSOI}
-Now, let's investigate the effect of the electric field for the Hubbard model with SOI, i.e. \ref{Hubbard}, in this case the hopping operator gets an extra spin-dependent term:
-
-\begin{equation}
-\hat{T} = \sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_0 + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
-\end{equation}
-
-The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI.
-In this case the hopping amplitudes are:
-
-\begin{equation}
-\label{HoppHubbSOI}
-t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
-	0 & \text{ otherwise}
-\end{cases} \quad
-\end{equation}
-
-And as before $\hat{H} = -\hat{T} + \text{U}\hat{D}$.
-In the presence of an electromagnetic field we can apply the Peierls substitution as we did before, and the effective Hamiltonian will be given by \ref{HeffSimplified}.
-inserting the spin operators \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} we get:
-
-\begin{align}
-\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
-&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
-\end{align}
-
-Now, since the spin orbit interaction is weaker than the kinetic term, we can neglect the term proportional to $\bs{\Delta}_{ij}^2$ and write:
-
-\begin{equation}
-(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \approx \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4})
-\end{equation}
-
-Where we used $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$.
-The term proportional to $t_0^2$ will lead to the modified exchange interaction, and it is exactly the same as in the previous section.
-The term proportional to $t_0\bs{\Delta}_{ij}$ will lead to the modified DMI interaction.
-
-Now we can rewrite \ref{HeffHubbSOI1} as:
-
-\begin{align*}
-\hat{H}_{\text{eff}}(t) &\approx - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
-&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
-&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
-&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
-&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
-&= \hat{H}_J'(t)+\hat{H}_D'(t)
-\end{align*}
-
-Where we used relations \ref{SpinRel1} and \ref{SpinRel2}. We have:
-
-\begin{align}
-J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
-\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI}
-\end{align}
-
-Kinetic hopping and the Rashba spin orbit are both NN hopping processes, so they are both renormalized in the same way by the laser field \cite{Stepanov2017}.
-For $\bs{D}_{ij}(t)$ this is:
-
-\begin{equation}
-\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{-i(\frac{\pi}{2}+\theta_{ij})m} \left\{ 
-    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
-\end{equation}
-
-\end{section}
-
-\input{Chapters/KaneMele}
-
-\begin{section}{Other general Hamiltonians}
-\label{SectionOtherHams}
-\input{Chapters/OtherHams}
-
-\end{section}
+\input{Chapters/Chap3/OtherHams}
 

### 2018-12-11 Chapters/Chap3/ModelsNNN.tex
moar

@@
 
-In subsection (add reference!!!!!!!!!!!) we will investigate this numerically.
+In section \ref{Numerics} we will investigate this numerically.
 The reason for this is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ (assuming flat field approximation).
@@
 \begin{align}
+\label{KMH}
 \hat{H}_{\text{KMH}} &= -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}
@@
 \begin{equation}
+\label{KMHeff}
 \hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j 
@@
 This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
-The same spin model is obtain in \cite{Rachel2010} without the laser perturbation.
+The same spin model is obtained in \cite{Rachel2010} without the laser perturbation.
 If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij}(t) > 0$.
@@
 
+\begin{subsection}{Modified Kane-Mele-Hubbard model}
+
+As we saw in the previous section the effective Hamiltonian \ref{KMHeff} does not contain NNN DMI terms.
+The reason for this is because in the original Hamiltonian $t_2 = 0$.
+Next we will study the same Hamiltonian adding a finite NNN hopping terms $t_2$.
+In general this is more accurate than imposing $t_2 = 0$, and it can be understood as a second order NN hopping process (the direct NNN hopping integral would usually be much smaller).
+Our next Hamiltonian is thus:
+
+\begin{equation}
+\label{MKMH}
+\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\text{U}\hat{D}
+\end{equation}
+
+This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$ in \ref{BigHam}. With this, the effective Hamiltonian will be:
+
+\begin{equation}
+\label{MKMHeff}
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j \right\}
+\end{equation}
+
+Where:
+
+\begin{align*}
+J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{\Gamma}_{2,ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
+\end{align*}
+
+Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
+In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
+In Hamiltonian \ref{MKMHeff} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
+In the next section we will do a numerical of study on how modifying the ratio between NN and NNN spin interaction factors can change the spin state of the system.
+
+\end{subsection}
+
 \end{section}

### 2018-12-11 Chapters/Chap3/Numerics.tex
moar

--- 2018-12-09 Chapters/Chap3/OtherHams.tex
@@
-\begin{section}{Other general Hamiltonians}
-\label{SectionOtherHams}
+\begin{section}{Numerics}
+\label{Numerics}
 
-In the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$, i.e.:
-
-\begin{equation}
-\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\text{U}\hat{D}
-\end{equation}
-
-We recover the original Kane-Mele model with only intrinsic SOI and an additional NNN kinetic hopping term proportional to $t_1$. With this, the effective Hamiltonian will be:
-
-\begin{equation}
-\label{OtherHamsSpinModel}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j \right\}
-\end{equation}
-
-Where:
-
-\begin{align*}
-J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{\Gamma}_{2,ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
-\end{align*}
-
-Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
-In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
-In the most general Hamiltonian \ref{OtherHamsSpinModel} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
-
-As an example, we will show this for the one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i\bs{S}_j$.
-In this case we can write generally $\bs{S}(r) = S(\cos(kr), \sin(kr), 0)$, where the real number $k$ plays the role of the wavevector, and $\theta = ka-\pi$ is the deviation from the N\'eel state.
+We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i\bs{S}_j$.
+This approximated Hamiltonian with no NNN exchange interaction is very simple, but it can describe some systems where it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
+In this case we can write $\bs{S}(r) = S(\cos(kr), \sin(kr), 0)$, where the real number $k$ plays the role of the wavevector, and $\theta = ka-\pi$ is the deviation from the N\'eel state.
 Then the classical energy per site is given by:
@@
 $\theta^* = \theta^*(\frac{J1}{D2})$.
-This approximated Hamiltonian with no NNN exchange interaction is very simple, but it can describe some systems where it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
 Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J1}{D2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
@@
 The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in \ref{Fig1:ratio}.
+Finally, in \ref{Fig2} we plot the SDW NN angle $\theta$.
 
@@
 
+\begin{figure}
+\centering
+  \includegraphics[width=0.5\linewidth]{Chapters/theta.jpg}
+  \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$. The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector.}
+\label{Fig2}
+\end{figure}
+
 \end{section}

### 2018-12-11 Chapters/SDW.r

@@ -2,8 +2,12 @@
 
 library(latex2exp)
 
+x <- seq(from = -10, to = 10, by = 0.5)
+
+for (i in x) {
+print(i)
 J1 <- 1
-D2 <- 0.01
+D2 <- i
 
 theta <- seq(from = -pi, by = 0.01, to = pi)
 E <- -J1*cos(theta) + D2*sin(2*theta)
@@ -14,5 +18,7 @@ soln <- asin((J1/D2 - sqrt((J1/D2)^2+32))/8)
 En <- -J1*cos(soln) + D2*sin(2*soln)
 
 plot(x = theta, y = E, type = 'l')
-lines(x = solp, y = Ep, lwd = 5, type = 'p', col = 'green')
+lines(x = solp, y = Ep, lwd = 5, type = 'p', col = 'red')
 lines(x = soln, y = En, lwd = 5, type = 'p', col = 'green')
+Sys.sleep(0.05)
+}

### 2018-12-11 Code/Chap3.R

@@ -10,9 +10,14 @@ plot_disconnect <- function(x, y, ylim, ...) {
   last_point <- 1
   for (current_point in discontinuities) {
     if (current_point > last_point + 1) {
+      cat('plotting from ', x[last_point], ' to ', x[current_point], ' with avg: ', range(y[last_point:current_point]) ,'\n')
       lines(x = x[last_point:current_point], y = y[last_point:current_point], type = 'l', ...)
     }
     last_point <- current_point + 1
+  }
+  if (last_point < length(x)) {
+    cat('plotting from ', x[last_point], ' to ', x[length(x)],'\n')
+    lines(x = x[last_point:length(x)], y = y[last_point:length(x)], type = 'l', ...)
   }
 }
 
@@ -24,7 +29,7 @@ U <- 10 #Interaction energy
 w <- 16 #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
-field_energies <- seq(from=0, by=0.01, to=20)
+field_energies <- seq(from=0, by=0.001, to=5)
 
 #J1 = 2*t1^2/U*J1_factor
 J1_factor <- vector(mode="numeric", length=length(field_energies))
@@ -43,7 +48,7 @@ for (n in -bessel_trunc_order:bessel_trunc_order) {
 ratioJD0 <- t1^2 / ( 2 * t2 * delta)
 ratioJD <-  ratioJD0*J1_factor/D2_factor
 
-jpeg('rplot.jpg')
+jpeg('rplot1.jpg')
 
 plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = TeX('$E$'), ylab = '', lwd = 2)
 lines(x=field_energies, y = D2_factor, type = 'l', col = "red", lwd = 2)
@@ -51,9 +56,21 @@ legend("topright", legend = c(TeX('$J_1/J_1^0$'), TeX('$D_2/D_2^0$')), fill = c(
 
 dev.off()
 
-jpeg('rplot.jpg')
+jpeg('rplot2.jpg')
 
-plot_disconnect(x=field_energies, y = ratioJD, ylim = c(-2*ratioJD0,2*ratioJD0), col = "blue", lwd = 2, xlab = TeX('$E$'), ylab = '')
[…]

### 2018-12-11 Chapters/Chap3/Numerics.tex
Nice plots in latex

@@
 
-We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i\bs{S}_j$.
+We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i \times \bs{S}_j$.
 This approximated Hamiltonian with no NNN exchange interaction is very simple, but it can describe some systems where it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
@@
 Now, using \ref{Def_alpha}, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$, where $a$ is the lattice constant and $\mathcal{E} = \frac{eaE_0}{\omega}$.
-Now, for $J_{1,ij}$, $i$ and $j$ are NN and so we can write $|\vec{R}_{ij}|=a$, whereas for $D_{2,ij}$, $i$ and $j$ are NNN and so $|\vec{R}_{ij}|=\sqrt{3}a$.
+Now, for $J_{1,ij}$, $i$ and $j$ are NN and so we can write $|\vec{R}_{ij}|=a$, whereas for $D_{2,ij}$, $i$ and $j$ are NNN and so $|\vec{R}_{ij}|=2a$.
 Thus:
@@
 J_{1,ij} &= J_{1} = J_{1}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
-D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{\frac{3}{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
+D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{2}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
 \end{align}
@@
   \centering
-  \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.jpg}
+  \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.pdf}
   \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$.}
@@
   \centering
-  \includegraphics[width=1\linewidth]{Chapters/ratio.jpg}
+  \includegraphics[width=1\linewidth]{Chapters/ratio.pdf}
   \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign.}
@@
 \centering
-  \includegraphics[width=0.5\linewidth]{Chapters/theta.jpg}
+  \includegraphics[width=0.5\linewidth]{Chapters/theta.pdf}
   \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$. The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector.}

### 2018-12-11 Code/Chap3.R

@@ -1,7 +1,12 @@
 #units: hbar=1 (Energy*Time)  t1=1(Energy),
 #electric field is measured in units of t1/ea
 
+setwd("~/Desktop/MT/Code")
 library(latex2exp)
+library(tikzDevice)
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+                               "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+                               "\\usepackage{amssymb}"))
 
 plot_disconnect <- function(x, y, ylim, ...) {
   Y_DISC <- 10
@@ -26,7 +31,7 @@ t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-w <- 16 #Laser frecuency
+w <- 6 #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
 field_energies <- seq(from=0, by=0.001, to=5)
@@ -42,35 +47,61 @@ for (n in -bessel_trunc_order:bessel_trunc_order) {
 D2_factor <- vector(mode="numeric", length=length(field_energies))
 
 for (n in -bessel_trunc_order:bessel_trunc_order) {
-  D2_factor <- D2_factor + besselJ(sqrt(3)*field_energies/sqrt(2), nu = n)^2 / (1 + n * w / U)
+  D2_factor <- D2_factor + besselJ(sqrt(2)*field_energies, nu = n)^2 / (1 + n * w / U)
 }
 
 ratioJD0 <- t1^2 / ( 2 * t2 * delta)
 ratioJD <-  ratioJD0*J1_factor/D2_factor
 
-jpeg('rplot1.jpg')
+current_file <- "NNvsNNN"
+tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,
+     packages = c("\\usepackage{tikz}",
+                  "\\usepackage[active,tightpage,psfixbb]{preview}",
+                  "\\PreviewEnvironment{pgfpicture}",
+                  "\\setlength\\PreviewBorder{0pt}",
+                  "\\usepackage{amssymb}"))
 
-plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = TeX('$E$'), ylab = '', lwd = 2)
+plot(x=field_energies, y=J1_factor, type='l', col = "green", xlab = "$\\mathcal{E}$", ylab = '', lwd = 2)
[…]

### 2018-12-11 Code/Chap3.R
commit before change

@@ -31,7 +31,7 @@ t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-w <- 6 #Laser frecuency
+w <- 16 #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
 field_energies <- seq(from=0, by=0.001, to=5)

### 2018-12-11 Chapters/Chap3/Numerics.tex
commit before change
change succesful

@@
-\begin{section}{Numerics}
+\begin{section}{Numeric results}
 \label{Numerics}
+
+\begin{subsection}{One dimensional system}
 
@@
 Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
-Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6$ we obtain \ref{Fig1:NNvsNNN}.
+Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$ we obtain \ref{Fig1:NNvsNNN}.
 The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in \ref{Fig1:ratio}.
@@
 \centering
-\begin{subfigure}{.5\textwidth}
-  \centering
+\begin{subfigure}{.45\textwidth}
+  %\centering
   \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.pdf}
-  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$.}
+  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$.
+Similar results are obtained in \cite{Mentink2015} for $J_{1}$.
+Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
   \label{Fig1:NNvsNNN}
 \end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
+\hspace*{\fill}
+\begin{subfigure}{.45\textwidth}
+  %\centering
   \includegraphics[width=1\linewidth]{Chapters/ratio.pdf}
-  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign.}
+  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
   \label{Fig1:ratio}
 \end{subfigure}
-%\caption{A figure with two subfigures}
 \label{Fig1}
@@
   \includegraphics[width=0.5\linewidth]{Chapters/theta.pdf}
-  \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$. The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector.}
+  \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$.
+The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector.
+Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
 \label{Fig2}
@@
 
+\end{subsection}
+
+\begin{subsection}{Two dimensional systems}
+
+In a honeycomb lattice described by \ref{MKMHeff} the usual approach is to write:
+
+\end{subsection}
+
 \end{section}

### 2018-12-11 Code/Chap3.R

@@ -8,9 +8,8 @@ options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
                                "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
                                "\\usepackage{amssymb}"))
 
-plot_disconnect <- function(x, y, ylim, ...) {
+plot_disconnect <- function(x, y, ...) {
   Y_DISC <- 10
-  plot(x = range(x), y = ylim, type = 'n', ...)
   discontinuities <- which(abs(diff(y)) > Y_DISC)
   last_point <- 1
   for (current_point in discontinuities) {
@@ -31,27 +30,27 @@ t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-w <- 16 #Laser frecuency
+frequencies <- list(6,16) #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
 field_energies <- seq(from=0, by=0.001, to=5)
 
 #J1 = 2*t1^2/U*J1_factor
-J1_factor <- vector(mode="numeric", length=length(field_energies))
-
-for (n in -bessel_trunc_order:bessel_trunc_order) {
-  J1_factor <- J1_factor + besselJ(field_energies/sqrt(2), nu = n)^2 / (1 + n * w / U)
-}
+J1_factor <- lapply(frequencies, function(x) vector(mode="numeric", length=length(field_energies)))
 
 #D2 = 4*t2*delta/U*D2_factor
-D2_factor <- vector(mode="numeric", length=length(field_energies))
-
-for (n in -bessel_trunc_order:bessel_trunc_order) {
-  D2_factor <- D2_factor + besselJ(sqrt(2)*field_energies, nu = n)^2 / (1 + n * w / U)
-}
+D2_factor <- lapply(frequencies, function(x) vector(mode="numeric", length=length(field_energies)))
 
 ratioJD0 <- t1^2 / ( 2 * t2 * delta)
-ratioJD <-  ratioJD0*J1_factor/D2_factor
+ratioJD <-  lapply(frequencies, function(x) vector(mode="numeric", length=length(field_energies)))
+
+for (i in 1:length(frequencies)) {
+  for (n in -bessel_trunc_order:bessel_trunc_order) {
[…]

### 2018-12-11 Chapters/Chap3/Numerics.tex
commit

@@
 
+\begin{align}
+\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{R}), \sin(\bs{Q}\bs{r}), 0 \right) \\
+\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{R} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
+\end{align}
+
+The $1, 2$ subindex stands for the sublattice.
+The $\hat{e}_z$ component vanishes in order to minimize the contribution of the pseudodipolar interaction.
+Then, the classical energy per spin is given by:
+
+\begin{align}
+\frac{E}{NS^2} &= -\frac{J_1}{2}\left( \cos(\theta) + \cos(\theta - Q_a - Q_b) + \cos(\theta - Q_b) \right) + \nonumber \\
+&+ (J_2-\Gamma) \left( \cos(Q_a) + \cos(Q_b) + \cos(Q_a+Q_b) \right)+ \nonumber \\
+&+D_2\left( \sin(Q_a) + \sin(Q_b) + \sin(Q_a+Q_b) \right)
+\end{align}
+
+The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space.
+
 \end{subsection}

### 2018-12-12 Chapters/Chap3/Numerics.tex
added more

@@
 
-We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i \times \bs{S}_j$.
-This approximated Hamiltonian with no NNN exchange interaction is very simple, but it can describe some systems where it has even been observed $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}.
+We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j - \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i \times \bs{S}_j$.
+This approximated Hamiltonian with no NNN exchange interaction is very simple, but in some systems where it has even been observed that $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018} it can be a good approximation.
+We write the absolute values in $|J_1|$ and $|D_2|$ to limit the analysis to the range in which the field does not change the sign of these factors.
 In this case we can write $\bs{S}(r) = S(\cos(kr), \sin(kr), 0)$, where the real number $k$ plays the role of the wavevector, and $\theta = ka-\pi$ is the deviation from the N\'eel state.
+This form assumes spiral order, with N\'eel state being the special case $\theta = 0$ (or $k = \pi$).
+From now we will use $\theta$ instead of $k$.
 Then the classical energy per site is given by:
@@
 \begin{equation}
-\frac{E(\theta)}{2S^2} = -|J_1|\cos(\theta) + |D_2|\sin(2 \theta)
+\frac{E(\theta)}{2S^2} = -|J_1|\cos(\theta) - |D_2|\sin(2 \theta)
 \end{equation}
 
-and the energy is minimized for $\theta^* = \arcsin(\frac{\frac{J1}{D2} - \sqrt{(\frac{J1}{D2})^2+32}}{8})$, i.e.
-$\theta^* = \theta^*(\frac{J1}{D2})$.
-Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J1}{D2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
+and the energy is minimized for $\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})$, i.e.
+$\theta^* = \theta^*(\frac{J_1}{D_2})$.
+This is the correct minimization for $J_1, D_2 > 0$.
+Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J_1}{D_2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.
 
@@
 Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
-Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$ we obtain \ref{Fig1:NNvsNNN}.
-The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in \ref{Fig1:ratio}.
-Finally, in \ref{Fig2} we plot the SDW NN angle $\theta$.
+Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}.
+The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}.
+The field can change the sign of $J_1$ and $D_2$ for strong amplitudes.
+Finally, in Figure \ref{Fig3.2} we plot the SDW NN angle $\theta$ limited to the case $J_1 > 0$ and $D_2 > 0$.
 
@@
 Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
-  \label{Fig1:NNvsNNN}
+  \label{Fig3.1:NNvsNNN}
 \end{subfigure}%
@@
   \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
-  \label{Fig1:ratio}
+  \label{Fig3.1:ratio}
 \end{subfigure}
-\label{Fig1}
+\label{Fig3.1}
 \end{figure}
@@
 Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
-\label{Fig2}
+\label{Fig3.2}
 \end{figure}
@@
 The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space.
+As in the one dimensional case, controlling the ratio between the NN and NNN coupling factors will allow us to control the angle state of the system.
 

### 2018-12-12 Chapters/Chapter2.tex
added more

@@
 \boldsymbol{\Delta}_{ij} = \begin{cases}
-             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbous} \\
+             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
              0,  & \text{otherwise}
@@
 
-\item The dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$ since the Coulomb interaction will be screened for further electrons. Therefore we approximate:
+Hubard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
+
+\item Taking into account the locality of the Wannier functions and the Coulomb interaction, the dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$.
+Terms with $i=k$ and $j=l$ also contribute when $i, j$ are nearest neighbours.
+Therefore we approximate:
 
@@
 		\text{U}, & \text{if } i=j=k=l \\
+		\text{V}, & \text{if } i=k \text{ and } j=l \text{ where } (i,j) \text{ nearest neighbours} \\
 		0, & \text{otherwise}
@@
 
-i.e.
-$\text{U} = \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}')^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}') \phi(\bs{r})$, where $\phi(\bs{r})$ is the Wannier function centered at the origin.
-Additionally, for $i=j=k=l$ the Pauli principle requires $\sigma' = \sigma$.
+Where we defined:
+
+\begin{align}
+\text{U} &= \frac{1}{2} \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}')^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}') \phi(\bs{r}) \\
+\text{V} &= \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}'-\bs{R}_1)^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}'-\bs{R}_1) \phi(\bs{r})
+\end{align}
+
+Where $\phi(\bs{r})$ is the Wannier function centered at the origin and $\bs{R}_1$ is a nearest neighbour lattice vector.
+Notice that we made explicit use of the translational invariance of the system.
+Also, for $i=j=k=l$ the Pauli principle requires $\sigma' = -\sigma$.
 
@@
 
-Taking these approximations we obtain the single band Hubbard model:
+Taking these approximations and writing $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \hat{c}_{i \sigma} = \hat{n}_{i \sigma} \hat{n}_{j \sigma'}$, we obtain:
+
+\begin{equation}
+\label{HubbardWithNonLocalInt}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \text{V} \sum_{i,j,\sigma,\sigma'}  \hat{n}_{i \sigma} \hat{n}_{j \sigma'}
+\end{equation}
+
+Now, in a half filling system this Hamiltonian can be well approximated by an effective Hamiltonian without non local Coulomb interactions:
+
+\begin{equation}
+\label{Intermediate}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}^* \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\text{U}^* = \text{U} - \text{V}$.
+The physical reason for this is that the energy difference when the Coulomb interaction pushes an electron from a double occupied site to an empty site is $\text{U}-\text{V}$ in \ref{HubbardWithNonLocalInt}, because the number of double occupied sites is reduced by one but the number of adjacent occupied sites is increased by one.
+This is illustred in Figure \ref{Fig2.1}.
+A more rigouros derivation of this effective model can be found in \cite{Schuler2013}.
+Altough $\text{V} < \text{U}$, they can be comparable in magnitude, and $\text{U}^*$ can be reduced by a factor of $0.5$ or more.
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.5\linewidth]{../Figures/non_local_coulomb.png}
+  \caption{Image from \cite{Schuler2013}.
+In a half-filled system decreasing the number of double occupancies increases the number of adjacent occupied sites, and so the energy difference is reduced to $\text{U}-\text{V}$.}
+\label{Fig2.1}
+\end{figure}
+
+Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the Hubbard model that we will use in the next sections:
 
@@
 \label{Hubbard}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
-$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
 Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.

### 2018-12-12 Code/Chap3.R

@@ -95,7 +95,7 @@ system(paste0("mv ", current_file, ".pdf ../Chapters/", current_file, ".pdf"))
 EMax <- lapply(1:length(frequencies), function(i) which(D2_factor[[i]] <= 0)[1]-1 )
 res_ratio <- lapply(1:length(frequencies), function(i)  ratioJD[[i]][1:EMax[[i]]] )
 res_field_energies <- lapply(1:length(frequencies), function(i)  field_energies[1:EMax[[i]]])
-theta <- lapply(1:length(frequencies), function(i) asin((res_ratio[[i]]-sqrt(res_ratio[[i]]^2+32))/8) )  
+theta <- lapply(1:length(frequencies), function(i) asin((-res_ratio[[i]]+sqrt(res_ratio[[i]]^2+32))/8) )  
 
 current_file <- "theta"
 tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,

### 2018-12-12 Chapters/Chapter2.tex
cites

@@
 We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
-This effective Hamiltonian will be the sum of a spin exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$ plus an anisotropic interaction of the form $\bs{D}\bs{S}_i\times\bs{S}_j$ \cite{Moriya1960}.
+This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
 
@@
 \begin{equation}
-\boldsymbol{\Delta}_{ij} = \begin{cases}
-             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
+\bs{\Delta}_{ij} = \begin{cases}
+             \bs{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
              0,  & \text{otherwise}
@@
 
-Hubard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
+Hubbard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
 
@@
 Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
+However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach.
 $\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya

### 2018-12-13 Chapters/Chap3/HNoSoi.tex
change

@@
 \begin{equation}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j
 \end{equation}
@@
 \begin{align}
-J_{ij}(t) &= t_0^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
+J_{ij} &= t_0^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
 &=\sum_{mn} t_0^2 e^{-i(\frac{\pi}{2}+\theta_{ij})m}\left(\frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij})}{\text{U}+n\omega} \right) e^{im\omega t} \label{Jij1}

### 2018-12-13 Chapters/Chap3/HWithSoi.tex
change

@@
 &= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
-&= \sum_{\langle i,j \rangle} \left\{ J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}(t)\bs{S}_j \right\}
+&= \sum_{\langle i,j \rangle} \left\{ J_{ij}\bs{S}_i\bs{S}_j +\bs{D}_{ij}\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j \right\}
 \end{align*}
@@
 \begin{align}
-J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
-\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI} \\
-\Gamma_{ij}^{\alpha \beta}(t) &= (\delta_{\alpha \beta} \bs{\Delta}_{ij}^2 - 2\Delta_{ij}^\alpha\Delta_{ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+J_{ij} &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
+\bs{D}_{ij} &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI} \\
+\Gamma_{ij}^{\alpha \beta} &= (\delta_{\alpha \beta} \bs{\Delta}_{ij}^2 - 2\Delta_{ij}^\alpha\Delta_{ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{align}

### 2018-12-13 Chapters/Chap3/ModelsNNN.tex
change

@@
 \begin{align}
-\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{1,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}(t)\bs{S}_j\right\} + \nonumber \\
-&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}(t)\bs{S}_j\right\}
+\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}\bs{S}_i\bs{S}_j + \bs{D}_{1,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
+&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
 \end{align}
@@
 \begin{align}
-J_{n,ij}(t) &= t_n^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JGeneral} \\
-\bs{D}_{n,ij}(t) &= 2it_n \bs{\Delta}_{n,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DGeneral} \\
-\Gamma_{n,ij}^{\alpha \beta}(t) &= (\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{GammaGeneral}
+J_{n,ij} &= t_n^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JGeneral} \\
+\bs{D}_{n,ij} &= 2it_n \bs{\Delta}_{n,ij}\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DGeneral} \\
+\Gamma_{n,ij}^{\alpha \beta} &= (\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{GammaGeneral}
 \end{align}
@@
 \label{KMHeff}
-\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij}(t) \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j 
+\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
 \end{equation}
@@
 \begin{align*}
-J_{ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{\Gamma}_{ij}(t) &= \Delta^2 \text{diag}(-1,-1,1)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
+J_{ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{\Gamma}_{ij} &= \Delta^2 \text{diag}(-1,-1,1)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
 \end{align*}
@@
 \begin{equation*}
-\bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left(S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y\right)
+\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left(S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y\right)
 \end{equation*}
@@
 The same spin model is obtained in \cite{Rachel2010} without the laser perturbation.
-If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij}(t) > 0$.
+If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij} > 0$.
 Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane.
-The exchange interaction $J_{ij}(t)$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned.
-Therefore, $\Gamma^{zz}_{ij}(t)$ will compete against $J_{ij}(t)$ in the $\hat{e}_z$ direction.
-In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$.
-In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
+The exchange interaction $J_{ij}$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned.
+Therefore, $\Gamma^{zz}_{ij}$ will compete against $J_{ij}$ in the $\hat{e}_z$ direction.
+In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}$.
+In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
 
@@
 \label{MKMHeff}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j \right\}
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
 \end{equation}
@@
 \begin{align*}
-J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{\Gamma}_{2,ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
+J_{1,ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+J_{2,ij} &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{2,ij} &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{\Gamma}_{2,ij} &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
 \end{align*}

### 2018-12-13 Chapters/Chap3/Numerics.tex
change

@@
 
-In a honeycomb lattice described by \ref{MKMHeff} the usual approach is to write:
+In a honeycomb lattice described by the effective spin model \ref{MKMHeff} the usual approach is to write:
 
 \begin{align}
-\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{R}), \sin(\bs{Q}\bs{r}), 0 \right) \\
-\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{R} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
+\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{r}), \sin(\bs{Q}\bs{r}), 0 \right) \\
+\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{r} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
 \end{align}
@@
 The $\hat{e}_z$ component vanishes in order to minimize the contribution of the pseudodipolar interaction.
+Let $Q_a = \bs{Q}\hat{\bs{a}}$ and $Q_b = \bs{Q}\hat{\bs{b}}$, where $\hat{\bs{a}}$ and $\hat{\bs{b}}$ are the primitive cell vectors.
 Then, the classical energy per spin is given by:
@@
 
-The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space.
-As in the one dimensional case, controlling the ratio between the NN and NNN coupling factors will allow us to control the angle state of the system.
+Notice that when the spins are constrained in the $\hat{e}_x, \hat{e}_y$ plane, the anisotropic interaction $\bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j$ becomes a ferromagnetic interaction.
+The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space (or equivalently, in the $t_1, t_2, \Delta$ space).
+We will not attempt to describe this phase diagram.
+However, as we have shown in the one dimensional case, by modulating the laser amplitude we can control the ratio between the NN and NNN coupling factors, and thus the parameters $\bs{Q}$ and $\theta$ of the system state.
 

### 2018-12-14 Chapters/Chapter2.tex
added hubbard discussion

@@
 
-Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the Hubbard model that we will use in the next sections:
+Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the model that we will use in the next sections:
 
@@
 \end{equation}
+
+\begin{subsection}{Hubbard model}
+
+In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
+This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}.
+Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
+Originally the Hubbard model was proposed to describe electron correlations in a simplified way and to predict metal-insulator transitions.
+It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory.
+Also, the attractive Hubbard model (where $\text{U} < 0$) is relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
+
+\end{subsection}
 

### 2018-12-14 Chapters/Chapter2.tex
changes

@@
 Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
-Originally the Hubbard model was proposed to describe electron correlations in a simplified way and to predict metal-insulator transitions.
-It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory.
-Also, the attractive Hubbard model (where $\text{U} < 0$) is relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
+Originally the Hubbard model was proposed to describe electron correlations in $d$ or $f$ bands in transition metals.
+The result was a simplified model to predict metal-insulator transitions.
+However, it exhibits much richer phenomena.
+It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
+they should be conductors according to band theory, but electron-electron interactions keep away from).
+Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
 

### 2018-12-16 Chapters/Chap3/ModelsNNN.tex
added time independent field

@@
 \begin{section}{Including next nearest neighbor hopping}
+
+\label{section3NNN}
 
@@
 \begin{equation}
+\label{BigHamHoppingAmp}
 t_{ij}^{\sigma \sigma'} = \begin{cases}
@@
 
+\begin{subsection}{Time independent electric field in the NN + NNN Hamiltonian}
+
+Now, let us examine the case in which the applied electric field is time independent.
+In this case the effective Hamiltonian is \ref{TimeIndepHeff}, which is the same Hamiltonian obtained when no electric field is applied except for a shift in the intermediate energy by $\pm \omega_0 = e\bs{\vec{R}}_{ij}\bs{\vec{E}}_0$.
+In this case, if we consider a Hamiltonian such as \ref{BigHam}, we can follow the same procedure done before: we plug in the hopping amplitudes \ref{BigHamHoppingAmp} into \ref{TimeIndepHeff} and apply \ref{SpinRel1} to sum over the spin states and obtain the corresponding spin Hamiltonian.
+We obtain:
+
+\begin{align}
+\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle ^*} \left\{ J_{1,ij}\bs{S}_i\bs{S}_j + \bs{D}_{1,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
+&\sum_{\langle \langle i,j \rangle \rangle^*} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
+\end{align}
+
+$\langle i,j \rangle ^*$ denotes sum over NN avoiding repeating the same two sites. The coupling factors are:
+
+\begin{align}
+J_{n,ij} &= 4\frac{t_n^2}{U^*_{ij}} \\
+\bs{D}_{n,ij} &= 8\frac{t_n i\bs{\Delta}_{n,ij}}{U^*_{ij}} \\
+\Gamma_{n,ij}^{\alpha \beta} &= \frac{4}{U^*_{ij}}(\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )
+\end{align}
+
+Where:
+
+\begin{equation}
+\frac{1}{U^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\bs{\vec{E}}_0} \right)
+\end{equation}
+
+\end{subsection}
+
 \end{section}

### 2018-12-16 Chapters/Chap3/TDHeff.tex
Big refactor
added time independent field

--- 2018-10-29 Chapters/TDHeff.tex
@@
+\begin{section}{Time dependent effective Hamiltonian}
+\label{SectionTDHeff}
+
 First we will start we a general Hamiltonian of the type:
@@
 
-Let us define $e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
+Let us define:
+
+\begin{equation}
+\label{Def_alpha}
+e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}
+\end{equation}
+
+With $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
 
@@
 \hat{H}_{\text{eff}}(t) &= \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = -\frac{1}{2}\sum_{mn} \left( \frac{\hat{P}_0  \hat{T}_{-1(m-n)}\hat{T}_{1n}\hat{P}_0}{\text{U}+n\omega} + \frac{\hat{P}_0 \hat{T}_{-1n} \hat{T}_{1(m-n)} \hat{P}_0}{\text{U}-n\omega} \right) e^{im\omega t} \nonumber \\
-&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{\text{U}+n\omega} \right\} e^{im\omega t}
+&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{\text{U}+n\omega} \right\} e^{im\omega t} \label{2ndOHeff}
 \end{align}
@@
 In the following sections we will apply what we have derived here for different models of the hopping operator.
+
+\begin{subsection}{Time independent field}
+
+We would like to investigate the case in which the electric field is time independent.
+In that case we can restrict the analysis to the one dimensional case, since in second order the electric field will only affect the bonds parallel to the field.
+Let us denote $\vec{\bs{E}} = E_0 \hat{e}_x$, then the Peiels transformed hopping amplitudes can be written as:
+
+\begin{equation}
+\label{TimeIndepHoppingAmpl}
+t_{ij}^{\sigma \sigma'} (t) = t_{ij}^{\sigma \sigma'} e^{ie \vec{\bs{R}}_{ij} \vec{\bs{E}} t}
+\end{equation}
+
+Therefore, there will be only two Fourier modes with frequency $\omega_0 = e \vec{\bs{R}}_{ij} \vec{\bs{E}} = \pm eaE_0$, where the sign $+(-)$ corresponds to the case $\vec{\bs{R}}_{ij} = \pm a \hat{e}_x$.
+Notice that this frequency $\omega_0$ does not correspond to a field frequency ($\vec{\bs{E}}$ is time independent), but to the Fourier mode in the hopping amplitudes (which is induced by the time independent field).
+From this point we can apply the same procedure as in the general case up to \ref{2ndOHeff}.
+We can greatly simplify this by considering that:
+\begin{itemize}
+	\item $n$ can only take values $ n = \pm 1$ (there are no additional Fourier modes).
+	\item When restricted to the low energy subspace a product $\hat{T}_{-1 a} \hat{T}_{1 b}$ will only contribute when $a$ and $b$ have opposite signs ($a=1, b=-1$ or viceversa).
+This is because, in the low energy subspace $\hat{T}_{-1 a} \hat{T}_{1 b}$ can only represent a hopping from a site $i$ to a site $j$ and the hopping back to $i$, we can see from \ref{TimeIndepHoppingAmpl} that these two amplitudes will be in opposite Fourier modes.
+\end{itemize}
+
+Taking this into consideration we see that only $m=0$ terms will remain, which is consistent with the fact that the two phases cancel out in the process $i \rightarrow j \rightarrow i$.
+We can thus rewrite \ref{2ndOHeff} as:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = -\hat{P}_0 \left\{ \frac{\hat{T}_{-1,1}\hat{T}_{1,-1} }{\text{U}-\omega_0} + \frac{\hat{T}_{-1,-1}\hat{T}_{1,1} }{\text{U}+\omega_0} \right\} \hat{P}_0
+\end{equation}
+
+Now, the first fraction represents a hopping process $i\rightarrow j \rightarrow i$ where $j$ lies left to $i$, whereas in the second fraction $j$ lies right to $i$:
+
+\begin{align*}
+\hat{P}_0 \hat{T}_{-1,1} \hat{T}_{1,-1} \hat{P}_0 &= \sum_{i > j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} \\
+\hat{P}_0 \hat{T}_{-1,-1} \hat{T}_{1,1} \hat{P}_0 &= \sum_{i < j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4}
+\end{align*}
+
+We can rewrite this in the more compact form:
+
+\begin{equation}
+\label{TimeIndepHeff}
+\hat{H}_{\text{eff}} = -\sum_{i, j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \frac{t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4}}{\text{U} + \text{sgn}(j-i)\omega_0}
+\end{equation}
+
+This is the same effective Hamiltonian obtained in the previous section without an electric field but with a shift in the intermediate state energy by $\pm \omega_0 = \pm eaE_0$.
+We will analyze the corresponding spin Hamiltonian of this effective Hamiltonian when we consider the Kane-Mele-Hubbard model in Section \ref{section3NNN}.
+
+\end{subsection}
+
+\end{section}

### 2018-12-29 Chapters/Chapter2.tex
added honeycomb lattice structure

@@
 
-Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\textbf{a}_\mu$:
+Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
 
 \begin{equation}
-\textbf{R} = \sum_{\mu=1}^3 m_\mu \textbf{a}_\mu
+\bs{R} = \sum_{\mu=1}^3 m_\mu \bs{a}_\mu
 \end{equation}
@@
 Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
-We will only consider cubic lattices where $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
 
+In the case of a cubic lattice we have $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
+
+In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
+
+\begin{align}
+\bs{a}_1 &= \frac{a_0}{2} \left(3, \sqrt{3} \right) \\
+\bs{a}_2 &= \frac{a_0}{2} \left(3, -\sqrt{3} \right)
+\end{align}
+
+Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
+Each unit cell contains two atoms, dividing the lattice into two sublattices, usually denoted A and B.
+The reciprocal lattice is defined by the vectors:
+
+\begin{align}
+\bs{b}_1 &= \frac{2\pi}{3a_0} \left(1, \sqrt{3} \right) \\
+\bs{b}_2 &= \frac{2\pi}{3a_0} \left(1, -\sqrt{3} \right)
+\end{align}
+
+These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
+
+\begin{align}
+\bs{R}^A_1 &= \frac{a_0}{2} \left( 1, \sqrt{3} \right) \\
+\bs{R}^A_2 &= \frac{a_0}{2} \left( 1, -\sqrt{3} \right) \\
+\bs{R}^A_3 &= a_0 \left( -1, 0 \right)
+\end{align}
+
+The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/honeycomb_lattice.png}
+  \caption{Image from a web source.
+In Fig.
+(a) the unit cell is sketched and the sublattices A and B are shown in blue and red respectively.
+In Fig.
+(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
+\label{Fig2.2}
+\end{figure}
 \end{section}

### 2019-01-14 Chapters/Chapter2.tex
4th order

@@
 
-At half filling, in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+At half filling and in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
 First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
@@
 These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
-These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
+This means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
 Now,
@@
 
+\begin{section}{Next-nearest neighbor hopping}
+This analysis can be easily extended to electronic Hamiltonians including next-nearest neighbor (NNN) hopping term. The simplest example of such a Hamiltonian is:
+
+\begin{equation}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma}t_{1}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -\sum_{\langle \langle i,j \rangle \rangle, \sigma} t_{2}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\langle \langle i,j \rangle \rangle$ denotes sum over NNN. If we follow the procedure as before we will obtain an effective spin Hamiltonian:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = J_1\sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j + J_2\sum_{\langle \langle i,j \rangle \rangle}\bs{S}_i\bs{S}_j
+\end{equation}
+
+Where $J_1 = \frac{t_1^2}{\text{U}}$ and $J_2 = \frac{t_2^2}{\text{U}}$.
+This Hamiltonian is known as $J_1-J_2$ Heisenberg model.
+This model has been extensively studied, and the $J_1-J_2-J_3$ is also of interest \cite{Reuther2011}.
+
+Notice that we can also obtain a $J_1-J_2$ Heisenberg model starting simply from a NN hamiltonian $\hat{H} = -\sum_{\langle i,j \rangle, \sigma}t_{1}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
+This is because the NNN exchange interaction comes from the possibility of the process $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ being $i,j$ NNN.
+This process is available when sites $i, j$ have opposite spins (otherwise it would violate the Pauli principle).
+Now, when $i,j$ are NNN, we can consider the fourth order process $i\sigma \rightarrow k\sigma \rightarrow j\sigma \rightarrow k\sigma \rightarrow i\sigma$, where $k$ is a site between $i$ and $j$.
+The resulting effective spin Hamiltonian has exchange couplings $J_1 = 2\frac{t_1^2}{\text{U}} - 8 \frac{t_1^4}{\text{U}^3}$ and $J_2 = 2\frac{t^4}{\text{U}}$.
+A rigorous derivation can be found in \cite{MacDonald1988}.
+
+\end{section}
+
 \begin{section}{AFM dynamics}

### 2019-01-16 Chapters/Chap3/ModelsNNN.tex
Disorder

@@
 This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
-The same spin model is obtained in \cite{Rachel2010} without the laser perturbation.
+Notice that the anisotropic term breaks the SU(2) symmetry of the bare Heisenberg model.
+The same spin model is obtained in \cite{Rachel2010} without the laser perturbation, this model has a much richer phase diagram than the $J_1-J_2$ Heisenberg model \cite{Vaezi2012}.
 If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij} > 0$.

### 2019-01-16 Chapters/Chapter2.tex
Disorder

@@
 
-\begin{section}{Next-nearest neighbor hopping}
+\begin{subsection}{Next-nearest neighbor hopping}
 This analysis can be easily extended to electronic Hamiltonians including next-nearest neighbor (NNN) hopping term. The simplest example of such a Hamiltonian is:
@@
 
-\end{section}
+\end{subsection}
+
+\begin{subsection}{Introducing disorder}
+
+It is possible to consider a disordered Hubbard model by adding random uncorrelated on-site energies. We neglect the SOI term for simplicity, then the disordered Hubbard model can be written as:
+
+\begin{equation}
+\label{DisorderedHubbardModel}
+\hat{H} = -t\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} +
+\sum_{i \sigma} \epsilon_i \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\epsilon_i$ are random variable $\epsilon_i \in [-W,W]$.
+At half filling we can derive an effective Hamiltonian using the same procedure as before.
+The second order virtual hopping $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ will give rise to an exchange spin interaction.
+In this case, however, the intermediate energy is $\text{U} + (\epsilon_j - \epsilon_i)$.
+Therefore the spin Hamiltonian will be:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \frac{2t^2}{\text{U} + (\epsilon_j - \epsilon_i)} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i\bs{S}_j
+\end{equation}
+
+Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
+This model is relevant for studying many-body localization phenomena \cite{Protopopov}.
+
+\end{subsection}
 

### 2019-01-19 Presentation/presentation.tex
Presentation

\documentclass{beamer}

\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Ultrafast manipulation of antiferromagnetic insulators]{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii Moriya interactions in antiferromagnetic insulators} % The short title appears at the bottom of every slide, the full title is only on the title page

%\author{Juan Manuel Losada Sosnovsky} % Your name
%\autoref{asdf}{asdf}
%\author[author1]{author1\inst{1}\\[1ex]  {\small supervisor1\inst{1,2}}}
\author[Juan Manuel Losada Sosnovsky]{Juan Manuel Losada Sosnovsky\\[10mm]{\small Supervisor: Alireza Qaiumzadeh}}
\institute[NTNU] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
QuSpin (NTNU)
}
\date{\today} % Date, can be changed to a custom date
\newcommand{\bs}[1] {\boldsymbol{#1}}
\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{First Section} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{Subsection Example} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
\frametitle{Spintronics}
Study and use the intrinsic spin of the electrons, in addition to their charge, to build devices. Example: Magnetoresistive random access memory.

\begin{figure}
\includegraphics[width=0.5\linewidth]{../Figures/fm_device.png}
\end{figure}

\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Antiferromagnetic Spintronics}
The development of information technology demands devices with high storage density, high energy efficiency and high write-read speeds. Antiferromagnets have appear as a natural alternative to ferromagnets due to some advantages: 
\begin{itemize}
\item Robustness against magnetic disturbances.
\item No hysteresis loss.
\item Produce no stray fields.
\item Ultrafast dynamics (femtosecond).
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Antiferromagnetic Spintronics}
\begin{figure}
\includegraphics[width=0.8\linewidth]{../Figures/afm_device.png}
\end{figure}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Heisenberg model}
\begin{equation} 
\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j \nonumber
\end{equation}
In antiferromagnets $J > 0$. Mentink, J. H. et al. showed that it is possible to manipulate the exchange constant by applying a laser field. $J = J_0 + \Delta J$.
\end{block}
\end{frame}

%------------------------------------------------

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Heisenberg model with DMI}
\begin{equation} 
\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j + \sum_{\langle i,j \rangle} \vec{D}_{ij}\boldsymbol{S}_i \times \boldsymbol{S}_j\nonumber
\end{equation}

Under some circumstances this Hamiltonian describes a canted antiferromagnet.

\begin{figure}
\includegraphics[width=0.8\linewidth]{../Figures/dmi_canting.png}
\end{figure}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Manipulation of the spin state}
If we can manipulate $J$ and $D$ we can control the canting angle.
\begin{figure}
\includegraphics[width=1\linewidth]{../Figures/canted_afm.png}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Manipulation of the spin state}
We need $\frac{J}{D} \neq \frac{J+\Delta J}{D+\Delta D}$.
\\[10mm]
However, $\frac{J}{D} = \frac{J+\Delta J}{D+\Delta D}$.
\end{frame}

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Kane-Mele-Hubbard model}
\begin{equation}
\hat{H}_{\text{KMH}} = -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}\nonumber
\end{equation}

It leads to a spin Hamiltonian:

\begin{equation}
\hat{H}_{\text{KMH}}^{\text{eff}} = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \nonumber
\end{equation}

\end{block}
\end{frame}

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Modified Kane-Mele-Hubbard model}
\begin{equation}
\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\text{U}\hat{D}\nonumber
\end{equation}

It leads to a spin Hamiltonian:

\begin{equation}
\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\} \nonumber
\end{equation}

What we wanted, in this case if we apply light $\frac{J}{D} \neq \frac{J+\Delta J}{D + \Delta D}$.

\end{block}
\end{frame}

\begin{frame}
\Huge{\centerline{The End}}
\end{frame}

\end{document}

### 2019-01-22 Chapters/Chap3/HNoSoi.tex
paper

@@
 
+\begin{subsection}{Dielectric permittivity}
+
+Using the approximation for the exchange coupling constant for circular polarized light derived in \ref{JijCPSQUARE} we can write the free energy of the system $\Phi$ as:
+
+\begin{align}
+\Phi &= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j = \nonumber \\
+&= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i \bs{S}_j + |\vec{E}_0|^2 \frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \bs{S}_j
+\end{align}
+
+Then, the dielectric permittivity is $\epsilon_{kl} = \frac{\partial^2 \Phi}{\partial E_k \partial E_l}$, i.e., the dielectric permittivity is isotropic $\epsilon_{kl} = \epsilon$ and:
+
+\begin{equation}
+\epsilon = \epsilon^0 + 2\frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \bs{S}_j
+\end{equation}
+
+Where $\epsilon^0 = \frac{\partial^2 \Phi_0}{\partial E_k \partial E_l}$.
+The refractive index will therefore depend on the magnetization of the antiferromagnet, this was already demonstrated experimentally in the 80's \cite{Demokritov1985}.
+\end{subsection}
+
 \end{section}

### 2019-01-22 Paper/example.tex
paper

% !TEX spellcheck = en-US
\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress]{revtex4}%
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{epstopdf}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{fancybox}
\usepackage{amsfonts}
\usepackage{amssymb}%
\usepackage[toc,page]{appendix}
\setcounter{MaxMatrixCols}{30}

\renewcommand{\cite}[1]{{[}\onlinecite{#1}{]}}

\newcommand{\s}{\sum\limits}
\newcommand{\p}{\prod\limits}
\newcommand{\pa}{\partial}
\newcommand{\il}{\int\limits}
\newcommand{\be}{\begin{equation}}
\newcommand{\e}{\end{equation}}
\newcommand{\beml}{\begin{subequations}}
\newcommand{\eml}{\end{subequations}}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eq}{\end{eqnarray}}
\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\bc}{\begin{cases}}
\newcommand{\ec}{\end{cases}}
\newcommand{\lt}{\left}
\newcommand{\rt}{\right}
\newcommand{\n}{\nonumber}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\ep}{\varepsilon}
\newcommand{\dd}{\displaystyle}
\newcommand{\bb}{\boldsymbol}
\newcommand{\h}{^\dagger}
\newcommand{\ph}{^{\phantom{\dagger}}}
\newcommand{\one}{\openone}
\newcommand{\ut}{\underaccent{\tilde}}
\newcommand{\ul}{\underaccent{\bar}}
\newcommand{\up}{\uparrow}
\newcommand{\dn}{\downarrow}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\re}{Re}
\DeclareMathOperator{\ctg}{cotan}
\DeclareMathOperator{\arcsh}{arcsinh}
\DeclareMathOperator{\csch}{csch}
\DeclareMathOperator{\rot}{rot}

\newcommand{\AQ}[1]{\textbf{\textcolor{red}{{#1}}}}

\begin{document}
\title{Theory of the Interfacial Dzyaloshinskii-Moriya Interaction in Rashba Antiferromagnets}

\author{Alireza Qaiumzadeh}
\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}

\author{Ivan A. Ado}
\affiliation{Radboud University, Institute for Molecules and Materials, 6525 AJ Nijmegen, Netherlands}

\author{Rembert A. Duine}
\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
\affiliation{Institute for Theoretical Physics and Center for Extreme Matter and Emergent Phenomena,
Utrecht University, Princetonplein 5, 3584 CC Utrecht, Netherlands}
\affiliation{Department of Applied Physics, Eindhoven University of Technology,
P.O. Box 513, 5600 MB Eindhoven, Netherlands}

\author{Mikhail Titov}
\affiliation{Radboud University, Institute for Molecules and Materials, 6525 AJ Nijmegen, Netherlands}
\affiliation{ITMO University, Saint Petersburg 197101, Russia}

\author{Arne Brataas}
\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}

\begin{abstract}
In antiferromagnetic (AFM) thin films, broken inversion symmetry or coupling to adjacent heavy metals can induce Dzyaloshinskii-Moriya (DM) interactions. Knowledge of the DM parameters is essential for understanding and designing exotic spin structures, such as hedgehog Skyrmions and chiral N\'{e}el walls, which are attractive for use in novel information storage technologies. We introduce a framework for computing the DM interaction in two-dimensional Rashba antiferromagnets. Unlike in Rashba ferromagnets, the DM interaction is not suppressed even at low temperatures. The material parameters control both the strength and sign of the interfacial DM interaction. Our results suggest a route toward controlling the DM interaction in AFM materials by means of doping and electric fields.
\end{abstract}

\date{\today}
\maketitle

Relativistic spin-orbit coupling (SOC) is the foundation of spin orbitronics, a rapidly developing branch of spintronics \cite{Manchon-Rashba1, Fert-Rashba3}. Anisotropic magnetoresistance \cite{Thomson} and the anomalous Hall effect \cite{Hall} are established SOC transport phenomena. More recent discoveries include the spin Hall and inverse spin Hall effects \cite{SHE}, topological surface states \cite{Fert-Rashba3,TSS1,TSS2}, spin-orbit torques \cite{Manchon-Rashba1, ManchonSOT, Alireza-Rashba2, AFM-Hamiltonian1, AFM-Hamiltonian2}, and chiral domain walls and Skyrmions \cite{skyrmion2009,Hoffmann,Emori,Thiaville,Alireza-skyrmion,Alireza-AFM1,Yudin}. These phenomena are essential to enable novel ultrafast, nonvolatile, nanoscale spin-based storage and computation devices.

%%%%%%%%%%%
% Fig. 1: fig:setup
%%%%%%%%%%%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{Fig1new.eps}
\caption{(a) The Rashba-AFM model is a model for systems with inversion asymmetry: an AFM/HM bilayer (left) and an AFM thin film asymmetrically embedded between two different insulator layers (right). (b) , (c) Electronic dispersion relations in the limit of strong exchange coupling (b) and in the limit of high SOC (c). The superscript $\eta=\pm$ refers to the conduction (blue) and valence (red) bands, whereas the superscript $s=\pm$ specifies chiral bands. In these two extreme limits, the band structure is almost isotropic for an AFM system with in-plane anisotropy.}
\label{fig:setup}
\vspace*{-6pt}
\end{figure}
%%%%%%%%%%%

The Dzyaloshinskii-Moriya (DM) interaction between localized spins in a magnetic material is induced by SOC \cite{Dzyaloshinsky, Moriya}. The DM interaction is important for stabilizing noncollinear magnetic structures in ferromagnets. The original proposal by Dzyaloshinskii and Moriya, however, concerned antiferromagnetic (AFM) systems with weak magnetization, i.e., weak ferromagnets; this weak magnetism can be explained in terms of antisymmetric exchange, which is also referred to as the DM interaction.

The energy associated with the DM interaction between two neighboring spins in a lattice, $\bm{S}_{1}$ and $\bm{S}_{2}$, can be written in the form of the mixed product $\mathcal{H}_{DM}=-\bm{D}_{12} \cdot \bm{S}_1 \times \bm{S}_2$, where $\bm{D}_{12}$ is called the DM vector. The DM interaction, therefore, favors a perpendicular orientation of neighboring spins. By contrast, the Heisenberg exchange interaction $\mathcal{H}_{\mathrm{ex}}=J_{\mathrm{ex}} \bm{S}_1 \cdot \bm{S}_2$ favors a collinear magnetic order, which can be either ferromagnetic (FM) for $J_{\mathrm{ex}}<0$ or AFM for $J_{\mathrm{ex}}>0$. The competition between the Heisenberg exchange interaction and the DM interaction leads to the formation of exotic structures such as chiral domain walls, helices, and Skyrmions \cite{Fert-Rashba3}.

In the bulk of a noncentrosymmetric magnetic crystal, the DM vector points along one of the lattice vectors and gives rise to so-called Bloch-like structures \cite{Dzyaloshinsky, Moriya, iDMI5}. In an ultrathin magnetic film with impurity- or interface-induced SOC, there is also an interfacial DM interaction that corresponds to a DM vector pointing out along the interface. This gives rise to so-called N\'{e}el-type textures \cite{iDMI1,iDMI2,iDMI3,iDMI4,iDMI5,Thiaville, iDMI7}. Both the sign and the amplitude of the DM vector are of critical importance for observing and engineering different chiral structures \cite{iDMI-exp0,katsnelson,iDMI-exp1,iDMI-exp2,iDMI-exp3,iDMI-exp4,iDMI-exp5,iDMI-exp6,iDMI-exp7,iDMI-exp8,iDMI-exp9,iDMI-exp10,iDMI-exp11,iDMI-exp12, AFMDMI-exp,iDMI-abinitio1,iDMI-abinitio2}.

AFM materials have recently attracted considerable attention as active spintronics elements \cite{AFM-review,AFM-review1}. The absence of stray fields, the possibility of operating at terahertz frequencies, and the existence of spin waves with opposite helicities make antiferromagnets promising candidates for use in the next generation of spin-based memory and processing devices \cite{AFM-review,AFM-review1} with a nanoscale element base.

The coexistence of strong SOC and spin ordering at the interfaces of AFM/heavy-metal (HM) bilayers makes such heterostructures particularly promising for low-dimensional spin orbitronics applications \cite{Interface-review}. An AFM thin film sandwiched between insulators is also a common functional geometry for spin-orbitronics due to interfacial SOC. The interfacial SOC in such a system is effectively described by Rashba SOC \cite{Manchon-Rashba2}. For magnetic films, the two-dimensional (2D) Rashba model captures the main physics and trends of SOC with a broken inversion symmetry \cite{Manchon-Rashba2}, such as fieldlike and dampinglike spin-orbit torques \cite{Manchon-Rashba1, Alireza-Rashba2, AFM-Hamiltonian1}, intrinsic spin Hall effects \cite{SHE}, intrinsic anomalous Hall effects \cite{AHE}, inverse Faraday effects \cite{Alireza-Rashba1}, and magnetic anisotropy \cite{Rashba-anisotropy}.

In this Letter, we develop a framework for computing the interfacial DM interaction in AFM layers with inversion asymmetry. The typical system illustrated in Fig.~\ref{fig:setup} is described on the basis of an effective 2D AFM-Rashba Hamiltonian. We find that both the sign and the magnitude of the DM vector depend on the ratio relating three energy scales: the chemical potential, the \textit{s-d} exchange interaction, and the Rashba SOC strength. In particular, the strong dependence on the chemical potential suggests that the DM interaction can be tuned by modifying the electron density by means of doping or voltage gating \cite{Fechner2012}.

A generic effective 2D Hamiltonian describing itinerant electrons in the AFM layer [see Fig.~\ref{fig:setup}(a)] can be written as
\begin{align}
\mathcal{H}=\mathcal{H}_{\mathrm{kin}}+\mathcal{H}_{\mathrm{sd}}+\mathcal{H}_{\mathrm{so}}, \label{hamiltonian}
\end{align}
where $\mathcal{H}_{\mathrm{kin}}$ is the kinetic energy of the electrons, $\mathcal{H}_{\mathrm{sd}}=J_{\mathrm{sd}}\,\bm{n} \cdot \bm{\Gamma}$ describes an effective interaction with a strength $J_{\mathrm{sd}}$ between the spins of the itinerant $s$ electrons and the localized $d$ electrons \cite{sd-model-referee-suggested}, and $\mathcal{H}_{\mathrm{SO}}$ describes the SOC. The operator $\bm{\Gamma}$ is the direct product of the electron spin operator and the sublattice position operator, which, in the case of an AFM system, accounts for the effects of sublattice staggering. The unit vector $\bm{n}$ is the order parameter, which can represent either the total magnetization in a ferromagnet or the staggered magnetization in an antiferromagnet.

We compute the electronic contributions to the DM interaction parameter $D$ and to the exchange stiffness $A$ in the following way. First, we evaluate how the itinerant electrons influence the magnetic subsystem by finding an effective action. We expand the effective action up to linear order with respect to the deviation of the spins from their equilibrium direction. The corresponding susceptibility tensor describes the influence of the electronic degrees of freedom on the localized magnetic moments. A linear expansion of the susceptibility tensor in spatial gradients of $\bb{n}$ defines the DM interaction strength $D$. The contribution of the itinerant electrons to the exchange stiffness $A$ is extracted from the second-order expansion in spatial gradients.

The action $\mathcal{S}$ defines the system partition function $\mathcal{Z}=\int d[\Phi^*] d[\Phi] d[\bm{n}] e^{-\mathcal{S}[\Phi^*,\Phi,\bm{n}]/\hbar}$, where $\Phi$ is the Grassmannian coherent-state spinor and $\hbar$ is Planck's constant. In the $s$-$d$ approach to magnetic systems, the action is decomposed into the sum $\mathcal{S}=\mathcal{S}_F+\mathcal{S}_B$, where $\mathcal{S}_F[\Phi^*,\Phi,\bm{n}]$ is the fermionic action corresponding to the Hamiltonian of Eq.~(\ref{hamiltonian}), which also includes the $s$-$d$ coupling, and $\mathcal{S}_B[\bm{n}]$ is the bosonic action describing the dynamics of the localized spins (magnons) in the absence of itinerant electrons. In our model, it is the coupling between the itinerant electrons and the local moments that determine the DM interaction, which is also directly linked to the SOC of the itinerant electrons. We will not specify the bosonic part of the action $\mathcal{S}_B[\bm{n}]$ since it is irrelevant for the subsequent discussion.

The fermionic action reads
\be
\mathcal{S}_F\!=\!\int\!\!\!\int_0^{\hbar\beta}\!\!d\tau d\tau'\!\! \int\!\!\!\int\! d{\bm{r}} d{\bm{r}}' \Phi^*_{\bm{r},\tau} [-\hbar  G^{-1}_{\bm{r},\tau;\bm{r}',\tau'}] \Phi_{\bm{r}',\tau'},
\e
where $\beta=1/k_B T$ is the inverse temperature and $\tau$ is the imaginary time. The inverse Green's function operator is  $\hbar\, G^{-1}_{\bm{r},\tau;\bm{r}',\tau'}=-\left(\hbar{\partial_\tau}+\mathcal{H}\right)\delta(\bm{r}-\bm{r}')\delta(\tau-\tau')$ in terms of the Hamiltonian of Eq.~(\ref{hamiltonian}). We compute the effective theory for the vector field $\bb{n}(\bb{r})$ by integrating out the fermionic degrees of freedom. This standard procedure results in an additional, effective contribution to the bosonic action of the form $\Delta \mathcal{S}_F^{\mathrm{eff}}[\bm{n}]=\int_0^{\hbar\beta} d\tau \int d{\bm{r}} \left(-\hbar \mathrm{Tr}[\ln(-G^{-1})]\right)$. Below, we analyze $\Delta \mathcal{S}_F^{\mathrm{eff}}[\bm{n}]$ and its influence on the magnet in the AFM-Rashba model.

%%%%%%%%%%%%%%
%Fig 2 %%%%%%% fig:diag
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{Fig2.eps}
\caption{ (a) The Feynman diagram corresponding to Eq.~(\ref{polarizibility-pi}) for a single-loop polarizability tensor. (b) The Feynman diagram corresponding to Eq.~(\ref{DMI-formula22}), describing the interfacial DM interaction for a system with inversion symmetry breaking in the $z$ direction and an order parameter vector $\bm{n}$ in the $x$ direction.}
\label{fig:diag}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In our system, the symmetry-breaking direction ($z$ direction) is perpendicular to the plane \cite{iDMI-exp3}. Without the loss of generality, we choose the $x$ axis to be in the direction of the in-plane vector field $\bb{n}$. A small deviation of the unit vector from its equilibrium direction is, then, parameterized by $\bm{n}=\hat{\bb{x}}+\delta\bm{n}$, where $\delta\bm{n}=\left( -(\delta n^2_y+\delta n^2_z)/2, \delta n_y, \delta n_z \right)$. The effective action is obtained from a perturbation with respect to $\delta \bb{n}$, \cite{sd-model-referee-suggested} that holds irrespective of the value of the exchange strength $J_{sd}$. The effective action is conveniently established from the Dyson equation, $G^{-1}={G^0}^{-1}-\Sigma$, where the unperturbed Green's function refers to $\delta\bb{n}=0$ and the self-energy $\hbar \Sigma=J_{\mathrm{sd}}\delta\bm{n}\cdot\bm{\Gamma}\, \delta(\bm{r}-\bm{r}')\delta(\tau-\tau')$ is introduced.

Computing the self-energy up to the second order in $\delta\bm{n}$ yields \cite{kzero}
\begin{align}
\label{eff-action4}
\Delta \mathcal{S}^{\mathrm{eff}}[\bm{n}]=\hbar\beta\sum_{\bm{k}\neq 0,l}\delta n^a_{\bm{k},\nu_l} \Pi^{ab}_{\bm{k},i\nu_l} \delta n^b_{-\bm{k},-\nu_l},
\end{align}
where the indices $a, b=(y,z)$ denote the transverse vector components with respect to the equilibrium $\hat{\bb{x}}$ direction, $\nu_l=2 n\pi/ \beta$ denotes the bosonic Matsubara frequencies, and
\be
\label{polarizibility-pi}
\Pi^{ab}_{\bm{k},i\nu_l}=\frac{J^2_{\mathrm{sd}}}{2\hbar\beta}\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}\Gamma_b G^0_{\bm{q}+\bm{k},i\omega_{n}+i\nu_l}]
\e
is the dynamical susceptibility tensor, pictured schematically in Fig.~\ref{fig:diag}a. Here, $G^0_{\bm{q},i\omega_{n}}=(i\hbar\omega_n-\mathcal{H})^{-1}$ is the equilibrium Green's function, and the $\omega_n=(2 n+1)\pi/ \beta$ are the fermionic Matsubara frequencies. We compute the sum over the fermionic Matsubara frequencies by using the identity $\sum_n (i \hbar\omega_n-E)^{-1}/\beta=f(E)$, where $f(E)$ is the Fermi distribution.

By expanding the static limit, $\nu_l=0$, on the spin susceptibility to the second order in the wave vector $\bm{k}$, we find both the electronic contribution to the symmetric Heisenberg exchange stiffness, which is determined by the symmetric terms in the diagonal elements of the susceptibility tensor, and the antisymmetric exchange interaction (DM interaction), which is determined by the antisymmetric terms in the off-diagonal elements. From the partition function of the canonical ensemble, $\mathcal{Z}=\int d[{\bm{n}}] e^{-\mathcal{S}^{\mathrm{eff}}[\bm{n}]/\hbar}=\int d[{\bm{n}}] e^{-\beta F[{\bm{n}}]}$, we obtain $\delta_{{\bm{n}}}\mathcal{S}^{\mathrm{eff}}/\hbar =\beta\delta_{\bm{n}} F[{\bm{n}}]$, where the micromagnetic free energy, including the stiffness and the DM interaction, is $F[{\bm{n}}]=\int d^2\bm{r} \left(A (\nabla {\bm{n}})^2-D {\bm{n}}\cdot(\hat{\bb{z}}\times \nabla)\times {\bm{n}}\right)$. By comparing the microscopic free energy with the expression for the effective action, Eq. (\ref{eff-action4}), we define the micromagnetic parameters $A$ and $D$, which characterize the free carrier contributions to the exchange stiffness and the DM interaction, respectively.

Upon expanding the off-diagonal elements of the tensor $\Pi$ to the first order in the wave vector $\bm{k}$ [see Fig.~\ref{fig:diag}(b)], we obtain the relation
\begin{subequations}
\label{DMI-formula22}
\begin{align}
D=&\lt.i\frac{\partial\Pi^{yz}_{\bm{k}}}{\partial {k_y}} \rt|_{\bm{k}=0}=-\lt.i\frac{\partial\Pi^{zy}_{\bm{k}}}{\partial {k_y}} \rt|_{\bm{k}=0}\\
\label{DMI-formula2}
=&i\frac{J^2_{\mathrm{sd}}}{2\beta}\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_y G^0_{\bm{q},i\omega_{n}}\Gamma_z G^0_{\bm{q},i\omega_{n}}v_y G^0_{\bm{q},i\omega_{n}}],
\end{align}
\end{subequations}
where $v_y=\hbar^{-1}\partial \mathcal{H}_{\bm{q}}/\pa q_y$ is the $y$ component of the velocity operator. From the second-order terms, we obtain the electron contribution to the exchange stiffness:
\begin{align}
\label{stiffness}
A=&-\lt.\frac{\partial^2\Pi^{yy}_{\bm{k}}}{\partial {k^2_x}} \rt|_{\bm{k}=0}=-\lt.\frac{\partial^2\Pi^{zz}_{\bm{k}}}{\partial {k^2_y}} \rt|_{\bm{k}=0} \, .
\end{align}
In our model, $A$ describes the contribution to the AFM exchange interaction from a superexchange-type interaction between the localized spins in the AFM layer via the itinerant spins.

We should emphasize here that in this approach, we have ignored the spin fluctuations of the localized AFM spins, which is a valid omission as long as the system temperature is much less than the critical N\'{e}el temperature.

To model an AFM system with interfacial SOC, we use the 2D AFM-Rashba Hamiltonian \cite{AFM-Hamiltonian1,AFM-Hamiltonian2} on a square lattice:
\begin{align}
\label{hamiltonian-AFM}
\mathcal{H}= \gamma_k \tau_x\sigma_0+J_{\mathrm{sd}} \tau_z\bm{\sigma}\cdot\bm{n}-\alpha_R \tau_x(\bm{\sigma}\times\bm{k})\cdot\hat{\bb{z}},
\end{align}
where $\bb{\sigma}$ and $\bb{\tau}$ are the vectors of Pauli matrices representing the spin and AFM sublattice degree of freedom, respectively; $\sigma_0$ is the identity matrix; $\bm{n}$ is the staggered order parameter (the normalized N\'{e}el vector); and $\alpha_R$ is the strength of the Rashba SOC. The kinetic energy of the itinerant electrons is $\gamma_k=a^2 t(k^2-k^2_0)$, where $t$ is the nearest-neighbor hopping energy and $k_0=2/a$, with $a$ being the lattice constant.

The band structure of the AFM-Rashba Hamiltonian of Eq.~(\ref{hamiltonian-AFM}) is, in general, anisotropic. It is convenient to parameterize the four spectral branches as follows:
\be
\label{energy-AFM}
E^{s,\eta}_k=\eta \sqrt{\gamma^2_k+J^2_{\mathrm{sd}}+\alpha^2_R k^2+2 s \alpha_R k \xi_k},
\e
where $s, \eta=\pm 1$ are the spin chirality and electron/hole band indices, respectively. We also introduce $\xi_k=\lt(\gamma^2_k+J^2_{\mathrm{sd}} \cos^2\phi\rt)^{1/2}$ with the in-plane wave vector $\bm{k}$ parameterized by the angle $\phi$, such that $\bm{k}=k(\cos\phi,\sin\phi,0)$.

%%%%%%%%%%%%%%
%% Fig. 3  fig:results
%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics[width=8cm]{Fig3a.eps}
\includegraphics[width=8cm]{Fig3b.eps}
\caption{Numerical results for the DM interaction as a function of the Fermi energy (top) and of the SOC strength (bottom) for different values of the \textit{s-d} exchange interaction. We set $\epsilon_F=2$ eV and $t=3$ eV in all cases.}
\label{fig:results}
\end{figure}
%%%%%%%%%%%%%%

Let us now analyze the expressions of Eqs.~(\ref{DMI-formula22}) and (\ref{stiffness}) for the AFM-Rashba Hamiltonian of Eq.~(\ref{hamiltonian-AFM}) in the limit of weak spin-orbit interaction, $\{k_0 \alpha_R, J_\mathrm{sd}\} \ll \min\{t, \epsilon_F\}$, and at zero temperature. Using the relation $\Gamma_a=\tau_z\sigma_a$, we obtain the relation
\begin{align}
\label{DMI-AFM-weakSO}
D = -\left(\frac{A k^2_0}{4 t}\right)\alpha_R ,
\end{align}
where the stiffness parameter is
\be
\label{A-AFM-weakSO}
A = \frac{t J^2_{\mathrm{sd}}}{2 \pi \epsilon^2_F}
\bc
2-\epsilon^2_F/16 t^2,& \epsilon_F < 4t, \\
1,& \epsilon_F > 4t,
\ec
\e
which is manifestly independent of the SOC strength in the limit of weak spin-orbit interaction. Here, the Fermi energy $\epsilon_F$ is measured with respect to the center of the energy gap [see Figs.~\ref{fig:setup}(b) and (c)]. In this regime, the energy gaps at $k=0$ and $k=\pm k_0$ are equal to $8t$ and $2J_{\mathrm{sd}}$, respectively.

For the case in which the Fermi energy lies within the band gap, i.\,e., for $|\epsilon_F| < J_{\mathrm{sd}}$,  and in the limit of $k_0 \alpha_R \ll J_{\mathrm{sd}} \ll t$, we obtain
\begin{align}
\label{DMI-AFM3}
D =\left(\frac{k^2_0}{2\pi}\right) \alpha_R,
\end{align}
which is of the opposite sign compared with the metallic regime of Eqs.~(\ref{DMI-AFM-weakSO}) and (\ref{A-AFM-weakSO}).

It is instructive to compare the results of Eqs.~(\ref{DMI-AFM-weakSO})-(\ref{DMI-AFM3}) with those for a Rashba-FM system \cite{RashbaFM-DMI}. If both FM chiral bands are occupied ($\epsilon_F> J_{\mathrm{sd}}$), the interfacial DM interaction in the Rashba-FM model vanishes at zero temperature due to the exact cancellation between the Fermi surface and Fermi sea contributions \cite{RashbaFM-DMI}. However, such a cancellation is absent in the AFM-Rashba model, giving rise to a finite result for Eq.~(\ref{DMI-AFM-weakSO}), by virtue of an additional contribution from the valence bands. For $\epsilon_F < J_{\mathrm{sd}}$, i.\,e., when only the lowest FM chiral band is occupied, the DM interaction in the weak SOC limit and at zero temperature is finite and linearly proportional to $A$ \cite{iDMI7, Mokrousov, Tatara,RashbaFM-DMI}.

On the other hand, in the Dirac model of an FM/topological-insulator bilayer characterized by the Hamiltonian of the Rashba SOC symmetry, the DM interaction vanishes inside the gap but remains finite outside the gap, even at zero temperature\cite{iDMI-theory-TI1,iDMI-theory-TI2}. Thus, we conclude that the DM interaction exhibits a qualitatively different behavior in antiferromagnets compared with that in ferromagnets.

In Fig.~\ref{fig:results}, we illustrate the behavior of the DM interaction on the basis of a numerical analysis of Eq.~(\ref{DMI-formula2}) beyond the weak SOC regime of Eqs.~(\ref{DMI-AFM-weakSO}-\ref{DMI-AFM3}), where typical material parameters are assumed: $t=3$~eV, $\epsilon_F=2$~eV, $J_{\mathrm{sd}}=1$~eV, $a=0.4$~nm and $k_0\alpha_R=0.1$~eV \cite{AFM-Hamiltonian1}. The results indicate a rather large interfacial DM interaction, with $D\simeq -1.6$~pJ/m. Moreover, when the Fermi energy lies within the gap, i.\,e., $|\epsilon_F| < J_{\mathrm{sd}}$, we find an order-of-magnitude enhancement of the DM interaction with the opposite sign, $D\simeq 12.7$~pJ/m. Importantly, the estimated strength of the DM interaction is at least an order of magnitude larger than that for a Rashba-FM layer with the same parameters \cite{RashbaFM-DMI}.

For small Fermi energies, the DM interaction is positive and almost independent of the Fermi energy (see the top panel in Fig.~\ref{fig:results}), as might be expected from Eq.~(\ref{DMI-AFM3}). In the metallic regime (i.\,e., for Fermi energies well above the gap), the DM interaction is negative, and its strength decreases in proportion to $\epsilon_F^{-2}$, in good agreement with Eqs.~(\ref{DMI-AFM-weakSO}) and (\ref{A-AFM-weakSO}). The sign inversion of the DM interaction is rather sharp and occurs at $\epsilon_F=\sqrt{J^2_{\mathrm{sd}}+\alpha^2_R k^2_0}$. The bottom panel of Fig.~\ref{fig:results} also confirms that the strength of the DM interaction is linearly proportional to $\alpha_R$ in the weak SOC regime, in agreement with Eq.~(\ref{DMI-AFM-weakSO}). Thus, we conclude that the DM interaction in an AFM material may vary by orders of magnitude depending on the material parameters, as illustrated in Fig.~\ref{fig:results}.

Our calculations also show that, unlike in FM-Rashba systems \cite{RashbaFM-DMI}, the temperature dependence of the DM interaction in the AFM-Rashba model of Eq.~(\ref{hamiltonian-AFM}) is weak due to a large contribution to the DM interaction from the valence bands (not shown). As we have already discussed, this is correct if the system temperature is much less than the N\'{e}el temperature, i.\,e., in a regime in which the spin fluctuations of the AFM layer are suppressed.

Controlling the DM interaction is essential for engineering chiral magnetic structures. If the DM interaction parameter exceeds a certain critical value, which is determined by the Heisenberg exchange interaction and the uniaxial anisotropy, then the ground state changes from a collinear configuration to either a helimagnetic state or a Skyrmion lattice. A weaker DM interaction enables the stabilization of isolated Skyrmions in a metastable state \cite{Alireza-skyrmion,Yudin}. In chiral magnets, the sign of the DM interaction determines the direction, or handedness, of spin rotation.

The asymmetry of the spin-wave dispersion in spin-polarized electron energy-loss spectroscopy and Brillouin light scattering is a measure of the DM interaction in FM systems \cite{iDMI-exp0,iDMI-exp2,AFM-iDMI-exp1}. Although the interfacial DM interactions in a few FM/HM bilayers have been experimentally studied in recent years \cite{iDMI-exp1,iDMI-exp2,iDMI-exp3,iDMI-exp4,iDMI-exp5,iDMI-exp6,iDMI-exp7,iDMI-exp8,iDMI-exp9,iDMI-exp10,iDMI-exp11,iDMI-exp12,iDMI-exp13,AFM-iDMI-exp1}, we are not aware of similar measurements in AFM heterostructures. However, the first observation of a bulk DM interaction in an AFM system, namely, the noncentrosymmetric $\alpha-\mathrm{Cu_2V_2O_7}$, has recently been reported in Ref. \cite{AFMDMI-exp} based on inelastic neutron scattering. Very recently, a large DM interaction in Fe/Ir bilayers on Rh(001) has been predicted on the basis of {\em ab initio} calculations \cite{AFM-iDMI-DFT-2}. We hope that our work will stimulate new experiments and {\em ab initio} works on such AFM heterostructures.

In summary, we have computed the DM interaction, both analytically and numerically, using an effective model for AFM layers with interfacial Rashba SOC.
In the AFM-Rashba model, the induced interfacial DM interaction appears as a Lifshitz-type invariant term. Our results show that both the sign and the strength of the DM interaction may be tuned by modifying the electron density, e.\,g., by applying a gate voltage or through doping. This tunability implies that a rich variety of chiral magnetic structures can emerge in layered AFM/HM systems with different interfacial charge densities, \textit{s-d} exchange interactions, and SOC interactions.

\section*{Acknowledgments}
The research leading to these results was supported by the European Research Council via Advanced Grant No. 669442, ``Insulatronics," and by the Research Council of Norway through its Centres of Excellence funding scheme, Project No. 262633, ``QuSpin." We also acknowledge the support received from the Dutch Science Foundation, NWO/FOM 13PR3118; the European Commission; and the Russian Science Foundation under Project No. 17-12-01359. R. A. D. is part of the D-ITP consortium, a program of the Netherlands Organisation for Scientific Research (NWO) that is funded by the Dutch Ministry of Education, Culture and Science (OCW). M.T. acknowledges support from an ITMO visiting professor fellowship.

\begin{thebibliography}{9}

\bibitem {Manchon-Rashba1}
A. Manchon, H. C. Koo, J. Nitta, S. M. Frolov, and R. A. Duine, Nat. Mater. \textbf{14}, 871 (2015).

\bibitem {Fert-Rashba3}
A. Soumyanarayanan, N. Reyren, A. Fert, and C. Panagopoulos, Nature (London) \textbf{539}, 509 (2015).

\bibitem {Thomson}
W. Thomson, Proc. R. Soc. Lond. \textbf{8}, 546 (1857).

\bibitem {Hall}
E. Hall, Philos. Mag. \textbf{12}, 157 (1881).

\bibitem {SHE}
J. Sinova, S. O. Valenzuela, J. Wunderlich, C. H. Back, and T. Jungwirth, Rev. Mod. Phys. \textbf{87}, 1213  (2015).

\bibitem {TSS1}
P. Roushan, J. Seo, C. V. Parker, Y. S. Hor, D. Hsieh, D. Qian, A. Richardella, M. Z. Hasan, R. J. Cava, and A. Yazdani, Nature (London) \textbf{460}, 1106 (2009).

\bibitem {TSS2}
T. Zhang, P. Cheng, X. Chen, J-F. Jia, X. Ma, K. He, L. Wang, H. Zhang, X. Dai, Z. Fang, X. Xie, and Q-K. Xue, Phys. Rev. B \textbf{79}, 094422 (2009).

\bibitem {ManchonSOT}
A. Manchon and S. Zhang, Phys. Rev. B \textbf{79}, 094422 (2009).

\bibitem {Alireza-Rashba2}
A. Qaiumzadeh, R. A. Duine, and M. Titov, Phys. Rev. B \textbf{92}, 014402 (2015).

\bibitem {AFM-Hamiltonian1}
J. \v{Z}elezn\'{y}, H. Gao, A. Manchon, F. Freimuth, Y. Mokrousov, J. Zemen, J. Ma\v{s}ek, J. Sinova, and T. Jungwirth
Phys. Rev. B \textbf{95}, 014403 (2017); J. \v{Z}elezn\'{y}, H. Gao, K. V\'{y}born\'{y}, J. Zemen, J. Ma\v{s}ek, A. Manchon, J. Wunderlich, J. Sinova, and T. Jungwirth,
Phys. Rev. Lett. \textbf{113}, 157201 (2014).

\bibitem {AFM-Hamiltonian2}
H. B. M. Saidaoui and A. Manchon, arXiv:1606.04261.

\bibitem {skyrmion2009}
S. M\"{u}hlbauer, B. Binz, F. Jonietz, C. Pfleiderer, A. Rosch, A. Neubauer, R. Georgii, and P. B\"{o}ni, Science \textbf{323}, 915 (2009).

\bibitem {Hoffmann}
W. Jiang, G. Chen, K. Liu, J. Zang, S. G. E. te Velthuis, and A. Hoffmann, Phys. Rep. \textbf{704}, 1 (2017).

\bibitem {Thiaville}
A. Thiaville, S. Rohart, \'{E}. Ju\'{e}, V. Cros, and A. Fert, Europhys. Lett. \textbf{100}, 57002 (2012).

\bibitem {Emori}
S. Emori, U. Bauer, S-M. Ahn, E. Martinez, and G. S. D. Beach, Nat. Mater. \textbf{12}, 611 (2013).

\bibitem {Alireza-skyrmion}
V. Flovik, A. Qaiumzadeh, A. K. Nandy, C. Heo, and T. Rasing,  Phys. Rev. B, \textbf{96}, 140411(R) (2017).

\bibitem {Alireza-AFM1}
A. Qaiumzadeh, L. A. Kristiansen, and A. Brataas, Phys. Rev. B \textbf{97}, 020402(R) (2018).

\bibitem{Yudin}
D. Yudin, D. R. Gulevich, and M. Titov, Phys. Rev. Lett. \textbf{119}, 147202 (2017).

\bibitem {Dzyaloshinsky}
I. Dzyaloshinsky, J. Phys. Chem. Solids \textbf{4}, 241 (1958); J. Exp. Theor. Phys. \textbf{32}, 1547 (1957).

\bibitem {Moriya}
T. Moriya, Phys. Rev. \textbf{120}, 91 (1960); Phys. Rev. Lett. \textbf{4}, 228 (1960).

\bibitem {iDMI5}
M. Heide, G. Bihlmayer, and S. Bl\"{u}gel, Phys. Rev. B \textbf{78}, 140403(R) (2008).

\bibitem {iDMI1}
A. Fert, Mater. Sci. Forum \textbf{59-60}, 439 (1990); A. Fert and P. M. Levy, Phys. Rev. Lett.  \textbf{44}, 1538 (1980).

\bibitem {iDMI2}
A. N. Bogdanov and D. A. Yablonskii, Sov. Phys. JETP \textbf{68}, 101 (1989); \textbf{69}, 142 (1989).

\bibitem {iDMI3}
A. Cr\'{e}pieux and C. Lacroix, J. Magn. Magn. Mater. \textbf{182}, 341 (1998).

\bibitem {iDMI4}
A. N. Bogdanov and U. K. R\"{o}{\ss}ler, Phys. Rev. Lett. \textbf{87}, 037203 (2001).

\bibitem {iDMI7}
J-H. Moon, S-M. Seo, K-J. Lee, K-W. Kim, J. Ryu, H-W. Lee, R. D. McMichael, and M. D. Stiles, Phys. Rev. B \textbf{88}, 184404 (2013); K-W. Kim, H-W. Lee, K-J. Lee, and M. D. Stiles, Phys. Rev. Lett. \textbf{111}, 216601 (2013).

\bibitem {iDMI-exp0}
Kh. Zakeri, Y. Zhang, J. Prokop, T.-H. Chuang, N. Sakr, W. X. Tang, and J. Kirschner, Phys. Rev. Lett. \textbf{104}, 137203 (2010); Kh. Zakeri, Y. Zhang, T.-H. Chuang, and J. Kirschner, \textit{ibid} \textbf{108}, 197205 (2012).

\bibitem {katsnelson}
V. E. Dmitrienko, E. N. Ovchinnikova, S. P. Collins, G. Nisbet, G. Beutier, Y. O. Kvashnin, V. V. Mazurenko, A. I. Lichtenstein, and M. I. Katsnelson, Nat. Phys. \textbf{10}, 202 (2014).

\bibitem {iDMI-exp1}
A. K. Chaurasiya, C. Banerjee, S. Pan, S. Sahoo, S. Choudhury, J. Sinha, and A. Barman, Sci. Rep. \textbf{6}, 32592 (2016).

\bibitem {iDMI-exp2}
J. Cho, N-H. Kim, S. Lee, J-S. Kim, R. Lavrijsen, A. Solignac, Y. Yin, D-S. Han, N. J. J. van Hoof, H. J. M. Swagten, B. Koopmans, and C-Y. You, Nat. Commun. \textbf{6}, 7635 (2015).

\bibitem {iDMI-exp3}
M. Belmeguenai, J-P. Adam, Y. Roussign\'{e}, S. Eimer, T. Devolder, J-V. Kim, S. M. Cherif, A. Stashkevich, and A. Thiaville, Phys. Rev. B \textbf{91}, 180405(R) (2015).

\bibitem {iDMI-exp4}
H. S. K\"{o}rner, J. Stigloher, H. G. Bauer, H. Hata, T. Taniguchi, T. Moriyama, T. Ono, and C. H. Back, Phys. Rev. B \textbf{92}, 220413(R) (2015).

\bibitem {iDMI-exp5}
K. Di, V. L. Zhang, H. S. Lim, S. C. Ng, M. H. Kuok, J. Yu, J. Yoon, X. Qiu, and H. Yang, Phys. Rev. Lett. \textbf{114}, 047201 (2015).

\bibitem {iDMI-exp6}
H. Yang, A. Thiaville, S. Rohart, A. Fert, and M. Chshiev, Phys. Rev. Lett. \textbf{115}, 267210 (2015).

\bibitem {iDMI-exp7}
H. T. Nembach, J. M. Shaw, M. Weiler, E. Ju\'{e}, and T. J. Silva, Nat. Phys. \textbf{11}, 825 (2015).

\bibitem {iDMI-exp8}
A. Hrabec,  M. Belmeguenai,  A. Stashkevich,  S. M. Ch\'{e}rif,  S. Rohart,  Y. Roussign\'{e}, and  A. Thiaville, Appl. Phys. Lett. \textbf{110}, 242402 (2017).

\bibitem {iDMI-exp9}
R. M. Rowan-Robinson, A. A. Stashkevich, Y. Roussigne, M. Belmeguenai, S-M. Cherif, A. Thiaville, T. P. A. Hase, A. T. Hindmarch, and D. Atkinson, Sci. Rep. \textbf{7}, 16835 (2017).

\bibitem {iDMI-exp10}
X. Ma, G. Yu, X. Li, T. Wang, D. Wu, K. S. Olsson, Z. Chu, K. An, J. Q. Xiao, K. L. Wang, and X. Li, Phys. Rev. B \textbf{94}, 180408(R) (2016).

\bibitem {iDMI-exp11}
H. Yang, G. Chen, A. A. C. Cotta, A. T. N'Diaye, S. A. Nikolaev, E. A. Soares, W. A. A. Macedo, A. K. Schmid, A. Fert, and M. Chshiev,  arXiv:1704.09023.

\bibitem {iDMI-exp12}
M. Ba\'{c}ani, M. A. Marioni, J. Schwenk, and H. J. Hug, arXiv:1609.01615.

\bibitem {iDMI-exp13}
X. Ma, G. Yu, S. A. Razavi, S. S. Sasaki, X. Li, K. Hao, S. H. Tolbert, K. L. Wang, and X. Li, Phys. Rev. Lett. \textbf{119}, 027202 (2017).

\bibitem {AFM-iDMI-exp1}
M. Belmeguenai, H. Bouloussa, Y. Roussigné, M. S. Gabor, T. Petrisor, jr., C. Tiusan, H. Yang, A. Stashkevich, and S. M. Ch\'{e}rif,  Phys. Rev. B \textbf{96}, 144402 (2017).

\bibitem {AFMDMI-exp}
G. Gitgeatpong, Y. Zhao, P. Piyawongwatthana, Y. Qiu, L. W. Harriger, N. P. Butch, T. J. Sato, and K. Matan, Phys. Rev. Lett. \textbf{119}, 047201 (2017).

\bibitem {iDMI-abinitio1}
L. Udvardi and L. Szunyogh, Phys. Rev. Lett. \textbf{102}, 207204 (2009).

\bibitem {iDMI-abinitio2}
J. Gayles, F. Freimuth, T. Schena, G. Lani, P. Mavropoulos, R. A. Duine, S. Bl\"{u}gel, J. Sinova, and Y. Mokrousov, Phys. Rev. Lett. \textbf{115}, 036602 (2015).

\bibitem {AFM-review}
T. Jungwirth, J. Sinova, A. Manchon, X. Marti, J. Wunderlich, and C. Felser, arXiv:1705.10489; O. Gomonay, T. Jungwirth, and J. Sinova, Phys. Status Solidi RRL \textbf{11}, 1700022 (2017); T. Jungwirth, X. Marti, P. Wadley, and J. Wunderlich, Nat. Nanotechnol. \textbf{11}, 231 (2016).

\bibitem {AFM-review1}
V. Baltz, A. Manchon, M. Tsoi, T. Moriyama, T. Ono, and Y. Tserkovnyak, Rev. Mod. Phys. \textbf{90}, 015005 (2018).

\bibitem {Interface-review}
F. Hellman, A. Hoffmann, Y. Tserkovnyak, G. Beach, E. Fullerton, C. Leighton, A. MacDonald, D. Ralph, D. Arena, H. Durr, P. Fischer, J. Grollier, J. Heremans, T. Jungwirth, A. Kimmel, B. Koopmans, I. Krivorotov, S. May, A. Petford-Long, J. Rondinelli, N. Samarth, I. Schuller, A. Slavin, M. Stiles, O. Tchernyshyov, A. Thiaville, and B. Zink, Rev. Mod. Phys. \textbf{89}, 25006 (2017).

\bibitem {Manchon-Rashba2}
S. Grytsyuk, A. Belabbes, P. M. Haney, H-W. Lee, K-J. Lee, M. D. Stiles, U. Schwingenschl\"{o}gl, and A. Manchon, Phys. Rev. B \textbf{93}, 174421 (2016).

\bibitem {AHE}
N. Nagaosa, J. Sinova, S. Onoda, and A. H. MacDonald, N. P. Ong, Rev. Mod. Phys. \textbf{82}, 1539 (2010).

\bibitem {Alireza-Rashba1}
A. Qaiumzadeh and M. Titov, Phys. Rev. B \textbf{94}, 014425 (2016).

\bibitem {Rashba-anisotropy}
K-W. Kim, K-J. Lee, H-W. Lee, and M. D. Stiles, Phys. Rev. B \textbf{94}, 184402 (2016).

\bibitem {sd-model-referee-suggested}
J. Schliemann, Phys. Rev. B \textbf{67}, 045202 (2003); A. Auerbach, \textit{Interacting Electrons and Quantum Magnetism} (Springer, New York, 1998).

\bibitem{Fechner2012}
A. D. Caviglia, M. Gabay, S. Gariglio, N. Reyren, C. Cancellieri, and J.-M. Triscone, Phys. Rev. Lett. \textbf{104}, 126803 (2010).

\bibitem {Mokrousov}
F. Freimuth, S. Bl\"{u}gel, and Y. Mokrousov, Phys. Rev. B \textbf{96}, 054403 (2017); J. Phys. Condens. Matter. \textbf{26}, 104202 (2014).

\bibitem {Tatara}
T. Kikuchi, T. Koretsune, R. Arita, and G. Tatara, Phys. Rev. Lett. \textbf{116}, 247201 (2016).

\bibitem {kzero}
In general, the effective action has two extra terms related to the spin susceptibilities with a long wavelength nature, i. e., $\bm{k}=0$, which have no contributions in the exchange stiffness and DM interaction:
$\Delta \mathcal{S}^{\mathrm{eff}}_{0}[\bm{n}]=\hbar\beta\left(\delta n^a \chi^{a}+\sum_{l}\delta n^a_{\nu_l} \Pi^{ab}_{i\nu_l} \delta n^b_{-\nu_l}\right)$. The static spin susceptibility related to the first-order term in $\delta n^a$ is $\chi^{a}=(J_{\mathrm{sd}}/\hbar\beta)\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}]$, and the dynamic spin susceptibility related to the second-order term in $\delta n^a$ is
$\Pi^{ab}_{i\nu_l}=\sum_{\bm{q},n}\big\{-(J_{\mathrm{sd}}/2\hbar\beta)\mathrm{Tr}[\Gamma_x G^0_{\bm{q},i\omega_{n}}]\delta_{ab}+(J^2_{\mathrm{sd}}/2\hbar\beta)\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}\Gamma_b G^0_{\bm{q},i\omega_{n}+i\nu_l}]\big\}$, where $\delta_{ab}$ is the Kronecker delta function.

\bibitem {RashbaFM-DMI}
I. A. Ado, A. Qaiumzadeh, R. A. Duine, A. Brataas, and M. Titov, arXiv:1804.03739.

\bibitem {iDMI-theory-TI1}
R. Wakatsuki, M. Ezawa, and N. Nagaosa, Sci. Rep. \textbf{5}, 13638 (2015); T. Koretsune, N. Nagaosa, and R. Arita, \textit{ibid} \textbf{5}, 13302 (2015).

\bibitem {iDMI-theory-TI2}
Y. Tserkovnyak, D. A. Pesin, and D. Loss, Phys. Rev. B \textbf{91}, 041121(R) (2015).

\bibitem {AFM-iDMI-DFT-2}
S. Meyer, B. Dup\'{e}, P. Ferriani, and S. Heinze, Phys. Rev. B \textbf{96}, 094408 (2017); A. Belabbes, G. Bihlmayer, F. Bechstedt, S. Bl\"{u}gel, and A. Manchon, Phys. Rev. Lett. \textbf{117}, 247202 (2016).

\end{thebibliography}

\end{document}

### 2019-01-22 Paper/paper.tex
paper

--- 2019-01-22 Paper/example.tex
@@
 \newcommand{\dd}{\displaystyle}
-\newcommand{\bb}{\boldsymbol}
+\newcommand{\bs}{\boldsymbol}
 \newcommand{\h}{^\dagger}
@@
 \begin{document}
-\title{Theory of the Interfacial Dzyaloshinskii-Moriya Interaction in Rashba Antiferromagnets}
-
-\author{Alireza Qaiumzadeh}
-\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
-
-\author{Ivan A. Ado}
-\affiliation{Radboud University, Institute for Molecules and Materials, 6525 AJ Nijmegen, Netherlands}
-
-\author{Rembert A. Duine}
-\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
-\affiliation{Institute for Theoretical Physics and Center for Extreme Matter and Emergent Phenomena,
-Utrecht University, Princetonplein 5, 3584 CC Utrecht, Netherlands}
-\affiliation{Department of Applied Physics, Eindhoven University of Technology,
-P.O. Box 513, 5600 MB Eindhoven, Netherlands}
-
-\author{Mikhail Titov}
-\affiliation{Radboud University, Institute for Molecules and Materials, 6525 AJ Nijmegen, Netherlands}
-\affiliation{ITMO University, Saint Petersburg 197101, Russia}
-
-\author{Arne Brataas}
-\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
+\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–Moriya interactions in antiferromagnetic insulators}
 
 \begin{abstract}
-In antiferromagnetic (AFM) thin films, broken inversion symmetry or coupling to adjacent heavy metals can induce Dzyaloshinskii-Moriya (DM) interactions.
-Knowledge of the DM parameters is essential for understanding and designing exotic spin structures, such as hedgehog Skyrmions and chiral N\'{e}el walls, which are attractive for use in novel information storage technologies.
-We introduce a framework for computing the DM interaction in two-dimensional Rashba antiferromagnets.
-Unlike in Rashba ferromagnets, the DM interaction is not suppressed even at low temperatures.
-The material parameters control both the strength and sign of the interfacial DM interaction.
-Our results suggest a route toward controlling the DM interaction in AFM materials by means of doping and electric fields.
+This is the abstract.
 \end{abstract}
@@
 
-Relativistic spin-orbit coupling (SOC) is the foundation of spin orbitronics, a rapidly developing branch of spintronics \cite{Manchon-Rashba1, Fert-Rashba3}.
-Anisotropic magnetoresistance \cite{Thomson} and the anomalous Hall effect \cite{Hall} are established SOC transport phenomena.
-More recent discoveries include the spin Hall and inverse spin Hall effects \cite{SHE}, topological surface states \cite{Fert-Rashba3,TSS1,TSS2}, spin-orbit torques \cite{Manchon-Rashba1, ManchonSOT, Alireza-Rashba2, AFM-Hamiltonian1, AFM-Hamiltonian2}, and chiral domain walls and Skyrmions \cite{skyrmion2009,Hoffmann,Emori,Thiaville,Alireza-skyrmion,Alireza-AFM1,Yudin}.
-These phenomena are essential to enable novel ultrafast, nonvolatile, nanoscale spin-based storage and computation devices.
+\begin{section}{Model and calculations}
 
-%%%%%%%%%%%
-% Fig. 1: fig:setup
-%%%%%%%%%%%
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{Fig1new.eps}
-\caption{(a) The Rashba-AFM model is a model for systems with inversion asymmetry: an AFM/HM bilayer (left) and an AFM thin film asymmetrically embedded between two different insulator layers (right).
-(b) , (c) Electronic dispersion relations in the limit of strong exchange coupling (b) and in the limit of high SOC (c).
-The superscript $\eta=\pm$ refers to the conduction (blue) and valence (red) bands, whereas the superscript $s=\pm$ specifies chiral bands.
-In these two extreme limits, the band structure is almost isotropic for an AFM system with in-plane anisotropy.}
-\label{fig:setup}
-\vspace*{-6pt}
-\end{figure}
-%%%%%%%%%%%
+We will start we a general Hamiltonian:
 
-The Dzyaloshinskii-Moriya (DM) interaction between localized spins in a magnetic material is induced by SOC \cite{Dzyaloshinsky, Moriya}.
-The DM interaction is important for stabilizing noncollinear magnetic structures in ferromagnets.
-The original proposal by Dzyaloshinskii and Moriya, however, concerned antiferromagnetic (AFM) systems with weak magnetization, i.e., weak ferromagnets; this weak magnetism can be explained in terms of antisymmetric exchange, which is also referred to as the DM interaction.
+\begin{equation}
+\hat{H} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}\hat{D}
+\end{equation}
 
-The energy associated with the DM interaction between two neighboring spins in a lattice, $\bm{S}_{1}$ and $\bm{S}_{2}$, can be written in the form of the mixed product $\mathcal{H}_{DM}=-\bm{D}_{12} \cdot \bm{S}_1 \times \bm{S}_2$, where $\bm{D}_{12}$ is called the DM vector.
-The DM interaction, therefore, favors a perpendicular orientation of neighboring spins.
-By contrast, the Heisenberg exchange interaction $\mathcal{H}_{\mathrm{ex}}=J_{\mathrm{ex}} \bm{S}_1 \cdot \bm{S}_2$ favors a collinear magnetic order, which can be either ferromagnetic (FM) for $J_{\mathrm{ex}}<0$ or AFM for $J_{\mathrm{ex}}>0$.
-The competition between the Heisenberg exchange interaction and the DM interaction leads to the formation of exotic structures such as chiral domain walls, helices, and Skyrmions \cite{Fert-Rashba3}.
+Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
+The hopping term $-\hat{T} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$ can describe various models.
+We will be interested in:
 
-In the bulk of a noncentrosymmetric magnetic crystal, the DM vector points along one of the lattice vectors and gives rise to so-called Bloch-like structures \cite{Dzyaloshinsky, Moriya, iDMI5}.
-In an ultrathin magnetic film with impurity- or interface-induced SOC, there is also an interfacial DM interaction that corresponds to a DM vector pointing out along the interface.
-This gives rise to so-called N\'{e}el-type textures \cite{iDMI1,iDMI2,iDMI3,iDMI4,iDMI5,Thiaville, iDMI7}.
-Both the sign and the amplitude of the DM vector are of critical importance for observing and engineering different chiral structures \cite{iDMI-exp0,katsnelson,iDMI-exp1,iDMI-exp2,iDMI-exp3,iDMI-exp4,iDMI-exp5,iDMI-exp6,iDMI-exp7,iDMI-exp8,iDMI-exp9,iDMI-exp10,iDMI-exp11,iDMI-exp12, AFMDMI-exp,iDMI-abinitio1,iDMI-abinitio2}.
+\begin{itemize}
+	\item The Hubbard model, in which the hopping does not change the spin, $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'}t$ for $i,j$ NN and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
+	\item The so-called Kane-Mele-Hubbard model, which includes a spin-dependent term araising from spin-obit interactions.
+	\begin{equation}
+t_{ij}^{\sigma \sigma'} = \begin{cases}
+	\delta_{\sigma \sigma'}t_1 & \text{for } i, j \text{ nearest neighbors} \\
+	-\Delta \nu_{ij} \hat{e}_z \cdot \bs{\sigma}_{\sigma, \sigma'} & \text{for } i, j \text{ next nearest neighbors} \\
+	0 & \text{ otherwise} \n
+\end{cases} \quad
+\end{equation}
+\end{itemize}
 
-AFM materials have recently attracted considerable attention as active spintronics elements \cite{AFM-review,AFM-review1}.
-The absence of stray fields, the possibility of operating at terahertz frequencies, and the existence of spin waves with opposite helicities make antiferromagnets promising candidates for use in the next generation of spin-based memory and processing devices \cite{AFM-review,AFM-review1} with a nanoscale element base.
+The only assumption we will make about $\hat{T}$ is that it is proportional to any power of $\hat{p}$ in which case we can apply the Peierls substitution (\ref{AP3A}) to introduce to take into account the effect of the electromagnetic perturbation in the lattice.
+The strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
 
-The coexistence of strong SOC and spin ordering at the interfaces of AFM/heavy-metal (HM) bilayers makes such heterostructures particularly promising for low-dimensional spin orbitronics applications \cite{Interface-review}.
-An AFM thin film sandwiched between insulators is also a common functional geometry for spin-orbitronics due to interfacial SOC.
-The interfacial SOC in such a system is effectively described by Rashba SOC \cite{Manchon-Rashba2}.
-For magnetic films, the two-dimensional (2D) Rashba model captures the main physics and trends of SOC with a broken inversion symmetry \cite{Manchon-Rashba2}, such as fieldlike and dampinglike spin-orbit torques \cite{Manchon-Rashba1, Alireza-Rashba2, AFM-Hamiltonian1}, intrinsic spin Hall effects \cite{SHE}, intrinsic anomalous Hall effects \cite{AHE}, inverse Faraday effects \cite{Alireza-Rashba1}, and magnetic anisotropy \cite{Rashba-anisotropy}.
-
-In this Letter, we develop a framework for computing the interfacial DM interaction in AFM layers with inversion asymmetry.
-The typical system illustrated in Fig.~\ref{fig:setup} is described on the basis of an effective 2D AFM-Rashba Hamiltonian.
-We find that both the sign and the magnitude of the DM vector depend on the ratio relating three energy scales: the chemical potential, the \textit{s-d} exchange interaction, and the Rashba SOC strength.
-In particular, the strong dependence on the chemical potential suggests that the DM interaction can be tuned by modifying the electron density by means of doping or voltage gating \cite{Fechner2012}.
-
-A generic effective 2D Hamiltonian describing itinerant electrons in the AFM layer [see Fig.~\ref{fig:setup}(a)] can be written as
-\begin{align}
-\mathcal{H}=\mathcal{H}_{\mathrm{kin}}+\mathcal{H}_{\mathrm{sd}}+\mathcal{H}_{\mathrm{so}}, \label{hamiltonian}
-\end{align}
-where $\mathcal{H}_{\mathrm{kin}}$ is the kinetic energy of the electrons, $\mathcal{H}_{\mathrm{sd}}=J_{\mathrm{sd}}\,\bm{n} \cdot \bm{\Gamma}$ describes an effective interaction with a strength $J_{\mathrm{sd}}$ between the spins of the itinerant $s$ electrons and the localized $d$ electrons \cite{sd-model-referee-suggested}, and $\mathcal{H}_{\mathrm{SO}}$ describes the SOC.
-The operator $\bm{\Gamma}$ is the direct product of the electron spin operator and the sublattice position operator, which, in the case of an AFM system, accounts for the effects of sublattice staggering.
-The unit vector $\bm{n}$ is the order parameter, which can represent either the total magnetization in a ferromagnet or the staggered magnetization in an antiferromagnet.
-
-We compute the electronic contributions to the DM interaction parameter $D$ and to the exchange stiffness $A$ in the following way.
-First, we evaluate how the itinerant electrons influence the magnetic subsystem by finding an effective action.
-We expand the effective action up to linear order with respect to the deviation of the spins from their equilibrium direction.
-The corresponding susceptibility tensor describes the influence of the electronic degrees of freedom on the localized magnetic moments.
-A linear expansion of the susceptibility tensor in spatial gradients of $\bb{n}$ defines the DM interaction strength $D$.
-The contribution of the itinerant electrons to the exchange stiffness $A$ is extracted from the second-order expansion in spatial gradients.
-
-The action $\mathcal{S}$ defines the system partition function $\mathcal{Z}=\int d[\Phi^*] d[\Phi] d[\bm{n}] e^{-\mathcal{S}[\Phi^*,\Phi,\bm{n}]/\hbar}$, where $\Phi$ is the Grassmannian coherent-state spinor and $\hbar$ is Planck's constant.
-In the $s$-$d$ approach to magnetic systems, the action is decomposed into the sum $\mathcal{S}=\mathcal{S}_F+\mathcal{S}_B$, where $\mathcal{S}_F[\Phi^*,\Phi,\bm{n}]$ is the fermionic action corresponding to the Hamiltonian of Eq.~(\ref{hamiltonian}), which also includes the $s$-$d$ coupling, and $\mathcal{S}_B[\bm{n}]$ is the bosonic action describing the dynamics of the localized spins (magnons) in the absence of itinerant electrons.
-In our model, it is the coupling between the itinerant electrons and the local moments that determine the DM interaction, which is also directly linked to the SOC of the itinerant electrons.
-We will not specify the bosonic part of the action $\mathcal{S}_B[\bm{n}]$ since it is irrelevant for the subsequent discussion.
-
-The fermionic action reads
-\be
-\mathcal{S}_F\!=\!\int\!\!\!\int_0^{\hbar\beta}\!\!d\tau d\tau'\!\! \int\!\!\!\int\! d{\bm{r}} d{\bm{r}}' \Phi^*_{\bm{r},\tau} [-\hbar  G^{-1}_{\bm{r},\tau;\bm{r}',\tau'}] \Phi_{\bm{r}',\tau'},
-\e
-where $\beta=1/k_B T$ is the inverse temperature and $\tau$ is the imaginary time.
-The inverse Green's function operator is  $\hbar\, G^{-1}_{\bm{r},\tau;\bm{r}',\tau'}=-\left(\hbar{\partial_\tau}+\mathcal{H}\right)\delta(\bm{r}-\bm{r}')\delta(\tau-\tau')$ in terms of the Hamiltonian of Eq.~(\ref{hamiltonian}).
-We compute the effective theory for the vector field $\bb{n}(\bb{r})$ by integrating out the fermionic degrees of freedom.
-This standard procedure results in an additional, effective contribution to the bosonic action of the form $\Delta \mathcal{S}_F^{\mathrm{eff}}[\bm{n}]=\int_0^{\hbar\beta} d\tau \int d{\bm{r}} \left(-\hbar \mathrm{Tr}[\ln(-G^{-1})]\right)$.
-Below, we analyze $\Delta \mathcal{S}_F^{\mathrm{eff}}[\bm{n}]$ and its influence on the magnet in the AFM-Rashba model.
-
-%%%%%%%%%%%%%%
-%Fig 2 %%%%%%% fig:diag
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{Fig2.eps}
-\caption{ (a) The Feynman diagram corresponding to Eq.~(\ref{polarizibility-pi}) for a single-loop polarizability tensor.
-(b) The Feynman diagram corresponding to Eq.~(\ref{DMI-formula22}), describing the interfacial DM interaction for a system with inversion symmetry breaking in the $z$ direction and an order parameter vector $\bm{n}$ in the $x$ direction.}
-\label{fig:diag}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In our system, the symmetry-breaking direction ($z$ direction) is perpendicular to the plane \cite{iDMI-exp3}.
-Without the loss of generality, we choose the $x$ axis to be in the direction of the in-plane vector field $\bb{n}$.
-A small deviation of the unit vector from its equilibrium direction is, then, parameterized by $\bm{n}=\hat{\bb{x}}+\delta\bm{n}$, where $\delta\bm{n}=\left( -(\delta n^2_y+\delta n^2_z)/2, \delta n_y, \delta n_z \right)$.
-The effective action is obtained from a perturbation with respect to $\delta \bb{n}$, \cite{sd-model-referee-suggested} that holds irrespective of the value of the exchange strength $J_{sd}$.
-The effective action is conveniently established from the Dyson equation, $G^{-1}={G^0}^{-1}-\Sigma$, where the unperturbed Green's function refers to $\delta\bb{n}=0$ and the self-energy $\hbar \Sigma=J_{\mathrm{sd}}\delta\bm{n}\cdot\bm{\Gamma}\, \delta(\bm{r}-\bm{r}')\delta(\tau-\tau')$ is introduced.
-
-Computing the self-energy up to the second order in $\delta\bm{n}$ yields \cite{kzero}
-\begin{align}
-\label{eff-action4}
-\Delta \mathcal{S}^{\mathrm{eff}}[\bm{n}]=\hbar\beta\sum_{\bm{k}\neq 0,l}\delta n^a_{\bm{k},\nu_l} \Pi^{ab}_{\bm{k},i\nu_l} \delta n^b_{-\bm{k},-\nu_l},
-\end{align}
-where the indices $a, b=(y,z)$ denote the transverse vector components with respect to the equilibrium $\hat{\bb{x}}$ direction, $\nu_l=2 n\pi/ \beta$ denotes the bosonic Matsubara frequencies, and
-\be
-\label{polarizibility-pi}
-\Pi^{ab}_{\bm{k},i\nu_l}=\frac{J^2_{\mathrm{sd}}}{2\hbar\beta}\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}\Gamma_b G^0_{\bm{q}+\bm{k},i\omega_{n}+i\nu_l}]
-\e
-is the dynamical susceptibility tensor, pictured schematically in Fig.~\ref{fig:diag}a.
-Here, $G^0_{\bm{q},i\omega_{n}}=(i\hbar\omega_n-\mathcal{H})^{-1}$ is the equilibrium Green's function, and the $\omega_n=(2 n+1)\pi/ \beta$ are the fermionic Matsubara frequencies.
-We compute the sum over the fermionic Matsubara frequencies by using the identity $\sum_n (i \hbar\omega_n-E)^{-1}/\beta=f(E)$, where $f(E)$ is the Fermi distribution.
-
-By expanding the static limit, $\nu_l=0$, on the spin susceptibility to the second order in the wave vector $\bm{k}$, we find both the electronic contribution to the symmetric Heisenberg exchange stiffness, which is determined by the symmetric terms in the diagonal elements of the susceptibility tensor, and the antisymmetric exchange interaction (DM interaction), which is determined by the antisymmetric terms in the off-diagonal elements.
-From the partition function of the canonical ensemble, $\mathcal{Z}=\int d[{\bm{n}}] e^{-\mathcal{S}^{\mathrm{eff}}[\bm{n}]/\hbar}=\int d[{\bm{n}}] e^{-\beta F[{\bm{n}}]}$, we obtain $\delta_{{\bm{n}}}\mathcal{S}^{\mathrm{eff}}/\hbar =\beta\delta_{\bm{n}} F[{\bm{n}}]$, where the micromagnetic free energy, including the stiffness and the DM interaction, is $F[{\bm{n}}]=\int d^2\bm{r} \left(A (\nabla {\bm{n}})^2-D {\bm{n}}\cdot(\hat{\bb{z}}\times \nabla)\times {\bm{n}}\right)$.
-By comparing the microscopic free energy with the expression for the effective action, Eq.
-(\ref{eff-action4}), we define the micromagnetic parameters $A$ and $D$, which characterize the free carrier contributions to the exchange stiffness and the DM interaction, respectively.
-
-Upon expanding the off-diagonal elements of the tensor $\Pi$ to the first order in the wave vector $\bm{k}$ [see Fig.~\ref{fig:diag}(b)], we obtain the relation
-\begin{subequations}
-\label{DMI-formula22}
-\begin{align}
-D=&\lt.i\frac{\partial\Pi^{yz}_{\bm{k}}}{\partial {k_y}} \rt|_{\bm{k}=0}=-\lt.i\frac{\partial\Pi^{zy}_{\bm{k}}}{\partial {k_y}} \rt|_{\bm{k}=0}\\
-\label{DMI-formula2}
-=&i\frac{J^2_{\mathrm{sd}}}{2\beta}\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_y G^0_{\bm{q},i\omega_{n}}\Gamma_z G^0_{\bm{q},i\omega_{n}}v_y G^0_{\bm{q},i\omega_{n}}],
-\end{align}
-\end{subequations}
-where $v_y=\hbar^{-1}\partial \mathcal{H}_{\bm{q}}/\pa q_y$ is the $y$ component of the velocity operator. From the second-order terms, we obtain the electron contribution to the exchange stiffness:
-\begin{align}
-\label{stiffness}
-A=&-\lt.\frac{\partial^2\Pi^{yy}_{\bm{k}}}{\partial {k^2_x}} \rt|_{\bm{k}=0}=-\lt.\frac{\partial^2\Pi^{zz}_{\bm{k}}}{\partial {k^2_y}} \rt|_{\bm{k}=0} \, .
-\end{align}
-In our model, $A$ describes the contribution to the AFM exchange interaction from a superexchange-type interaction between the localized spins in the AFM layer via the itinerant spins.
-
-We should emphasize here that in this approach, we have ignored the spin fluctuations of the localized AFM spins, which is a valid omission as long as the system temperature is much less than the critical N\'{e}el temperature.
-
-To model an AFM system with interfacial SOC, we use the 2D AFM-Rashba Hamiltonian \cite{AFM-Hamiltonian1,AFM-Hamiltonian2} on a square lattice:
-\begin{align}
-\label{hamiltonian-AFM}
-\mathcal{H}= \gamma_k \tau_x\sigma_0+J_{\mathrm{sd}} \tau_z\bm{\sigma}\cdot\bm{n}-\alpha_R \tau_x(\bm{\sigma}\times\bm{k})\cdot\hat{\bb{z}},
-\end{align}
-where $\bb{\sigma}$ and $\bb{\tau}$ are the vectors of Pauli matrices representing the spin and AFM sublattice degree of freedom, respectively; $\sigma_0$ is the identity matrix; $\bm{n}$ is the staggered order parameter (the normalized N\'{e}el vector); and $\alpha_R$ is the strength of the Rashba SOC.
-The kinetic energy of the itinerant electrons is $\gamma_k=a^2 t(k^2-k^2_0)$, where $t$ is the nearest-neighbor hopping energy and $k_0=2/a$, with $a$ being the lattice constant.
-
-The band structure of the AFM-Rashba Hamiltonian of Eq.~(\ref{hamiltonian-AFM}) is, in general, anisotropic. It is convenient to parameterize the four spectral branches as follows:
-\be
-\label{energy-AFM}
-E^{s,\eta}_k=\eta \sqrt{\gamma^2_k+J^2_{\mathrm{sd}}+\alpha^2_R k^2+2 s \alpha_R k \xi_k},
-\e
-where $s, \eta=\pm 1$ are the spin chirality and electron/hole band indices, respectively.
-We also introduce $\xi_k=\lt(\gamma^2_k+J^2_{\mathrm{sd}} \cos^2\phi\rt)^{1/2}$ with the in-plane wave vector $\bm{k}$ parameterized by the angle $\phi$, such that $\bm{k}=k(\cos\phi,\sin\phi,0)$.
-
-%%%%%%%%%%%%%%
-%% Fig. 3  fig:results
-%%%%%%%%%%%%%%
-\begin{figure}[t]
-\includegraphics[width=8cm]{Fig3a.eps}
-\includegraphics[width=8cm]{Fig3b.eps}
-\caption{Numerical results for the DM interaction as a function of the Fermi energy (top) and of the SOC strength (bottom) for different values of the \textit{s-d} exchange interaction.
-We set $\epsilon_F=2$ eV and $t=3$ eV in all cases.}
-\label{fig:results}
-\end{figure}
-%%%%%%%%%%%%%%
-
-Let us now analyze the expressions of Eqs.~(\ref{DMI-formula22}) and (\ref{stiffness}) for the AFM-Rashba Hamiltonian of Eq.~(\ref{hamiltonian-AFM}) in the limit of weak spin-orbit interaction, $\{k_0 \alpha_R, J_\mathrm{sd}\} \ll \min\{t, \epsilon_F\}$, and at zero temperature.
-Using the relation $\Gamma_a=\tau_z\sigma_a$, we obtain the relation
-\begin{align}
-\label{DMI-AFM-weakSO}
-D = -\left(\frac{A k^2_0}{4 t}\right)\alpha_R ,
-\end{align}
-where the stiffness parameter is
-\be
-\label{A-AFM-weakSO}
-A = \frac{t J^2_{\mathrm{sd}}}{2 \pi \epsilon^2_F}
-\bc
-2-\epsilon^2_F/16 t^2,& \epsilon_F < 4t, \\
-1,& \epsilon_F > 4t,
-\ec
-\e
-which is manifestly independent of the SOC strength in the limit of weak spin-orbit interaction.
-Here, the Fermi energy $\epsilon_F$ is measured with respect to the center of the energy gap [see Figs.~\ref{fig:setup}(b) and (c)].
-In this regime, the energy gaps at $k=0$ and $k=\pm k_0$ are equal to $8t$ and $2J_{\mathrm{sd}}$, respectively.
-
-For the case in which the Fermi energy lies within the band gap, i.\,e., for $|\epsilon_F| < J_{\mathrm{sd}}$,  and in the limit of $k_0 \alpha_R \ll J_{\mathrm{sd}} \ll t$, we obtain
-\begin{align}
-\label{DMI-AFM3}
-D =\left(\frac{k^2_0}{2\pi}\right) \alpha_R,
-\end{align}
-which is of the opposite sign compared with the metallic regime of Eqs.~(\ref{DMI-AFM-weakSO}) and (\ref{A-AFM-weakSO}).
-
-It is instructive to compare the results of Eqs.~(\ref{DMI-AFM-weakSO})-(\ref{DMI-AFM3}) with those for a Rashba-FM system \cite{RashbaFM-DMI}.
-If both FM chiral bands are occupied ($\epsilon_F> J_{\mathrm{sd}}$), the interfacial DM interaction in the Rashba-FM model vanishes at zero temperature due to the exact cancellation between the Fermi surface and Fermi sea contributions \cite{RashbaFM-DMI}.
-However, such a cancellation is absent in the AFM-Rashba model, giving rise to a finite result for Eq.~(\ref{DMI-AFM-weakSO}), by virtue of an additional contribution from the valence bands.
-For $\epsilon_F < J_{\mathrm{sd}}$, i.\,e., when only the lowest FM chiral band is occupied, the DM interaction in the weak SOC limit and at zero temperature is finite and linearly proportional to $A$ \cite{iDMI7, Mokrousov, Tatara,RashbaFM-DMI}.
-
-On the other hand, in the Dirac model of an FM/topological-insulator bilayer characterized by the Hamiltonian of the Rashba SOC symmetry, the DM interaction vanishes inside the gap but remains finite outside the gap, even at zero temperature\cite{iDMI-theory-TI1,iDMI-theory-TI2}.
-Thus, we conclude that the DM interaction exhibits a qualitatively different behavior in antiferromagnets compared with that in ferromagnets.
-
-In Fig.~\ref{fig:results}, we illustrate the behavior of the DM interaction on the basis of a numerical analysis of Eq.~(\ref{DMI-formula2}) beyond the weak SOC regime of Eqs.~(\ref{DMI-AFM-weakSO}-\ref{DMI-AFM3}), where typical material parameters are assumed: $t=3$~eV, $\epsilon_F=2$~eV, $J_{\mathrm{sd}}=1$~eV, $a=0.4$~nm and $k_0\alpha_R=0.1$~eV \cite{AFM-Hamiltonian1}.
-The results indicate a rather large interfacial DM interaction, with $D\simeq -1.6$~pJ/m.
-Moreover, when the Fermi energy lies within the gap, i.\,e., $|\epsilon_F| < J_{\mathrm{sd}}$, we find an order-of-magnitude enhancement of the DM interaction with the opposite sign, $D\simeq 12.7$~pJ/m.
-Importantly, the estimated strength of the DM interaction is at least an order of magnitude larger than that for a Rashba-FM layer with the same parameters \cite{RashbaFM-DMI}.
-
-For small Fermi energies, the DM interaction is positive and almost independent of the Fermi energy (see the top panel in Fig.~\ref{fig:results}), as might be expected from Eq.~(\ref{DMI-AFM3}).
-In the metallic regime (i.\,e., for Fermi energies well above the gap), the DM interaction is negative, and its strength decreases in proportion to $\epsilon_F^{-2}$, in good agreement with Eqs.~(\ref{DMI-AFM-weakSO}) and (\ref{A-AFM-weakSO}).
-The sign inversion of the DM interaction is rather sharp and occurs at $\epsilon_F=\sqrt{J^2_{\mathrm{sd}}+\alpha^2_R k^2_0}$.
-The bottom panel of Fig.~\ref{fig:results} also confirms that the strength of the DM interaction is linearly proportional to $\alpha_R$ in the weak SOC regime, in agreement with Eq.~(\ref{DMI-AFM-weakSO}).
-Thus, we conclude that the DM interaction in an AFM material may vary by orders of magnitude depending on the material parameters, as illustrated in Fig.~\ref{fig:results}.
-
-Our calculations also show that, unlike in FM-Rashba systems \cite{RashbaFM-DMI}, the temperature dependence of the DM interaction in the AFM-Rashba model of Eq.~(\ref{hamiltonian-AFM}) is weak due to a large contribution to the DM interaction from the valence bands (not shown).
-As we have already discussed, this is correct if the system temperature is much less than the N\'{e}el temperature, i.\,e., in a regime in which the spin fluctuations of the AFM layer are suppressed.
-
-Controlling the DM interaction is essential for engineering chiral magnetic structures.
-If the DM interaction parameter exceeds a certain critical value, which is determined by the Heisenberg exchange interaction and the uniaxial anisotropy, then the ground state changes from a collinear configuration to either a helimagnetic state or a Skyrmion lattice.
-A weaker DM interaction enables the stabilization of isolated Skyrmions in a metastable state \cite{Alireza-skyrmion,Yudin}.
-In chiral magnets, the sign of the DM interaction determines the direction, or handedness, of spin rotation.
-
-The asymmetry of the spin-wave dispersion in spin-polarized electron energy-loss spectroscopy and Brillouin light scattering is a measure of the DM interaction in FM systems \cite{iDMI-exp0,iDMI-exp2,AFM-iDMI-exp1}.
-Although the interfacial DM interactions in a few FM/HM bilayers have been experimentally studied in recent years \cite{iDMI-exp1,iDMI-exp2,iDMI-exp3,iDMI-exp4,iDMI-exp5,iDMI-exp6,iDMI-exp7,iDMI-exp8,iDMI-exp9,iDMI-exp10,iDMI-exp11,iDMI-exp12,iDMI-exp13,AFM-iDMI-exp1}, we are not aware of similar measurements in AFM heterostructures.
-However, the first observation of a bulk DM interaction in an AFM system, namely, the noncentrosymmetric $\alpha-\mathrm{Cu_2V_2O_7}$, has recently been reported in Ref.
-\cite{AFMDMI-exp} based on inelastic neutron scattering.
-Very recently, a large DM interaction in Fe/Ir bilayers on Rh(001) has been predicted on the basis of {\em ab initio} calculations \cite{AFM-iDMI-DFT-2}.
-We hope that our work will stimulate new experiments and {\em ab initio} works on such AFM heterostructures.
-
-In summary, we have computed the DM interaction, both analytically and numerically, using an effective model for AFM layers with interfacial Rashba SOC.
-In the AFM-Rashba model, the induced interfacial DM interaction appears as a Lifshitz-type invariant term.
-Our results show that both the sign and the strength of the DM interaction may be tuned by modifying the electron density, e.\,g., by applying a gate voltage or through doping.
-This tunability implies that a rich variety of chiral magnetic structures can emerge in layered AFM/HM systems with different interfacial charge densities, \textit{s-d} exchange interactions, and SOC interactions.
+In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+In the simplest case, for example, the sum would be restricted to nearest neighbors and the hopping amplitude would be diagonal in the spin state.
+With this notation, in presence of a vector potential $\vec{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:
+\end{section}
 
 \section*{Acknowledgments}
-The research leading to these results was supported by the European Research Council via Advanced Grant No.
-669442, ``Insulatronics," and by the Research Council of Norway through its Centres of Excellence funding scheme, Project No.
-262633, ``QuSpin." We also acknowledge the support received from the Dutch Science Foundation, NWO/FOM 13PR3118; the European Commission; and the Russian Science Foundation under Project No.
-17-12-01359.
-R.
-A.
-D.
-is part of the D-ITP consortium, a program of the Netherlands Organisation for Scientific Research (NWO) that is funded by the Dutch Ministry of Education, Culture and Science (OCW).
-M.T.
-acknowledges support from an ITMO visiting professor fellowship.
 
 \begin{thebibliography}{9}
-
-\bibitem {Manchon-Rashba1}
-A. Manchon, H. C. Koo, J. Nitta, S. M. Frolov, and R. A. Duine, Nat. Mater. \textbf{14}, 871 (2015).
-
-\bibitem {Fert-Rashba3}
-A. Soumyanarayanan, N. Reyren, A. Fert, and C. Panagopoulos, Nature (London) \textbf{539}, 509 (2015).
-
-\bibitem {Thomson}
-W. Thomson, Proc. R. Soc. Lond. \textbf{8}, 546 (1857).
-
-\bibitem {Hall}
-E. Hall, Philos. Mag. \textbf{12}, 157 (1881).
-
-\bibitem {SHE}
-J. Sinova, S. O. Valenzuela, J. Wunderlich, C. H. Back, and T. Jungwirth, Rev. Mod. Phys. \textbf{87}, 1213  (2015).
-
-\bibitem {TSS1}
-P. Roushan, J. Seo, C. V. Parker, Y. S. Hor, D. Hsieh, D. Qian, A. Richardella, M. Z. Hasan, R. J. Cava, and A. Yazdani, Nature (London) \textbf{460}, 1106 (2009).
-
-\bibitem {TSS2}
-T. Zhang, P. Cheng, X. Chen, J-F. Jia, X. Ma, K. He, L. Wang, H. Zhang, X. Dai, Z. Fang, X. Xie, and Q-K. Xue, Phys. Rev. B \textbf{79}, 094422 (2009).
-
-\bibitem {ManchonSOT}
-A. Manchon and S. Zhang, Phys. Rev. B \textbf{79}, 094422 (2009).
-
-\bibitem {Alireza-Rashba2}
-A. Qaiumzadeh, R. A. Duine, and M. Titov, Phys. Rev. B \textbf{92}, 014402 (2015).
-
-\bibitem {AFM-Hamiltonian1}
-J. \v{Z}elezn\'{y}, H. Gao, A. Manchon, F. Freimuth, Y. Mokrousov, J. Zemen, J. Ma\v{s}ek, J. Sinova, and T. Jungwirth
-Phys. Rev. B \textbf{95}, 014403 (2017); J. \v{Z}elezn\'{y}, H. Gao, K. V\'{y}born\'{y}, J. Zemen, J. Ma\v{s}ek, A. Manchon, J. Wunderlich, J. Sinova, and T. Jungwirth,
-Phys. Rev. Lett. \textbf{113}, 157201 (2014).
-
-\bibitem {AFM-Hamiltonian2}
-H. B. M. Saidaoui and A. Manchon, arXiv:1606.04261.
-
-\bibitem {skyrmion2009}
-S. M\"{u}hlbauer, B. Binz, F. Jonietz, C. Pfleiderer, A. Rosch, A. Neubauer, R. Georgii, and P. B\"{o}ni, Science \textbf{323}, 915 (2009).
-
-\bibitem {Hoffmann}
-W. Jiang, G. Chen, K. Liu, J. Zang, S. G. E. te Velthuis, and A. Hoffmann, Phys. Rep. \textbf{704}, 1 (2017).
-
-\bibitem {Thiaville}
-A. Thiaville, S. Rohart, \'{E}. Ju\'{e}, V. Cros, and A. Fert, Europhys. Lett. \textbf{100}, 57002 (2012).
-
-\bibitem {Emori}
-S. Emori, U. Bauer, S-M. Ahn, E. Martinez, and G. S. D. Beach, Nat. Mater. \textbf{12}, 611 (2013).
-
-\bibitem {Alireza-skyrmion}
-V. Flovik, A. Qaiumzadeh, A. K. Nandy, C. Heo, and T. Rasing,  Phys. Rev. B, \textbf{96}, 140411(R) (2017).
-
-\bibitem {Alireza-AFM1}
-A. Qaiumzadeh, L. A. Kristiansen, and A. Brataas, Phys. Rev. B \textbf{97}, 020402(R) (2018).
-
-\bibitem{Yudin}
-D. Yudin, D. R. Gulevich, and M. Titov, Phys. Rev. Lett. \textbf{119}, 147202 (2017).
-
-\bibitem {Dzyaloshinsky}
-I. Dzyaloshinsky, J. Phys. Chem. Solids \textbf{4}, 241 (1958); J. Exp. Theor. Phys. \textbf{32}, 1547 (1957).
-
-\bibitem {Moriya}
-T. Moriya, Phys. Rev. \textbf{120}, 91 (1960); Phys. Rev. Lett. \textbf{4}, 228 (1960).
-
-\bibitem {iDMI5}
-M. Heide, G. Bihlmayer, and S. Bl\"{u}gel, Phys. Rev. B \textbf{78}, 140403(R) (2008).
-
-\bibitem {iDMI1}
-A. Fert, Mater. Sci. Forum \textbf{59-60}, 439 (1990); A. Fert and P. M. Levy, Phys. Rev. Lett.  \textbf{44}, 1538 (1980).
-
-\bibitem {iDMI2}
-A. N. Bogdanov and D. A. Yablonskii, Sov. Phys. JETP \textbf{68}, 101 (1989); \textbf{69}, 142 (1989).
-
-\bibitem {iDMI3}
-A. Cr\'{e}pieux and C. Lacroix, J. Magn. Magn. Mater. \textbf{182}, 341 (1998).
-
-\bibitem {iDMI4}
-A. N. Bogdanov and U. K. R\"{o}{\ss}ler, Phys. Rev. Lett. \textbf{87}, 037203 (2001).
-
-\bibitem {iDMI7}
-J-H.
-Moon, S-M.
-Seo, K-J.
-Lee, K-W.
-Kim, J.
-Ryu, H-W.
-Lee, R.
-D.
-McMichael, and M.
-D.
-Stiles, Phys.
-Rev.
-B \textbf{88}, 184404 (2013); K-W.
-Kim, H-W.
-Lee, K-J.
-Lee, and M.
-D.
-Stiles, Phys.
-Rev.
-Lett.
-\textbf{111}, 216601 (2013).
-
-\bibitem {iDMI-exp0}
-Kh.
-Zakeri, Y.
-Zhang, J.
-Prokop, T.-H.
-Chuang, N.
-Sakr, W.
-X.
-Tang, and J.
-Kirschner, Phys.
-Rev.
-Lett.
-\textbf{104}, 137203 (2010); Kh.
-Zakeri, Y.
-Zhang, T.-H.
-Chuang, and J.
-Kirschner, \textit{ibid} \textbf{108}, 197205 (2012).
-
-\bibitem {katsnelson}
-V. E. Dmitrienko, E. N. Ovchinnikova, S. P. Collins, G. Nisbet, G. Beutier, Y. O. Kvashnin, V. V. Mazurenko, A. I. Lichtenstein, and M. I. Katsnelson, Nat. Phys. \textbf{10}, 202 (2014).
-
-\bibitem {iDMI-exp1}
-A. K. Chaurasiya, C. Banerjee, S. Pan, S. Sahoo, S. Choudhury, J. Sinha, and A. Barman, Sci. Rep. \textbf{6}, 32592 (2016).
-
-\bibitem {iDMI-exp2}
-J. Cho, N-H. Kim, S. Lee, J-S. Kim, R. Lavrijsen, A. Solignac, Y. Yin, D-S. Han, N. J. J. van Hoof, H. J. M. Swagten, B. Koopmans, and C-Y. You, Nat. Commun. \textbf{6}, 7635 (2015).
-
-\bibitem {iDMI-exp3}
-M. Belmeguenai, J-P. Adam, Y. Roussign\'{e}, S. Eimer, T. Devolder, J-V. Kim, S. M. Cherif, A. Stashkevich, and A. Thiaville, Phys. Rev. B \textbf{91}, 180405(R) (2015).
-
-\bibitem {iDMI-exp4}
-H. S. K\"{o}rner, J. Stigloher, H. G. Bauer, H. Hata, T. Taniguchi, T. Moriyama, T. Ono, and C. H. Back, Phys. Rev. B \textbf{92}, 220413(R) (2015).
-
-\bibitem {iDMI-exp5}
-K. Di, V. L. Zhang, H. S. Lim, S. C. Ng, M. H. Kuok, J. Yu, J. Yoon, X. Qiu, and H. Yang, Phys. Rev. Lett. \textbf{114}, 047201 (2015).
-
-\bibitem {iDMI-exp6}
-H. Yang, A. Thiaville, S. Rohart, A. Fert, and M. Chshiev, Phys. Rev. Lett. \textbf{115}, 267210 (2015).
-
-\bibitem {iDMI-exp7}
-H. T. Nembach, J. M. Shaw, M. Weiler, E. Ju\'{e}, and T. J. Silva, Nat. Phys. \textbf{11}, 825 (2015).
-
-\bibitem {iDMI-exp8}
-A. Hrabec,  M. Belmeguenai,  A. Stashkevich,  S. M. Ch\'{e}rif,  S. Rohart,  Y. Roussign\'{e}, and  A. Thiaville, Appl. Phys. Lett. \textbf{110}, 242402 (2017).
-
-\bibitem {iDMI-exp9}
-R. M. Rowan-Robinson, A. A. Stashkevich, Y. Roussigne, M. Belmeguenai, S-M. Cherif, A. Thiaville, T. P. A. Hase, A. T. Hindmarch, and D. Atkinson, Sci. Rep. \textbf{7}, 16835 (2017).
-
-\bibitem {iDMI-exp10}
-X. Ma, G. Yu, X. Li, T. Wang, D. Wu, K. S. Olsson, Z. Chu, K. An, J. Q. Xiao, K. L. Wang, and X. Li, Phys. Rev. B \textbf{94}, 180408(R) (2016).
-
-\bibitem {iDMI-exp11}
-H. Yang, G. Chen, A. A. C. Cotta, A. T. N'Diaye, S. A. Nikolaev, E. A. Soares, W. A. A. Macedo, A. K. Schmid, A. Fert, and M. Chshiev,  arXiv:1704.09023.
-
-\bibitem {iDMI-exp12}
-M. Ba\'{c}ani, M. A. Marioni, J. Schwenk, and H. J. Hug, arXiv:1609.01615.
-
-\bibitem {iDMI-exp13}
-X. Ma, G. Yu, S. A. Razavi, S. S. Sasaki, X. Li, K. Hao, S. H. Tolbert, K. L. Wang, and X. Li, Phys. Rev. Lett. \textbf{119}, 027202 (2017).
-
-\bibitem {AFM-iDMI-exp1}
-M. Belmeguenai, H. Bouloussa, Y. Roussigné, M. S. Gabor, T. Petrisor, jr., C. Tiusan, H. Yang, A. Stashkevich, and S. M. Ch\'{e}rif,  Phys. Rev. B \textbf{96}, 144402 (2017).
-
-\bibitem {AFMDMI-exp}
-G. Gitgeatpong, Y. Zhao, P. Piyawongwatthana, Y. Qiu, L. W. Harriger, N. P. Butch, T. J. Sato, and K. Matan, Phys. Rev. Lett. \textbf{119}, 047201 (2017).
-
-\bibitem {iDMI-abinitio1}
-L. Udvardi and L. Szunyogh, Phys. Rev. Lett. \textbf{102}, 207204 (2009).
-
-\bibitem {iDMI-abinitio2}
-J. Gayles, F. Freimuth, T. Schena, G. Lani, P. Mavropoulos, R. A. Duine, S. Bl\"{u}gel, J. Sinova, and Y. Mokrousov, Phys. Rev. Lett. \textbf{115}, 036602 (2015).
-
-\bibitem {AFM-review}
-T.
-Jungwirth, J.
-Sinova, A.
-Manchon, X.
-Marti, J.
-Wunderlich, and C.
-Felser, arXiv:1705.10489; O.
-Gomonay, T.
-Jungwirth, and J.
-Sinova, Phys.
-Status Solidi RRL \textbf{11}, 1700022 (2017); T.
-Jungwirth, X.
-Marti, P.
-Wadley, and J.
-Wunderlich, Nat.
-Nanotechnol.
-\textbf{11}, 231 (2016).
-
-\bibitem {AFM-review1}
-V. Baltz, A. Manchon, M. Tsoi, T. Moriyama, T. Ono, and Y. Tserkovnyak, Rev. Mod. Phys. \textbf{90}, 015005 (2018).
-
-\bibitem {Interface-review}
-F.
-Hellman, A.
-Hoffmann, Y.
-Tserkovnyak, G.
-Beach, E.
-Fullerton, C.
-Leighton, A.
-MacDonald, D.
-Ralph, D.
-Arena, H.
-Durr, P.
-Fischer, J.
-Grollier, J.
-Heremans, T.
-Jungwirth, A.
-Kimmel, B.
-Koopmans, I.
-Krivorotov, S.
-May, A.
-Petford-Long, J.
-Rondinelli, N.
-Samarth, I.
-Schuller, A.
-Slavin, M.
-Stiles, O.
-Tchernyshyov, A.
-Thiaville, and B.
-Zink, Rev.
-Mod.
-Phys.
-\textbf{89}, 25006 (2017).
-
-\bibitem {Manchon-Rashba2}
-S. Grytsyuk, A. Belabbes, P. M. Haney, H-W. Lee, K-J. Lee, M. D. Stiles, U. Schwingenschl\"{o}gl, and A. Manchon, Phys. Rev. B \textbf{93}, 174421 (2016).
-
-\bibitem {AHE}
-N. Nagaosa, J. Sinova, S. Onoda, and A. H. MacDonald, N. P. Ong, Rev. Mod. Phys. \textbf{82}, 1539 (2010).
-
-\bibitem {Alireza-Rashba1}
-A. Qaiumzadeh and M. Titov, Phys. Rev. B \textbf{94}, 014425 (2016).
-
-\bibitem {Rashba-anisotropy}
-K-W. Kim, K-J. Lee, H-W. Lee, and M. D. Stiles, Phys. Rev. B \textbf{94}, 184402 (2016).
-
-\bibitem {sd-model-referee-suggested}
-J. Schliemann, Phys. Rev. B \textbf{67}, 045202 (2003); A. Auerbach, \textit{Interacting Electrons and Quantum Magnetism} (Springer, New York, 1998).
-
-\bibitem{Fechner2012}
-A. D. Caviglia, M. Gabay, S. Gariglio, N. Reyren, C. Cancellieri, and J.-M. Triscone, Phys. Rev. Lett. \textbf{104}, 126803 (2010).
-
-\bibitem {Mokrousov}
-F. Freimuth, S. Bl\"{u}gel, and Y. Mokrousov, Phys. Rev. B \textbf{96}, 054403 (2017); J. Phys. Condens. Matter. \textbf{26}, 104202 (2014).
-
-\bibitem {Tatara}
-T. Kikuchi, T. Koretsune, R. Arita, and G. Tatara, Phys. Rev. Lett. \textbf{116}, 247201 (2016).
-
-\bibitem {kzero}
-In general, the effective action has two extra terms related to the spin susceptibilities with a long wavelength nature, i.
-e., $\bm{k}=0$, which have no contributions in the exchange stiffness and DM interaction:
-$\Delta \mathcal{S}^{\mathrm{eff}}_{0}[\bm{n}]=\hbar\beta\left(\delta n^a \chi^{a}+\sum_{l}\delta n^a_{\nu_l} \Pi^{ab}_{i\nu_l} \delta n^b_{-\nu_l}\right)$.
-The static spin susceptibility related to the first-order term in $\delta n^a$ is $\chi^{a}=(J_{\mathrm{sd}}/\hbar\beta)\sum_{\bm{q},n}\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}]$, and the dynamic spin susceptibility related to the second-order term in $\delta n^a$ is
-$\Pi^{ab}_{i\nu_l}=\sum_{\bm{q},n}\big\{-(J_{\mathrm{sd}}/2\hbar\beta)\mathrm{Tr}[\Gamma_x G^0_{\bm{q},i\omega_{n}}]\delta_{ab}+(J^2_{\mathrm{sd}}/2\hbar\beta)\mathrm{Tr}[\Gamma_a G^0_{\bm{q},i\omega_{n}}\Gamma_b G^0_{\bm{q},i\omega_{n}+i\nu_l}]\big\}$, where $\delta_{ab}$ is the Kronecker delta function.
-
-\bibitem {RashbaFM-DMI}
-I. A. Ado, A. Qaiumzadeh, R. A. Duine, A. Brataas, and M. Titov, arXiv:1804.03739.
-
-\bibitem {iDMI-theory-TI1}
-R. Wakatsuki, M. Ezawa, and N. Nagaosa, Sci. Rep. \textbf{5}, 13638 (2015); T. Koretsune, N. Nagaosa, and R. Arita, \textit{ibid} \textbf{5}, 13302 (2015).
-
-\bibitem {iDMI-theory-TI2}
-Y. Tserkovnyak, D. A. Pesin, and D. Loss, Phys. Rev. B \textbf{91}, 041121(R) (2015).
-
-\bibitem {AFM-iDMI-DFT-2}
-S.
-Meyer, B.
-Dup\'{e}, P.
-Ferriani, and S.
-Heinze, Phys.
-Rev.
-B \textbf{96}, 094408 (2017); A.
-Belabbes, G.
-Bihlmayer, F.
-Bechstedt, S.
-Bl\"{u}gel, and A.
-Manchon, Phys.
-Rev.
-Lett.
-\textbf{117}, 247202 (2016).
 

### 2019-01-24 Paper/paper.tex
asdf

@@
 % !TEX spellcheck = en-US
-\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress]{revtex4}%
+\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4}%
 \usepackage{graphicx}
@@
 \usepackage[toc,page]{appendix}
+%\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}
 \setcounter{MaxMatrixCols}{30}
@@
 Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
-The hopping term $-\hat{T} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$ can describe various models.
-We will be interested in:
+We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes, therefore the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
+
+The hopping term $-\hat{T} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$ can describe various models. We will be interested in:
 
@@
 
-The only assumption we will make about $\hat{T}$ is that it is proportional to any power of $\hat{p}$ in which case we can apply the Peierls substitution (\ref{AP3A}) to introduce to take into account the effect of the electromagnetic perturbation in the lattice.
-The strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
+In the prescence of an laser perturbation we can use the Peirls substitution to introduce the effect of the field trough the hopping amplitudes.
+We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
+According to the Peierls rule the hopping amplitudes gain a phase:
+\begin{equation}
+t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)}
+\end{equation}
+where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
 
-In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-In the simplest case, for example, the sum would be restricted to nearest neighbors and the hopping amplitude would be diagonal in the spin state.
-With this notation, in presence of a vector potential $\vec{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:
+Let us define:
+
+\begin{equation}
+\label{Def_alpha}
+e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}
+\end{equation}
+
+With $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
+
+\begin{align}
+\alpha_{ij} &= -\alpha_{ji} \label{alphaSym} \\
+\theta_{ij} &= \theta_{ji} \label{thetaSym}
+\end{align}
+
+and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
+
+\begin{align*}
+t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
+\end{align*}
+
+Where we defined
+
+\begin{equation}
+\label{HoppAmpFourier}
+t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})
+\end{equation}
+
+Which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}. 
 \end{section}
@@
 
-\begin{thebibliography}{9}
-
-\end{thebibliography}
+%\begin{thebibliography}
+\bibliography{paper}
+%\end{thebibliography}
 

### 2019-01-27 Paper/paper.tex
Project_prop

@@
 
-Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
+Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $t_{ij}^{\sigma \sigma'}$ are the hopping amplitudes originating from kinetik terms or spin orbit interaction.
+$\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
 We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes, therefore the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
@@
 
-and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
+and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi-–Anger expansion:
+
+\begin{align}
+t_{ij}^{\sigma \sigma'}(t) &= t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \n \\
+&= \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
+\end{align}
+
+Where we defined $t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$, which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
+In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
+The transformed Hamiltonian is:
+
+\begin{equation}
+\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
+\end{equation}
+
+We perform the unitary transformation perturbatively in the hopping operator, we can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion.
+We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
+In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
+With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e.
+we can write:
+\begin{equation}
+\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
+\end{equation}
+where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
+
+Let $\hat{P}_0$ be the projection operator to the $d=0$ subspace.
+Then we obtain $\hat{P}_0\hat{H}'^{1}(t)\hat{P}_0 = 0$, we define $\hat{H}_{\text{eff}}$ to be the time average of $\hat{P}_0\hat{H}'^{2}(t)\hat{P}_0$.
+We obtain:
+
+\begin{align}
+\hat{H}_{\text{eff}} &= - \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left\{ \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} \right. \n \\
+&t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \left. \right\} \label{GeneralHeff}
+\end{align}
+
+We can obtain the spin Hamiltonian by using the relations:
+\begin{align}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\end{align}
+and $n_{i \uparrow} + n_{i \downarrow} = 1$.
+
+\begin{subsection}{Kane--Mele--Hubbard model}
+
+The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene.
+In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
+In these circumstances the system can be modeled by the Kane-Mele-Hubbard model, which has hopping amplitudes:
+
+\begin{equation}
+t_{ij}^{\sigma \sigma'} = \begin{cases}
+	\delta_{\sigma \sigma'}t_1 & \text{for } i, j \text{ nearest neighbors} \\
+	-\Delta \nu_{ij} \hat{e}_z \cdot \bs{\sigma}_{\sigma, \sigma'} & \text{for } i, j \text{ next nearest neighbors} \\
+	0 & \text{ otherwise} \n
+\end{cases} \quad
+\end{equation}
+
+Where $\Delta$ is the intrinsic spin orbit coupling constant.
+$\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).
+Then, introducing the spin operators and the corresponding hopping amplitudes in (\ref{GeneralHeff}) we obtain the effective spin Hamiltonian of this model:
+
+\begin{equation}
+\label{KMHeff}
+\hat{H}_{\text{KMH}}^{\text{eff}} = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
+\end{equation}
+
+Where the exchange interaction couples NN spins and an anisotropic exchange interaction couples NNN spins:
 
 \begin{align*}
-t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
+J_{ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+\bs{\Gamma}_{ij} &= 2\Delta^2 \text{diag}(-1,-1,1)\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
+\end{align*}
+\end{subsection}
+
+\begin{subsection}{Modified Kane--Mele--Hubbard model}
+
+As we saw in the previous section the effective Hamiltonian \ref{KMHeff} does not contain NNN DMI terms.
+The reason for this is because DMI originates from the virtual hoppings $i\rightarrow j\rightarrow i$ combining SOI hopping and kinetik hopping, since in the original Kane-Mele model we don't find NNN kinetik hopping, the DMI term vanishes.
+Next we will study the same Hamiltonian adding a finite NNN hopping term $t_2$, which can be understood as a second order NN hopping process (the direct NNN hopping integral would usually be much smaller).
+Thus we start with:
+
+\begin{align}
+\label{MKMH}
+\hat{H} &= - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
+	&+\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\text{U}\hat{D}
+\end{align}
+
+Proceeding in the same way we find the effective spin Hamiltonian:
+
+\begin{align}
+\label{MKMHeff}
+&\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
+\end{align}
+
+Where:
+
+\begin{align*}
+J_{1,ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+J_{2,ij} &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
 \end{align*}
 
-Where we defined
+Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
+In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
+In Hamiltonian \ref{MKMHeff} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
+In the next section we will do a numerical of study on how modifying the ratio between NN and NNN spin interaction factors can change the spin state of the system.
 
-\begin{equation}
-\label{HoppAmpFourier}
-t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})
-\end{equation}
+\end{subsection}
 
-Which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}. 
 \end{section}

### 2019-01-27 Project/project.tex
Project_prop

\documentclass{article}

\usepackage{amsmath,amsfonts,stmaryrd,amssymb} 
\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}

\addbibresource{MT.bib}

\title{Ultrafast manipulation of magnetic systems}

\author{Juan Manuel Losada\\[1cm]{\small Supervisor: Alireza Qaiumzadeh}}

\date{\today}

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

\section{Introduction} % Numbered section

The discovery of the giant magnetoresistance effect by P. Grünberg \cite{Binasch1989} and A. Fert \cite{Baibich1988} in the 80s opened the gate for a new field of study known as spintronics, in which electron spin is exploited in improved electronic devices. Magnetoresistive random-access memory (MRAM) is an example of a new type of memory in which data is stored in magnetic elements \citep{Akerman2005}. Newer techniques include thermal assisted switching (TA-MRAM) \citep{Bandiera2015} and spin transfer torque (SPRAM) \citep{Kawahara2012}.

However, so far in most current spintronic devices antiferromagnets play only a minor role. During several decades after the discovery of antiferromagnetics, these materials were perceived as useless from a practical point of view. On contrast, ferromagnets have been widely studied historically for its technical applications. However, the development of information technology demands devices with high storage density, high energy efficiency and high write-read speeds. Therefore, controlling magnetically ordered systems on subpicosecond timescales is currently a widely studied area. Antiferromagnets aim to complement or even replace ferromagnets due to their higher magnetic dynamics, their rigidity to external magnetic field, and the absence  of stray field.

\section{Project description}

In this project we want to investigate the magnetic dynamics of antiferromagnets in both insulating and metallic phases as well as in the novel two dimensional ferromagnets. The goal is to propose efficient techniques to manipulate the magnetic state of such materials. A possible way to do this is to study the interaction between light and the exchange interaction and the Dzyaloshinskii-–Moriya interaction \cite{Mentink2015}. For ferromagnetic materials it has already been shown that short laser pulses can induce an effective magnetic field that can reach an amplitude of a few Tesla (\cite{Qaiumzadeh2016}, \cite{Qaiumzadeh2013}). The results of this project could lead not only to applications for ultra-fast writing devices, but also to a better understanding of the ultrafast dynamics of many-body systems which is still an open topic.

Additionally, we want to study the magnetic properties of topological insulators with special interest in the mathematical formulation of topological invariants. Topological materials are of great interest and promises potential applications for spintronics.

\printbibliography

\end{document}

### 2019-01-27 Paper/paper.tex
pap

@@
 
-Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $t_{ij}^{\sigma \sigma'}$ are the hopping amplitudes originating from kinetik terms or spin orbit interaction.
+Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $t_{ij}^{\sigma \sigma'}$ are the hopping amplitudes originating from both kinetic terms or spin orbit interaction.
 $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
@@
 \hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
+\label{Htransformed}
 \end{equation}
@@
 where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
+From here the procedure is simple but lenghty, we expand \ref{Htransformed} in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+Up to second order we obtain:
+\begin{align}
+&\hat{H}'(t) \approx \text{U}\hat{D} - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
+&+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{align}
 
 Let $\hat{P}_0$ be the projection operator to the $d=0$ subspace.
-Then we obtain $\hat{P}_0\hat{H}'^{1}(t)\hat{P}_0 = 0$, we define $\hat{H}_{\text{eff}}$ to be the time average of $\hat{P}_0\hat{H}'^{2}(t)\hat{P}_0$.
-We obtain:
+Then notice that $\hat{P}_0\hat{H}'^{1}(t)\hat{P}_0 = 0$, we define $\hat{H}_{\text{eff}}$ to be the time average of $\hat{P}_0\hat{H}'^{2}(t)\hat{P}_0$.
+Expressed in terms of creation and anihilation operators we obtain:
 

### 2019-01-28 Chapters/Chapter2.tex
Add tightbinding-hubbard chapter

--- 2018-12-29 Chapters/Chapter2.tex
@@
-\chapter{Effective Spin Hamiltonian}
+\chapter{Basic models for solid state}
 
-In this chapter we will start with a Hamiltonian
+Many properties of solids can be understood using one-electron models, that is, non-interacting models.
+When the interaction between the ions and the valence electrons can be mostly neglected one can adapt the free electron approximation.
+This model is mostly limited to the study of metals and despite its simplicity it successfully explains phenomena related with electrical conductivity and heat capacity.
+In the opposite limit, we can consider systems in which the ion potential is so large that the electrons are bound in the cores with occasional jumps from site to site.
+This is known as tight binding model and it can be used to study a wide variety of solids.
+It is typically used for calculations of the electronic band structure.
 
-\begin{equation}
-\label{Ham1}
-\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
-\end{equation}
+Despite the success of the single particle models, there are several phenomena which cannot be explained neglecting electron correlations.
+For example, high temperature superconductivity cannot be understood with these models.
+The Hubbard model is the simplest model including electron correlations and despite its simplicity it is not fully understood yet.
+In this Chapter we will outline the main features of the tight binding model and the Hubbard model, which are basic tools for any condensed matter researcher.
 
-where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian:
-
-\begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\bs{\sigma}\bs{\nabla}V(\textbf{r}) \times \textbf{p}
-\end{equation}
-
-Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $\text{U}(\bs{r})$ is a periodic potential.
-The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
-The original Hubbard model, was developed to describe the single-band magnetism \cite{Hubbard1963}, it also describes the transition between conducting and insulating systems, predicting the existence of Mott insulators, materials which should be conducting according to band theory, but they are insulating due to electron-electron interactions.
-
-We will consider a half filled system in the strong coupling limit.
-Ignoring electron hopping and spin orbit interaction, the ground state of this system is massively degenerated.
-We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
-This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
-
-\begin{section}{Single particle in a periodic potential}
-
-First we will define a suitable basis for the single particle wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
-
-\begin{equation}
-\label{LaticeHam}
-\hat{H}^{(1)}_{\text{NSOI}}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r})
-\end{equation}
-
-Where $\text{U}(\textbf{r})$ has the symmetry of the lattice, i.e.
-$\text{U}(\textbf{r} + \textbf{R}) = \text{U}(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
-Let $\hat{H}^{(1)}_{\text{NSOI}}$ act on a Hilbert space $\mathcal{H}$ and let $\ket{\phi} \in \mathcal{H}$, then, the group of translation symmetries defined by $\bra{\bs{r}} T_{\textbf{R}} \ket{\phi} = \bra{\bs{r} + \bs{R}} \ket{\phi}$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong.
-If $\Gamma^{\textbf{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\textbf{R}}\ket{\phi_{n, \textbf{k}}} = \Gamma^{\textbf{k}}(\textbf{R}) \ket{\phi_{n, \textbf{k}}}$.
-Now, imposing periodic boundary conditions, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
-This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
-Therefore, for a wavefunction in a periodic lattice we have:
-
-\begin{equation}
-\label{Bloch1}
-\bra{\bs{r}+\bs{R}} \ket{\phi_{n, \textbf{k}}} = e^{i\textbf{k}\textbf{R}}\bra{\bs{r}} \ket{\phi_{n, \textbf{k}}}
-\end{equation}
-
-Which is the well-known Bloch function form.
-Here, $n$ is called the band index, and $\textbf{k}$ is the quasimomentum.
-The energy of this wavefunction is $\epsilon_{n \textbf{k}}$.
-Notice that both $\phi_{n,\textbf{k}}$ and $\epsilon_{n \textbf{k}}$ are periodic functions of $\textbf{k}$ in the reciprocal lattice.
-
-The Bloch function is extended over the whole crystal volume $V$.
-We would like to work with a localized basis.
-An alternative orthonormal basis are the Wannier functions $\ket{\psi_{in}}$, defined in terms of the Bloch functions as:
-
-\begin{align}
-\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
-\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\textbf{k}\textbf{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
-\end{align}
-
-Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
-Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
-From now on we will restrict ourselves to a fixed band, so we will drop the band index.
-Additionally, we will include the spin state, therefore the basis states will have two quantum numbers one for the site and one for the spin state.
-We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant.
-Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
-
-\end{section}
-
-\begin{section}{Derivation of the single-band Hubbard model}
-
-In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
-Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\ket{j\sigma}$.
-In this basis, the second quantized form of \ref{Ham1} is:
-
-\begin{equation}
-\hat{H} = \sum_{i,j,\sigma, \sigma'} \bra{i\sigma} \hat{H}^{(1)} \ket{j\sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
-\end{equation}
-
-Where we assumed $\hat{v}$ to be spin independent. This can be rewritten as:
-
-\begin{equation}
-\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
-\end{equation}
-
-Where $t_{ij} = -\bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = -\bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
-Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$, for example, in the $x$ component:
-
-\begin{align*}
-\Delta_{ij,x} &= -\bra{i} \lambda (\partial_y V(\bs{r}) p_z - \partial_z V(\bs{r}) p_y) \ket{j} = i \hbar \lambda \int d \bs{r} \phi_i(\bs{r})^* (\partial_y V(\bs{r}) \partial_z - \partial_z V(\bs{r}) \partial_y) \phi_j(\bs{r}) = \\
-&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z(\phi_i(\bs{r})^*\partial_y V(\bs{r}) - \partial_y(\phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
-&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z \phi_i(\bs{r})^* \partial_y V(\bs{r}) - \partial_y \phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
-&= \int d\bs{r} \phi_j(\bs{r}) \lambda (\bs{\nabla}V(\bs{r}) \times \bs{p})_x \phi_i(\bs{r})^* = - \Delta_{ji,x}
-\end{align*}
-
-Therefore $\bs{\Delta}_{ii} = 0$. Notice also that $\bs{\Delta}_{ij}$ is purely imaginary.
-We can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
-
-\begin{itemize}
-\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\boldsymbol{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
-In an isotropic system we can approximate:
-
-\begin{equation}
-t_{ij} = \begin{cases}
-             t,  & \text{for } (i,j) \text{ nearest neighbous} \\
-             0,  & \text{otherwise}
-       \end{cases} \quad
-\end{equation}
-
-and
-
-\begin{equation}
-\bs{\Delta}_{ij} = \begin{cases}
-             \bs{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
-             0,  & \text{otherwise}
-       \end{cases} \quad
-\end{equation}
-
-Hubbard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
-
-\item Taking into account the locality of the Wannier functions and the Coulomb interaction, the dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$.
-Terms with $i=k$ and $j=l$ also contribute when $i, j$ are nearest neighbours.
-Therefore we approximate:
-
-\begin{equation}
-\bra{ij} \hat{v} \ket{kl} =
-	\begin{cases}
-		\text{U}, & \text{if } i=j=k=l \\
-		\text{V}, & \text{if } i=k \text{ and } j=l \text{ where } (i,j) \text{ nearest neighbours} \\
-		0, & \text{otherwise}
-	\end{cases}						
-\end{equation}
-
-Where we defined:
-
-\begin{align}
-\text{U} &= \frac{1}{2} \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}')^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}') \phi(\bs{r}) \\
-\text{V} &= \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}'-\bs{R}_1)^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}'-\bs{R}_1) \phi(\bs{r})
-\end{align}
-
-Where $\phi(\bs{r})$ is the Wannier function centered at the origin and $\bs{R}_1$ is a nearest neighbour lattice vector.
-Notice that we made explicit use of the translational invariance of the system.
-Also, for $i=j=k=l$ the Pauli principle requires $\sigma' = -\sigma$.
-
-\end{itemize}
-
-Taking these approximations and writing $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \hat{c}_{i \sigma} = \hat{n}_{i \sigma} \hat{n}_{j \sigma'}$, we obtain:
-
-\begin{equation}
-\label{HubbardWithNonLocalInt}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \text{V} \sum_{i,j,\sigma,\sigma'}  \hat{n}_{i \sigma} \hat{n}_{j \sigma'}
-\end{equation}
-
-Now, in a half filling system this Hamiltonian can be well approximated by an effective Hamiltonian without non local Coulomb interactions:
-
-\begin{equation}
-\label{Intermediate}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}^* \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation}
-
-Where $\text{U}^* = \text{U} - \text{V}$.
-The physical reason for this is that the energy difference when the Coulomb interaction pushes an electron from a double occupied site to an empty site is $\text{U}-\text{V}$ in \ref{HubbardWithNonLocalInt}, because the number of double occupied sites is reduced by one but the number of adjacent occupied sites is increased by one.
-This is illustred in Figure \ref{Fig2.1}.
-A more rigouros derivation of this effective model can be found in \cite{Schuler2013}.
-Altough $\text{V} < \text{U}$, they can be comparable in magnitude, and $\text{U}^*$ can be reduced by a factor of $0.5$ or more.
-
-\begin{figure}
-\centering
-  \includegraphics[width=0.5\linewidth]{../Figures/non_local_coulomb.png}
-  \caption{Image from \cite{Schuler2013}.
-In a half-filled system decreasing the number of double occupancies increases the number of adjacent occupied sites, and so the energy difference is reduced to $\text{U}-\text{V}$.}
-\label{Fig2.1}
-\end{figure}
-
-Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the model that we will use in the next sections:
-
-\begin{equation}
-\label{Hubbard}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation}
-
-\begin{subsection}{Hubbard model}
-
-In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
-This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}.
-Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
-Originally the Hubbard model was proposed to describe electron correlations in $d$ or $f$ bands in transition metals.
-The result was a simplified model to predict metal-insulator transitions.
-However, it exhibits much richer phenomena.
-It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
-they should be conductors according to band theory, but electron-electron interactions keep away from).
-Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
-
-\end{subsection}
-
-\end{section}
-
-\begin{section}{Effective Hamiltonian for half-filling system}
-
-At half filling, in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
-First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
-There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
-The ground state energy is $0$.
-The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
-The energy of one of these states is $\text{U}$.
-Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
-Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
-
-Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
-$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
-In second order we have:
-
-\begin{equation}
-\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
-\end{equation}
-
-The sum being over all excited states.
-Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
-These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
-These means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
-Now,
-
-\begin{align}
-\label{PertNoEMF}
-&\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
-&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
-&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
-& \bra{\phi'} \hat{H}_J + \hat{H}_D + \hat{H}_P \ket{\phi}
-\end{align}
-
-In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
-We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
-We defined:
-
-\begin{align}
-\hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \\
-\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \\
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
-\end{align}
-
-Let us now introduce the on-site spin operators:
-
-\begin{equation}
-\label{SpinOperators}
-\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
-\end{equation}
-
-Which satisfy:
-
-\begin{align}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
-\end{align}
-
-In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:
-
-\begin{align*}
-&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\}= \\
-&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
-\end{align*}
-
-Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
-We also used the well known property $tr(\bs{\sigma}^a\bs{\sigma}^b)=2\delta_{a,b}$.
-And second:
-
-\begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
- &= \left\{ \right.
-	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
-	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
-	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
-	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
-	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
-	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
-	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
-	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
-	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
-	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
-	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
-	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
-	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
-	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
-	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
-	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
-\left. \right\} = \\
-&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
-&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
-\end{align*}
-
-Where in the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
-We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$.
-Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
-
-Also:
-
-\begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&= \overbrace{\Delta_{ij}^z\Delta_{ij}^z(\frac{1}{2}+S_i^z)(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \uparrow} +
-	\overbrace{\Delta_{ij}^z\Delta_{ij}^+S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
-	\overbrace{\Delta_{ij}^z\Delta_{ij}^-(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
-	\overbrace{\Delta_{ij}^z(-\Delta_{ij}^z) S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
-	&\overbrace{\Delta_{ij}^+\Delta_{ij}^z (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
-	\overbrace{\Delta_{ij}^+\Delta_{ij}^+S_i^-(-S_j^-)}^{\uparrow \downarrow \uparrow \downarrow} +
-	\overbrace{\Delta_{ij}^+\Delta_{ij}^-(\frac{1}{2}+S_i^z)(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \uparrow} +
-	\overbrace{\Delta_{ij}^+(-\Delta_{ij}^z) S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
-	&\overbrace{\Delta_{ij}^-\Delta_{ij}^z S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
-	\overbrace{\Delta_{ij}^-\Delta_{ij}^+(\frac{1}{2}-S_i^z)(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \downarrow} +
-	\overbrace{\Delta_{ij}^-\Delta_{ij}^-S_i^+(-S_j^+)}^{\downarrow \uparrow \downarrow \uparrow} +
-	\overbrace{\Delta_{ij}^-(-\Delta_{ij}^z) (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
-	& \overbrace{(-\Delta_{ij}^z)\Delta_{ij}^z S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
-	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^+ (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
-	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^- S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} + \\
-	&+\overbrace{(-\Delta_{ij}^z)(-\Delta_{ij}^z)(\frac{1}{2}-S_i^z)(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \downarrow} = \\
-&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z (-2(\Delta_{ij}^z)^2 + 2\Delta_{ij}^+\Delta_{ij}^-) + S_i^zS_j^+(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^zS_j^-(-2\Delta_{ij}^z\Delta_{ij}^+) +\\
-&+ S_i^+S_j^z(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^+S_j^+(-\Delta_{ij}^-\Delta_{ij}^-) + S_i^+S_j^-(\Delta_{ij}^z)^2 +\\
-&+ S_i^-S_j^z(-2\Delta_{ij}^z\Delta_{ij}^+) + S_i^-S_j^+(\Delta_{ij}^z)^2 + S_i^-S_j^-(-(\Delta_{ij}^+)^2) = \\
-&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z(-2(\Delta_{ij}^z)^2+2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 + S_i^zS_j^y(-4\Delta_{ij}^z\Delta_{ij}^y)+S_i^zS_j^x(-4\Delta_{ij}^z\Delta_{ij}^x) + \\
-&+S_i^yS_j^z(-4\Delta_{ij}^y\Delta_{ij}^z)+S_i^yS_j^y(2(\Delta_{ij}^z)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^x)^2)+S_i^yS_j^x(-4\Delta_{ij}^y\Delta_{ij}^x) + \\
-&+ S_i^xS_j^z(-4\Delta_{ij}^x\Delta_{ij}^z) + S_i^xS_j^y(-4\Delta_{ij}^x\Delta_{ij}^y) + S_i^xS_j^x(2(\Delta_{ij}^z)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^x)^2) = \\
-&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \begin{pmatrix}
-S_i^x & S_i^y & S_i^z
-\end{pmatrix}
-\\
-&\begin{pmatrix}
-2(\Delta_{ij}^z)^2 + 2(\Delta_{ij}^y)^2 - 2(\Delta_{ij}^x)^2 & -4\Delta_{ij}^x\Delta_{ij}^y & -4\Delta_{ij}^x\Delta_{ij}^z \\ -4\Delta_{ij}^y\Delta_{ij}^x & +2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2 +2(\Delta_{ij}^z)^2 & -4\Delta_{ij}^y\Delta_{ij}^z \\ -4\Delta_{ij}^z\Delta_{ij}^x & -4\Delta_{ij}^z\Delta_{ij}^y & 2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^z)^2
-\end{pmatrix}
-\begin{pmatrix}
-S_j^x \\ S_j^y \\ S_j^z
-\end{pmatrix} = \\
-&\frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \sum_{\alpha, \beta} S_i^\alpha (4\Delta_{ij}^\alpha\Delta_{ij}^\beta - \delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2) S_j^\beta
-\end{align*}
-
-These three relations are important and will be used in the next chapter:
-
-\begin{align}
-&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2} \\
-& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
-\end{align}
-
-Now introducing the spin operators into  $\hat{H}_J$ with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
-
-\begin{align*}
-\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
-\end{align*}
-
-The constant term can be neglected leaving:
-
-\begin{equation}
-\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i\bs{S}_j
-\end{equation}
-
-Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
-
-\begin{align*}
-\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j
-\end{align*}
-
-Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$, notice that being $\bs{\Delta}_{ij}$ purely imaginary, $\bs{D}_{ij}^0$ is a real vector. 
-Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ leads to:
-
-\begin{align*}
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&\frac{1}{\text{U}} \sum_{\langle i,j \rangle} \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta = \sum_{\langle i,j \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j
-\end{align*}
-
-With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
-The total effective Hamiltonian is:
-
-\begin{equation}
-\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right) \label{HeffNOEMF}
-\end{equation}
-
-With:
-
-\begin{align}
-J_{ij}^0 &= \frac{2t^2}{\text{U}} \label{Jij0} \\
-\bs{D}_{ij}^0 &= \frac{4it}{\text{U}}\bs{\Delta}_{ij} \label{Dij0} \\ 
-\bs{\Gamma_{ij}}^{\alpha \beta} &= \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta) \label{Gij0}
-\end{align}
-
-The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
-Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
-However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach.
-$\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
-interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}.
-In the next chapter we will examine this further.
-Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
-
-\end{section}
-
-\begin{section}{AFM dynamics}
-
-In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics \cite{Tveten2016}.
-We write the Heisenberg Hamiltonian as $\hat{H} = J \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j - K \sum_i S_{iz}^2$ with $J>0$ and $K$ is the anisotropy energy.
-Let the lattice be a one dimensional chain with $2N$ sites, such lattice can be described by the repetition of $N$ unit cells consisting of two sites $\alpha$ and $\beta$ for the left and right site respectively.
-Then the ground state of this Hamiltonian is double degenerated and is obtained by aligning the spins in the $\alpha$ sites in the $\hat{z}$ direction and the $\beta$ spins in the $-\hat{z}$ direction or vice versa.
-Let us introduce the parameters:
-
-\begin{align}
-\bs{m}_i &= \frac{\bs{S}_{\alpha}^i + \bs{S}_{\beta}^i}{2S} \\
-\bs{l}_i &= \frac{\bs{S}_{\alpha}^i - \bs{S}_{\beta}^i}{2S}
-\end{align}
-
-Where $S$ is the spin angular momentum in units of $\hbar$. Inverting these relations, introducing them into the Hamiltonian and neglecting edge terms we obtain:
-
-\begin{align}
-\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
-& 2JS^2\sum_i^{N} (\bs{m}_i^2-\bs{l}_i^2)+\frac{JS^2}{2}\sum_i^{N-1}\left[(\bs{l}_{i+1}-\bs{l}_i)^2-(\bs{m}_{i+1}-\bs{m}_i)^2 \right] \nonumber \\
-& + JS^2\sum_i^{N-1} \left[ \bs{m}_i(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
-\end{align}
-
-Now we can take the continuum limit with:
-
-\begin{align*}
-\bs{m}_i &\rightarrow \bs{m}(x) \\
-\bs{l}_i &\rightarrow \bs{l}(x) \\
-2d \sum_i &\rightarrow \int dx \\
-\hat{H} &\rightarrow \int \frac{dx}{2d} \mathcal{H}(\bs{l},\bs{m})
-\end{align*}
-
-This, together with $\bs{m}_i-\bs{l}_i = 2\bs{m}_i-1$ and $\bs{m}_{i+1} \rightarrow \bs{m}(x) + 2d \partial_x\bs{m}(x)$ gives:
-
-\begin{equation}
-\mathcal{H}(\bs{l},\bs{m}) = JS^2\left\{ 4|\bs{m}|^2 + |\partial_x\bs{l}'|^2 -  |\partial_x\bs{m}'|^2 +(\bs{m}\partial_x\bs{l} -\bs{l}\partial_x\bs{m}) \right\} -KS^2\left\{ (\bs{l}\hat{z})^2 + (\bs{m}\hat{z})^2 \right\}
-\end{equation}
-
-\end{section}
-
-\begin{subappendices}
-\begin{section}{Crystal structure and reciprocal lattice}
-\label{AP1A}
-
-Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
-
-\begin{equation}
-\bs{R} = \sum_{\mu=1}^3 m_\mu \bs{a}_\mu
-\end{equation}
-
-Where $m_\mu$ are integers.
-The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
-The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
-The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
-With this notation the first Brillouin zone is:
-
-\begin{equation}
-\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
-\end{equation}
-
-Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
-
-In the case of a cubic lattice we have $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
-
-In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
-
-\begin{align}
-\bs{a}_1 &= \frac{a_0}{2} \left(3, \sqrt{3} \right) \\
-\bs{a}_2 &= \frac{a_0}{2} \left(3, -\sqrt{3} \right)
-\end{align}
-
-Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
-Each unit cell contains two atoms, dividing the lattice into two sublattices, usually denoted A and B.
-The reciprocal lattice is defined by the vectors:
-
-\begin{align}
-\bs{b}_1 &= \frac{2\pi}{3a_0} \left(1, \sqrt{3} \right) \\
-\bs{b}_2 &= \frac{2\pi}{3a_0} \left(1, -\sqrt{3} \right)
-\end{align}
-
-These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
-
-\begin{align}
-\bs{R}^A_1 &= \frac{a_0}{2} \left( 1, \sqrt{3} \right) \\
-\bs{R}^A_2 &= \frac{a_0}{2} \left( 1, -\sqrt{3} \right) \\
-\bs{R}^A_3 &= a_0 \left( -1, 0 \right)
-\end{align}
-
-The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$
-
-\begin{figure}
-\centering
-  \includegraphics[width=0.7\linewidth]{../Figures/honeycomb_lattice.png}
-  \caption{Image from a web source.
-In Fig.
-(a) the unit cell is sketched and the sublattices A and B are shown in blue and red respectively.
-In Fig.
-(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
-\label{Fig2.2}
-\end{figure}
-\end{section}
-\end{subappendices}
+\section{Tight binding}

### 2019-01-28 Paper/paper.tex
Start with MKMH

@@
 
-We will start we a general Hamiltonian:
+The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene.
+In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
+In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:
 
-\begin{equation}
-\hat{H} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}\hat{D}
-\end{equation}
+\begin{align}
+\label{MKMH}
+\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
+	&+\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	\text{U}\hat{D}
+\end{align}
 
-Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $t_{ij}^{\sigma \sigma'}$ are the hopping amplitudes originating from both kinetic terms or spin orbit interaction.
+Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$.
 $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
+$t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping.
+Where $\Delta$ is the intrinsic spin orbit coupling constant.
+$\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).
+$\sigma^{z}$ is the third Pauli matrix.
 We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes, therefore the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
-
-The hopping term $-\hat{T} = -\sum_{ij\sigma \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$ can describe various models. We will be interested in:
-
-\begin{itemize}
-	\item The Hubbard model, in which the hopping does not change the spin, $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'}t$ for $i,j$ NN and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
-	\item The so-called Kane-Mele-Hubbard model, which includes a spin-dependent term araising from spin-obit interactions.
-	\begin{equation}
-t_{ij}^{\sigma \sigma'} = \begin{cases}
-	\delta_{\sigma \sigma'}t_1 & \text{for } i, j \text{ nearest neighbors} \\
-	-\Delta \nu_{ij} \hat{e}_z \cdot \bs{\sigma}_{\sigma, \sigma'} & \text{for } i, j \text{ next nearest neighbors} \\
-	0 & \text{ otherwise} \n
-\end{cases} \quad
-\end{equation}
-\end{itemize}
 
@@
 We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
-According to the Peierls rule the hopping amplitudes gain a phase:
-\begin{equation}
-t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)}
-\end{equation}
-where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
+According to the Peierls rule the hopping amplitudes gain a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
 
@@
 
-and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi-–Anger expansion:
+and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi-–Anger expansion to Fourier transform the hopping amplitues:
+\begin{equation}
+\label{JacobiAnger}
+e^{ie\bs{R}_{ij}\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} 
+\end{equation}
+where $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}, modulating the weight of the \textit{m}th Fourier mode of the hopping amplitude.
+Let $\hat{T}_0$ be the hopping part of the hamiltonian, so that $\hat{H}_0 = \hat{T}_0 + \text{U}\hat{D}$.
+When an electric field is applied, the hopping amplitudes become time dependent so that $\hat{H}(t) = \hat{T}(t) +  \text{U}\hat{D}$.
+Using \ref{JacobiAnger} we can write $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$ where $\hat{T}_m$ is the sum of all the \textit{m}th Fourier mode of the hopping terms.
+Additionaly we can further decompose the hopping operator into:
 
-\begin{align}
-t_{ij}^{\sigma \sigma'}(t) &= t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \n \\
-&= \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
-\end{align}
+\begin{equation}
+\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
+\end{equation}
 
-Where we defined $t_{ij,m}^{\sigma \sigma'} = t_{ij}^{\sigma \sigma'} e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})$, which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
-In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$.
-The transformed Hamiltonian is:
+Where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
+
+In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$. The transformed Hamiltonian is:
 
@@
 \begin{align}
-\hat{H}_{\text{eff}} &= - \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left\{ \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} \right. \n \\
-&t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \left. \right\} \label{GeneralHeff}
+\hat{H}_{\text{eff}} &= - \sum_{i,j, \sigma, \sigma'} \left\{ \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \right. \n \\
+&t_{ij}^{\sigma} t_{ji}^{\sigma'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \left. \right\} \label{GeneralHeff}
 \end{align}
 
+Where $t_{ij}^{\sigma}$ are the corresponding amplitudes for the unperturbed Hamiltonian, i.e.
+$t_{ij}^{\sigma} = t_1$ for $i,j$ being NN and $t_{ij}^{\sigma} = t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}$ for $i,j$ being NNN.
 We can obtain the spin Hamiltonian by using the relations:

### 2019-01-29 Paper/paper.tex
wrap on

@@
 and $n_{i \uparrow} + n_{i \downarrow} = 1$. 
-
-\begin{subsection}{Kane--Mele--Hubbard model}
-
-The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene.
-In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
-In these circumstances the system can be modeled by the Kane-Mele-Hubbard model, which has hopping amplitudes:
-
-\begin{equation}
-t_{ij}^{\sigma \sigma'} = \begin{cases}
-	\delta_{\sigma \sigma'}t_1 & \text{for } i, j \text{ nearest neighbors} \\
-	-\Delta \nu_{ij} \hat{e}_z \cdot \bs{\sigma}_{\sigma, \sigma'} & \text{for } i, j \text{ next nearest neighbors} \\
-	0 & \text{ otherwise} \n
-\end{cases} \quad
-\end{equation}
-
-Where $\Delta$ is the intrinsic spin orbit coupling constant.
-$\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).
-Then, introducing the spin operators and the corresponding hopping amplitudes in (\ref{GeneralHeff}) we obtain the effective spin Hamiltonian of this model:
-
-\begin{equation}
-\label{KMHeff}
-\hat{H}_{\text{KMH}}^{\text{eff}} = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
-\end{equation}
-
-Where the exchange interaction couples NN spins and an anisotropic exchange interaction couples NNN spins:
-
-\begin{align*}
-J_{ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-\bs{\Gamma}_{ij} &= 2\Delta^2 \text{diag}(-1,-1,1)\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
-\end{align*}
-\end{subsection}
-
-\begin{subsection}{Modified Kane--Mele--Hubbard model}
-
-As we saw in the previous section the effective Hamiltonian \ref{KMHeff} does not contain NNN DMI terms.
-The reason for this is because DMI originates from the virtual hoppings $i\rightarrow j\rightarrow i$ combining SOI hopping and kinetik hopping, since in the original Kane-Mele model we don't find NNN kinetik hopping, the DMI term vanishes.
-Next we will study the same Hamiltonian adding a finite NNN hopping term $t_2$, which can be understood as a second order NN hopping process (the direct NNN hopping integral would usually be much smaller).
-Thus we start with:
-
-\begin{align}
-\label{MKMH}
-\hat{H} &= - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
-	&+\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\text{U}\hat{D}
-\end{align}
-
-Proceeding in the same way we find the effective spin Hamiltonian:
+and summing over the spin states. The resulting effective spin Hamiltonian is:
 
@@
 \label{MKMHeff}
-&\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
+&\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
 &+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
@@
 
-\end{subsection}
-
 \end{section}

### 2019-01-29 Paper/paper.tex
Introduce disorder to paper

@@
 \hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
-	&+\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+	&-\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
 	\text{U}\hat{D}
@@
 
+\begin{subsection}{Disorder}
+It is possible to introduce the effect of disorder in the model \ref{MKMH} by adding random uncorrelated on-site energies:
+
+\begin{align}
+\label{DisorderedHubbardModel}
+\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \n \\
+	& + \sum_{i \sigma} \epsilon_i \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma} +
+	\text{U}\hat{D}
+\end{align}
+
+Where $\epsilon_i$ are uncorrelated random variables $\epsilon_i \in [-W,W]$.
+At half filling we can derive an effective Hamiltonian using the same procedure as before.
+The second order virtual hopping $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ will give rise to an exchange spin interaction.
+In this case, however, the intermediate energy is $\text{U} + (\epsilon_j - \epsilon_i)$.
+Therefore the spin Hamiltonian will be:
+
+\begin{align}
+&\hat{H}_{\text{eff}}^{\text{Dis}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
+\end{align}
+
+With:
+
+\begin{align*}
+J_{1,ij} &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
+J_{2,ij} &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
+\bs{D}_{2,ij} &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
+\bs{\Gamma}_{2,ij} &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
+\end{align*}
+
+Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
+This model is relevant for studying many-body localization phenomena \cite{Protopopov}.
+\end{subsection}
+
 \end{section}

### 2019-01-31 Paper/paper.tex
derive spin ham first

@@
 \label{MKMH}
-\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
+\hat{H}^0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
 	&-\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
@@
 $\sigma^{z}$ is the third Pauli matrix.
-We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes, therefore the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
+We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes.
+In the strong coupling limit any state with a nonzero number of double occupancies ($d /neq 0$) will have much larger energy than those with $d=0$.
+We can therfore obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second order perturbation techniques in the hopping terms.
+We can then obtain the effective spin Hamiltonian by using the relations:
+\begin{align}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\end{align}
+Following this procedure we obtain the following effective spin Hamiltonian:
+
+\begin{align}
+\label{MKMHeff0}
+&\hat{H}_{\text{eff}}^0 = \sum_{\langle i,j \rangle} J_{1,ij}^0\bs{S}_i\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}^0\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}^0 \bs{S}_j \right\}
+\end{align}
+
+Where:
+
+\begin{align*}
+J_{1,ij}^0 &= 2t_1^2 \\
+J_{2,ij}^0 &= 2t_2^2 \\
+\bs{D}_{2,ij}^0 &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
+\bs{\Gamma}_{2,ij}^0 &= 2\Delta^2 \text{diag}(-1,-1,1)
+\end{align*}
 
@@
 $t_{ij}^{\sigma} = t_1$ for $i,j$ being NN and $t_{ij}^{\sigma} = t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}$ for $i,j$ being NNN.
-We can obtain the spin Hamiltonian by using the relations:
-\begin{align}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
-\end{align}
-and $n_{i \uparrow} + n_{i \downarrow} = 1$. 
-and summing over the spin states. The resulting effective spin Hamiltonian is:
-
-\begin{align}
-\label{MKMHeff}
-&\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
-\end{align}
-
-Where:
+We can obtain the spin Hamiltonian by using the relations \ref{SpinOperatorInv1} \ref{SpinOperatorInv2} and summing over the spin states.
+The resulting effective spin Hamiltonian is \ref{MKMHeff0} with renormalized coupling constants:
 
@@
 Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
-This model is relevant for studying many-body localization phenomena \cite{Protopopov}.
+This model is relevant for studying many-body localization phenomena \cite{Protopopov2018}.
 \end{subsection}

### 2019-01-31 Chapters/Chap3/ModelsNNN.tex
Add some references

@@
 
+Such a Hamiltonian was first proposed by S.
+A.
+Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}.
+Experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.
+This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
+
 Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.

### 2019-01-31 Chapters/Chapter3.tex
moar
Add some references

@@
-\chapter{Perturbing the lattice}
+\chapter{Effective Spin Hamiltonian}
 
-In this chapter we will derive an effective spin Hamiltonian for different models in the presence of a high frequency electromagnetic perturbation.
-The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
-This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:
-
-\begin{equation*}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role.
-The electromagnetic perturbation is then introduced via the Peierls substitution.
-We reproduce the result in section \ref{Section3Hubbard}.
-In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions.
-The simplest model with spin orbit interaction is \ref{Hubbard}:
-
-\begin{equation*}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.
-In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
-
-In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator.
-For this case we examine the Kane-Mele-Hubbard model.
-The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
-This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.
-
-Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
-
-\input{Chapters/Chap3/TDHeff}
-
-\input{Chapters/Chap3/HNoSoi}
-
-\input{Chapters/Chap3/HWithSoi}
-
-\input{Chapters/Chap3/ModelsNNN}
-
-\input{Chapters/Chap3/OtherHams}
-
-\begin{subappendices}
-\begin{section}{Peierls Substitution}
-\label{AP3A}
-
-In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the lattice \ref{LaticeHam} to:
+In this chapter we will start with a Hamiltonian
 
 \begin{equation}
-\label{HamEMF}
-  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
+\label{Ham1}
+\hat{H} = \sum_{i=1}^{N_e} \hat{H}^{(1)}(\textbf{r}_i) + \frac{1}{2} \sum_{\substack{i,j = 1 \\ i \neq j}} ^ {N_e} v(\textbf{r}_i - \textbf{r}_j)
 \end{equation}
 
-Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian.
-We define a new set of Wannier functions in terms of those defined in \ref{Wannier2}, and obtain the new Bloch functions.
+where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian:
+
+\begin{equation}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\bs{\sigma}\bs{\nabla}V(\textbf{r}) \times \textbf{p}
+\end{equation}
+
+Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $\text{U}(\bs{r})$ is a periodic potential.
+The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
+The original Hubbard model, was developed to describe the single-band magnetism \cite{Hubbard1963}, it also describes the transition between conducting and insulating systems, predicting the existence of Mott insulators, materials which should be conducting according to band theory, but they are insulating due to electron-electron interactions.
+
+We will consider a half filled system in the strong coupling limit.
+Ignoring electron hopping and spin orbit interaction, the ground state of this system is massively degenerated.
+We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
+This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
+
+\begin{section}{Single particle in a periodic potential}
+
+First we will define a suitable basis for the single particle wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
+
+\begin{equation}
+\label{LaticeHam}
+\hat{H}^{(1)}_{\text{NSOI}}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r})
+\end{equation}
+
+Where $\text{U}(\textbf{r})$ has the symmetry of the lattice, i.e.
+$\text{U}(\textbf{r} + \textbf{R}) = \text{U}(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
+Let $\hat{H}^{(1)}_{\text{NSOI}}$ act on a Hilbert space $\mathcal{H}$ and let $\ket{\phi} \in \mathcal{H}$, then, the group of translation symmetries defined by $\bra{\bs{r}} T_{\textbf{R}} \ket{\phi} = \bra{\bs{r} + \bs{R}} \ket{\phi}$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong.
+If $\Gamma^{\textbf{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\textbf{R}}\ket{\phi_{n, \textbf{k}}} = \Gamma^{\textbf{k}}(\textbf{R}) \ket{\phi_{n, \textbf{k}}}$.
+Now, imposing periodic boundary conditions, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
+This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
+Therefore, for a wavefunction in a periodic lattice we have:
+
+\begin{equation}
+\label{Bloch1}
+\bra{\bs{r}+\bs{R}} \ket{\phi_{n, \textbf{k}}} = e^{i\textbf{k}\textbf{R}}\bra{\bs{r}} \ket{\phi_{n, \textbf{k}}}
+\end{equation}
+
+Which is the well-known Bloch function form.
+Here, $n$ is called the band index, and $\textbf{k}$ is the quasimomentum.
+The energy of this wavefunction is $\epsilon_{n \textbf{k}}$.
+Notice that both $\phi_{n,\textbf{k}}$ and $\epsilon_{n \textbf{k}}$ are periodic functions of $\textbf{k}$ in the reciprocal lattice.
+
+The Bloch function is extended over the whole crystal volume $V$.
+We would like to work with a localized basis.
+An alternative orthonormal basis are the Wannier functions $\ket{\psi_{in}}$, defined in terms of the Bloch functions as:
 
 \begin{align}
-\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
-\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
+\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
+\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\textbf{k}\textbf{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
 \end{align}
 
-Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:
-
-\begin{align*}
-\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
-&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
-&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
-\end{align*}
-
-And so, the matrix elements as in the case without field except for a phase:
-
-\begin{equation}
-\label{PeierlsMtxElem}
-t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
-\end{equation}
-
-When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.
-
-Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
-
-\begin{align*}
-  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
-  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
-\end{align*}
-
-Therefore relation \ref{PeierlsMtxElem} still holds.
+Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
+Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+From now on we will restrict ourselves to a fixed band, so we will drop the band index.
+Additionally, we will include the spin state, therefore the basis states will have two quantum numbers one for the site and one for the spin state.
+We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant.
+Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
 
@@
 
-\begin{section}{Identities}
-\label{AP3B}
-Let $Z(t)$ be an operator dependent on the parameter $t$. Then:
+\begin{section}{Derivation of the single-band Hubbard model}
+
+In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
+Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\ket{j\sigma}$.
+In this basis, the second quantized form of \ref{Ham1} is:
+
+\begin{equation}
+\hat{H} = \sum_{i,j,\sigma, \sigma'} \bra{i\sigma} \hat{H}^{(1)} \ket{j\sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\end{equation}
+
+Where we assumed $\hat{v}$ to be spin independent. This can be rewritten as:
+
+\begin{equation}
+\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\end{equation}
+
+Where $t_{ij} = -\bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = -\bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
+Notice that $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$, for example, in the $x$ component:
 
 \begin{align*}
-d_t e^{Z} &= d_t \sum_{n=0}^\infty \frac{1}{n!} Z^n = \sum_{n=0}^\infty \sum_{m=0}^{n-1} \frac{1}{n!} Z^m \frac{\partial Z}{\partial t} Z^{n-m-1} = \\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{1}{(m+p+1)!}Z^m \frac{\partial Z}{\partial t} Z^p = \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{m!p!}{(m+p+1)!} \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} =\\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \int_0^1 dx x^m (1-x)^p \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} = \int_0^1 dx e^{Zx} \frac{\partial Z}{\partial t} e^{Z(1-x)} = \\
-&= \int_0^1 dx \sum_{n=0}^\infty \frac{1}{n!} \left[xZ, \dots, \left[xZ, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
+\Delta_{ij,x} &= -\bra{i} \lambda (\partial_y V(\bs{r}) p_z - \partial_z V(\bs{r}) p_y) \ket{j} = i \hbar \lambda \int d \bs{r} \phi_i(\bs{r})^* (\partial_y V(\bs{r}) \partial_z - \partial_z V(\bs{r}) \partial_y) \phi_j(\bs{r}) = \\
+&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z(\phi_i(\bs{r})^*\partial_y V(\bs{r}) - \partial_y(\phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
+&= -i\hbar\lambda \int d\bs{r} \left[ \partial_z \phi_i(\bs{r})^* \partial_y V(\bs{r}) - \partial_y \phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
+&= \int d\bs{r} \phi_j(\bs{r}) \lambda (\bs{\nabla}V(\bs{r}) \times \bs{p})_x \phi_i(\bs{r})^* = - \Delta_{ji,x}
 \end{align*}
 
-Where we used the Beta function $\int_0^1 dx x^m (1-x)^p = \frac{m!p!}{(m+p+1)!}$ and we also used the Baker–Campbell–Hausdorff expansion for $e^{xZ}\frac{\partial Z}{\partial t}e^{-xZ}$ and $\int_0^1 x^n = \frac{1}{n+1}$.
-Therefore we proved:
+Therefore $\bs{\Delta}_{ii} = 0$. Notice also that $\bs{\Delta}_{ij}$ is purely imaginary.
+We can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
+
+\begin{itemize}
+\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\boldsymbol{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
+In an isotropic system we can approximate:
 
 \begin{equation}
-\label{SneidersID}
-d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \text{ad}_Z ^n \left(\frac{\partial Z}{\partial t}\right) e^Z
+t_{ij} = \begin{cases}
+             t,  & \text{for } (i,j) \text{ nearest neighbous} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
 \end{equation}
 
-Where $\text{ad}_A(B) = [A,B]$.
+and
+
+\begin{equation}
+\bs{\Delta}_{ij} = \begin{cases}
+             \bs{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
+             0,  & \text{otherwise}
+       \end{cases} \quad
+\end{equation}
+
+Hubbard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
+
+\item Taking into account the locality of the Wannier functions and the Coulomb interaction, the dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$.
+Terms with $i=k$ and $j=l$ also contribute when $i, j$ are nearest neighbours.
+Therefore we approximate:
+
+\begin{equation}
+\bra{ij} \hat{v} \ket{kl} =
+	\begin{cases}
+		\text{U}, & \text{if } i=j=k=l \\
+		\text{V}, & \text{if } i=k \text{ and } j=l \text{ where } (i,j) \text{ nearest neighbours} \\
+		0, & \text{otherwise}
+	\end{cases}						
+\end{equation}
+
+Where we defined:
+
+\begin{align}
+\text{U} &= \frac{1}{2} \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}')^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}') \phi(\bs{r}) \\
+\text{V} &= \int d\bs{r} d\bs{r}' \phi(\bs{r})^* \phi(\bs{r}'-\bs{R}_1)^* \hat{v}(\bs{r}-\bs{r}') \phi(\bs{r}'-\bs{R}_1) \phi(\bs{r})
+\end{align}
+
+Where $\phi(\bs{r})$ is the Wannier function centered at the origin and $\bs{R}_1$ is a nearest neighbour lattice vector.
+Notice that we made explicit use of the translational invariance of the system.
+Also, for $i=j=k=l$ the Pauli principle requires $\sigma' = -\sigma$.
+
+\end{itemize}
+
+Taking these approximations and writing $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{j \sigma'} \hat{c}_{i \sigma} = \hat{n}_{i \sigma} \hat{n}_{j \sigma'}$, we obtain:
+
+\begin{equation}
+\label{HubbardWithNonLocalInt}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \text{V} \sum_{i,j,\sigma,\sigma'}  \hat{n}_{i \sigma} \hat{n}_{j \sigma'}
+\end{equation}
+
+Now, in a half filling system this Hamiltonian can be well approximated by an effective Hamiltonian without non local Coulomb interactions:
+
+\begin{equation}
+\label{Intermediate}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}^* \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\text{U}^* = \text{U} - \text{V}$.
+The physical reason for this is that the energy difference when the Coulomb interaction pushes an electron from a double occupied site to an empty site is $\text{U}-\text{V}$ in \ref{HubbardWithNonLocalInt}, because the number of double occupied sites is reduced by one but the number of adjacent occupied sites is increased by one.
+This is illustred in Figure \ref{Fig2.1}.
+A more rigouros derivation of this effective model can be found in \cite{Schuler2013}.
+Altough $\text{V} < \text{U}$, they can be comparable in magnitude, and $\text{U}^*$ can be reduced by a factor of $0.5$ or more.
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.5\linewidth]{../Figures/non_local_coulomb.png}
+  \caption{Image from \cite{Schuler2013}.
+In a half-filled system decreasing the number of double occupancies increases the number of adjacent occupied sites, and so the energy difference is reduced to $\text{U}-\text{V}$.}
+\label{Fig2.1}
+\end{figure}
+
+Now, abusing the notation and writing $\text{U} = \text{U}^*$ we arrive at the model that we will use in the next sections:
+
+\begin{equation}
+\label{Hubbard}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+\begin{subsection}{Hubbard model}
+
+In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
+This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}.
+Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
+Originally the Hubbard model was proposed to describe electron correlations in $d$ or $f$ bands in transition metals.
+The result was a simplified model to predict metal-insulator transitions.
+However, it exhibits much richer phenomena.
+It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
+they should be conductors according to band theory, but electron-electron interactions keep away from).
+Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
+
+\end{subsection}
 
@@
 
+\begin{section}{Effective Hamiltonian for half-filling system}
+
+At half filling and in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
+There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
+The ground state energy is $0$.
+The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
+The energy of one of these states is $\text{U}$.
+Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
+Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
+
+Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
+$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
+In second order we have:
+
+\begin{equation}
+\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
+\end{equation}
+
+The sum being over all excited states.
+Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
+These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
+This means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
+Now,
+
+\begin{align}
+\label{PertNoEMF}
+&\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
+& \bra{\phi'} \hat{H}_J + \hat{H}_D + \hat{H}_P \ket{\phi}
+\end{align}
+
+In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
+We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
+We defined:
+
+\begin{align}
+\hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \\
+\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \\
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
+\end{align}
+
+Let us now introduce the on-site spin operators:
+
+\begin{equation}
+\label{SpinOperators}
+\boldsymbol{S}_i = \frac{1}{2} \sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \boldsymbol{\sigma}_{\sigma, \sigma'} \hat{c}_{i \sigma'}
+\end{equation}
+
+Which satisfy:
+
+\begin{align}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\end{align}
+
+In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:
+
+\begin{align*}
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\}= \\
+&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+\end{align*}
+
+Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
+We also used the well known property $tr(\bs{\sigma}^a\bs{\sigma}^b)=2\delta_{a,b}$.
+And second:
+
+\begin{align*}
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+ &= \left\{ \right.
+	\overbrace{0}^{\uparrow \uparrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^+)S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^-)(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
+	\overbrace{2\Delta_{ij}^z S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^+ (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
+	\overbrace{0}^{\uparrow \downarrow \uparrow \downarrow} +
+	\overbrace{0}^{\uparrow \downarrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^+ S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^- S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
+	\overbrace{0}^{\downarrow \uparrow \uparrow \downarrow} +
+	\overbrace{0}^{\downarrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^- (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
+	& \overbrace{(-2\Delta_{ij}^z)S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^+) (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^-) S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} +
+	\overbrace{0}^{\downarrow \downarrow \downarrow \downarrow}
+\left. \right\} = \\
+&= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
+&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+\end{align*}
+
+Where in the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
+We also used that for any vector $\vec{v}$ we can define $\bs{\sigma}_{12}\vec{v} = v^x+iv^y = v^+$, $\bs{\sigma}_{21}\vec{v} = v^x-iv^y = v^-$, $\bs{\sigma}_{11}\vec{v} = v^z$ and $\bs{\sigma}_{22}\vec{v} = -v^z$.
+Also, for any two vectors $\vec{a}$ and $\vec{b}$, the following applies $a^-b^z-a^zb^- = -i(\vec{a}\times\vec{b})^-$, $a^zb^+-a^+b^z=-i(\vec{a}\times\vec{b})^+$, $a^+b^--a^-b^+=-2i(\vec{a}\times \vec{b})^z$ and $a^+b^-+a^-b^+=2(a^xb^x+a^yb^y)$.
+
+Also:
+
+\begin{align*}
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= \overbrace{\Delta_{ij}^z\Delta_{ij}^z(\frac{1}{2}+S_i^z)(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^z\Delta_{ij}^+S_i^-(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^z\Delta_{ij}^-(\frac{1}{2}+ S_i^z)(-S_j^+)}^{\uparrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^z(-\Delta_{ij}^z) S_i^-(-S_j^+)}^{\uparrow \uparrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^+\Delta_{ij}^z (\frac{1}{2}+S_i^z)(-S_j^-)}^{\uparrow \downarrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^+\Delta_{ij}^+S_i^-(-S_j^-)}^{\uparrow \downarrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^+\Delta_{ij}^-(\frac{1}{2}+S_i^z)(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^+(-\Delta_{ij}^z) S_i^-(\frac{1}{2}+S_j^z)}^{\uparrow \downarrow \downarrow \downarrow} + \\
+	&\overbrace{\Delta_{ij}^-\Delta_{ij}^z S_i^+(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \uparrow} +
+	\overbrace{\Delta_{ij}^-\Delta_{ij}^+(\frac{1}{2}-S_i^z)(\frac{1}{2}-S_j^z)}^{\downarrow \uparrow \uparrow \downarrow} +
+	\overbrace{\Delta_{ij}^-\Delta_{ij}^-S_i^+(-S_j^+)}^{\downarrow \uparrow \downarrow \uparrow} +
+	\overbrace{\Delta_{ij}^-(-\Delta_{ij}^z) (\frac{1}{2} - S_i^z) (-S_j^+)}^{\downarrow \uparrow \downarrow \downarrow} + \\
+	& \overbrace{(-\Delta_{ij}^z)\Delta_{ij}^z S_i^+(-S_j^-)}^{\downarrow \downarrow \uparrow \uparrow} +
+	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^+ (\frac{1}{2}-S_i^z)(-S_j^-)}^{\downarrow \downarrow \uparrow \downarrow} +
+	\overbrace{(-\Delta_{ij}^z)\Delta_{ij}^- S_i^+(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \uparrow} + \\
+	&+\overbrace{(-\Delta_{ij}^z)(-\Delta_{ij}^z)(\frac{1}{2}-S_i^z)(\frac{1}{2}+S_j^z)}^{\downarrow \downarrow \downarrow \downarrow} = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z (-2(\Delta_{ij}^z)^2 + 2\Delta_{ij}^+\Delta_{ij}^-) + S_i^zS_j^+(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^zS_j^-(-2\Delta_{ij}^z\Delta_{ij}^+) +\\
+&+ S_i^+S_j^z(-2\Delta_{ij}^z\Delta_{ij}^-) + S_i^+S_j^+(-\Delta_{ij}^-\Delta_{ij}^-) + S_i^+S_j^-(\Delta_{ij}^z)^2 +\\
+&+ S_i^-S_j^z(-2\Delta_{ij}^z\Delta_{ij}^+) + S_i^-S_j^+(\Delta_{ij}^z)^2 + S_i^-S_j^-(-(\Delta_{ij}^+)^2) = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + S_i^zS_j^z(-2(\Delta_{ij}^z)^2+2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2 + S_i^zS_j^y(-4\Delta_{ij}^z\Delta_{ij}^y)+S_i^zS_j^x(-4\Delta_{ij}^z\Delta_{ij}^x) + \\
+&+S_i^yS_j^z(-4\Delta_{ij}^y\Delta_{ij}^z)+S_i^yS_j^y(2(\Delta_{ij}^z)^2-2(\Delta_{ij}^y)^2+2(\Delta_{ij}^x)^2)+S_i^yS_j^x(-4\Delta_{ij}^y\Delta_{ij}^x) + \\
+&+ S_i^xS_j^z(-4\Delta_{ij}^x\Delta_{ij}^z) + S_i^xS_j^y(-4\Delta_{ij}^x\Delta_{ij}^y) + S_i^xS_j^x(2(\Delta_{ij}^z)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^x)^2) = \\
+&= \frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \begin{pmatrix}
+S_i^x & S_i^y & S_i^z
+\end{pmatrix}
+\\
+&\begin{pmatrix}
+2(\Delta_{ij}^z)^2 + 2(\Delta_{ij}^y)^2 - 2(\Delta_{ij}^x)^2 & -4\Delta_{ij}^x\Delta_{ij}^y & -4\Delta_{ij}^x\Delta_{ij}^z \\ -4\Delta_{ij}^y\Delta_{ij}^x & +2(\Delta_{ij}^x)^2-2(\Delta_{ij}^y)^2 +2(\Delta_{ij}^z)^2 & -4\Delta_{ij}^y\Delta_{ij}^z \\ -4\Delta_{ij}^z\Delta_{ij}^x & -4\Delta_{ij}^z\Delta_{ij}^y & 2(\Delta_{ij}^x)^2+2(\Delta_{ij}^y)^2-2(\Delta_{ij}^z)^2
+\end{pmatrix}
+\begin{pmatrix}
+S_j^x \\ S_j^y \\ S_j^z
+\end{pmatrix} = \\
+&\frac{(\Delta_{ij}^z)^2+\Delta_{ij}^+\Delta_{ij}^-}{2} + \sum_{\alpha, \beta} S_i^\alpha (4\Delta_{ij}^\alpha\Delta_{ij}^\beta - \delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2) S_j^\beta
+\end{align*}
+
+These three relations are important and will be used in the next chapter:
+
+\begin{align}
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2} \\
+& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
+\end{align}
+
+Now introducing the spin operators into  $\hat{H}_J$ with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
+
+\begin{align*}
+\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
+\end{align*}
+
+The constant term can be neglected leaving:
+
+\begin{equation}
+\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i\bs{S}_j
+\end{equation}
+
+Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
+
+\begin{align*}
+\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j
+\end{align*}
+
+Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$, notice that being $\bs{\Delta}_{ij}$ purely imaginary, $\bs{D}_{ij}^0$ is a real vector. 
+Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ leads to:
+
+\begin{align*}
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&\frac{1}{\text{U}} \sum_{\langle i,j \rangle} \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta = \sum_{\langle i,j \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j
+\end{align*}
+
+With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
+The total effective Hamiltonian is:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right) \label{HeffNOEMF}
+\end{equation}
+
+With:
+
+\begin{align}
+J_{ij}^0 &= \frac{2t^2}{\text{U}} \label{Jij0} \\
+\bs{D}_{ij}^0 &= \frac{4it}{\text{U}}\bs{\Delta}_{ij} \label{Dij0} \\ 
+\bs{\Gamma_{ij}}^{\alpha \beta} &= \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta) \label{Gij0}
+\end{align}
+
+The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
+Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
+However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach.
+$\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
+interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}.
+In the next chapter we will examine this further.
+Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
+
+\end{section}
+
+\begin{subsection}{Next-nearest neighbor hopping}
+This analysis can be easily extended to electronic Hamiltonians including next-nearest neighbor (NNN) hopping term. The simplest example of such a Hamiltonian is:
+
+\begin{equation}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma}t_{1}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -\sum_{\langle \langle i,j \rangle \rangle, \sigma} t_{2}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\langle \langle i,j \rangle \rangle$ denotes sum over NNN. If we follow the procedure as before we will obtain an effective spin Hamiltonian:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = J_1\sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j + J_2\sum_{\langle \langle i,j \rangle \rangle}\bs{S}_i\bs{S}_j
+\end{equation}
+
+Where $J_1 = \frac{t_1^2}{\text{U}}$ and $J_2 = \frac{t_2^2}{\text{U}}$.
+This Hamiltonian is known as $J_1-J_2$ Heisenberg model.
+This model has been extensively studied, and the $J_1-J_2-J_3$ is also of interest \cite{Reuther2011}.
+
+Notice that we can also obtain a $J_1-J_2$ Heisenberg model starting simply from a NN hamiltonian $\hat{H} = -\sum_{\langle i,j \rangle, \sigma}t_{1}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
+This is because the NNN exchange interaction comes from the possibility of the process $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ being $i,j$ NNN.
+This process is available when sites $i, j$ have opposite spins (otherwise it would violate the Pauli principle).
+Now, when $i,j$ are NNN, we can consider the fourth order process $i\sigma \rightarrow k\sigma \rightarrow j\sigma \rightarrow k\sigma \rightarrow i\sigma$, where $k$ is a site between $i$ and $j$.
+The resulting effective spin Hamiltonian has exchange couplings $J_1 = 2\frac{t_1^2}{\text{U}} - 8 \frac{t_1^4}{\text{U}^3}$ and $J_2 = 2\frac{t^4}{\text{U}}$.
+A rigorous derivation can be found in \cite{MacDonald1988}.
+
+\end{subsection}
+
+\begin{subsection}{Introducing disorder}
+
+It is possible to consider a disordered Hubbard model by adding random uncorrelated on-site energies. We neglect the SOI term for simplicity, then the disordered Hubbard model can be written as:
+
+\begin{equation}
+\label{DisorderedHubbardModel}
+\hat{H} = -t\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} +
+\sum_{i \sigma} \epsilon_i \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+
+Where $\epsilon_i$ are random variable $\epsilon_i \in [-W,W]$.
+At half filling we can derive an effective Hamiltonian using the same procedure as before.
+The second order virtual hopping $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ will give rise to an exchange spin interaction.
+In this case, however, the intermediate energy is $\text{U} + (\epsilon_j - \epsilon_i)$.
+Therefore the spin Hamiltonian will be:
+
+\begin{equation}
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \frac{2t^2}{\text{U} + (\epsilon_j - \epsilon_i)} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i\bs{S}_j
+\end{equation}
+
+Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
+This model is relevant for studying many-body localization phenomena \cite{Protopopov2018}.
+
+\end{subsection}
+
+\begin{section}{AFM dynamics}
+
+In this section we will show how a continuum one dimensional model can be obtained from the discrete Heisenberg Hamiltonian in order to describe the AFM order and its dynamics \cite{Tveten2016}.
+We write the Heisenberg Hamiltonian as $\hat{H} = J \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j - K \sum_i S_{iz}^2$ with $J>0$ and $K$ is the anisotropy energy.
+Let the lattice be a one dimensional chain with $2N$ sites, such lattice can be described by the repetition of $N$ unit cells consisting of two sites $\alpha$ and $\beta$ for the left and right site respectively.
+Then the ground state of this Hamiltonian is double degenerated and is obtained by aligning the spins in the $\alpha$ sites in the $\hat{z}$ direction and the $\beta$ spins in the $-\hat{z}$ direction or vice versa.
+Let us introduce the parameters:
+
+\begin{align}
+\bs{m}_i &= \frac{\bs{S}_{\alpha}^i + \bs{S}_{\beta}^i}{2S} \\
+\bs{l}_i &= \frac{\bs{S}_{\alpha}^i - \bs{S}_{\beta}^i}{2S}
+\end{align}
+
+Where $S$ is the spin angular momentum in units of $\hbar$. Inverting these relations, introducing them into the Hamiltonian and neglecting edge terms we obtain:
+
+\begin{align}
+\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
+& 2JS^2\sum_i^{N} (\bs{m}_i^2-\bs{l}_i^2)+\frac{JS^2}{2}\sum_i^{N-1}\left[(\bs{l}_{i+1}-\bs{l}_i)^2-(\bs{m}_{i+1}-\bs{m}_i)^2 \right] \nonumber \\
+& + JS^2\sum_i^{N-1} \left[ \bs{m}_i(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
+\end{align}
+
+Now we can take the continuum limit with:
+
+\begin{align*}
+\bs{m}_i &\rightarrow \bs{m}(x) \\
+\bs{l}_i &\rightarrow \bs{l}(x) \\
+2d \sum_i &\rightarrow \int dx \\
+\hat{H} &\rightarrow \int \frac{dx}{2d} \mathcal{H}(\bs{l},\bs{m})
+\end{align*}
+
+This, together with $\bs{m}_i-\bs{l}_i = 2\bs{m}_i-1$ and $\bs{m}_{i+1} \rightarrow \bs{m}(x) + 2d \partial_x\bs{m}(x)$ gives:
+
+\begin{equation}
+\mathcal{H}(\bs{l},\bs{m}) = JS^2\left\{ 4|\bs{m}|^2 + |\partial_x\bs{l}'|^2 -  |\partial_x\bs{m}'|^2 +(\bs{m}\partial_x\bs{l} -\bs{l}\partial_x\bs{m}) \right\} -KS^2\left\{ (\bs{l}\hat{z})^2 + (\bs{m}\hat{z})^2 \right\}
+\end{equation}
+
+\end{section}
+
+\begin{subappendices}
+\begin{section}{Crystal structure and reciprocal lattice}
+\label{AP1A}
+
+Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
+
+\begin{equation}
+\bs{R} = \sum_{\mu=1}^3 m_\mu \bs{a}_\mu
+\end{equation}
+
+Where $m_\mu$ are integers.
+The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
+The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
+The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
+With this notation the first Brillouin zone is:
+
+\begin{equation}
+\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
+\end{equation}
+
+Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
+
+In the case of a cubic lattice we have $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
+
+In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
+
+\begin{align}
+\bs{a}_1 &= \frac{a_0}{2} \left(3, \sqrt{3} \right) \\
+\bs{a}_2 &= \frac{a_0}{2} \left(3, -\sqrt{3} \right)
+\end{align}
+
+Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
+Each unit cell contains two atoms, dividing the lattice into two sublattices, usually denoted A and B.
+The reciprocal lattice is defined by the vectors:
+
+\begin{align}
+\bs{b}_1 &= \frac{2\pi}{3a_0} \left(1, \sqrt{3} \right) \\
+\bs{b}_2 &= \frac{2\pi}{3a_0} \left(1, -\sqrt{3} \right)
+\end{align}
+
+These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
+
+\begin{align}
+\bs{R}^A_1 &= \frac{a_0}{2} \left( 1, \sqrt{3} \right) \\
+\bs{R}^A_2 &= \frac{a_0}{2} \left( 1, -\sqrt{3} \right) \\
+\bs{R}^A_3 &= a_0 \left( -1, 0 \right)
+\end{align}
+
+The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/honeycomb_lattice.png}
+  \caption{Image from a web source.
+In Fig.
+(a) the unit cell is sketched and the sublattices A and B are shown in blue and red respectively.
+In Fig.
+(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
+\label{Fig2.2}
+\end{figure}
+\end{section}
 \end{subappendices}

### 2019-02-04 Chapters/Chapter2.tex
TB and cdots

@@
 \section{Tight binding}
+
+When the electrons are strongly localized in the atom cores, the wavefunction describing such an electron is similar to the corresponding atomic orbital.
+Therefore it is natural to consider linear superposition of atomic orbitals as an anstatz for the crystal electron states.
+
+Let $\phi_i(\bs{r})$ be the i-\textit{th} eigenstate of the atomic Hamiltonian $\hat{H}_a(\bs{r}) = -\frac{\hbar^2p^2}{2m} + V_a(\bs{r}-bs{r}_n)$ with energy $E_i$ and where $V_a(\bs{r})$ is the atomic potential.
+The crystal Hamiltonian is:
+
+\begin{equation}
+\label{CrystalHam}
+\hat{H} = -\frac{\hbar^2p^2}{2m} + \sum_n V_a(\bs{r}-\bs{r}_n)
+\end{equation}
+
+An electron localized around the atom at $\bs{r}_n$ will mainly feel the potential of that atom, and the potential of the rest of the atoms will be a perturbation to the free atom problem.
+That is, we can spit \ref{CrystalHam} into:
+\begin{equation}
+\label{SplitCrystalHam}
+\hat{H} = \hat{H}_a + v(\bs{r}-\bs{r}_n)
+\end{equation}
+Where $v(\bs{r}-\bs{r}_n) = \sum_{m \neq n} V_a(\bs{r}-\bs{r}_m)$ is a small perturbation.
+We can expect the crystal electron to retain the properties of the free atom electron, and so, it is natural to describe the crystal electron as a superposition of atomic orbitals.
+Thus, we will try to find solutions of the form:
+
+\begin{equation}
+\psi_i(\bs{r}) = \sum_n b_i(\bs{r}_n) \phi_i(\bs{r}-\bs{r}_n)
+\end{equation}
+
+Now, the Bloch theorem states that an eigenfunction of the crystal Hamiltonian should only change by a phase from site to site, that is $\psi_i(\bs{r}+\bs{r}_m)=e^{i \bs{k} \cdot \bs{r}_m}\psi_i(\bs{r})$, where $\bs{k}$ is the crystal momentum of the Bloch wave.
+We can see that see implies $b_i(\bs{r}_m) = e^{i \bs{k} \cdot \bs{r}_m}b_i(0)$, by normalizing $\psi_i(\bs{r})$ we find $b_i(0) = \frac{1}{\sqrt{N}}$, where $N$ is the number of atoms in the crystal.
+We therefore obtain:
+
+\begin{equation}
+\psi_{i\bs{k}}(\bs{r}) = \frac{1}{\sqrt{N}}\sum_n  e^{i \bs{k} \cdot \bs{r}_n} \phi_i(\bs{r}-\bs{r}_n)
+\end{equation}
+
+The energy of this state is $E_i(\bs{k}) = \bra{\psi_{i\bs{k}}} \hat{H} \ket{\psi_{i\bs{k}}}$, using \ref{SplitCrystalHam} this can be written as:
+
+\begin{equation}
+E_i(\bs{k}) = \frac{1}{N} \sum_{n,m} e^{i\bs{k}\cdot(\bs{r}_n-\bs{r}_m)} \int \phi_i^* (E_i+v(\bs{r}-\bs{r}_n)) \phi_i(\bs{r}-\bs{r}_n) d\bs{r}
+\end{equation}

### 2019-02-04 Chapters/Chapter3.tex
TB and cdots

@@
 \begin{equation}
-\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\bs{\sigma}\bs{\nabla}V(\textbf{r}) \times \textbf{p}
+\hat{H}^{(1)}(\textbf{r}) = -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) + \lambda\bs{\sigma}\cdot\bs{\nabla}V(\textbf{r}) \times \textbf{p}
 \end{equation}
@@
 We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
-This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
+This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\cdot\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
 
@@
 
-Where $\text{U}(\textbf{r})$ has the symmetry of the lattice, i.e.
-$\text{U}(\textbf{r} + \textbf{R}) = \text{U}(\textbf{r})$ for all Bravais lattice vectors $\textbf{R}$(\ref{AP1A}).
-Let $\hat{H}^{(1)}_{\text{NSOI}}$ act on a Hilbert space $\mathcal{H}$ and let $\ket{\phi} \in \mathcal{H}$, then, the group of translation symmetries defined by $\bra{\bs{r}} T_{\textbf{R}} \ket{\phi} = \bra{\bs{r} + \bs{R}} \ket{\phi}$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong.
-If $\Gamma^{\textbf{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\textbf{R}}\ket{\phi_{n, \textbf{k}}} = \Gamma^{\textbf{k}}(\textbf{R}) \ket{\phi_{n, \textbf{k}}}$.
-Now, imposing periodic boundary conditions, $\Gamma^{\textbf{k}}(\textbf{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
-This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\textbf{k}}(R) = e^{i \textbf{k} \textbf{R}}$.
+Where $\text{U}(\bs{r})$ has the symmetry of the lattice, i.e.
+$\text{U}(\bs{r} + \bs{R}) = \text{U}(\bs{r})$ for all Bravais lattice vectors $\bs{R}$(\ref{AP1A}).
+Let $\hat{H}^{(1)}_{\text{NSOI}}$ act on a Hilbert space $\mathcal{H}$ and let $\ket{\phi} \in \mathcal{H}$, then, the group of translation symmetries defined by $\bra{\bs{r}} T_{\bs{R}} \ket{\phi} = \bra{\bs{r} + \bs{R}} \ket{\phi}$ is an abelian group, therefore its irreducible representations are one-dimensional, that is, within an energy level $n$ the wavefunctions of that level transform according to the representation they belong.
+If $\Gamma^{\bs{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\bs{R}}\ket{\phi_{n, \bs{k}}} = \Gamma^{\bs{k}}(\bs{R}) \ket{\phi_{n, \bs{k}}}$.
+Now, imposing periodic boundary conditions, $\Gamma^{\bs{k}}(\bs{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
+This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\bs{k}}(R) = e^{i \bs{k} \cdot \bs{R}}$.
 Therefore, for a wavefunction in a periodic lattice we have:
@@
 \label{Bloch1}
-\bra{\bs{r}+\bs{R}} \ket{\phi_{n, \textbf{k}}} = e^{i\textbf{k}\textbf{R}}\bra{\bs{r}} \ket{\phi_{n, \textbf{k}}}
+\bra{\bs{r}+\bs{R}} \ket{\phi_{n, \textbf{k}}} = e^{i\bs{k}\cdot\bs{R}}\bra{\bs{r}} \ket{\phi_{n, \textbf{k}}}
 \end{equation}
@@
 \begin{align}
-\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
-\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\textbf{k}\textbf{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
+\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\cdot\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
+\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\bs{k}\cdot\bs{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
 \end{align}
@@
 \begin{equation}
-\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \boldsymbol{\Delta}_{ij} \boldsymbol{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
+\hat{H} = -\sum_{i,j,\sigma, \sigma'} (\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma, \sigma'}) \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \frac{1}{2} \sum_{i,j,k,l, \sigma, \sigma'} \bra{ij} \hat{v} \ket{kl} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}^\dagger \hat{c}_{l \sigma'} \hat{c}_{k \sigma}
 \end{equation}
@@
 \label{HubbardWithNonLocalInt}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \text{V} \sum_{i,j,\sigma,\sigma'}  \hat{n}_{i \sigma} \hat{n}_{j \sigma'}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \text{V} \sum_{i,j,\sigma,\sigma'}  \hat{n}_{i \sigma} \hat{n}_{j \sigma'}
 \end{equation}
@@
 \label{Intermediate}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}^* \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}^* \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 \label{Hubbard}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{ij} + \bs{\Delta}_{ij} \cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
 \end{equation}
@@
 Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
-$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
+$\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
 Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
@@
 &\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
-&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
-&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
 & \bra{\phi'} \hat{H}_J + \hat{H}_D + \hat{H}_P \ket{\phi}
@@
 \hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \\
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
 \end{align}
@@
 \begin{align}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \cdot\bs{S}_i\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
 \end{align}
@@
 \begin{align*}
-&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\boldsymbol{\sigma}_{\sigma'\sigma}^a \boldsymbol{\sigma}_{\sigma \sigma'}^b \right\}= \\
-&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right) = \sum_{\sigma \sigma'} \left\{ \frac{1}{4}\delta_{\sigma \sigma'} - \sum_{ab} S_i^aS_j^b 	\bs{\sigma}_{\sigma'\sigma}^a \cdot \bs{\sigma}_{\sigma \sigma'}^b \right\}= \\
+&= \frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\bs{S}_i\cdot\bs{S}_j
 \end{align*}
 
-Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
+Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\cdot\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\cdot\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
 We also used the well known property $tr(\bs{\sigma}^a\bs{\sigma}^b)=2\delta_{a,b}$.
@@
 \begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
  &= \left\{ \right.
@@
 &= 2\left\{ \Delta_{ij}^+ (S_i^-S_j^z - S_i^zS_j^-) + \Delta_{ij}^- (S_i^zS_j^+ - S_i^+S_j^z) + \Delta_{ij}^z (S_i^+S_j^- - S_i^-S_j^+) \right\} = \\
-&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j
+&= -2i\left\{ \Delta_{ij}^+ (\bs{S}_i\times\bs{S}_j)^- + \Delta_{ij}^- (\bs{S}_i\times\bs{S}_j)^+ + 2\Delta_{ij}^z (\bs{S}_i\times\bs{S}_j)^z \right\} = -4i \bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j
 \end{align*}
@@
 \begin{align*}
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &= \overbrace{\Delta_{ij}^z\Delta_{ij}^z(\frac{1}{2}+S_i^z)(\frac{1}{2}-S_j^z)}^{\uparrow \uparrow \uparrow \uparrow} +
@@
 \begin{align}
-&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) =\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \label{SpinRel1} \\
-&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\boldsymbol{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\boldsymbol{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \boldsymbol{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma_2 \sigma_3}\right)= -4i \boldsymbol{\Delta}_{ij} \boldsymbol{S}_i \times \boldsymbol{S}_j \label{SpinRel2} \\
-& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
+&\sum_{\sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right) = \nonumber \\
+&=\frac{1}{2} - \sum_{ab} S_i^aS_j^b	2\delta_{ab} = \frac{1}{2} - 2\bs{S}_i\cdot\bs{S}_j \label{SpinRel1} \\
+&\sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \nonumber \\
+&= -4i \bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j \label{SpinRel2} \\
+& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \nonumber \\
+&= \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
 \end{align}
@@
 \begin{align*}
-\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\boldsymbol{S}_j\boldsymbol{\sigma}_{\sigma \sigma'}\right) = \\
-&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\boldsymbol{S}_i\boldsymbol{S}_j \right)
+\hat{H}_{J} = &-\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right) = \\
+&-\frac{t^2}{\text{U}}\sum_{\langle i,j \rangle} \left( \frac{1}{2} - 2\bs{S}_i\cdot\bs{S}_j \right)
 \end{align*}
@@
 \begin{equation}
-\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i\bs{S}_j
+\hat{H}_{J} = \frac{2t^2}{\text{U}} \sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i\cdot\bs{S}_j
 \end{equation}
@@
 \begin{align*}
-\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
-&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j
+\hat{H}_D = &-\frac{t}{\text{U}} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3\sigma_4})\left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+&= +\frac{4it}{\text{U}} \sum_{\langle i,j \rangle} \bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j = \sum_{\langle i,j \rangle} \bs{D}_{ij}^0\cdot \bs{S}_i \times \bs{S}_j
 \end{align*}
@@
 \begin{align*}
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_3 \sigma_4}) \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma_3 \sigma_4}) \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \\
 &\frac{1}{\text{U}} \sum_{\langle i,j \rangle} \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta = \sum_{\langle i,j \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j
@@
 \begin{equation}
-\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\bs{S}_j + \bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right) \label{HeffNOEMF}
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \left( J_{ij}^0 \bs{S}_i\cdot\bs{S}_j + \bs{D}_{ij}^0 \cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right) \label{HeffNOEMF}
 \end{equation}
@@
 
-The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
+The $J_{ij}^0\bs{S}_i\cdot\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
 Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
 However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach.
-$\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
+$\bs{D}_{ij}^0 \cdot\bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
 interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}.
@@
 \begin{equation}
-\hat{H}_{\text{eff}} = J_1\sum_{\langle i,j \rangle} \bs{S}_i\bs{S}_j + J_2\sum_{\langle \langle i,j \rangle \rangle}\bs{S}_i\bs{S}_j
+\hat{H}_{\text{eff}} = J_1\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + J_2\sum_{\langle \langle i,j \rangle \rangle}\bs{S}_i\cdot\bs{S}_j
 \end{equation}
@@
 \begin{equation}
-\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \frac{2t^2}{\text{U} + (\epsilon_j - \epsilon_i)} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \bs{S}_i\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i\bs{S}_j
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} \frac{2t^2}{\text{U} + (\epsilon_j - \epsilon_i)} \bs{S}_i\cdot\bs{S}_j = \sum_{\langle i,j \rangle} \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \bs{S}_i\cdot\bs{S}_j = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i\cdot\bs{S}_j
 \end{equation}

### 2019-02-05 Paper/paper.tex
Rotate labels

@@
 In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
-In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:
+In these circumstances the system can be modeled by the Kane-Mele-Hubbard which we write as a sum of a kinetic term, an interaction term and a SOI term:
 
+\begin{equation}
+\label{MKMH}
+\hat{H}^0 = \hat{\mathcal{H}}_t + \hat{\mathcal{H}}_{\text{SOI}} + \hat{\mathcal{H}}_{\text{int}}
+\end{equation}
+Where:
 \begin{align}
-\label{MKMH}
-\hat{H}^0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \n \\
-	&-\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\text{U}\hat{D}
+&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
+&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
+&\hat{\mathcal{H}}_{\text{int}} = \text{U}\hat{D}
 \end{align}
@@
 We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes.
-In the strong coupling limit any state with a nonzero number of double occupancies ($d /neq 0$) will have much larger energy than those with $d=0$.
+In the strong coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
 We can therfore obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second order perturbation techniques in the hopping terms.
@@
 \begin{align}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \boldsymbol{S}_i\boldsymbol{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \bs{S}_i\cdot\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
 \end{align}
@@
 \label{MKMHeff0}
-&\hat{H}_{\text{eff}}^0 = \sum_{\langle i,j \rangle} J_{1,ij}^0\bs{S}_i\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}^0\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}^0 \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}^0 \bs{S}_j \right\}
+&\hat{H}_{\text{eff}}^0 = \sum_{\langle i,j \rangle} J_{1,ij}^0\bs{S}_i\cdot\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}^0\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}^0\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}^0 \bs{S}_j \right\}
 \end{align}
@@
 \label{Def_alpha}
-e\bs{R}_{ij}\vec{A} = \alpha_{ij} e^{i \theta_{ij}}
+e\bs{R}_{ij}\cdot\vec{A} = \alpha_{ij} e^{i \theta_{ij}}
 \end{equation}
@@
 \label{JacobiAnger}
-e^{ie\bs{R}_{ij}\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} 
+e^{ie\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} 
 \end{equation}
@@
 \begin{align}
-&\hat{H}_{\text{eff}}^{\text{Dis}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
+&\hat{H}_{\text{eff}}^{\text{Dis}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
 \end{align}

### 2019-02-05 Code/Chap3.R

@@ -60,12 +60,13 @@ tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,
                   "\\setlength\\PreviewBorder{0pt}",
                   "\\usepackage{amssymb}"))
 
-plot(x=range(field_energies), y = range(J1_factor), type='n', xlab = "$\\mathcal{E}$", ylab = '')
+plot(x=range(field_energies), y = range(J1_factor), type='n', xlab = "$\\mathcal{E}$", ylab = '', las =1)
 for (i in 1:length(frequencies)) {
   lines(x = field_energies, y = J1_factor[[i]], type = 'l', col = "green", lwd = 2, lty = i)
   lines(x = field_energies, y = D2_factor[[i]], type = 'l', col = "red", lwd = 2, lty = i)
 }
-legend("topright", legend = c("$\\frac{J_1}{J_1^0}$", "$\\frac{D_2}{D_2^0}$"), fill = c("green", "red"))
+mtext(text=paste0("$\\tilde{J_1}$",'\n',"$\\tilde{D_2}$"), side =2, line = 3, las=1)
+legend("topright", legend = c("$\\tilde{J_1}$", "$\\tilde{D_2}$"), fill = c("green", "red"))
 
 dev.off()
 tools::texi2pdf(paste0(current_file, '.tex'))

### 2019-02-06 Paper/paper.tex
Add Figures

@@
 \begin{document}
-\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–Moriya interactions in antiferromagnetic insulators}
+\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators}
 
@@
 $\sigma^{z}$ is the third Pauli matrix.
+\begin{figure}[t]
+\includegraphics[width=0.6\columnwidth]{../Figures/kmh.png}
+\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$.
+$\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
+\label{fig1}
+\vspace*{-6pt}
+\end{figure}
 We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes.
@@
 
+\begin{figure}[t]
+\includegraphics[width=0.6\columnwidth]{../Figures/NNvsNNN.pdf}
+\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
+The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$.
+Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.
+For $\tilde{J}_1$, similar results are obtained by Mentink et Al.
+\cite{Mentink2015}.}
+\label{fig2}
+\vspace*{-6pt}
+\end{figure}
+
 Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.

### 2019-02-06 Paper/paper.tex
style
more refs

@@
 
-In the prescence of an laser perturbation we can use the Peirls substitution to introduce the effect of the field trough the hopping amplitudes.
+\textit{Introducing laser perturbation}.
+In the prescence of an laser perturbation we can use the Peirls substitution to include the effect of the field trough the hopping amplitudes.
 We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
@@
 \end{figure}
+A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S.
+A.
+Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}.
+Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.
+This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
 
@@
 %\begin{thebibliography}
-\bibliography{paper}
+\bibliography{../MT}
 %\end{thebibliography}

### 2019-02-07 Chapters/Chapter2.tex
TB

@@
 \begin{equation}
-E_i(\bs{k}) = \frac{1}{N} \sum_{n,m} e^{i\bs{k}\cdot(\bs{r}_n-\bs{r}_m)} \int \phi_i^* (E_i+v(\bs{r}-\bs{r}_n)) \phi_i(\bs{r}-\bs{r}_n) d\bs{r}
+E_i(\bs{k}) = \frac{1}{N} \sum_{n,m} e^{i\bs{k}\cdot(\bs{r}_n-\bs{r}_m)} \int \phi_i^*(\bs{r}-\bs{r}_m) (E_i+v(\bs{r}-\bs{r}_n)) \phi_i(\bs{r}-\bs{r}_n) d\bs{r}
 \end{equation}
+
+Assuming that $\phi_i$ is spherically symmetric, and neglecting the perturbation $v(\bs{r}-\bs{r}_n)$ further away than nearest neighbors, we can simplify this expression to:
+
+\begin{equation}
+\label{TBBand}
+E_i(\bs{k}) = E_i - A - B\sum_{\bs{\delta}} e^{i\bs{k}\cdot \bs{\delta}}
+\end{equation}
+
+Where $A = -\bra{\phi_i(\bs{r}-\bs{r}_n)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)}$ and $B = -\bra{\phi_i(\bs{r}-\bs{r}_m)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)}$ and where $\bs{\delta}$ are the NN vectors.
+$A$ measures the amount of energy reduced when the atom forms a crystal, $B$ is a measure of the width of the band.
+In second quantization formalism we can write the tight binding single band Hamiltonian as:
+
+\begin{equation}
+\label{TBModel}
+\hat{H} = -t\sum_{\langle i,j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma}
+\end{equation}
+
+Where $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron in site $i$ and spin state $\sigma$.
+The quantity $t$ is the hopping amplitude, and plays the same role $B$ in the first quantization formalism.
+We can obtain back \ref{TBBand} by changing basis to momentum space $\hat{c}_{k\sigma} = \frac{1}{\sqrt{N}}\sum_j e^{-i\bs{k}\cdot\bs{r}_j}\hat{c}_{j\sigma}$.
+
+\section{The Hubbard model}
+
+As we discuss earlier, even tough the tight binding model is successful in describing the band structure of most solids, it fails in some cases.
+In strongly correlated electron systems, the effect of electron-electron Coulomb interactions is important, and this effect is neglected in \ref{TBModel}.
+The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
+This term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.

### 2019-02-07 Chapters/Chapter2.tex
hm

@@
 In strongly correlated electron systems, the effect of electron-electron Coulomb interactions is important, and this effect is neglected in \ref{TBModel}.
-The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
-This term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
+The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$:
+\begin{equation}
+\label{HH}
+\hat{H} = -t\sum_{\langle i,j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + \text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+This new term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
+The half-filled case is most commonly studied, this is the situation where the system has one electron per site (or it has half the maximum allowed number).
+This situation is simpler in many ways and it exhibits a lot of interesting phenomena (Mott insulating behavior, antiferromagnetic order, etc.).
+However, other cases have also been widely studied.
+
+Notice that if we set $\text{U}=0$ in \ref{HH} we recover the tight binding Hamiltonian, therefore we can say that the Hubbard model is an expansion of the tight binding model.
+The opposite limit $t=0$ is more interesting.
+In the half-filling case, for $\text{U}>0$ the ground state will be any state with exactly one electron per site.
+Since each electron can be in two spin states there is a $2^N$ degeneracy.

### 2019-02-08 Chapters/Chapter2.tex
moar

@@
 Since each electron can be in two spin states there is a $2^N$ degeneracy.
+The subspace spaned by these states is referred to as low energy subspace, and in this case is has energy $E_0 = 0$.
+If we switch $0 \neq t \ll \text{U}$ this hopping term will allow an even further decrease in energy by allowing virtual processes $i \rightarrow j \rightarrow i$ that delocalized the electrons withing their neighbor sites.
+For $t \ll \text{U}$ the dynamics of the system can be described withing the low energy subspace only, by doing so we can obtain an effective spin Hamiltonian $\hat{H}_{\text{eff}} = \sum{\langle i,j \rangle} J \bs{S}_i\cdot\bs{S}_j$ where $J>0$ describing an antiferromagnetic system.
+A rigurous derivation of this will be ofered in the next Chapter, however we can intuitively understand this result in the following way: the virtual processes $i \rightarrow j \rightarrow i$ will be allowed when the electrons at sites $i$ and $j$ have opposite spin (otherwise it would contradict the Pauli principle), therefore states where neighbor sites have opposite spins will have a lower energy due to the delocalization mechanism.
+Additionally, the constant $J$ will be proportional to the amplitude of the process $i \rightarrow j \rightarrow i$.
+We can already see that this amplitude is $2\frac{t^2}{\text{U}}$, $t^2$ due to two hoppings, $\frac{1}{\text{U}}$ due to the energy of the intermediate state and the factor $2$ due to the two spin possibilities.

### 2019-02-09 Appendices/AppendixA.tex
Add apendixes to the end

--- 2018-12-09 Chapters/Chapter3.tex
@@
-\chapter{Perturbing the lattice}
+\chapter{Crystal structure and reciprocal lattice}
+\label{AP1A}
 
-In this chapter we will derive an effective spin Hamiltonian for different models in the presence of a high frequency electromagnetic perturbation.
-The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
-This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:
-
-\begin{equation*}
-\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role.
-The electromagnetic perturbation is then introduced via the Peierls substitution.
-We reproduce the result in section \ref{Section3Hubbard}.
-In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions.
-The simplest model with spin orbit interaction is \ref{Hubbard}:
-
-\begin{equation*}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*}
-
-Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.
-In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
-
-In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator.
-For this case we examine the Kane-Mele-Hubbard model.
-The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
-This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.
-
-Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
-
-\input{Chapters/Chap3/TDHeff}
-
-\input{Chapters/Chap3/HNoSoi}
-
-\input{Chapters/Chap3/HWithSoi}
-
-\input{Chapters/Chap3/ModelsNNN}
-
-\input{Chapters/Chap3/OtherHams}
-
-\begin{subappendices}
-\begin{section}{Peierls Substitution}
-\label{AP3A}
-
-In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the lattice \ref{LaticeHam} to:
+Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
 
 \begin{equation}
-\label{HamEMF}
-  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
+\bs{R} = \sum_{\mu=1}^3 m_\mu \bs{a}_\mu
 \end{equation}
 
-Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian.
-We define a new set of Wannier functions in terms of those defined in \ref{Wannier2}, and obtain the new Bloch functions.
+Where $m_\mu$ are integers.
+The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
+The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
+The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
+With this notation the first Brillouin zone is:
+
+\begin{equation}
+\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
+\end{equation}
+
+Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
+
+In the case of a cubic lattice we have $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
+
+In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
 
 \begin{align}
-\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
-\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
+\bs{a}_1 &= \frac{a_0}{2} \left(3, \sqrt{3} \right) \\
+\bs{a}_2 &= \frac{a_0}{2} \left(3, -\sqrt{3} \right)
 \end{align}
 
-Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:
+Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
+Each unit cell contains two atoms, dividing the lattice into two sublattices, usually denoted A and B.
+The reciprocal lattice is defined by the vectors:
 
-\begin{align*}
-\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
-&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
-&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
-\end{align*}
+\begin{align}
+\bs{b}_1 &= \frac{2\pi}{3a_0} \left(1, \sqrt{3} \right) \\
+\bs{b}_2 &= \frac{2\pi}{3a_0} \left(1, -\sqrt{3} \right)
+\end{align}
 
-And so, the matrix elements as in the case without field except for a phase:
+These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
 
-\begin{equation}
-\label{PeierlsMtxElem}
-t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
-\end{equation}
+\begin{align}
+\bs{R}^A_1 &= \frac{a_0}{2} \left( 1, \sqrt{3} \right) \\
+\bs{R}^A_2 &= \frac{a_0}{2} \left( 1, -\sqrt{3} \right) \\
+\bs{R}^A_3 &= a_0 \left( -1, 0 \right)
+\end{align}
 
-When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.
+The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$
 
-Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
-
-\begin{align*}
-  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
-  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
-\end{align*}
-
-Therefore relation \ref{PeierlsMtxElem} still holds.
-
-\end{section}
-
-\begin{section}{Identities}
-\label{AP3B}
-Let $Z(t)$ be an operator dependent on the parameter $t$. Then:
-
-\begin{align*}
-d_t e^{Z} &= d_t \sum_{n=0}^\infty \frac{1}{n!} Z^n = \sum_{n=0}^\infty \sum_{m=0}^{n-1} \frac{1}{n!} Z^m \frac{\partial Z}{\partial t} Z^{n-m-1} = \\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{1}{(m+p+1)!}Z^m \frac{\partial Z}{\partial t} Z^p = \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{m!p!}{(m+p+1)!} \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} =\\
-&= \sum_{m=0}^\infty \sum_{p=0}^\infty \int_0^1 dx x^m (1-x)^p \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} = \int_0^1 dx e^{Zx} \frac{\partial Z}{\partial t} e^{Z(1-x)} = \\
-&= \int_0^1 dx \sum_{n=0}^\infty \frac{1}{n!} \left[xZ, \dots, \left[xZ, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
-\end{align*}
-
-Where we used the Beta function $\int_0^1 dx x^m (1-x)^p = \frac{m!p!}{(m+p+1)!}$ and we also used the Baker–Campbell–Hausdorff expansion for $e^{xZ}\frac{\partial Z}{\partial t}e^{-xZ}$ and $\int_0^1 x^n = \frac{1}{n+1}$.
-Therefore we proved:
-
-\begin{equation}
-\label{SneidersID}
-d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \text{ad}_Z ^n \left(\frac{\partial Z}{\partial t}\right) e^Z
-\end{equation}
-
-Where $\text{ad}_A(B) = [A,B]$.
-
-\end{section}
-
-\end{subappendices}
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/honeycomb_lattice.png}
+  \caption{Image from a web source.
+In Fig.
+(a) the unit cell is sketched and the sublattices A and B are shown in blue and red respectively.
+In Fig.
+(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
+\label{Fig2.2}
+\end{figure}

### 2019-02-09 Appendices/AppendixB.tex
Add apendixes to the end

\chapter{Peierls Substitution}
\label{AP3A}

In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the lattice \ref{LaticeHam} to:

\begin{equation}
\label{HamEMF}
  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
\end{equation}

Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian. We define a new set of Wannier functions in terms of those defined in \ref{Wannier2}, and obtain the new Bloch functions.

\begin{align}
\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
\end{align}

Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:

\begin{align*}
\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
\end{align*}

And so, the matrix elements as in the case without field except for a phase:

\begin{equation}
\label{PeierlsMtxElem}
t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
\end{equation}

When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.

Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then

\begin{align*}
  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
\end{align*}

Therefore relation \ref{PeierlsMtxElem} still holds.

### 2019-02-09 Chapters/Chapter3.tex
Add apendixes to the end

@@
 \end{section}
-
-\begin{subappendices}
-\begin{section}{Crystal structure and reciprocal lattice}
-\label{AP1A}
-
-Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
-
-\begin{equation}
-\bs{R} = \sum_{\mu=1}^3 m_\mu \bs{a}_\mu
-\end{equation}
-
-Where $m_\mu$ are integers.
-The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
-The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
-The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
-With this notation the first Brillouin zone is:
-
-\begin{equation}
-\textbf{k} = \sum_{\mu=1}^3 \kappa_\mu \textbf{b}_\mu
-\end{equation}
-
-Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
-
-In the case of a cubic lattice we have $|\textbf{a}_\mu| = a$ and $|b_\mu| = \frac{2\pi}{a}$ and the vectors of the first Brillouin zone have components $k_\mu = \frac{2 \pi \nu_\mu}{aL}$.
-
-In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
-
-\begin{align}
-\bs{a}_1 &= \frac{a_0}{2} \left(3, \sqrt{3} \right) \\
-\bs{a}_2 &= \frac{a_0}{2} \left(3, -\sqrt{3} \right)
-\end{align}
-
-Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
-Each unit cell contains two atoms, dividing the lattice into two sublattices, usually denoted A and B.
-The reciprocal lattice is defined by the vectors:
-
-\begin{align}
-\bs{b}_1 &= \frac{2\pi}{3a_0} \left(1, \sqrt{3} \right) \\
-\bs{b}_2 &= \frac{2\pi}{3a_0} \left(1, -\sqrt{3} \right)
-\end{align}
-
-These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
-
-\begin{align}
-\bs{R}^A_1 &= \frac{a_0}{2} \left( 1, \sqrt{3} \right) \\
-\bs{R}^A_2 &= \frac{a_0}{2} \left( 1, -\sqrt{3} \right) \\
-\bs{R}^A_3 &= a_0 \left( -1, 0 \right)
-\end{align}
-
-The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$
-
-\begin{figure}
-\centering
-  \includegraphics[width=0.7\linewidth]{../Figures/honeycomb_lattice.png}
-  \caption{Image from a web source.
-In Fig.
-(a) the unit cell is sketched and the sublattices A and B are shown in blue and red respectively.
-In Fig.
-(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
-\label{Fig2.2}
-\end{figure}
-\end{section}
-\end{subappendices}

### 2019-02-09 Chapters/Chapter4.tex
Add apendixes to the end

\chapter{Perturbing the lattice}

In this chapter we will derive an effective spin Hamiltonian for different models in the presence of a high frequency electromagnetic perturbation. The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately. This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:

\begin{equation*}
\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*}

In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role. The electromagnetic perturbation is then introduced via the Peierls substitution. We reproduce the result in section \ref{Section3Hubbard}. In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions. The simplest model with spin orbit interaction is \ref{Hubbard}:

\begin{equation*}
\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*}

Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$. In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.

In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator. For this case we examine the Kane-Mele-Hubbard model. The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term. This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.

Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.

\input{Chapters/Chap3/TDHeff}

\input{Chapters/Chap3/HNoSoi}

\input{Chapters/Chap3/HWithSoi}

\input{Chapters/Chap3/ModelsNNN}

\input{Chapters/Chap3/Numerics}

### 2019-02-11 Paper/paper.tex
Mod picture and add NN interaction

@@
 &\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
-&\hat{\mathcal{H}}_{\text{int}} = \text{U}\hat{D}
+&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'}
 \end{align}
 
-Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$.
-$\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction.
+Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $\text{U}_{00}$ and $\text{U}_{ij}$ are the on-site and NN Coulomb interactions.
 $t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping.
-Where $\Delta$ is the intrinsic spin orbit coupling constant.
+$\Delta$ is the intrinsic spin orbit coupling constant.
 $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).
 $\sigma^{z}$ is the third Pauli matrix.
+In practice the NN Coulomb interaction can be effectively approximated by a reduced on-site interaction $\text{U} = \text{U}_{00} - \bar{\text{U}}$ where $\bar{\text{U}}$ is an average of the NN Coulomb interacion \cite{Schuler2013}, we therefore can take:
+\begin{equation}
+\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
+\end{equation}
+With $\text{U} = \text{U}_{00} - \bar{\text{U}}$.
+
 \begin{figure}[t]
@@
 \end{figure}
+Let us define $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ the doublon number operator so that $\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\hat{D}$ with eigenvalues $d$ and projection operators $\hat{P}_d$.
 We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes.
@@
 \begin{figure}[t]
-\includegraphics[width=0.6\columnwidth]{../Figures/NNvsNNN.pdf}
+\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
 \caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
@@
 In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
-In Hamiltonian \ref{MKMHeff} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
-In the next section we will do a numerical of study on how modifying the ratio between NN and NNN spin interaction factors can change the spin state of the system.
+In Hamiltonian \ref{MKMHeff0} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
+We have shown that we can modulate these parameters thus providing a techique to manipulate the SDW in the ground state.
 

### 2019-02-12 Paper/paper.tex
Relabel

@@
 \label{MKMHeff0}
-&\hat{H}_{\text{eff}}^0 = \sum_{\langle i,j \rangle} J_{1,ij}^0\bs{S}_i\cdot\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}^0\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}^0\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}^0 \bs{S}_j \right\}
+&\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j +\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
 \end{align}
@@
 \begin{align*}
-J_{1,ij}^0 &= 2t_1^2 \\
-J_{2,ij}^0 &= 2t_2^2 \\
-\bs{D}_{2,ij}^0 &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
-\bs{\Gamma}_{2,ij}^0 &= 2\Delta^2 \text{diag}(-1,-1,1)
+J_{1,ij} &= 2t_1^2 \\
+J_{2,ij} &= 2t_2^2 \\
+\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
+\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1)
 \end{align*}
@@
 \begin{align*}
-J_{1,ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-J_{2,ij} &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
+J_{1,ij}' &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+J_{2,ij}' &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+\bs{D}_{2,ij}' &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
+\bs{\Gamma}'_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
 \end{align*}
@@
 \includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
-\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
+\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
 The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$.
@@
 \begin{align*}
-J_{1,ij} &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
-J_{2,ij} &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
-\bs{D}_{2,ij} &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
-\bs{\Gamma}_{2,ij} &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
+J_{1,ij}' &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
+J_{2,ij}' &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
+\bs{D}_{2,ij}' &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
+\bs{\Gamma}_{2,ij}' &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
 \end{align*}

### 2019-02-12 Code/Chap3.R
Update

@@ -30,7 +30,7 @@ t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-frequencies <- list(6,16) #Laser frecuency
+frequencies <- list(4,14) #Laser frecuency
 bessel_trunc_order <- 10
 lattice_cte <- 1
 field_energies <- seq(from=0, by=0.001, to=5)
@@ -65,12 +65,12 @@ for (i in 1:length(frequencies)) {
   lines(x = field_energies, y = J1_factor[[i]], type = 'l', col = "green", lwd = 2, lty = i)
   lines(x = field_energies, y = D2_factor[[i]], type = 'l', col = "red", lwd = 2, lty = i)
 }
-mtext(text=paste0("$\\tilde{J_1}$",'\n',"$\\tilde{D_2}$"), side =2, line = 3, las=1)
-legend("topright", legend = c("$\\tilde{J_1}$", "$\\tilde{D_2}$"), fill = c("green", "red"))
+#mtext(text=paste0("$\\tilde{J_1}$",'\n',"$\\tilde{D_2}$"), side =2, line = 3, las=1)
+legend("topright", legend = c("$\\tilde{J_1}$", "$\\tilde{D_2}$"), fill = c("green", "red"), x = 0.8*range(field_energies)[2], y = range(J1_factor)[2])
 
 dev.off()
 tools::texi2pdf(paste0(current_file, '.tex'))
-system(paste0("mv ", current_file, ".pdf ../Chapters/", current_file, ".pdf"))
+system(paste0("mv ", current_file, ".pdf ../Figures/", current_file, ".pdf"))
 #system(paste(getOption("pdfviewer"), "formula.pdf"))
 
 current_file <- "ratio"

### 2019-02-12 Chapters/Chap3/Numerics.tex
Add Figures
update figures

@@
 Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
-Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}.
+Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}.
 The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}.
@@
   %\centering
-  \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.pdf}
+  \includegraphics[width=1\linewidth]{Figures/NNvsNNN.pdf}
   \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$.
 Similar results are obtained in \cite{Mentink2015} for $J_{1}$.
-Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
   \label{Fig3.1:NNvsNNN}
@@
   %\centering
-  \includegraphics[width=1\linewidth]{Chapters/ratio.pdf}
-  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
+  \includegraphics[width=1\linewidth]{Figures/ratio.pdf}
+  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
   \label{Fig3.1:ratio}
@@
 \centering
-  \includegraphics[width=0.5\linewidth]{Chapters/theta.pdf}
+  \includegraphics[width=0.5\linewidth]{Figures/theta.pdf}
   \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$.
 The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector.
-Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
 \label{Fig3.2}

### 2019-02-12 Paper/paper.tex
update figures

@@
 \caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
-The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$.
-Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.
+The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$.
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.
 For $\tilde{J}_1$, similar results are obtained by Mentink et Al.

### 2019-02-12 Code/Chap3.R

@@ -83,7 +83,8 @@ tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,
 
 ylim <- c(-3*ratioJD0,2*ratioJD0)
 plot(x = range(field_energies), y = ylim, type = 'n', 
-     xlab = "$\\mathcal{E}$", ylab = '$\\frac{J_1}{D_2}$')
+     xlab = "$\\mathcal{E}$", ylab = '')
+mtext(text='$\\frac{J_1}{D_2}$', side =2, line = 3, las=1)
 
 for (i in 1:length(frequencies)) {
   plot_disconnect(x=field_energies, y = ratioJD[[i]], col = "blue", lwd = 2, lty = i, ylim = ylim)
@@ -107,7 +108,8 @@ tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,
                   "\\usepackage{amssymb}"))
 
 plot(x = range(sapply(res_field_energies, range)), y = range(sapply(theta, range)), type = 'n',
-     xlab = "$\\mathcal{E}$", ylab="$\\theta$" )
+     xlab = "$\\mathcal{E}$", ylab="" )
+mtext(text='$\\theta$', side =2, line = 3, las=1)
 for (i in 1:length(frequencies)) {
   lines(x = res_field_energies[[i]], y = theta[[i]], type = 'l', lwd =2, lty = i,
          col = "purple")

### 2019-02-12 Paper/paper.tex
add exp values

@@
 
+In Figure \ref{fig2} we show the dependence of $J_{1,ij}'$ and $\bs{D}_{2,ij}'$ in the electric parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ where $e$ is the electron charge and $a$ is the lattice constant.
+The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{CastroNeto2009}) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+
 \begin{figure}[t]
 \includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
-\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant.
-The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$.
-Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.
-For $\tilde{J}_1$, similar results are obtained by Mentink et Al.
-\cite{Mentink2015}.}
+\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$.
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
 \label{fig2}

### 2019-02-12 Paper/paper.tex
add noncoplanar disc

@@
 % !TEX spellcheck = en-US
-\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4}%
+\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4-1}%
 \usepackage{graphicx}
@@
 \begin{align}
-&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
-&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
-&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'}
+&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Ht} \\
+&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Hsoi} \\
+&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'} \label{Hint}
 \end{align}
@@
 $\sigma^{z}$ is the third Pauli matrix.
+Notice that Rashba SOI interactions are not included in \ref{Hsoi}, the reason is that such terms are not allowed by symmetry in the honeycomb lattice, however Rashba interactions should be considered in lower symmetry lattices such a non-coplanar honeycomb lattice \cite{Liu2011}.
 In practice the NN Coulomb interaction can be effectively approximated by a reduced on-site interaction $\text{U} = \text{U}_{00} - \bar{\text{U}}$ where $\bar{\text{U}}$ is an average of the NN Coulomb interacion \cite{Schuler2013}, we therefore can take:
@@
 %\begin{thebibliography}
+\bibliographystyle{apsrev4-1}
 \bibliography{../MT}

### 2019-02-14 Paper/paper.tex
Fix references

@@
 In Figure \ref{fig2} we show the dependence of $J_{1,ij}'$ and $\bs{D}_{2,ij}'$ in the electric parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ where $e$ is the electron charge and $a$ is the lattice constant.
-The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{CastroNeto2009}) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{Castro2009}) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
 
@@
 Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.
-This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
+This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2016}.
 

### 2019-02-20 Appendices/AppendixD.tex
app d

\chapter{Tight binding model in the honeycomb lattice}
\label{APD}

Graphene, as a representative two dimensional solid with honeycomb lattice structure has some interesting electrical properties induced by its lattice structure. Graphene is a zero gap semiconductor, meaning that its conduction and valence bands touch each other at the $\bs{K}$ points in the momentum space. Around these points the electrons have a linear dispersion relation, resembling that of massless Dirac fermions. In the following we will show this in detail.

Using the same notation introduced in \ref{AP1A} we can introduce the fermionic operators $\hat{a}^\dagger_i$ and $\hat{b}^\dagger_j$ which create and electron on the A and B site receptively, at position $\bs{R}_i$ or $\bs{R}_i$. Then, the tight binding Hamiltonian considering only NN hopping is:

\begin{equation}
\hat{H} = -t\sum_{i \in A}\sum_{\bs{\delta}} (\hat{a}^\dagger_i\hat{b}_{i+\bs{\delta}} + \hat{b}^\dagger_{i+\bs{\delta}}\hat{a}_i)
\end{equation}

Where $i$ labels sites in sublattice A and $\bs{\delta}$ are the NN vectors, we make an abuse of notation by summing $i+\bs{\delta}$ referring, of course, to the site at position $\bs{R}_i+\bs{delta}$.

### 2019-02-20 Chapters/Chapter2.tex
app d

@@
 \end{equation}
+Figure \ref{fig:Hubbard} shows a graphical representation of these parameters.
 This new term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
@@
 However, other cases have also been widely studied.
+
+\begin{figure}
+\centering
+  \includegraphics[width=\linewidth]{../Figures/hubbard.png}
+  \caption{Image from Scalettar's notes representing the kinetic term $t$ and the on-site interaction $\text{U}$ in the Hubbard model.} 
+\label{fig:Hubbard}
+\end{figure}
 

### 2019-02-20 Appendices/AppendixD.tex
til structure

@@
 \begin{equation}
+\label{TBHex}
 \hat{H} = -t\sum_{i \in A}\sum_{\bs{\delta}} (\hat{a}^\dagger_i\hat{b}_{i+\bs{\delta}} + \hat{b}^\dagger_{i+\bs{\delta}}\hat{a}_i)
@@
 
-Where $i$ labels sites in sublattice A and $\bs{\delta}$ are the NN vectors, we make an abuse of notation by summing $i+\bs{\delta}$ referring, of course, to the site at position $\bs{R}_i+\bs{delta}$.
+Where $i$ labels sites in sublattice A and $\bs{\delta}$ are the NN vectors, we make an abuse of notation by summing $i+\bs{\delta}$ referring, of course, to the site at position $\bs{R}_i+\bs{\delta}$.
+In order to diagonalize this Hamiltonian we change to momentum space:
+
+\begin{align}
+\hat{a}^\dagger_i &= \frac{1}{\sqrt{N}} \sum_{\bs{k}} e^{i\bs{k}\cdot\bs{r}_i}\hat{a}^\dagger_{\bs{k}} \\
+\hat{b}^\dagger_j &= \frac{1}{\sqrt{N}} \sum_{\bs{k}} e^{i\bs{k}\cdot\bs{r}_j}\hat{b}^\dagger_{\bs{k}} 
+\end{align}
+
+Then \ref{TBHex} reads:
+
+\begin{align*}
+\hat{H} &= -\frac{t}{N} \sum_{i \in A}\sum_{\bs{\delta}} \sum_{\bs{k}\bs{k}'} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i}e^{-i\bs{k}'\cdot\bs{\delta}} \hat{a}^\dagger_{\bs{k}}\hat{b}_{\bs{k}'} + e^{i(\bs{k}'-\bs{k})\cdot\bs{r}_i}e^{i\bs{k}'\cdot\bs{\delta}} \hat{b}^\dagger_{\bs{k}'}\hat{a}_{\bs{k}} = \\
+&= -t \sum_{\bs{\delta}\bs{k}} e^{-i\bs{k}\cdot\bs{\delta}} \hat{a}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} +e^{i\bs{k}\cdot\bs{\delta}} \hat{b}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} = \sum_{\bs{k}} \psi^\dagger(\bs{k})h(\bs{k})\psi(\bs{k})
+\end{align*}
+
+Where $\psi(\bs{k}) = \left( \hat{a}_{\bs{k}}, \hat{b}_{\bs{k}} \right)^T$ and:
+
+\begin{equation}
+h(\bs{k}) = \begin{pmatrix}
+    0 & f(\bs{k}) \\
+    f^*(\bs{k}) & 0
+\end{pmatrix}
+\end{equation}
+
+being $f(\bs{k}) = -t\sum_{\bs{\delta}} e^{i\bs{k}\cdot\bs{\delta}}$

### 2019-02-20 Paper/paper.tex
fix a citation

@@
 In Figure \ref{fig2} we show the dependence of $J_{1,ij}'$ and $\bs{D}_{2,ij}'$ in the electric parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ where $e$ is the electron charge and $a$ is the lattice constant.
-The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{Castro2009}) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{Castro2009}) $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
 
@@
 \caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$.
-Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.
+Notice that $\tilde{J}_1$ and $\tilde{D}_{2}$ do not depend on the parameters $t_1$, $t_2$ and $\Delta$.}
 \label{fig2}
@@
 A.
-Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}.
+Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}.
 Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.

### 2019-02-21 Appendices/AppendixD.tex
more honeycomb tb

@@
 
-being $f(\bs{k}) = -t\sum_{\bs{\delta}} e^{i\bs{k}\cdot\bs{\delta}}$
+being $f(\bs{k}) = -t\sum_{\bs{\delta}} e^{i\bs{k}\cdot\bs{\delta}}$.
+In order to obtain the band structure we need to diagonalize $h(\bs{k})$.
+This is straightforward and the resulting energy bands are:
+
+\begin{equation}
+E(\bs{k})_{\pm} = \pm|f(\bs{k})| = \pm t\sqrt{3+2\cos(\sqrt{3}k_ya) +4\cos(\sqrt{3}k_y\frac{a}{2})\cos(3k_x\frac{a}{2})}
+\end{equation}
+
+The bands will cross, or equivalently the band gap will vanish if $f(\bs{k})=0$ has a solution, which it does at the corners of the first Brillouin zone, i.e. the points:
+
+\begin{align*}
+\bs{K} &= \frac{2\pi}{3a}\left( 1, \frac{1}{\sqrt{3}}\right) \\
+\bs{K}' &= \frac{2\pi}{3a}\left( 1, -\frac{1}{\sqrt{3}}\right) 
+\end{align*}
+
+Where $a$ is the lattice constant. The other corner points are equivalent to either one of these (that is, they can be obtained by a translation of a reciprocal lattice vector).
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/graphene_bands.png}
+  \caption{Image from \cite{Ando2009}. The energy bands of graphene.} 
+\label{FigD1}
+\end{figure}
+
+As depicted in \ref{FigD1} the bands touch in the $\bs{K}$ and $\bs{K}'$ points of the first Brillouin zone.
+Now, since the system has one electron per atom with two possible spin states it is clear that at zero temperature the lower energy band will be filled (and the upper band will be empty).
+Thus, the excitations of the system will occur near the crossings at the $\bs{K}$ points.
+In order to study these excitations it is interesting to linearize the Hamiltonian around these points.
+Around the $\bs{K}$ point for example, since $f(bs{k})$ vanishes, we can write:
+
+\begin{equation}
+h(\bs{K}+\bs{q}) \approx \begin{pmatrix}
+    0 & \frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} \\
+    \frac{\partial f^*(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} & 0
+\end{pmatrix}
+\end{equation}
+
+Now,
+
+\begin{equation}
+\frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} = -ie^{\frac{2\pi i}{3}} \frac{3a}{2}(q_x+iq_y)
+\end{equation}
+
+We can ignore the phase and write:
+
+\begin{equation}
+h(\bs{K}+\bs{q}) = v_F \begin{pmatrix}
+    0 & q_x+iq_y \\
+    q_x-iq_y & 0
+\end{pmatrix}
+\end{equation}
+
+Where $v_F = \frac{3at}{2}$. This result is usually written in terms of Pauli matrices as:
+
+\begin{equation}
+h(\bs{K}+\bs{q}) = v_F(q_x\sigma_x-q_y\sigma_y)
+\end{equation}

### 2019-02-21 Appendices/AppendixD.tex
finish graphene

@@
 \begin{equation}
-E(\bs{k})_{\pm} = \pm|f(\bs{k})| = \pm t\sqrt{3+2\cos(\sqrt{3}k_ya) +4\cos(\sqrt{3}k_y\frac{a}{2})\cos(3k_x\frac{a}{2})}
+E_{\pm}(\bs{k}) = \pm|f(\bs{k})| = \pm t\sqrt{3+2\cos(\sqrt{3}k_ya) +4\cos(\sqrt{3}k_y\frac{a}{2})\cos(3k_x\frac{a}{2})}
 \end{equation}
@@
 \end{equation}
+
+We can write this more compactly as $h(\bs{K}+\bs{q}) = v_F \left(\bs{q}\bs{\sigma}\right)^*$.
+Analogously for the $\bs{K}'$ point we obtain $h(\bs{K}'+\bs{q}) = v_F\bs{q}\bs{\sigma}$.
+This result is identical to the massless Dirac Hamiltonian for relativistic electrons where the speed of light is changed to $v_F$.
+The linearized energy is simply given by $E_{\pm}(\bs{K}+\bs{q}) = \pm v_F|\bs{q}|$.
+In \cite{Kane2005}, Kane and Mele added a term :
+\begin{equation}
+h_{SO} = \Delta_{SO}\sigma_z\tau_z s_z
+\end{equation} 
+to this Hamiltonian (where $\tau_z = \pm 1$ describing states around the $\bs{K}$ or $\bs{K}'$ points respectively and $s_z$ representing the electron's spin).
+This term leads to an energy $E_{\pm}(\bs{K}+\bs{q}) = \pm \sqrt{\left(v_F\bs{q} \right)^2 + \Delta_{SO}^2}$, i.e.
+it opens an energy gap $2\Delta_{SO}$.
+If this gap is large enough, the material becomes insulator in the bulk, while supporting states at the boundaries.
+This states are known as edge states and are of relevance for the transport of charge and spin.

### 2019-02-25 Appendices/AppendixE.tex
Fix references

\chapter{Floquet Theory}
\label{APE}
In this appendix we will state and proof the Floquet theorem and employ the Floquet formalism to derive a perturbative analysis of high frequency time periodic Hamiltonians. This formalism been widely used recently in many-body driven systems (\cite{Desbuquois2017}, \cite{Bordia2017}, \cite{Gorg2018}).

### 2019-02-25 Chapters/Chap3/ModelsNNN.tex
moar
Fix references

@@
 
-This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$ in \ref{BigHam}. With this, the effective Hamiltonian will be:
+\begin{figure}
+\centering
+\includegraphics[width=0.5\columnwidth]{../Figures/kmh.png}
+\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$.
+$\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
+\label{fig:MKMH}
+\vspace*{-6pt}
+\end{figure}
+
+This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$ in \ref{BigHam}.
+The Hamiltonian parameters are sketched in Figure \ref{fig:MKMH}.
+With this, the effective Hamiltonian will be:
 
@@
 A.
-Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}.
+Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}.
 Experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.
-This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
+This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2016}.
 

### 2019-02-25 Appendices/AppendixE.tex
Floquet theorem

@@
 This formalism been widely used recently in many-body driven systems (\cite{Desbuquois2017}, \cite{Bordia2017}, \cite{Gorg2018}).
+
+We will start with a periodic Hamiltonian:
+
+\begin{equation}
+\hat{H}(t) = \hat{H}(t+T)
+\end{equation}
+
+The Floquet theorem states that the eigenstates for the time evolution operator for one period, $\hat{U}(t+T,t)$ can be written as:
+
+\begin{equation}
+\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
+\end{equation}
+
+Where $\ket{u_n(t+T)} = \ket{u_n(t)}$ is a periodic function, called Floquet mode, and $\epsilon_n$ is a real number known as the quasienergy.
+To show this, let $a_n(t)$ be the eigenvalue of $\ket{\psi_n(t)}$ under $\hat{U(t+T,t)}$, that is $\hat{U(t+T,t)}\ket{\psi_n(t)} = a_n(t)\ket{\psi_n(t)}$, then by multiplying this equation by $\hat{U}(t',t)$ from the left and using the periodicity of the Hamiltonian in $\hat{U}(t',t) = \hat{U}(t'+T,t+T)$ we obtain:
+
+\begin{align*}
+\hat{U}(t'+T,t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
+\hat{U}(t'+T,t) \hat{U}(t,t')\hat{U}(t',t) \ket{\psi_n(t)} &= a_n(t)\ket{\psi_n(t')} \rightarrow \\
+\hat{U}(t'+T,t') \ket{\psi_n(t')} &= a_n(t)\ket{\psi_n(t')}
+\end{align*}
+
+Which means that $a_n(t') = a_n(t)$, so the eigenvalue does not depend on time, and since it is an eigenvalue of an unitary operator it can be written as $a_n = a_n(t) = e^{-i\epsilon_nT}$ for certain real number $\epsilon_n$.
+Therefore, we have
+
+\begin{align*}
+\ket{\psi_n(t+T)} &= e^{-i\epsilon_nT} \ket{\psi_n(t)} \rightarrow \\
+\ket{\psi_n(t)} &= e^{-i\epsilon_nt} \ket{\u_n(t)}
+\end{align*}
+
+For $\ket{\u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{\u_n(t+T)}$, and this proves the theorem.

### 2019-02-26 Appendices/AppendixE.tex
More Floquet theory

@@
 Where $\ket{u_n(t+T)} = \ket{u_n(t)}$ is a periodic function, called Floquet mode, and $\epsilon_n$ is a real number known as the quasienergy.
-To show this, let $a_n(t)$ be the eigenvalue of $\ket{\psi_n(t)}$ under $\hat{U(t+T,t)}$, that is $\hat{U(t+T,t)}\ket{\psi_n(t)} = a_n(t)\ket{\psi_n(t)}$, then by multiplying this equation by $\hat{U}(t',t)$ from the left and using the periodicity of the Hamiltonian in $\hat{U}(t',t) = \hat{U}(t'+T,t+T)$ we obtain:
+To show this, let $a_n(t)$ be the eigenvalue of $\ket{\psi_n(t)}$ under $\hat{U}(t+T,t)$, that is $\hat{U}(t+T,t)\ket{\psi_n(t)} = a_n(t)\ket{\psi_n(t)}$, then by multiplying this equation by $\hat{U}(t',t)$ from the left and using the periodicity of the Hamiltonian in $\hat{U}(t',t) = \hat{U}(t'+T,t+T)$ we obtain:
 
@@
 \ket{\psi_n(t+T)} &= e^{-i\epsilon_nT} \ket{\psi_n(t)} \rightarrow \\
-\ket{\psi_n(t)} &= e^{-i\epsilon_nt} \ket{\u_n(t)}
+\ket{\psi_n(t)} &= e^{-i\epsilon_nt} \ket{u_n(t)}
 \end{align*}
 
-For $\ket{\u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{\u_n(t+T)}$, and this proves the theorem.
+For $\ket{u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{u_n(t+T)}$, and this proves the theorem.
+The states $\ket{\psi_n(t)}$ are called Floquet states and are solutions of the time dependent Schr\"{o}dinger equation $i\text{d}_t\ket{\psi_n(t)} = \hat{H}(t)\ket{\psi_n(t)}$.
+The time evolution operator can be written as:
+
+\begin{equation}
+\hat{U}(t_2,t_1) = \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)}
+\end{equation}
+
+Therefore the time evolution of a superposition of Floquet states will be determined by two different contributions:
+
+\begin{itemize}
+\item The periodic evolution of the superposing Floquet modes. This is called micromotion.
+\item The non-periodic dephasing due to the factor $e^{-i\epsilon_n(t_2-t_1)}$ depending on the quasienergies $\epsilon_n$.
+\end{itemize}
+
+It is interesting to study these two time dependencies separately. With his purpose we define the micromotion operator and the Floquet Hamiltnian. The micromotion operator is defined as:
+\begin{equation}
+\hat{U}_F(t_2,t_1) \equiv \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)}
+\end{equation}
+so that $\ket{u_n(t_2)} = \hat{U}_F(t_2,t_1)\ket{u_n(t_1)}$, i.e.
+it is responsible of the periodic time evolution intrinsic of the Floquet modes.
+On the other hand, the Floquet Hamiltonian $\hat{H}_{t_0}^F$ is a time-independent Hamiltonian defined such that:
+\begin{equation}
+e^{-iT\hat{H}_{t_0}^F} \equiv \hat{U}(t_0+T,t_0)
+\end{equation}
+or equivalently:
+\begin{equation}
+e^{-it\hat{H}_{t_0}^F} = \sum_n e^{-i\epsilon_nt}\ket{u_n(t_0)}\bra{u_n(t_0)}
+\end{equation}
+this Hamiltonian will time-evolve states by adding a phase $e^{-i\epsilon_n(t_2-t_1)}$ to the correspondent fixed-time modes. The full time evolution operator is a combination of both time evolutions:
+\begin{align*}
+\hat{U}(t_2,t_1) &= \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_1)} = \\
+&\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_2)}\bra{u_n(t_2)} \right)\left( \sum_n\ket{u_n(t_2)}\bra{u_n(t_1)}\right) = \\
+&\left( \sum_n \ket{u_n(t_2)}\bra{u_n(t_1)} \right)\left( \sum_n e^{-i\epsilon_n(t_2-t_1)}\ket{u_n(t_1)}\bra{u_n(t_1)} \right)
+\end{align*}
+That is:
+\begin{equation}
+\hat{U}(t_2,t_1) = e^{-i(t_2-t_1)\hat{H}_{t_2}^F}\hat{U}_F(t_2,t_1) = \hat{U}_F(t_2,t_1)e^{-i(t_2-t_1)\hat{H}_{t_1}^F}
+\end{equation}

### 2019-03-04 Code/Chap3.R
few code changes

@@ -31,9 +31,9 @@ delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
 frequencies <- list(4,14) #Laser frecuency
-bessel_trunc_order <- 10
+bessel_trunc_order <- 100
 lattice_cte <- 1
-field_energies <- seq(from=0, by=0.001, to=5)
+field_energies <- seq(from=0, by=0.01, to=5)
 
 #J1 = 2*t1^2/U*J1_factor
 J1_factor <- lapply(frequencies, function(x) vector(mode="numeric", length=length(field_energies)))
@@ -47,7 +47,7 @@ ratioJD <-  lapply(frequencies, function(x) vector(mode="numeric", length=length
 for (i in 1:length(frequencies)) {
   for (n in -bessel_trunc_order:bessel_trunc_order) {
     J1_factor[[i]] <- J1_factor[[i]] + besselJ(field_energies/sqrt(2), nu = n)^2 / (1 + n * frequencies[[i]] / U)
-    D2_factor[[i]] <- D2_factor[[i]] + besselJ(sqrt(2)*field_energies, nu = n)^2 / (1 + n * frequencies[[i]] / U)
+    D2_factor[[i]] <- D2_factor[[i]] + besselJ(sqrt(3/2)*field_energies, nu = n)^2 / (1 + n * frequencies[[i]] / U)
   }
   ratioJD[[i]] <- ratioJD0*J1_factor[[i]]/D2_factor[[i]]
 }
@@ -60,7 +60,7 @@ tikz(paste0(current_file, '.tex'), width = 4, height = 4, standAlone = TRUE,
                   "\\setlength\\PreviewBorder{0pt}",
                   "\\usepackage{amssymb}"))
 
-plot(x=range(field_energies), y = range(J1_factor), type='n', xlab = "$\\mathcal{E}$", ylab = '', las =1)
+plot(x=range(field_energies), y = range(c(J1_factor, D2_factor)), type='n', xlab = "$\\mathcal{E}$", ylab = '', las =1)
 for (i in 1:length(frequencies)) {
   lines(x = field_energies, y = J1_factor[[i]], type = 'l', col = "green", lwd = 2, lty = i)
   lines(x = field_energies, y = D2_factor[[i]], type = 'l', col = "red", lwd = 2, lty = i)

### 2019-03-04 Paper/paper.tex
Add first version paper

@@
 % !TEX spellcheck = en-US
-\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4-1}%
+\documentclass[aps,prl,twocolumn,amsmath,amssymb,nobibnotes]{revtex4-1}%
 \usepackage{graphicx}
@@
 \usepackage[toc,page]{appendix}
+\usepackage[symbol]{footmisc}
 %\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}
@@
 \begin{document}
-\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators}
+\title{Ultrafast Control of Spin-Spin Interactions in Two-Dimensional Magnetic Systems: Kane-Mele-Hubbard Model}
+
+\author{Juan M. Losada}
+\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
+\author{Arne Brataas}
+\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
+\author{Alireza Qaiumzadeh}
+\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
+\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
+%\affiliation{Institute for Advanced Studies in Basic Science (IASBS), Zanjan, Iran}
 
 \begin{abstract}
-This is the abstract.
+
 \end{abstract}
@@
 
-\begin{section}{Model and calculations}
-
-The first model to describe topological insulators was introduced by Kane and Mele \cite{Kane2005} to describe quantum spin Hall effect in graphene.
-In a honeycomb lattice time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling.
-In these circumstances the system can be modeled by the Kane-Mele-Hubbard which we write as a sum of a kinetic term, an interaction term and a SOI term:
-
+\textit{Model Hamiltonian}.---
+Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,Griset2012,Auerbach}.
+\AQ{cite papers for KMH model.
+Also cite Auerbach's book for Hubbard model!}
+The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and electron-electron interaction modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
 \begin{equation}
 \label{MKMH}
-\hat{H}^0 = \hat{\mathcal{H}}_t + \hat{\mathcal{H}}_{\text{SOI}} + \hat{\mathcal{H}}_{\text{int}}
+\hat{H}_0 = \hat{\mathcal{H}}_{\text{K}} + \hat{\mathcal{H}}_{\text{SOI}} + \hat{\mathcal{H}}_{\text{int}},
 \end{equation}
-Where:
+where
 \begin{align}
-&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Ht} \\
-&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Hsoi} \\
-&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'} \label{Hint}
+\hat{\mathcal{H}}_{\text{K}} &= - \sum_{\langle i,j \rangle, \tau} t_{1}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} - \sum_{\langle \langle i,j \rangle \rangle, \tau} t_{2}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \label{Ht} \\
+\hat{\mathcal{H}}_{\text{SOI}} & = \sum_{\langle \langle i,j \rangle \rangle, \tau,\tau'} i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'} \label{Hsoi} \\
+\hat{\mathcal{H}}_{\text{int}} &= U_{00}\sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \tau \tau'} V_{ij}\hat{n}_{i\tau}\hat{n}_{j\tau'} \label{Hint}.
 \end{align}
-
-Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $\text{U}_{00}$ and $\text{U}_{ij}$ are the on-site and NN Coulomb interactions.
-$t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping.
-$\Delta$ is the intrinsic spin orbit coupling constant.
-$\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).
-$\sigma^{z}$ is the third Pauli matrix.
-Notice that Rashba SOI interactions are not included in \ref{Hsoi}, the reason is that such terms are not allowed by symmetry in the honeycomb lattice, however Rashba interactions should be considered in lower symmetry lattices such a non-coplanar honeycomb lattice \cite{Liu2011}.
-In practice the NN Coulomb interaction can be effectively approximated by a reduced on-site interaction $\text{U} = \text{U}_{00} - \bar{\text{U}}$ where $\bar{\text{U}}$ is an average of the NN Coulomb interacion \cite{Schuler2013}, we therefore can take:
-\begin{equation}
-\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation}
-With $\text{U} = \text{U}_{00} - \bar{\text{U}}$.
-
 \begin{figure}[t]
@@
 \end{figure}
-Let us define $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ the doublon number operator so that $\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\hat{D}$ with eigenvalues $d$ and projection operators $\hat{P}_d$.
-We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes.
-In the strong coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
-We can therfore obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second order perturbation techniques in the hopping terms.
-We can then obtain the effective spin Hamiltonian by using the relations:
+where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are nearest-neighbour (nn) and  next-nearest-neighbour (nnn) hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and nn Coulomb interactions.
+The presence of the intrinsic SOI, Eq. (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of a pure Hubbard model to the $\mathrm{U}(1)$ spin group.
+
+Using the variational principle, it has been shown that the nn Coulomb interaction can be effectively approximated by a renormalized on-site interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the nn Coulomb interaction \cite{Schuler2013,Stepanov2017}.
+Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and rewrite the interaction part of the Hamiltonian (\ref{Hint}),
+\begin{equation}
+\hat{\mathcal{H}}_{\text{int}} \approx U\hat{d},
+\end{equation}
+where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$ and projection operators $\hat{P}_d$.
+We are interested to Kane-Mele-Hubbard model at half-filling in strong-coupling regime $U\gg t_{1(2)}$.
+In the strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
+We obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second-order perturbation theory in the hopping terms.
+Using the following relations,
 \begin{align}
-\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \bs{S}_i\cdot\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\hat{c}_{i \tau}^\dagger \hat{c}_{i \tau'} &= \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow})\delta_{\tau \tau'}  + \bs{S}_i\cdot\bs{\tau}_{\tau', \tau}, \label{SpinOperatorInv1}\\
+\hat{c}_{i \tau} \hat{c}_{i \tau'}^\dagger &= \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) \delta_{\tau \tau'} - \bs{S}_i\cdot\bs{\tau}_{\tau, \tau'}, \label{SpinOperatorInv2}
 \end{align}
-Following this procedure we obtain the following effective spin Hamiltonian:
-
+we find the spin Hamiltonian for 2D AFM Mott insulators,
 \begin{align}
 \label{MKMHeff0}
-&\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
+H_{\text{S}} =& J_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + J_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \bs{D}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
 \end{align}
+with the following spin-spin interactions,
+\begin{align}
+J_{1(2)} &= \frac{2t_{1(2)}^2}{U}, \\
+\bs{\Gamma}_{ij} &=\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
+\bs{D}_{ij} &= - \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
+\end{align}
+The first and second terms in the spin Hamiltonian, Eq.
+(\ref{MKMHeff0}), are the nn and nnn symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is a nnn Heisenberg XXZ-like term arising from the intrinsic SOI, and finally, the last term is the intrinsic nnn DMI.
+The intrinsic SOI in Eq.
+(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane while it is straightforward to show that the Rashba SOI, arising from breaking the inversion symmetry of the honeycomb lattice, results an inplane DMI vector perpendicular to the lattice bonds.
+For the sake of completeness, we explain shortly the effect of disorders by adding an on-site disorder $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian \ref{MKMH}, where $\varepsilon_i$ is an uncorrelated random variable.
+Following the above procedure, it can be shown that the spin interaction parameters are only renormalized by $U^{-1} \rightarrow U/\left(U^2-(\epsilon_j-\epsilon_i)^2\right)$ \cite{Protopopov2018}.
+In the large $U$ limit, the effect of disorder is negligible and we thus ignore it in the rest of this Letter.
 
-Where:
+Different terms appeared in the spin Hamiltonian derived in Eq.
+(\ref{MKMHeff0}) has already been obtained phenomenologically in several  \cite{Owerre2016} and confirmed experimentally \cite{Chen2018} but, to the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from the Kane-Mele-Hubbard model.
+It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, Zyuzin2018} \AQ{cite two PRLs by Ran Cheng and Alexy Kovalev}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
 
-\begin{align*}
-J_{1,ij} &= 2t_1^2 \\
-J_{2,ij} &= 2t_2^2 \\
-\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
-\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1)
-\end{align*}
+\textit{Laser illumination}.
+The effect of laser irradiation on the honeycomb lattice is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
+(\ref{MKMH}), via the Peierls substitution method.
+\AQ{cite to Pierls paper in Z Physics} The electric-field component of a polarized laser pulse is given by $\bs{E}(t) = \frac{E_0}{2}( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the polarization unit vector with $\lambda= 0$ for linear polarization and $\lambda= \pm 1$ for right- and left handed polarizations.
 
-\textit{Introducing laser perturbation}.
-In the prescence of an laser perturbation we can use the Peirls substitution to include the effect of the field trough the hopping amplitudes.
-We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
-According to the Peierls rule the hopping amplitudes gain a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
-
-Let us define:
-
-\begin{equation}
-\label{Def_alpha}
-e\bs{R}_{ij}\cdot\vec{A} = \alpha_{ij} e^{i \theta_{ij}}
-\end{equation}
-
-With $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
-
-\begin{align}
-\alpha_{ij} &= -\alpha_{ji} \label{alphaSym} \\
-\theta_{ij} &= \theta_{ji} \label{thetaSym}
-\end{align}
-
-and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi-–Anger expansion to Fourier transform the hopping amplitues:
+It is more convenient to rewrite the noninteracting part of the Kane-Mele-Hubbard Hamiltonian, Eq.
+(\ref{MKMH}), from now on the hopping part, as $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
+t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being nn and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being nnn.
+According to the Peierls substitution method, the hopping part of the Hamiltonian in the presence of electromagnetic fields gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}/\hbar}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, $\hbar$ is the reduced Planck constant, and $\bs{A}$ is the vector potential of laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
+The argument of the Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A}/\hbar \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|/\hbar$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
+Now, we use the Jacobi–-Anger expansion to rewrite the Peierls phase in the basis of its harmonics,
 \begin{equation}
 \label{JacobiAnger}
-e^{ie\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} 
+e^{i\frac{e}{\hbar}\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t}
 \end{equation}
-where $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}, modulating the weight of the \textit{m}th Fourier mode of the hopping amplitude.
-Let $\hat{T}_0$ be the hopping part of the hamiltonian, so that $\hat{H}_0 = \hat{T}_0 + \text{U}\hat{D}$.
-When an electric field is applied, the hopping amplitudes become time dependent so that $\hat{H}(t) = \hat{T}(t) +  \text{U}\hat{D}$.
-Using \ref{JacobiAnger} we can write $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$ where $\hat{T}_m$ is the sum of all the \textit{m}th Fourier mode of the hopping terms.
-Additionaly we can further decompose the hopping operator into:
+where $\mathcal{J}_m(x)$ is the \textit{m}-th Bessel function of the first kind \cite{Kitamura2017}.
 
+The total Hamiltonian in the presence of the laser field is time depended through its hopping part, $\hat{H}(t) = \hat{T}(t) +  U\hat{d}$.
+Using Eq.
+(\ref{JacobiAnger}), we find $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$, where $\hat{T}_m$ is the sum of all the \textit{m}-th Fourier mode of the hopping terms.
+Finally, we decompose the hopping operator into,
 \begin{equation}
-\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}
+\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t},
 \end{equation}
+where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
 
-Where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
-
-In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$. The transformed Hamiltonian is:
-
+To find the renormalized spin Hamiltonian, first, we have to find an effective time-independent Hamiltonian.
+To do that, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
 \begin{equation}
-\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
+\hat{H}'(t) = e^{i\hat{S}(t)} \left(\hat{H}(t)  -  i\partial_t \right) e^{-i\hat{S}(t)}.
 \label{Htransformed}
 \end{equation}
-
-We perform the unitary transformation perturbatively in the hopping operator, we can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion.
+We perform the unitary transformation perturbatively in the hopping parameter.
+We can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ play the role of a bookkeeping parameter in the perturbation expansion.
 We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
-In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
-Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
-With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e.
-we can write:
+Our demand is that the transformed Hamiltonian must have the same periodicity of the original time-dependent Hamiltonian thus the unitary transformation itself must have the same periodicity of the driven laser field so that $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+Additionally, we impose that the transformed Hamiltonian to be block diagonal in the doublon number $d$ while $\hat{S}(t)$ does not contain block-diagonal terms.
+With these conditions the unitary transformation might be uniquely determined,
 \begin{equation}
@@
 where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
-From here the procedure is simple but lenghty, we expand \ref{Htransformed} in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
-Up to second order we obtain:
+We expand the transformed Hamiltonian \ref{Htransformed} in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+After tedious but straightforward calculations, the transformed Hamiltonian up to the second order in the hopping parameter is obtained $\hat{H}'(t)= \hat{T}'(t)+\text{U}\hat{d}$, where
 \begin{align}
-&\hat{H}'(t) \approx \text{U}\hat{D} - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
-&+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\label{transformedH}
+\hat{T}'(t) \approx & - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
+&+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1,n}, \hat{T}_{-1,m-n} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1,n}, \hat{T}_{1,m-n} \right]}{\text{U}-n\omega} \right) e^{im\omega t}.
+\end{align}
+Now, we are in the situation that we can calculate the effective time-independent Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
+Doing some algebra, the effective time-independent Hamiltonian in terms of creation and annihilation operators is obtained,
+\begin{align}
+\hat{H}_{\text{eff}} &= - \sum_{i,j, \tau, \tau'} \left(t_{ij}^{\tau} t_{ji}^{\tau'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \right)  \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \hat{c}_{j \tau'}^\dagger \hat{c}_{i \tau'}+\text{U}\hat{d}.
+\label{GeneralHeff}
 \end{align}
 
-Let $\hat{P}_0$ be the projection operator to the $d=0$ subspace.
-Then notice that $\hat{P}_0\hat{H}'^{1}(t)\hat{P}_0 = 0$, we define $\hat{H}_{\text{eff}}$ to be the time average of $\hat{P}_0\hat{H}'^{2}(t)\hat{P}_0$.
-Expressed in terms of creation and anihilation operators we obtain:
-
+Finally, the spin Hamiltonian, at half-filling and strong interaction limit of the effective Hamiltonian $\hat{H}_{\text{eff}}$, using the relations Eqs.
+(\ref{SpinOperatorInv1}) and (\ref{SpinOperatorInv2}), is given by,
 \begin{align}
-\hat{H}_{\text{eff}} &= - \sum_{i,j, \sigma, \sigma'} \left\{ \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} \right. \n \\
-&t_{ij}^{\sigma} t_{ji}^{\sigma'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \left. \right\} \label{GeneralHeff}
+\label{MKMHeffw}
+\tilde{H}_{\text{S}}(\omega) =& \tilde{J}_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + \tilde{J}_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j\n \\
+&+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \tilde{\bs{\Gamma}}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \tilde{\bs{D}}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
 \end{align}
-
-Where $t_{ij}^{\sigma}$ are the corresponding amplitudes for the unperturbed Hamiltonian, i.e.
-$t_{ij}^{\sigma} = t_1$ for $i,j$ being NN and $t_{ij}^{\sigma} = t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}$ for $i,j$ being NNN.
-We can obtain the spin Hamiltonian by using the relations \ref{SpinOperatorInv1} \ref{SpinOperatorInv2} and summing over the spin states.
-The resulting effective spin Hamiltonian is \ref{MKMHeff0} with renormalized coupling constants:
-
-\begin{align*}
-J_{1,ij}' &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-J_{2,ij}' &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-\bs{D}_{2,ij}' &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
-\bs{\Gamma}'_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
-\end{align*}
-
-In Figure \ref{fig2} we show the dependence of $J_{1,ij}'$ and $\bs{D}_{2,ij}'$ in the electric parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ where $e$ is the electron charge and $a$ is the lattice constant.
-The results are obtained for (units of $\hbar=t_1=1$, typically $t \approx 2.8 \text{eV}$ in graphene \cite{Castro2009}) $\text{U} = 10$ (typical value is $\text{U} \approx 9.3\text{eV}$ in graphene \cite{Wehling2011}) and $\omega = 4, 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+with the following renormalized spin interactions,
+\begin{align}
+\label{Renor-para}
+\tilde{J}_{1,ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
+\tilde{J}_{2,ij} &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
+\tilde{\bs{D}}_{ij} &= - 4 t_2 \Delta \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z, \\
+\tilde{\bs{\Gamma}}_{ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}.
+\end{align}
+All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for nn and nnn parameters which is peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
+Thus, the ratios between these renormalized parameters are different than non-perturbed parameters.
+The renormalized spin interactions presented in Eq.
+\ref{Renor-para} are independent from helicity of laser pulse and are the same for both circular and linear polarizations.
 
@@
 \end{figure}
-A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S.
-A.
-Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}.
-Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.
-This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2016}.
 
-Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
-In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.
-In Hamiltonian \ref{MKMHeff0} we expect SDW to appear in the ground state and the SDW wavevector will be determined by a function of the parameters of this model.
-We have shown that we can modulate these parameters thus providing a techique to manipulate the SDW in the ground state.
+Figure \ref{fig2}, shows the dependence of normalized nn exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and normalized nnn DMI $\tilde{D}_{ij}/D_{ij}$ in the dimensionless electric field parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
+The results are obtained for dimensionless material parameters $t_1=1$, $\text{U} = 10$ and $\omega = 4 \mathrm{and} 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+Figure \ref{fig2}, shows that it is possible not only change the sign and amplitude of the exchange interaction as already reported in Ref.
+\cite{Mentink2015} but its is possible to change the signa nd amplitude of intrinsic DMI.
+More importantly, the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$ can be tuned by laser excitations which is responsible for ultarafast photoinduced spin dynamics and magnon scattering phenomena.
 
-\begin{subsection}{Disorder}
-It is possible to introduce the effect of disorder in the model \ref{MKMH} by adding random uncorrelated on-site energies:
+Eqs.
+(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ stand for spatial component of vectors, and $i$ and $j$ refer to the lattice cite.
+Thus, the dielectric permittivity tensor is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$, where $g$ is the response function tensor.
+This optomagnetic effect described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the scattered light $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
 
-\begin{align}
-\label{DisorderedHubbardModel}
-\hat{H}_0 &= - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \n \\
-	& + \sum_{i \sigma} \epsilon_i \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma} +
-	\text{U}\hat{D}
-\end{align}
+In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think about heating and concerning on the validity of our approach.
+Recent theoretical \cite{Rudner2019} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.
+Thus, rapidly driven systems have a very long prethermalization period and this implies that the evolution of these systems in the presence of short laser pulses can be described by our formalism safely.
 
-Where $\epsilon_i$ are uncorrelated random variables $\epsilon_i \in [-W,W]$.
-At half filling we can derive an effective Hamiltonian using the same procedure as before.
-The second order virtual hopping $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ will give rise to an exchange spin interaction.
-In this case, however, the intermediate energy is $\text{U} + (\epsilon_j - \epsilon_i)$.
-Therefore the spin Hamiltonian will be:
-
-\begin{align}
-&\hat{H}_{\text{eff}}^{\text{Dis}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j +\n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
-\end{align}
-
-With:
-
-\begin{align*}
-J_{1,ij}' &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
-J_{2,ij}' &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
-\bs{D}_{2,ij}' &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
-\bs{\Gamma}_{2,ij}' &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
-\end{align*}
-
-Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
-This model is relevant for studying many-body localization phenomena \cite{Protopopov2018}.
-\end{subsection}
-
-\end{section}
+There are some recent experiments on possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides \cite{Mikhaylovskiy2015,Kim2016,Jin2014} \AQ{cite to Nature Communications volume 6, Article number: 8190 (2015)and find similar papers}.
+We hope that our work stimulate new experiments on measuring exchange interaction and DMI in 2D magnetic systems.
 
 \section*{Acknowledgments}
+The research leading to these results was supported by the European Research Council via Advanced Grant No.
+669442, ``Insulatronics,'' and by the Research Council of Norway through its Centres of Excellence funding scheme, Project No.
+262633, ``QuSpin.''
 
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{../MT}
+\bibliography{paper}
 %\end{thebibliography}

### 2019-03-04 Paper/paper.tex
Add a reference
test

@@
 
-\textit{Model Hamiltonian}.---
+\textit{Model Hamiltoniantest}.---
 Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,Griset2012,Auerbach}.
@@
 The effect of laser irradiation on the honeycomb lattice is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
-(\ref{MKMH}), via the Peierls substitution method.
+(\ref{MKMH}), via the Peierls substitution method \cite{Peierls1933}.
 \AQ{cite to Pierls paper in Z Physics} The electric-field component of a polarized laser pulse is given by $\bs{E}(t) = \frac{E_0}{2}( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the polarization unit vector with $\lambda= 0$ for linear polarization and $\lambda= \pm 1$ for right- and left handed polarizations.

### 2019-03-04 Code/Chap3.R
Added new figure

@@ -30,10 +30,10 @@ t2 <- 0.1 #NNN hoping integral
 delta <- 0.5 #NNN intrinsic SOI coupling
 
 U <- 10 #Interaction energy
-frequencies <- list(4,14) #Laser frecuency
+frequencies <- list(0.15) #Laser frecuency
 bessel_trunc_order <- 100
 lattice_cte <- 1
-field_energies <- seq(from=0, by=0.01, to=5)
+field_energies <- seq(from=0, by=0.1, to=200)
 
 #J1 = 2*t1^2/U*J1_factor
 J1_factor <- lapply(frequencies, function(x) vector(mode="numeric", length=length(field_energies)))

### 2019-03-05 Paper/paper.tex
Added new figure
1st revision

--- 2019-03-04 Paper/paper.tex
@@
 \setcounter{MaxMatrixCols}{30}
+%\usepackage{subcaption}
 
@@
 \begin{abstract}
-
+We study ultrafast optical control of exchange and Dzyaloshinskii-Moriya interactions in two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and strongly correlated limit, i.e., Mott insulator regime of a canted antiferromagnet.
+Based on Floquet theory calculations, we show that by changing the amplitude and frequency of laser pulses, it is possible to tune the amplitude, the sign and even the ratio between these two spin interactions.
+Our results pave the way for ultrafast optical manipulation of spins in recently discovered two-dimensional magnetic materials.
 \end{abstract}
@@
 
+\textit{Introduction}.--- Discovery of athermal all-optical control of antiferromagnetic (AFM) and ferromagnetic (FM) spins by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism.
+Although the underlying microscopic mechanism behind this phenomena is unclear yet, there have been many attempts to uncover its origins.
+Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction, the strongest spin interaction in magnetic systems.
+This finding has been indirectly supported by a few recent experiments.
+Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system.
+While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials, stabilizing topological objects like chiral skyrmions and domain walls, and exotic phase of topological magnon insulators.
+The ratio between these two interactions control the tilting angle of canted spins.
+Proposing a mechanism to tune this ratio has important consequences in ultrafast spin dynamics and switching.
+In this Letter, we show that intense and high-frequency laser pulses can change this ratio in a class of two-dimensional (2D) magnetic materials described by the Kane-Mele-Hubbard model.
+
+2D van der Waals magnetic materials have been recently discovered with metallic, semiconducting and insulating band structures in both AFM and FM phases.
+We can now use the advantage of both low dimensionality and magnetic order in the same material for the first time which promises novel spintronics devices with exceptional performances.
+
 \textit{Model Hamiltonian}.---
 Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,Griset2012,Auerbach}. 
-\AQ{cite papers for KMH model.
-Also cite Auerbach's book for Hubbard model!}
 The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and electron-electron interaction modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
@@
 \end{align}
+where $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
+The presence of the intrinsic SOI, Eq. (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of a pure Hubbard model to the $\mathrm{U}(1)$ spin group.
+
 \begin{figure}[t]
+\centering
 \includegraphics[width=0.6\columnwidth]{../Figures/kmh.png}
@@
 \end{figure}
-where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are nearest-neighbour (nn) and  next-nearest-neighbour (nnn) hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and nn Coulomb interactions.
-The presence of the intrinsic SOI, Eq. (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of a pure Hubbard model to the $\mathrm{U}(1)$ spin group.
 
-Using the variational principle, it has been shown that the nn Coulomb interaction can be effectively approximated by a renormalized on-site interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the nn Coulomb interaction \cite{Schuler2013,Stepanov2017}.
+Using the variational principle, it has been shown that the NN Coulomb interaction can be effectively approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013,Stepanov2017}.
 Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and rewrite the interaction part of the Hamiltonian (\ref{Hint}),
@@
 The first and second terms in the spin Hamiltonian, Eq.
-(\ref{MKMHeff0}), are the nn and nnn symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is a nnn Heisenberg XXZ-like term arising from the intrinsic SOI, and finally, the last term is the intrinsic nnn DMI.
+(\ref{MKMHeff0}), are the NN and NNN symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is a NNN Heisenberg XXZ-like term arising from the intrinsic SOI, and finally, the last term is the intrinsic NNN DMI.
 The intrinsic SOI in Eq.
@@
 (\ref{MKMHeff0}) has already been obtained phenomenologically in several  \cite{Owerre2016} and confirmed experimentally \cite{Chen2018} but, to the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from the Kane-Mele-Hubbard model.
-It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, Zyuzin2018} \AQ{cite two PRLs by Ran Cheng and Alexy Kovalev}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
+It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
 
@@
 The effect of laser irradiation on the honeycomb lattice is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
-(\ref{MKMH}), via the Peierls substitution method.
-\AQ{cite to Pierls paper in Z Physics} The electric-field component of a polarized laser pulse is given by $\bs{E}(t) = \frac{E_0}{2}( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the polarization unit vector with $\lambda= 0$ for linear polarization and $\lambda= \pm 1$ for right- and left handed polarizations.
+(\ref{MKMH}), via the Peierls substitution method \cite{Peierls1933}.
+The electric-field component of a polarized laser pulse is given by $\bs{E}(t) = \frac{E_0}{2}( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the polarization unit vector with $\lambda= 0$ for linear polarization and $\lambda= \pm 1$ for right- and left handed polarizations.
 
@@
 (\ref{MKMH}), from now on the hopping part, as $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
-t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being nn and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being nnn.
+t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being nn and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being NNN.
 According to the Peierls substitution method, the hopping part of the Hamiltonian in the presence of electromagnetic fields gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}/\hbar}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, $\hbar$ is the reduced Planck constant, and $\bs{A}$ is the vector potential of laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
@@
 \label{transformedH}
-\hat{T}'(t) \approx & - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
+&\hat{T}'(t) \approx  - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
 &+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1,n}, \hat{T}_{-1,m-n} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1,n}, \hat{T}_{1,m-n} \right]}{\text{U}-n\omega} \right) e^{im\omega t}.
@@
 \end{align}
-All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for nn and nnn parameters which is peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
+All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for NN and NNN parameters which is peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
 Thus, the ratios between these renormalized parameters are different than non-perturbed parameters.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
-\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$.
-Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.
-Notice that $\tilde{J}_1$ and $\tilde{D}_{2}$ do not depend on the parameters $t_1$, $t_2$ and $\Delta$.}
+\centering
+\includegraphics[width=\columnwidth]{../Figures/NNvsNNN1.pdf}
+\caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as a function of $\mathcal{E} = \frac{eaE_0}{\omega}$, for two laser frequencies $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
 \label{fig2}
-\vspace*{-6pt}
 \end{figure}
 
-Figure \ref{fig2}, shows the dependence of normalized nn exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and normalized nnn DMI $\tilde{D}_{ij}/D_{ij}$ in the dimensionless electric field parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
+Figure \ref{fig2}, shows the dependence of normalized nn exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and normalized NNN DMI $\tilde{D}_{ij}/D_{ij}$ in the dimensionless electric field parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
 The results are obtained for dimensionless material parameters $t_1=1$, $\text{U} = 10$ and $\omega = 4 \mathrm{and} 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
@@
 
-There are some recent experiments on possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides \cite{Mikhaylovskiy2015,Kim2016,Jin2014} \AQ{cite to Nature Communications volume 6, Article number: 8190 (2015)and find similar papers}.
+There are some recent experiments on possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides \cite{Mikhaylovskiy2015,Kim2016,Jin2014}.
 We hope that our work stimulate new experiments on measuring exchange interaction and DMI in 2D magnetic systems.

### 2019-03-05 Paper/paper.tex
first version 12:00-05March

@@
 We study ultrafast optical control of exchange and Dzyaloshinskii-Moriya interactions in two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and strongly correlated limit, i.e., Mott insulator regime of a canted antiferromagnet.
-Based on Floquet theory calculations, we show that by changing the amplitude and frequency of laser pulses, it is possible to tune the amplitude, the sign and even the ratio between these two spin interactions.
+Based on Floquet theory calculations, we show that by changing the amplitude and frequency of polarized laser pulses, it is possible to tune the amplitude, the sign and even the ratio between these two spin interactions.
+We find that in this model, the renormaization of spin interactions are helicity independent.
 Our results pave the way for ultrafast optical manipulation of spins in recently discovered two-dimensional magnetic materials.
@@
 
-\textit{Introduction}.--- Discovery of athermal all-optical control of antiferromagnetic (AFM) and ferromagnetic (FM) spins by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism.
+\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism.
 Although the underlying microscopic mechanism behind this phenomena is unclear yet, there have been many attempts to uncover its origins.
@@
 
-2D van der Waals magnetic materials have been recently discovered with metallic, semiconducting and insulating band structures in both AFM and FM phases.
+2D van der Waals magnetic materials with metallic, semiconducting and insulating band structures have been recently discovered in both AFM and FM phases.
 We can now use the advantage of both low dimensionality and magnetic order in the same material for the first time which promises novel spintronics devices with exceptional performances.
@@
 where $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
-The presence of the intrinsic SOI, Eq. (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of a pure Hubbard model to the $\mathrm{U}(1)$ spin group.
+The presence of the intrinsic NNN SOI, Eq.
+(\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of original Hubbard model to the $\mathrm{U}(1)$ spin group.
+In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, presence of, respectively, NNN and NN Rashba SOIs, furthur reduces the symmetry to $Z_2$.
 
@@
 where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$ and projection operators $\hat{P}_d$.
-We are interested to Kane-Mele-Hubbard model at half-filling in strong-coupling regime $U\gg t_{1(2)}$.
-In the strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
+We are interested to Kane-Mele-Hubbard model at half-filling in strongly correlated regime $U\gg t_{1(2)}$.
+In such strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
 We obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second-order perturbation theory in the hopping terms.
@@
 The intrinsic SOI in Eq.
-(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane while it is straightforward to show that the Rashba SOI, arising from breaking the inversion symmetry of the honeycomb lattice, results an inplane DMI vector perpendicular to the lattice bonds.
+(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane while it is straightforward to show that the Rashba SOI results an inplane DMI vector perpendicular to the lattice bonds.
 For the sake of completeness, we explain shortly the effect of disorders by adding an on-site disorder $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian \ref{MKMH}, where $\varepsilon_i$ is an uncorrelated random variable.
@@
 There are some recent experiments on possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides \cite{Mikhaylovskiy2015,Kim2016,Jin2014}.
-We hope that our work stimulate new experiments on measuring exchange interaction and DMI in 2D magnetic systems.
+We hope that our work stimulate new experiments on measuring both exchange interaction and DMI in 2D magnetic systems.
+
+In summary, using Floquet theory we have investigated the effect of polarized and intense high-frequency laser pulses on 2D canted antiferromagnetic Mott insulators.
+We have found that both amplitude and sign of the ratio between the exchange interaction and DMI is changed in honeycomb lattices irrespective to the helicity of laser pulses.
+Our calculations open a new way to ultrafast energy-efficient control of spins and engineering of topological objects and topological properties of 2D van der Waals magnetic materials.
 

### 2019-03-05 Paper/paper.tex
2nd version

@@
 
-\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism.
+\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
 Although the underlying microscopic mechanism behind this phenomena is unclear yet, there have been many attempts to uncover its origins.
-Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction, the strongest spin interaction in magnetic systems.
-This finding has been indirectly supported by a few recent experiments.
-Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system.
-While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials, stabilizing topological objects like chiral skyrmions and domain walls, and exotic phase of topological magnon insulators.
+Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction \cite{PhysRevLett.113.057201,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
+This finding has been supported by recent experiments \cite{Mikhaylovskiy2015,2018Natur.553..481G}.
+Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
+While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, stabilizing topological objects like chiral skyrmions \cite{AlirezaSk1, AlirezaSk2} and domain walls \cite{AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
 The ratio between these two interactions control the tilting angle of canted spins.
-Proposing a mechanism to tune this ratio has important consequences in ultrafast spin dynamics and switching.
+Proposing a mechanism to tune this ratio has important consequences in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
 In this Letter, we show that intense and high-frequency laser pulses can change this ratio in a class of two-dimensional (2D) magnetic materials described by the Kane-Mele-Hubbard model.
 
-2D van der Waals magnetic materials with metallic, semiconducting and insulating band structures have been recently discovered in both AFM and FM phases.
+2D van der Waals magnetic materials with metallic, semiconducting and insulating band structures have been recently discovered in both AFM and FM phases \cite{2D1,2D2}.
 We can now use the advantage of both low dimensionality and magnetic order in the same material for the first time which promises novel spintronics devices with exceptional performances.
@@
 Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,Griset2012,Auerbach}. 
-The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and electron-electron interaction modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
+The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and Coulomb interaction between electrons modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
 \begin{equation}
@@
 \end{align}
-All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for NN and NNN parameters which is peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
-Thus, the ratios between these renormalized parameters are different than non-perturbed parameters.
+All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for NN and NNN parameters.
+Thus, the ratios between these renormalized parameters are different than non-perturbed parameters which is a peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
 The renormalized spin interactions presented in Eq.
-\ref{Renor-para} are independent from helicity of laser pulse and are the same for both circular and linear polarizations.
+(\ref{Renor-para}) are helicity independent.
 
@@
 
-There are some recent experiments on possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides \cite{Mikhaylovskiy2015,Kim2016,Jin2014}.
-We hope that our work stimulate new experiments on measuring both exchange interaction and DMI in 2D magnetic systems.
+Possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides has been recently reported \cite{Mikhaylovskiy2015}.
+We hope that our work stimulate new experiments on measuring both exchange interaction and DMI in novel 2D magnetic systems.
 

### 2019-03-06 Paper/paper.tex
3rd version

@@
 
-\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by intense and high-frequency laser pulses has elevated spintronics to a new era called ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
+\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by ultrashort, intense and high-frequency laser pulses has elevated spintronics to a new era of ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
 Although the underlying microscopic mechanism behind this phenomena is unclear yet, there have been many attempts to uncover its origins.
-Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction \cite{PhysRevLett.113.057201,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
+Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
 This finding has been supported by recent experiments \cite{Mikhaylovskiy2015,2018Natur.553..481G}.
 Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
-While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, stabilizing topological objects like chiral skyrmions \cite{AlirezaSk1, AlirezaSk2} and domain walls \cite{AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
+While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, stabilizing topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
 The ratio between these two interactions control the tilting angle of canted spins.
 Proposing a mechanism to tune this ratio has important consequences in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
-In this Letter, we show that intense and high-frequency laser pulses can change this ratio in a class of two-dimensional (2D) magnetic materials described by the Kane-Mele-Hubbard model.
 
-2D van der Waals magnetic materials with metallic, semiconducting and insulating band structures have been recently discovered in both AFM and FM phases \cite{2D1,2D2}.
+Another important breakthrough in spintronics happened in recent few years is the discovery of two-dimensional (2D) van der Waals magnetic materials with metallic, semiconducting and insulating band structures in both AFM and FM phases \cite{2D1,2D2}.
 We can now use the advantage of both low dimensionality and magnetic order in the same material for the first time which promises novel spintronics devices with exceptional performances.
 
+In this Letter, we show that intense and high-frequency laser pulses can change spin-spin interactions and the ratio between exchange interaction and DMI drastically in a class of 2D magnetic materials described by the Kane-Mele-Hubbard model.
+
 \textit{Model Hamiltonian}.---
-Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,Griset2012,Auerbach}. 
+Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.84.235149,Griset2012,Auerbach}.
 The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and Coulomb interaction between electrons modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
@@
 \begin{align}
-\hat{\mathcal{H}}_{\text{K}} &= - \sum_{\langle i,j \rangle, \tau} t_{1}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} - \sum_{\langle \langle i,j \rangle \rangle, \tau} t_{2}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \label{Ht} \\
-\hat{\mathcal{H}}_{\text{SOI}} & = \sum_{\langle \langle i,j \rangle \rangle, \tau,\tau'} i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'} \label{Hsoi} \\
+\hat{\mathcal{H}}_{\text{K}} &= - t_{1}\sum_{\langle i,j \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} - t_{2}\sum_{\langle \langle i,j \rangle \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \label{Ht} \\
+\hat{\mathcal{H}}_{\text{SOI}} & = i \Delta \sum_{\langle \langle i,j \rangle \rangle, \tau,\tau'} \nu_{ij}\sigma^z_{\tau, \tau'}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'} \label{Hsoi} \\
 \hat{\mathcal{H}}_{\text{int}} &= U_{00}\sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \tau \tau'} V_{ij}\hat{n}_{i\tau}\hat{n}_{j\tau'} \label{Hint}.
@@
 It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
+Ultrafast control of DMI and exchange interaction by laser pulses also open a way to engineer all these phenomena.
 
@@
 
-To find the renormalized spin Hamiltonian, first, we have to find an effective time-independent Hamiltonian.
+To find renormalized spin Hamiltonian, we first drive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,Floquet2}.
 To do that, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
@@
 \end{align}
-Now, we are in the situation that we can calculate the effective time-independent Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
+Now, we are in the situation that we can calculate the effective static Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
 Doing some algebra, the effective time-independent Hamiltonian in terms of creation and annihilation operators is obtained,
@@
 \centering
-\includegraphics[width=\columnwidth]{../Figures/NNvsNNN1.pdf}
+\vspace{-1.3cm}
+\includegraphics[width=\columnwidth]{NNvsNNN1.pdf}
+\vspace{-1cm}
 \caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as a function of $\mathcal{E} = \frac{eaE_0}{\omega}$, for two laser frequencies $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
@@
 In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think about heating and concerning on the validity of our approach.
-Recent theoretical \cite{Rudner2019} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.
+Recent theoretical \cite{Rudner2019,PhysRevB.97.014311} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.
 Thus, rapidly driven systems have a very long prethermalization period and this implies that the evolution of these systems in the presence of short laser pulses can be described by our formalism safely.
@@
 
-In summary, using Floquet theory we have investigated the effect of polarized and intense high-frequency laser pulses on 2D canted antiferromagnetic Mott insulators.
-We have found that both amplitude and sign of the ratio between the exchange interaction and DMI is changed in honeycomb lattices irrespective to the helicity of laser pulses.
-Our calculations open a new way to ultrafast energy-efficient control of spins and engineering of topological objects and topological properties of 2D van der Waals magnetic materials.
+In summary, we have investigated the effect of polarized and intense high-frequency laser pulses on 2D canted antiferromagnetic Mott insulators using Floquet theory.
+We have found that both sign and amplitude of the ratio between the exchange interaction and DMI is changed in honeycomb lattices irrespective to the helicity of laser pulses.
+Our calculations open a new way to ultrafast and energy-efficient control of spins and engineering of topological objects and topological properties of 2D van der Waals magnetic materials.
 

### 2019-03-07 Paper/paper.tex
3rd version before Arne's comments
v4

@@
 \author{Alireza Qaiumzadeh}
-\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
+%\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
 \affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
@@
 \textit{Model Hamiltonian}.---
-Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.84.235149,Griset2012,Auerbach}.
+Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
 The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and Coulomb interaction between electrons modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
@@
 \begin{align}
-\hat{\mathcal{H}}_{\text{K}} &= - t_{1}\sum_{\langle i,j \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} - t_{2}\sum_{\langle \langle i,j \rangle \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \label{Ht} \\
-\hat{\mathcal{H}}_{\text{SOI}} & = i \Delta \sum_{\langle \langle i,j \rangle \rangle, \tau,\tau'} \nu_{ij}\sigma^z_{\tau, \tau'}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'} \label{Hsoi} \\
-\hat{\mathcal{H}}_{\text{int}} &= U_{00}\sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \tau \tau'} V_{ij}\hat{n}_{i\tau}\hat{n}_{j\tau'} \label{Hint}.
+&\hat{\mathcal{H}}_{\text{K}} = - t_{1}\sum_{\langle i,j \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} - t_{2}\sum_{\langle \langle i,j \rangle \rangle, \tau} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau}, \label{Ht} \\
+&\hat{\mathcal{H}}_{\text{SOI}}  = i \Delta \sum_{\langle \langle i,j \rangle \rangle, \tau,\tau'} \nu_{ij}\sigma^z_{\tau, \tau'}\hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'} \label{Hsoi}, \\
+&\hat{\mathcal{H}}_{\text{int}} = U_{00}\sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \tau \tau'} V_{ij}\hat{n}_{i\tau}\hat{n}_{j\tau'} \label{Hint}.
 \end{align}
-where $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
+Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
 The presence of the intrinsic NNN SOI, Eq.
@@
 \centering
-\includegraphics[width=0.6\columnwidth]{../Figures/kmh.png}
+\includegraphics[width=0.6\columnwidth]{kmh.png}
 \caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$.
@@
 \begin{align}
-\hat{c}_{i \tau}^\dagger \hat{c}_{i \tau'} &= \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow})\delta_{\tau \tau'}  + \bs{S}_i\cdot\bs{\tau}_{\tau', \tau}, \label{SpinOperatorInv1}\\
-\hat{c}_{i \tau} \hat{c}_{i \tau'}^\dagger &= \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) \delta_{\tau \tau'} - \bs{S}_i\cdot\bs{\tau}_{\tau, \tau'}, \label{SpinOperatorInv2}
+&\hat{c}_{i \tau}^\dagger \hat{c}_{i \tau'} = \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow})\delta_{\tau \tau'}  + \bs{S}_i\cdot\bs{\tau}_{\tau', \tau}, \label{SpinOperatorInv1}\\
+&\hat{c}_{i \tau} \hat{c}_{i \tau'}^\dagger = \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) \delta_{\tau \tau'} - \bs{S}_i\cdot\bs{\tau}_{\tau, \tau'}, \label{SpinOperatorInv2}
 \end{align}
@@
 \label{MKMHeff0}
-H_{\text{S}} =& J_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + J_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j\n \\
+H_{\text{S}} =& J_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + J_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j,  \n \\
 &+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \bs{D}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
@@
 with the following spin-spin interactions,
+\begin{subequations}
+\label{spin-para}
 \begin{align}
-J_{1(2)} &= \frac{2t_{1(2)}^2}{U}, \\
-\bs{\Gamma}_{ij} &=\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
-\bs{D}_{ij} &= - \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
+&J_{1(2)} = \frac{2t_{1(2)}^2}{U}, \\
+&\bs{\Gamma}_{ij} =\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
+&\bs{D}_{ij} = - \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
 \end{align}
+\end{subequations}
 The first and second terms in the spin Hamiltonian, Eq.
-(\ref{MKMHeff0}), are the NN and NNN symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is a NNN Heisenberg XXZ-like term arising from the intrinsic SOI, and finally, the last term is the intrinsic NNN DMI.
+(\ref{MKMHeff0}), are the NN and NNN symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is the NNN anisotropic Heisenberg exchange interaction (XXZ-like term) arising from the intrinsic SOI, and finally, the last term is the intrinsic NNN DMI.
 The intrinsic SOI in Eq.
@@
 Different terms appeared in the spin Hamiltonian derived in Eq.
-(\ref{MKMHeff0}) has already been obtained phenomenologically in several  \cite{Owerre2016} and confirmed experimentally \cite{Chen2018} but, to the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from the Kane-Mele-Hubbard model.
+(\ref{MKMHeff0}) has already been obtained phenomenologically \cite{Owerre2016} and even confirmed experimentally \cite{Chen2018} but, to the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from microscopic Kane-Mele-Hubbard model.
 It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
@@
 \label{JacobiAnger}
-e^{i\frac{e}{\hbar}\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t}
+e^{i\frac{e}{\hbar}\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t},
 \end{equation}
@@
 \begin{equation}
-\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t}
+\hat{S}^{(\nu)}(t) = \sum_{d \neq 0} \sum_m \eta^\nu \hat{S}^{(\nu)}_{d,m} e^{im\omega t},
 \end{equation}
@@
 Now, we are in the situation that we can calculate the effective static Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
-Doing some algebra, the effective time-independent Hamiltonian in terms of creation and annihilation operators is obtained,
+Doing some algebra, the effective static Hamiltonian in terms of creation and annihilation operators is obtained,
 \begin{align}
@@
 \label{MKMHeffw}
-\tilde{H}_{\text{S}}(\omega) =& \tilde{J}_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + \tilde{J}_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j\n \\
+\tilde{H}_{\text{S}}(\omega) =& \tilde{J}_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + \tilde{J}_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j, \n \\
 &+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \tilde{\bs{\Gamma}}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \tilde{\bs{D}}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
@@
 with the following renormalized spin interactions,
+\begin{subequations}
+\label{Renor-para}
 \begin{align}
-\label{Renor-para}
-\tilde{J}_{1,ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
-\tilde{J}_{2,ij} &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
-\tilde{\bs{D}}_{ij} &= - 4 t_2 \Delta \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z, \\
-\tilde{\bs{\Gamma}}_{ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}.
+&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\ 
+&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega},\\ 
+&\tilde{\bs{D}}_{ij} = - 4 t_2 \Delta \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z. 
 \end{align}
+\end{subequations}
 All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for NN and NNN parameters.
@@
 Eqs.
-(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ stand for spatial component of vectors, and $i$ and $j$ refer to the lattice cite.
-Thus, the dielectric permittivity tensor is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$, where $g$ is the response function tensor.
-This optomagnetic effect described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the scattered light $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
+(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ stand for spatial component of vectors, $i$ and $j$ refer to the lattice cite, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
+(\ref{Renor-para}).
+Thus, the dielectric permittivity tensor which determine optical properties of the medium, is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$.
+This opto-magnetic effect described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the scattered light $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
 

### 2019-03-07 Paper/paper.tex
v4.1

@@
 \vspace{-1cm}
-\caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as a function of $\mathcal{E} = \frac{eaE_0}{\omega}$, for two laser frequencies $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
+\caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as a function of the Floquet parameter $\mathcal{E} = \frac{eaE_0}{\omega}$, for two laser frequencies $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
 \label{fig2}
@@
 
-Figure \ref{fig2}, shows the dependence of normalized nn exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and normalized NNN DMI $\tilde{D}_{ij}/D_{ij}$ in the dimensionless electric field parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
-The results are obtained for dimensionless material parameters $t_1=1$, $\text{U} = 10$ and $\omega = 4 \mathrm{and} 14$ (equivalently, $T = \frac{2\pi}{\omega} \approx 10^{-16}\text{s}$).
+Figure \ref{fig2}, shows the dependence of dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant, for two different laser pulse frequencies.
+The results are obtained for dimensionless material parameters $t_1=1$ and $\text{U} = 10$.
 Figure \ref{fig2}, shows that it is possible not only change the sign and amplitude of the exchange interaction as already reported in Ref.

### 2019-03-07 Paper/paper.tex
v4.2

@@
 \includegraphics[width=0.6\columnwidth]{kmh.png}
-\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$.
-$\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
+\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counter-clockwise hoping.}
 \label{fig1}

### 2019-03-07 Paper/paper.tex
v5

@@
 Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
-This finding has been supported by recent experiments \cite{Mikhaylovskiy2015,2018Natur.553..481G}.
+This finding has been supported by recent experiments \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
 Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
@@
 
-To find renormalized spin Hamiltonian, we first drive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,Floquet2}.
+To find renormalized spin Hamiltonian, we first drive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,2018NJPh...20i3022R,Floquet2}.
 To do that, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
@@
 \begin{align}
-&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\ 
-&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega},\\ 
-&\tilde{\bs{D}}_{ij} = - 4 t_2 \Delta \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z. 
+&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
+&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega},\\
+&\tilde{\bs{D}}_{ij} = - 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
 \end{align}

### 2019-03-08 Appendices/AppendixE.tex
Figure2 changes

@@
 \begin{equation}
+\label{FloquetMode}
 \ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}
@@
 \end{equation}
+
+\section{Extended Hilbert space}
+
+Having introduced the micromotion operator and the Floquet Hamiltonian, we turn on to introduce the concept of extended Hilbert space.
+Introducing \ref{FloquetMode} in the Scr\"{o}dinger equation we get:
+
+\begin{equation}
+\left[ \hat{H}-i\text{d}_t\right] \ket{u_n(t)} = \epsilon_n\ket{u_n(t)}
+\end{equation}
+
+This can be regarded as an eigenvalue problem in the space $\mathcal{F}=\mathcal{H}\otimes\mathcal{L}_T$, where $\mathcal{L}_T$ is the space of square integrable T-periodic functions.
+The operator $\hat{Q} = \hat{H}-i\text{d}_t$ acting on $\mathcal{F}$ is referred to as the quasienergy operator.
+States in the extended Hilbert space (that is, a state plus its periodic time dependence) is usually denoted as $\ket{u}\rangle$, and the inner product in this space is defined as:
+
+\begin{equation}
+\langle \bra{u}\ket{v} \rangle = \frac{1}{T}\int_0^T \text{d}t \bra{u(t)}\ket{v(t)}
+\end{equation}
+
+An orthonormal basis for the extended Hilbert space can be obtained as the direct product an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$.
+A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, therefore, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$.
+In this basis, the quasienergy operator has matrix elements:
+
+\begin{align}
+\langle \bra{\alpha' m'}\hat{Q}\ket{\alpha m} \rangle &= \frac{1}{T}\int_0^T \text{d}t e^{-im'\omega t}\bra{\alpha'} \hat{H}(t)-i\hbar\text{d}_t \ket{\alpha}e^{im\omega t} = \nonumber \\
+&= \bra{\alpha'} \hat{H}_{m'-m} \ket{\alpha} + \delta_{m'm}\delta_{\alpha' \alpha}m\hbar\omega \label{QOmatelem}
+\end{align}
+
+Where
+\begin{equation}
+\hat{H}_m = \frac{1}{T}\int_0^T \text{d}t e^{-im\omega t}\hat{H}(t) 
+\end{equation}
+is the Fourier transform of the Hamiltonian.
+Now, a Floquet state $\ket{\psi_n(t)} = e^{-i \epsilon_n t}\ket{u_n(t)}$ can be expanded as $\ket{u_n(t)} = \sum_m e^{im\omega t}\ket{u_{nm}}$, using \ref{QOmatelem} and projecting onto the \textit{m}th Fourier mode we can rewrite the Scr\"{o}dinger equation as:
+
+\begin{equation}
+(\epsilon_n+m\omega)\ket{u_{nm}} = \sum_{m'}\hat{H}_{m-m'}\ket{u_{nm'}}
+\end{equation}

### 2019-03-09 Paper/paper.tex
Figure2 changes
add figure with E closer to horiz axis
Arne's changes + minor changes

@@
 \usepackage[symbol]{footmisc}
-%\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}
+%\usepackage[style=numeric-comp]{biblatex}
 \setcounter{MaxMatrixCols}{30}
@@
 \begin{document}
-\title{Ultrafast Control of Spin-Spin Interactions in Two-Dimensional Magnetic Systems: Kane-Mele-Hubbard Model}
+\title{Ultrafast Control of Spin-Spin Interactions in Two-Dimensional Magnets}
 
@@
 %\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
-\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
+\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and TechFnology, NO-7491 Trondheim, Norway}
 %\affiliation{Institute for Advanced Studies in Basic Science (IASBS), Zanjan, Iran}
@@
 \begin{abstract}
-We study ultrafast optical control of exchange and Dzyaloshinskii-Moriya interactions in two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and strongly correlated limit, i.e., Mott insulator regime of a canted antiferromagnet.
-Based on Floquet theory calculations, we show that by changing the amplitude and frequency of polarized laser pulses, it is possible to tune the amplitude, the sign and even the ratio between these two spin interactions.
-We find that in this model, the renormaization of spin interactions are helicity independent.
+Light provides ultrafast control of exchange and Dzyaloshinskii-Moriya interactions, we consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and in the strongly correlated limit, i.e., the Mott insulator regime of a canted antiferromagnet.
+Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
+Furthermore, the renormalizations of the spin interactions are helicity independent.
 Our results pave the way for ultrafast optical manipulation of spins in recently discovered two-dimensional magnetic materials.
@@
 
-\textit{Introduction}.--- Discovery of athermal all-optical control of order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by ultrashort, intense and high-frequency laser pulses has elevated spintronics to a new era of ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
-Although the underlying microscopic mechanism behind this phenomena is unclear yet, there have been many attempts to uncover its origins.
-Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
+\textit{Introduction}.--- The discovery of all-optical control of the order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by ultrashort, intense and high-frequency laser pulses has transformed spintronics to a new era of ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
+Although the underlying microscopic mechanism remains unclear, there have been many attempts to uncover its origins.
+Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of the exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
 This finding has been supported by recent experiments \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
-Another important spin interaction is Dzyaloshinskii-Moriya intercation (DMI), an antisymmetric exchange interaction appeared in inversion symmetry broken systems, that breaks the chiral symmetry of the system \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
-While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials such as weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, stabilizing topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
-The ratio between these two interactions control the tilting angle of canted spins.
-Proposing a mechanism to tune this ratio has important consequences in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
+Another important spin interaction is the Dzyaloshinskii-Moriya interaction (DMI), an antisymmetric exchange interaction in inversion symmetry broken systems, where the chiral symmetry of the system is broken \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
+While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials and causes weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
+The ratio between these two interactions controls the tilting angle of the canted spins.
+Finding a mechanism to tune this ratio enables new phenomena in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
 
-Another important breakthrough in spintronics happened in recent few years is the discovery of two-dimensional (2D) van der Waals magnetic materials with metallic, semiconducting and insulating band structures in both AFM and FM phases \cite{2D1,2D2}.
-We can now use the advantage of both low dimensionality and magnetic order in the same material for the first time which promises novel spintronics devices with exceptional performances.
+Another recent important breakthrough in spintronics is the discovery of two-dimensional (2D) van der Waals AFM and FM materials with metallic, semiconducting and insulating band structures \cite{2D1,2D2}.
+The advantage of low dimensionality and magnetic order in the same material enables novel spintronics devices with exceptional performances.
 
-In this Letter, we show that intense and high-frequency laser pulses can change spin-spin interactions and the ratio between exchange interaction and DMI drastically in a class of 2D magnetic materials described by the Kane-Mele-Hubbard model.
+In this Letter, we show that intense and high-frequency laser pulses can change the spin-spin interactions and the ratio between the exchange interaction and the DMI dramatically in a wide class of 2D magnetic materials described by the Kane-Mele-Hubbard model.
 
 \textit{Model Hamiltonian}.---
-Effective Hamiltonian of a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
-The Hamitlonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and Coulomb interaction between electrons modelled by extended Hubbard model $\hat{\mathcal{H}}_{\text{int}}$,
+Electrons in a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by the Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
+The Hamiltonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and the Coulomb interaction between the electrons modelled by the extended Hubbard interaction $\hat{\mathcal{H}}_{\text{int}}$,
 \begin{equation}
@@
 \end{align}
-Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI constant, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
+Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI parameter, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
 The presence of the intrinsic NNN SOI, Eq.
-(\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of original Hubbard model to the $\mathrm{U}(1)$ spin group.
-In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, presence of, respectively, NNN and NN Rashba SOIs, furthur reduces the symmetry to $Z_2$.
+(\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of the original Hubbard model to the $\mathrm{U}(1)$ spin group.
+In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, the presence of, respectively, NNN and NN Rashba SOIs, furthur reduces the symmetry to $Z_2$.
 
@@
 
-Using the variational principle, it has been shown that the NN Coulomb interaction can be effectively approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013,Stepanov2017}.
-Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and rewrite the interaction part of the Hamiltonian (\ref{Hint}),
+Using the variational principle, it has been shown that the NN Coulomb interaction can be approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013,Stepanov2017}.
+Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and express the interaction part of the Hamiltonian (\ref{Hint}) as
 \begin{equation}
@@
 \end{equation}
-where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$ and projection operators $\hat{P}_d$.
-We are interested to Kane-Mele-Hubbard model at half-filling in strongly correlated regime $U\gg t_{1(2)}$.
-In such strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$.
+where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$.
+We denote the projection operator to the subspace of states with eigenvale $d$ (i.e.
+states with exactly $d$ double occupancies) by $\hat{P}_d$.
+We are interested in the limit of strongly correlated regime $U\gg t_{1(2)}$.
+In such a strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) has a much larger energy than those with no double occupancies ($d=0$).
 We obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second-order perturbation theory in the hopping terms.
@@
 The intrinsic SOI in Eq.
-(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane while it is straightforward to show that the Rashba SOI results an inplane DMI vector perpendicular to the lattice bonds.
-For the sake of completeness, we explain shortly the effect of disorders by adding an on-site disorder $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian \ref{MKMH}, where $\varepsilon_i$ is an uncorrelated random variable.
-Following the above procedure, it can be shown that the spin interaction parameters are only renormalized by $U^{-1} \rightarrow U/\left(U^2-(\epsilon_j-\epsilon_i)^2\right)$ \cite{Protopopov2018}.
+(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane.
+It can also be shown that the Rashba SOI results in an in-plane DMI vector that is perpendicular to the lattice bonds.
+For the sake of completeness, we explain shortly the effect of disorder by adding an on-site disorder potential $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian \ref{MKMH}, where $\varepsilon_i$ is an uncorrelated random variable.
+Following the above procedure, it can be shown that the spin interaction parameters are renormalized as $U^{-1} \rightarrow U/\left(U^2-(\epsilon_j-\epsilon_i)^2\right)$ \cite{Protopopov2018}.
 In the large $U$ limit, the effect of disorder is negligible and we thus ignore it in the rest of this Letter.
 
-Different terms appeared in the spin Hamiltonian derived in Eq.
-(\ref{MKMHeff0}) has already been obtained phenomenologically \cite{Owerre2016} and even confirmed experimentally \cite{Chen2018} but, to the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from microscopic Kane-Mele-Hubbard model.
-It has been shown that this Hamiltonian has interesting features and exotic phases like, existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
-Ultrafast control of DMI and exchange interaction by laser pulses also open a way to engineer all these phenomena.
+The terms in the spin Hamiltonian derived in Eq.
+(\ref{MKMHeff0}) have already been obtained phenomenologically \cite{Owerre2016} and confirmed experimentally \cite{Chen2018}.
+To the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from the microscopic Kane-Mele-Hubbard model.
+This Hamiltonian has interesting features and exotic phases like, the existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
+Ultrafast control of DMI and exchange interaction by laser pulses enables engineering all these phenomena.
 
 \textit{Laser illumination}.
-The effect of laser irradiation on the honeycomb lattice is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
+The effect of laser irradiation is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
 (\ref{MKMH}), via the Peierls substitution method \cite{Peierls1933}.
@@
 It is more convenient to rewrite the noninteracting part of the Kane-Mele-Hubbard Hamiltonian, Eq.
-(\ref{MKMH}), from now on the hopping part, as $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
-t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being nn and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being NNN.
-According to the Peierls substitution method, the hopping part of the Hamiltonian in the presence of electromagnetic fields gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}/\hbar}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, $\hbar$ is the reduced Planck constant, and $\bs{A}$ is the vector potential of laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
-The argument of the Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A}/\hbar \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|/\hbar$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
+(\ref{MKMH}), as $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
+t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being NN and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being NNN.
+According to the Peierls substitution method, the hopping part of the Hamiltonian gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}/\hbar}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, $\hbar$ is the reduced Planck constant, and $\bs{A}$ is the vector potential of the laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
+The Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A}/\hbar \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|/\hbar$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
 Now, we use the Jacobi–-Anger expansion to rewrite the Peierls phase in the basis of its harmonics,
@@
 
-The total Hamiltonian in the presence of the laser field is time depended through its hopping part, $\hat{H}(t) = \hat{T}(t) +  U\hat{d}$.
+The total Hamiltonian in the presence of the laser field is time dependent through its hopping part, $\hat{H}(t) = \hat{T}(t) +  U\hat{d}$.
 Using Eq.
 (\ref{JacobiAnger}), we find $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$, where $\hat{T}_m$ is the sum of all the \textit{m}-th Fourier mode of the hopping terms.
-Finally, we decompose the hopping operator into,
+We can additionally decompose $\hat{T}_m = \hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m}$, where $\hat{T}_{dm}(t)$ changes the doublon number by adding $d$ double occupancies, $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
+With this, we can write the hopping operator as
 \begin{equation}
@@
 \end{equation}
-where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
 
-To find renormalized spin Hamiltonian, we first drive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,2018NJPh...20i3022R,Floquet2}.
-To do that, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
+To find the renormalized spin Hamiltonian, we first derive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,2018NJPh...20i3022R,Floquet2}.
+To this end, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, by using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
 \begin{equation}
@@
 We perform the unitary transformation perturbatively in the hopping parameter.
-We can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ play the role of a bookkeeping parameter in the perturbation expansion.
+We can formally express $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ plays the role of a bookkeeping parameter in the perturbation expansion.
 We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
-Our demand is that the transformed Hamiltonian must have the same periodicity of the original time-dependent Hamiltonian thus the unitary transformation itself must have the same periodicity of the driven laser field so that $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
-Additionally, we impose that the transformed Hamiltonian to be block diagonal in the doublon number $d$ while $\hat{S}(t)$ does not contain block-diagonal terms.
-With these conditions the unitary transformation might be uniquely determined,
+We require that the transformed Hamiltonian must have the same periodicity as the original time-dependent Hamiltonian.
+Thus the unitary transformation must have the same periodicity as the driven laser field so that $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+Additionally, we impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
+With the further requirement that $\hat{S}(t)$ does not contain block-diagonal terms we can uniquely determine the unitary transformation.
+Following the same procedure we used for the hopping operator, we write
 \begin{equation}
@@
 where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
-We expand the transformed Hamiltonian \ref{Htransformed} in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
-After tedious but straightforward calculations, the transformed Hamiltonian up to the second order in the hopping parameter is obtained $\hat{H}'(t)= \hat{T}'(t)+\text{U}\hat{d}$, where
+We expand the transformed Hamiltonian Eq.
+(\ref{Htransformed}) in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+After tedious, but straightforward calculations, the transformed Hamiltonian up to the second order in the hopping parameter is obtained $\hat{H}'(t)= \hat{T}'(t)+\text{U}\hat{d}$, where
 \begin{align}
@@
 Now, we are in the situation that we can calculate the effective static Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
-Doing some algebra, the effective static Hamiltonian in terms of creation and annihilation operators is obtained,
+After some algebra, the effective static Hamiltonian in terms of creation and annihilation operators is obtained,
 \begin{align}
-\hat{H}_{\text{eff}} &= - \sum_{i,j, \tau, \tau'} \left(t_{ij}^{\tau} t_{ji}^{\tau'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \right)  \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \hat{c}_{j \tau'}^\dagger \hat{c}_{i \tau'}+\text{U}\hat{d}.
+\hat{H}_{\text{eff}} &= - \sum_{i,j, \tau, \tau'} \left(t_{ij}^{\tau} t_{ji}^{\tau'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \right)  \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \hat{c}_{j \tau'}^\dagger \hat{c}_{i \tau'}.
 \label{GeneralHeff}
@@
 
-Finally, the spin Hamiltonian, at half-filling and strong interaction limit of the effective Hamiltonian $\hat{H}_{\text{eff}}$, using the relations Eqs.
-(\ref{SpinOperatorInv1}) and (\ref{SpinOperatorInv2}), is given by,
+Finally, the spin Hamiltonian at half-filling is obtained using the relations Eqs. (\ref{SpinOperatorInv1}) and (\ref{SpinOperatorInv2}):
 \begin{align}
@@
 \end{subequations}
-All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ is different for NN and NNN parameters.
+All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ differs for NN and NNN parameters.
 Thus, the ratios between these renormalized parameters are different than non-perturbed parameters which is a peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
@@
 \vspace{-1.3cm}
-\includegraphics[width=\columnwidth]{NNvsNNN1.pdf}
+\includegraphics[width=\columnwidth]{NNvsNNN1_big_margin.pdf}
 \vspace{-1cm}
@@
 Figure \ref{fig2}, shows the dependence of dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant, for two different laser pulse frequencies.
-The results are obtained for dimensionless material parameters $t_1=1$ and $\text{U} = 10$.
-Figure \ref{fig2}, shows that it is possible not only change the sign and amplitude of the exchange interaction as already reported in Ref.
-\cite{Mentink2015} but its is possible to change the signa nd amplitude of intrinsic DMI.
+We set $\hbar = 1$ and $t_1=1$ and measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
+The results are obtained for material parameters $t_2=0.1$ and $\text{U} = 10$.
+Figure \ref{fig2}, shows that it is possible not only to change the sign and amplitude of the exchange interaction as already reported in Ref.
+\cite{Mentink2015} but it is possible to change the sign and amplitude of the intrinsic DMI.
 More importantly, the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$ can be tuned by laser excitations which is responsible for ultarafast photoinduced spin dynamics and magnon scattering phenomena.
@@
 Eqs.
-(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ stand for spatial component of vectors, $i$ and $j$ refer to the lattice cite, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
+(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ represent the spatial component of vectors, $i$ and $j$ refer to the lattice cite, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
 (\ref{Renor-para}).
-Thus, the dielectric permittivity tensor which determine optical properties of the medium, is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$.
+Thus, the dielectric permittivity tensor which determines the optical properties of the medium, is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$.
 This opto-magnetic effect described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the scattered light $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
 
-In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think about heating and concerning on the validity of our approach.
+In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think about heating and the validity of our approach.
 Recent theoretical \cite{Rudner2019,PhysRevB.97.014311} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.
@@
 
-Possibility of ultrafast optical modification of exchange interactions in the bulk of iron oxides has been recently reported \cite{Mikhaylovskiy2015}.
-We hope that our work stimulate new experiments on measuring both exchange interaction and DMI in novel 2D magnetic systems.
+The possibility of ultrafast optical modification of the exchange interactions in the bulk of iron oxides has been recently reported \cite{Mikhaylovskiy2015}.
+We hope that our work will stimulate new experiments on measuring both exchange interaction and DMI in novel 2D magnetic systems.
 

### 2019-03-10 Paper/paper.tex
Few more changes

@@
 \usepackage{amssymb}%
+\usepackage{natbib}
 \usepackage[toc,page]{appendix}
@@
 %\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
-\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and TechFnology, NO-7491 Trondheim, Norway}
+\affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
 %\affiliation{Institute for Advanced Studies in Basic Science (IASBS), Zanjan, Iran}
@@
 Light provides ultrafast control of exchange and Dzyaloshinskii-Moriya interactions, we consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and in the strongly correlated limit, i.e., the Mott insulator regime of a canted antiferromagnet.
-Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
+Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of circularly polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
 Furthermore, the renormalizations of the spin interactions are helicity independent.
@@
 (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of the original Hubbard model to the $\mathrm{U}(1)$ spin group.
-In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, the presence of, respectively, NNN and NN Rashba SOIs, furthur reduces the symmetry to $Z_2$.
+In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, the presence of, respectively, NNN and NN Rashba SOIs, further reduces the symmetry to $Z_2$.
 
@@
 \includegraphics[width=0.6\columnwidth]{kmh.png}
-\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counter-clockwise hoping.}
+\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counterclockwise hoping.}
 \label{fig1}
@@
 Using the variational principle, it has been shown that the NN Coulomb interaction can be approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013,Stepanov2017}.
-Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and express the interaction part of the Hamiltonian (\ref{Hint}) as
+Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and express the interaction part of the Hamiltonian in Eq.
+(\ref{Hint}) as
 \begin{equation}
@@
 where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$.
-We denote the projection operator to the subspace of states with eigenvale $d$ (i.e.
+We denote the projection operator to the subspace of states with eigenvalue $d$ (i.e.
 states with exactly $d$ double occupancies) by $\hat{P}_d$.
-We are interested in the limit of strongly correlated regime $U\gg t_{1(2)}$.
+We are interested in the strongly correlated regime $U\gg t_{1(2)}$.
 In such a strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) has a much larger energy than those with no double occupancies ($d=0$).
@@
 &\bs{\Gamma}_{ij} =\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
-&\bs{D}_{ij} = - \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
+&\bs{D}_{ij} = \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
 \end{align}
@@
 It can also be shown that the Rashba SOI results in an in-plane DMI vector that is perpendicular to the lattice bonds.
-For the sake of completeness, we explain shortly the effect of disorder by adding an on-site disorder potential $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian \ref{MKMH}, where $\varepsilon_i$ is an uncorrelated random variable.
+For the sake of completeness, we explain shortly the effect of disorder by adding an on-site disorder potential $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian Eq.
+(\ref{MKMH}), where $\varepsilon_i$ is an uncorrelated random variable.
 Following the above procedure, it can be shown that the spin interaction parameters are renormalized as $U^{-1} \rightarrow U/\left(U^2-(\epsilon_j-\epsilon_i)^2\right)$ \cite{Protopopov2018}.
@@
 t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being NN and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being NNN.
-According to the Peierls substitution method, the hopping part of the Hamiltonian gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}/\hbar}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, $\hbar$ is the reduced Planck constant, and $\bs{A}$ is the vector potential of the laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
-The Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A}/\hbar \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|/\hbar$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
+According to the Peierls substitution method, the hopping part of the Hamiltonian gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, and $\bs{A}$ is the vector potential of the laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
+The Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A} \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
 Now, we use the Jacobi–-Anger expansion to rewrite the Peierls phase in the basis of its harmonics,
@@
 \label{JacobiAnger}
-e^{i\frac{e}{\hbar}\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t},
+e^{ie\bs{R}_{ij}\cdot\bs{A}(t)} = \sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t},
 \end{equation}
@@
 &\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega},\\
-&\tilde{\bs{D}}_{ij} = - 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
+&\tilde{\bs{D}}_{ij} = 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
 \end{align}
 \end{subequations}
-All spin interaction parameters are renormalized by the same function but $\alpha_{ij}$ differs for NN and NNN parameters.
-Thus, the ratios between these renormalized parameters are different than non-perturbed parameters which is a peculiar of honeycomb lattices described by the Kane-Mele-Hubbard model.
+All spin interaction parameters are renormalized by the same function, but $\alpha_{ij}$ differs for NN and NNN parameters.
+Thus, the ratios between the NN and NNN renormalized parameters are different than those of non-perturbed parameters.
 The renormalized spin interactions presented in Eq.
@@
 
-Figure \ref{fig2}, shows the dependence of dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant, for two different laser pulse frequencies.
+Figure \ref{fig2}, shows the dependence of dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
+We show this dependence for two different laser pulse frequencies.
 We set $\hbar = 1$ and $t_1=1$ and measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
@@
 \cite{Mentink2015} but it is possible to change the sign and amplitude of the intrinsic DMI.
-More importantly, the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$ can be tuned by laser excitations which is responsible for ultarafast photoinduced spin dynamics and magnon scattering phenomena.
+More importantly, the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$ can be tuned by laser excitations which is responsible for ultrafast photoinduced spin dynamics and magnon scattering phenomena.
 
 Eqs.
-(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ represent the spatial component of vectors, $i$ and $j$ refer to the lattice cite, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
+(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ represent the spatial component of vectors, $i$ and $j$ refer to the lattice site, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
 (\ref{Renor-para}).
@@
 
-In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think about heating and the validity of our approach.
+In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think on how heating might affect the validity of our approach.
 Recent theoretical \cite{Rudner2019,PhysRevB.97.014311} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.

### 2019-03-10 Paper/paper.tex
v6

@@
 \begin{abstract}
-Light provides ultrafast control of exchange and Dzyaloshinskii-Moriya interactions, we consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and in the strongly correlated limit, i.e., the Mott insulator regime of a canted antiferromagnet.
-Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of circularly polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
+Light provides ultrafast, direct and non-thermal control of exchange and Dzyaloshinskii-Moriya interactions.
+We consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and in the strongly correlated limit, i.e., the Mott insulator regime of a canted antiferromagnet.
+Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
 Furthermore, the renormalizations of the spin interactions are helicity independent.
@@
 \textit{Introduction}.--- The discovery of all-optical control of the order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by ultrashort, intense and high-frequency laser pulses has transformed spintronics to a new era of ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
+Recent experiments have shown that laser pulses can directly modify the amplitude and sign of the exchange interaction, the strongest spin interaction in magnetically ordered systems \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
 Although the underlying microscopic mechanism remains unclear, there have been many attempts to uncover its origins.
-Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of the exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
-This finding has been supported by recent experiments \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
-Another important spin interaction is the Dzyaloshinskii-Moriya interaction (DMI), an antisymmetric exchange interaction in inversion symmetry broken systems, where the chiral symmetry of the system is broken \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
-While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials and causes weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
+Recently, it has been theoretically proposed that the non-thermal optical modification of exchange interaction is possible through direct coupling between electric field of light and spins \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}.
+In magnetic systems with broken inversion symmetry there is an antisymmetric exchange interaction between spins that breaks the chiral symmetry called the Dzyaloshinskii-Moriya interaction (DMI) \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
+Although this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials and causes weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
 The ratio between these two interactions controls the tilting angle of the canted spins.
@@
 where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$.
-We denote the projection operator to the subspace of states with eigenvalue $d$ (i.e.
-states with exactly $d$ double occupancies) by $\hat{P}_d$.
-We are interested in the strongly correlated regime $U\gg t_{1(2)}$.
+We denote the projection operator to the subspace of states with eigenvalue $d$, i.e., states with exactly $d$ double occupancies, by $\hat{P}_d$.
+We are interested in the strongly correlated regime $U\gg t_{1(2)}$ at half-filling.
 In such a strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) has a much larger energy than those with no double occupancies ($d=0$).

### 2019-03-11 Paper/paper.tex
v7

@@
 \textit{Model Hamiltonian}.---
-Electrons in a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by the Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
-The Hamiltonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and the Coulomb interaction between the electrons modelled by the extended Hubbard interaction $\hat{\mathcal{H}}_{\text{int}}$,
+Electron dynamics in a 2D planar honeycomb lattice, plotted in Fig.
+\ref{fig1}, can be described by the Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
+The Hamiltonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and the repulsive Coulomb interaction between the electrons modelled by the extended Hubbard interaction $\hat{\mathcal{H}}_{\text{int}}$,
 \begin{equation}
@@
 \end{align}
-Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI parameter, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
+Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI parameter, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), see Fig.
+\ref{fig1}, $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
 The presence of the intrinsic NNN SOI, Eq.
@@
 where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$.
-We denote the projection operator to the subspace of states with eigenvalue $d$, i.e., states with exactly $d$ double occupancies, by $\hat{P}_d$.
+We denote the projection operator to the subspace of states with eigenvalue $d$, i.e., states with exactly $d$ double occupancies, by $\hat{P}_d$ \cite{Fazekas}.
 We are interested in the strongly correlated regime $U\gg t_{1(2)}$ at half-filling.

### 2019-03-12 Chapters/Chapter1.tex
Add more references and short summary in the intro

@@
-\chapter{AFM spinotronics}
-
-\section{History and background}
+\chapter{Introduction}
+\label{ChapIntro}
 
@@
 For ferromagnetic materials it has already been shown that short laser pulses can induce an effective magnetic field that can reach an amplitude of a few Tesla (\cite{Qaiumzadeh2016}, \cite{Qaiumzadeh2013}).
+
+A simple model of antiferromagnetic insulators is provided by the half-filling Hubbard model in the strongly correlated regime.
+In Chapter \ref{ChapBasicModels} we do a quick review of the tight binding model and introduce the Hubbard model.
+A half filled system described by the Hubbard model leads to a spin Hamiltonian characterized by an exchange interaction between spins.
+This exchange interaction will favor antiferromagnetic order.
+Now, in many magnetic systems, spin orbit interaction plays an important role in the spin dynamics.
+This interaction is not included in the original Hubbard model.
+In Chapter \ref{ChapEffectiveSpin} we show that adding a SOI hopping term to the Hubbard model leads to a spin Hamiltonian including the same exchange interaction as before, plus an antisymmetric exchange interaction known as Dzyaloshinskii–Moriya interaction.
+This interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials and causes weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, Moriya1960}, topological objects like chiral skyrmions \cite{muhlbauer2009,Fert2017,Alireza-DMI1,Alireza-DMI2} and chiral domain walls \cite{Thiaville2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016,Elyasi2018,Chen2018,Owerre1,Owerre2}.
+Once we have shown the relation between the electronic Hamiltonian, i.e.
+the Hubbard model with a SOI hopping term, and the effective spin Hamiltonian we are in the position to introduce the effect of light in the system.
+It has been shown that short, high-frequency laser pulse can tune the exchange interaction\cite{Mentink2014,Itin2015,Mentink2015,Meyer2017,Stepanov2017,Kitamura2017,MentinkReview,Barbeau2018}.
+In Chapter \ref{ChapPerturbing} we use the Floquet formalism to show how light can tune, not only the exchange interaction, but also the DMI.
+We apply this technique to some more specific, well-known models, such as the Kane-Mele-Hubbard model.

### 2019-03-16 Chapters/Chapter1.tex
minor thesis changes

@@
 Our goal in this project is to investigate the techniques to manipulate the magnetic state in an antiferromagnetic insulator, which could potantially lead to applications for ultra-fast writing devices.
-For ferromagnetic materials it has already been shown that short laser pulses can induce an effective magnetic field that can reach an amplitude of a few Tesla (\cite{Qaiumzadeh2016}, \cite{Qaiumzadeh2013}).
+For ferromagnetic materials it has already been shown that short laser pulses can induce an effective magnetic field that can reach an amplitude of a few Tesla \cite{Qaiumzadeh2016}, \cite{Qaiumzadeh2013}.
 

### 2019-03-16 Chapters/Chapter2.tex
Add more references and short summary in the intro
minor thesis changes

--- 2019-02-07 Chapters/Chapter2.tex
@@
 \chapter{Basic models for solid state}
+\label{ChapBasicModels}
 
@@
 We can obtain back \ref{TBBand} by changing basis to momentum space $\hat{c}_{k\sigma} = \frac{1}{\sqrt{N}}\sum_j e^{-i\bs{k}\cdot\bs{r}_j}\hat{c}_{j\sigma}$.
+In Appendix \ref{APD} we use this formalism to compute the band structure of a two dimensional system in a honeycomb lattice (i.e.
+graphene).
 
@@
 \end{equation}
-This new term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
+
+This is known as the Hubbard model, which was first proposed by Hubbard \cite{Hubbard1963} to describe electron correlations in $d$ or $f$ bands in transition metals.
+The result was a simplified model to predict metal-insulator transitions.
+However, it exhibits much richer phenomena.
+It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
+they should be conductors according to band theory, but electron-electron interactions keep away from).
+Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
+Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
+
+ Figure \ref{fig:Hubbard} shows a graphical representation of the parameters in \ref{HH}.
+The new term $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
 The half-filled case is most commonly studied, this is the situation where the system has one electron per site (or it has half the maximum allowed number).
@@
 Since each electron can be in two spin states there is a $2^N$ degeneracy.
+The subspace spanned by these states is referred to as low energy subspace, and in this case is has energy $E_0 = 0$.
+If we switch $0 \neq t \ll \text{U}$ this hopping term will allow an even further decrease in energy by allowing virtual processes $i \rightarrow j \rightarrow i$ that localized the electrons withing their neighbor sites.
+For $t \ll \text{U}$ the dynamics of the system can be described withing the low energy subspace only, by doing so we can obtain an effective spin Hamiltonian $\hat{H}_{\text{eff}} = \sum{\langle i,j \rangle} J \bs{S}_i\cdot\bs{S}_j$ where $J>0$ describing an antiferromagnetic system.
+A rigorous derivation of this will be offered in the next Chapter, however we can intuitively understand this result in the following way: the virtual processes $i \rightarrow j \rightarrow i$ will be allowed when the electrons at sites $i$ and $j$ have opposite spin (otherwise it would contradict the Pauli principle), therefore states where neighbor sites have opposite spins will have a lower energy due to the delocalization mechanism.
+Additionally, the constant $J$ will be proportional to the amplitude of the process $i \rightarrow j \rightarrow i$.
+We can already see that this amplitude is $2\frac{t^2}{\text{U}}$, $t^2$ due to two hopping processes, $\frac{1}{\text{U}}$ due to the energy of the intermediate state and the factor $2$ due to the two spin possibilities.
+
+In the next Chapter and in the rest of this thesis we will consider the effects of spin orbit interaction (SOI) in strongly correlated systems.
+For this reason we will have an additionally spin dependent hopping term in \ref{HH} arising from the SOI.
+This additional term will lead to a DMI when deriving the effective spin Hamiltonian in the $t \ll \text{U}$ limit.

### 2019-03-16 Chapters/Chapter3.tex
Add more references and short summary in the intro
minor thesis changes

@@
 \chapter{Effective Spin Hamiltonian}
+\label{ChapEffectiveSpin}
 
@@
 
-\begin{subsection}{Hubbard model}
-
-In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
-This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}.
-Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
-Originally the Hubbard model was proposed to describe electron correlations in $d$ or $f$ bands in transition metals.
-The result was a simplified model to predict metal-insulator transitions.
-However, it exhibits much richer phenomena.
-It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
-they should be conductors according to band theory, but electron-electron interactions keep away from).
-Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
-
-\end{subsection}
+This Hamiltonian is identical to the Hubbard Hamiltonian \ref{HH} adding a spin dependent hopping, which arises from the SOI.
 

### 2019-03-28 Chapters/Chapter5.tex
spin wave

\chapter{Spin wave theory of antiferromagnets}
\label{SpinWave}

We will start with the Heisenberg antiferromagnet:

\begin{equation}
\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j
\end{equation}

In order to obtain the magnon Hamiltonian for this model we introduce the antiferromagnet Holstein-Primakoff transformation:

\begin{align}
S^+_{Ai} &= \sqrt{2S-\hat{a}^\dagger_i \hat{a}_i} \hat{a}_i \\
S^-_{Ai} &= \hat{a}^\dagger_i\sqrt{2S-\hat{a}^\dagger_i \hat{a}_i}  \\
S^z_{Ai} &= S - \hat{a}^\dagger_i \hat{a}_i \\
S^+_{Bj} &=\hat{b}^\dagger_j\sqrt{2S-\hat{b}^\dagger_j \hat{b}_j} \\
S^-_{Bj} &= \sqrt{2S-\hat{b}^\dagger_j \hat{b}_j} \hat{b}_j \\
S^z_{Bj} &= -S + \hat{b}^\dagger_j \hat{b}_j
\end{align}

Where $A$ and $B$ denote two Ne\'{e}l sublattices and $\hat{a}_i$, $\hat{b}_i$ are bosonic annihilation operators. In the large-S limit we approximate $ \sqrt{2S-\hat{a}^\dagger_i \hat{a}_i} \approx \sqrt{2S}$. Then, the exchange term becomes:

\begin{align*}
\bs{S}_i\bs{S}_j = S_i^zS_j^z + \frac{1}{2}\left(S_i^+S_j^- + S_i^-S_j^+ \right) = S \left( \hat{a}^\dagger_i \hat{a}_i + \hat{b}^\dagger_j \hat{b}_j + \hat{a}_i\hat{b}_j + \hat{a}^\dagger_i\hat{b}^\dagger_j \right) - \hat{a}^\dagger_i \hat{a}_i\hat{b}^\dagger_j \hat{b}_j - S^2
\end{align*}

Now the $S^2$ term is a constant that lowers the energy of the antiferromagnet, therefore is shall not be taken into account to compute the magnon dispersion. The term $\hat{a}^\dagger_i \hat{a}_i\hat{b}^\dagger_j \hat{b}_j$ is zeroth order in $S$ and therefore neglected. We can rewrite the sum over NN as:

\begin{equation}
\sum_{\langle i j \rangle} = 2\sum_{i \in A \delta}
\end{equation}

Where $\delta$ are the NN vectors. Using this, and the Fourier relations:

\begin{align}
\hat{a}_i^\dagger &= \frac{1}{\sqrt{N}} \sum_{\bs{k}} e^{i \bs{k} \cdot \bs{r}_i} \hat{a}_{\bs{k}}^\dagger \\
\hat{b}_j^\dagger &= \frac{1}{\sqrt{N}} \sum_{\bs{k}} e^{i \bs{k} \cdot \bs{r}_j} \hat{b}_{\bs{k}}^\dagger
\end{align}

Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i{\bs{k}-\bs{k}'}\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ we find:

\begin{equation}
\hat{H} = 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
\end{equation}

At this point it is common to define $\gamma_{\bs{k}} = \sum_\delta e^{i \bs{k} \cdot \bs{\delta}}$, then denoting $z = \sum_\delta$ we get:

\begin{equation}
\hat{H} = 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
\end{equation}

Which can be written in matrix form as:

\begin{equation}
\hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
z & 0 & 0 & \gamma_{\bs{k}} \\
0 & z & 0 & 0 \\
0 & 0 & 0 & 0 \\
\gamma_{-\bs{k}} & 0 & 0 & 0 
\end{pmatrix}
\end{equation}

Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{\bs{k}},\hat{a}_{-\bs{k}}^\dagger,\hat{b}_{-\bs{k}}^\dagger \right)^T$. That is, $\hat{H} = \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$

### 2019-04-01 Chapters/Chapter5.tex
more spin waves

@@
 \label{SpinWave}
+
+\section{Heisenberg antiferromagnet}
 
@@
 \begin{equation}
-\hat{H} = 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
+\label{MagnonicH}
+\hat{H} = 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
 \end{equation}
@@
 \hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
-z & 0 & 0 & \gamma_{\bs{k}} \\
-0 & z & 0 & 0 \\
-0 & 0 & 0 & 0 \\
-\gamma_{-\bs{k}} & 0 & 0 & 0 
+z & \gamma_{\bs{k}} \\
+\gamma_{-\bs{k}} & z
 \end{pmatrix}
@@
 
-Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{\bs{k}},\hat{a}_{-\bs{k}}^\dagger,\hat{b}_{-\bs{k}}^\dagger \right)^T$.
-That is, $\hat{H} = \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$
+Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{-\bs{k}}^\dagger \right)^T$.
+That is, $\hat{H} = \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$.
+In order to diagonalize this Hamiltonian we introduce the Bogoliubov transformation:
+
+\begin{equation}
+\begin{pmatrix}
+\hat{\alpha}_{\bs{k}} \\
+\hat{\beta}_{\bs{k}}^\dagger
+\end{pmatrix} = 
+\begin{pmatrix}
+u_{\bs{k}} & -v_{\bs{k}} \\
+-v_{\bs{k}} & u_{\bs{k}}
+\end{pmatrix}
+\begin{pmatrix}
+\hat{a}_{\bs{k}} \\
+\hat{b}_{-\bs{k}}^\dagger
+\end{pmatrix}
+\end{equation}
+
+Where $u_{\bs{k}}$ and $v_{\bs{k}}$ are real functions satisfying $u_{\bs{k}}^2-v_{\bs{k}}^2 = 1$ in order to perserve the bosonic commutation relations. The inverse transformation is given by:
+
+\begin{equation}
+\begin{pmatrix}
+\hat{a}_{\bs{k}} \\
+\hat{b}_{-\bs{k}}^\dagger
+\end{pmatrix} = 
+\begin{pmatrix}
+u_{\bs{k}} & v_{\bs{k}} \\
+v_{\bs{k}} & u_{\bs{k}}
+\end{pmatrix}
+\begin{pmatrix}
+\hat{\alpha}_{\bs{k}} \\
+\hat{\beta}_{\bs{k}}^\dagger
+\end{pmatrix}
+\end{equation}
+
+Inserting this in \ref{MagnonicH} and ignoring constant terms we get:
+
+\begin{align*}
+\hat{H} &= 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(u_{\bs{k}}^2+v_{\bs{k}}^2) +u_{\bs{k}}v_{\bs{k}}( \gamma_{\bs{k}}+ \gamma_{-\bs{k}}) \right) + \right.
+\\
+&+ \left.
+\hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}^\dagger_{\bs{k}} \left( 2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}v_{\bs{k}}^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\alpha}_{\bs{k}}\hat{\beta}_{\bs{k}} \left( 2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}u_{\bs{k}}^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) \right\}
+\end{align*}
+
+($\gamma_{\bs{k}} = \gamma_{-\bs{k}}$)Therefore, in order to erase the non diagonal terms we impose $2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^2+v_{\bs{k}}^2) = 0$, which together with $u_{\bs{k}}^2-v_{\bs{k}}^2 = 1$ determines $u_{\bs{k}}$ and $v_{\bs{k}}$:
+
+\begin{align*}
+u_{\bs{k}}^2 &= \frac{1}{2}\left( \frac{1}{\sqrt{1-(\gamma_{\bs{k}}/z)^2}}+1\right) \\
+v_{\bs{k}}^2 &= \frac{1}{2}\left( \frac{1}{\sqrt{1-(\gamma_{\bs{k}}/z)^2}}-1\right)
+\end{align*}
+
+And so, the we get the dispersion relation:
+
+\begin{align}
+\hat{H} &= \sum_{\bs{k}} \omega_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \\
+\omega_{\bs{k}} &= 2JSz\sqrt{1-(\gamma_{\bs{k}}/z)^2}
+\end{align}
+
+\section{Adding DMI}
+
+Let's now consider
+
+\begin{equation}
+\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j + D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j
+\end{equation}
+
+The NNN DMI term will couple spins within the same sublattice. Using the HP transformation:
+
+\begin{equation}
+\hat{e}_z \bs{S}_i \times \bs{S}_j = \frac{i}{2}(S_i^+S_j^--S_i^-S_j^+) = \begin{cases}
+             iS(\hat{a}_j^\dagger\hat{a}_i-\hat{a}_i^\dagger\hat{a}_j),  & \text{for } (i,j) \in A \\
+             iS(\hat{b}_i^\dagger\hat{b}_j-\hat{b}_j^\dagger\hat{b}_i),  & \text{for } (i,j) \in B
+       \end{cases} \quad
+\end{equation}
+
+Now we will make the sum over NNN in the following way:
+
+\begin{equation}
+\sum_{\langle \langle i j \rangle \rangle} = \sum_{i\in A \bs{\delta}^{NNN}} +  \sum_{i\in B \bs{\delta}^{NNN}}
+\end{equation}
+
+Where $\bs{\delta}^{NNN}$ are the NNN vectors. Following the same procedure as before we get and additional magnonic term:
+
+\begin{equation}
+D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} - \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
+\end{equation}
+
+Where $\Delta_{\bs{k}} = \frac{D}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$. The full magnonic Hamiltonian now is:
+
+\begin{equation}
+\label{MagnonicH2}
+\hat{H} = 2JS \sum_{\bs{k}} \left\{ \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}(z+\Delta_{\bs{k}}) + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}(z-\Delta_{-\bs{k}}) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
+\end{equation}
+
+Or:
+
+\begin{equation}
+\hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
+z + \Delta_{\bs{k}}& \gamma_{\bs{k}} \\
+\gamma_{-\bs{k}} & z - \Delta_{-\bs{k}}
+\end{pmatrix}
+\end{equation}
+
+\section{NNN exchange}
+
+Let's now introduce a term:
+
+\begin{equation}
+\sum_{\langle \langle i,j \rangle \rangle} \left\{ \Gamma_{xy}(S_i^xS_j^x + S_i^yS_j^y) + \Gamma_zS_i^zS_j^z\right\}
+\end{equation}
+In terms of bosonic operators we have:
+\begin{equation}
+\Gamma_{xy}(S_i^xS_j^x + S_i^yS_j^y) + \Gamma_zS_i^zS_j^z = \begin{cases}
+             S\Gamma_{xy}(\hat{a}_i^\dagger\hat{a}_j+\hat{a}_j^\dagger\hat{a}_i) - S\Gamma_z(\hat{a}_i^\dagger\hat{a}_i+\hat{a}_j^\dagger\hat{a}_j),  & \text{for } (i,j) \in A \\
+             S\Gamma_{xy}(\hat{b}_i^\dagger\hat{b}_j+\hat{b}_j^\dagger\hat{b}_i) - S\Gamma_z(\hat{b}_i^\dagger\hat{b}_i+\hat{b}_j^\dagger\hat{b}_j),  & \text{for } (i,j) \in B
+       \end{cases} \quad
+\end{equation}
+Fourier transform leads to:
+
+\begin{align*}
+&\sum_{\langle \langle i,j \rangle \rangle} \left\{ \Gamma_{xy}(S_i^xS_j^x + S_i^yS_j^y) + \Gamma_zS_i^zS_j^z\right\}
+= S\sum_{\bs{k}} (\Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z) (\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}+\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}) = \\
+&=2JS\sum_{\bs{k}} \tilde{\Gamma}_{\bs{k}}(\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}+\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}})
+\end{align*}
+
+Where $\Delta'_{\bs{k}} = \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right)$ and $\tilde{\Gamma}_{\bs{k}} = \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)$.
+Therefore, now:
+
+\begin{equation}
+\hat{H}_{\bs{k}} = 2JS\begin{pmatrix} 
+z + \Delta_{\bs{k}} + \tilde{\Gamma}_{\bs{k}} & \gamma_{\bs{k}} \\
+\gamma_{-\bs{k}} & z - \Delta_{-\bs{k}} + \tilde{\Gamma}_{\bs{k}}
+\end{pmatrix}
+\end{equation}

### 2019-04-04 Chapters/Chapter5.tex
Add dispersion relations

@@
 \begin{equation}
+\label{Bogoliubov}
 \begin{pmatrix}
 \hat{\alpha}_{\bs{k}} \\
-\hat{\beta}_{\bs{k}}^\dagger
+\hat{\beta}_{\bs{k}}
 \end{pmatrix} = 
 \begin{pmatrix}
-u_{\bs{k}} & -v_{\bs{k}} \\
--v_{\bs{k}} & u_{\bs{k}}
+u_{\bs{k}} & v_{\bs{k}}^* \\
+v_{\bs{k}} & u_{\bs{k}}^*
 \end{pmatrix}
@@
 
-Where $u_{\bs{k}}$ and $v_{\bs{k}}$ are real functions satisfying $u_{\bs{k}}^2-v_{\bs{k}}^2 = 1$ in order to perserve the bosonic commutation relations. The inverse transformation is given by:
+Where $u_{\bs{k}}$ and $v_{\bs{k}}$ are complex functions satisfying $\abs{u_{\bs{k}}}^2-\abs{v_{\bs{k}}}^2 = 1$ in order to perserve the bosonic commutation relations.
+The inverse transformation is given by:
 
 \begin{equation}
+\label{BogoliubovInv}
 \begin{pmatrix}
@@
 \begin{pmatrix}
-u_{\bs{k}} & v_{\bs{k}} \\
-v_{\bs{k}} & u_{\bs{k}}
+u_{\bs{k}}^* & -v_{\bs{k}}^* \\
+-v_{\bs{k}} & u_{\bs{k}}
 \end{pmatrix}
@@
 
+\begin{align}
+\hat{H} &= 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(\abs{u_{\bs{k}}}^2+\abs{v_{\bs{k}}}^2) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right.
+\nonumber \\
+&+ \left.
+\hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}_{\bs{k}} \left( -2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\beta}_{\bs{k}}^\dagger\hat{\alpha}_{\bs{k}} \left( -2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) \right\} \label{BeforeBogo}
+\end{align}
+
+Therefore, in order to erase the non diagonal terms we impose:
+\begin{equation}
+\label{condition}
+-2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 = 0
+\end{equation}
+Notice that for the $\hat{\beta}_{\bs{k}}^\dagger\hat{\alpha}_{\bs{k}}$ term $-2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2=0$ is the same equation.
+This, together with $\abs{u_{\bs{k}}}^2-\abs{v_{\bs{k}}}^2 = 1$ determines $u_{\bs{k}}$ and $v_{\bs{k}}$.
+To see this, first notice that an overall phase in both $u_{\bs{k}}$ and $v_{\bs{k}}$ leads to the same physical state.
+We can use this fact to impose that $v_{\bs{k}}$ is real, and we can use $\abs{u_{\bs{k}}}^2-\abs{v_{\bs{k}}}^2 = 1$ to parametrize $u_{\bs{k}}$ and $v_{\bs{k}}$ in the following way:
+
 \begin{align*}
-\hat{H} &= 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(u_{\bs{k}}^2+v_{\bs{k}}^2) +u_{\bs{k}}v_{\bs{k}}( \gamma_{\bs{k}}+ \gamma_{-\bs{k}}) \right) + \right.
-\\
-&+ \left.
-\hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}^\dagger_{\bs{k}} \left( 2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}v_{\bs{k}}^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\alpha}_{\bs{k}}\hat{\beta}_{\bs{k}} \left( 2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}u_{\bs{k}}^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) \right\}
+u_{\bs{k}} &= \cosh(\frac{\theta_{\bs{k}}}{2})e^{i \xi_{\bs{k}}} \\
+v_{\bs{k}} &= \sinh(\frac{\theta_{\bs{k}}}{2})
 \end{align*}
 
-($\gamma_{\bs{k}} = \gamma_{-\bs{k}}$)Therefore, in order to erase the non diagonal terms we impose $2zu_{\bs{k}}v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^2+v_{\bs{k}}^2) = 0$, which together with $u_{\bs{k}}^2-v_{\bs{k}}^2 = 1$ determines $u_{\bs{k}}$ and $v_{\bs{k}}$:
+Where $\theta_{\bs{k}}$ and $\xi_{\bs{k}}$ are real functions to be determined. Introducing these relations in \ref{condition}:
 
-\begin{align*}
-u_{\bs{k}}^2 &= \frac{1}{2}\left( \frac{1}{\sqrt{1-(\gamma_{\bs{k}}/z)^2}}+1\right) \\
-v_{\bs{k}}^2 &= \frac{1}{2}\left( \frac{1}{\sqrt{1-(\gamma_{\bs{k}}/z)^2}}-1\right)
-\end{align*}
+\begin{equation}
+- z\sinh(\theta_{\bs{k}}) +\gamma_{\bs{k}}e^{-i \xi_{\bs{k}}}\frac{ \cosh(\theta_{\bs{k}})-1}{2} +\gamma_{-\bs{k}}e^{i\xi_{\bs{k}}}\frac{ \cosh(\theta_{\bs{k}})+1}{2} = 0
+\end{equation}
 
-And so, the we get the dispersion relation:
+By taking $\xi_{\bs{k}}$ to be the phase of $\gamma_{\bs{k}}$, i.e. $\gamma_{\bs{k}} = \abs{\gamma_{\bs{k}}} e^{i\xi_{\bs{k}}}$ we get a real equation on $\theta_{\bs{k}}$. Altogether we find:
 
 \begin{align}
-\hat{H} &= \sum_{\bs{k}} \omega_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \\
-\omega_{\bs{k}} &= 2JSz\sqrt{1-(\gamma_{\bs{k}}/z)^2}
+\gamma_{\bs{k}} &= \abs{\gamma_{\bs{k}}} e^{i\xi_{\bs{k}}} \\
+\tanh(\theta_{\bs{k}}) &= \frac{\abs{\gamma_{\bs{k}}}}{z}
+\end{align}
+
+This erases the non diagonal terms in \ref{BeforeBogo} leading to a diagonal term:
+\begin{equation}
+z\cosh(\theta_{\bs{k}})-\abs{\gamma_{\bs{k}}}\sinh(\theta_{\bs{k}}) = \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
+\end{equation}
+
+Then, the dispersion relation is:
+
+\begin{align}
+\hat{H} &= \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \epsilon_{\bs{k}} \\
+\epsilon_{\bs{k}} &= 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
 \end{align}
@@
 
+In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, whereas the energy gets lifted:
+
+\begin{align}
+\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
+\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} + \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} \right)
+\end{align}
+
 \section{NNN exchange}
@@
 \end{equation}
+
+We obtain the dispersion relation by changing $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$ in \ref{DispWithDMI}:
+
+\begin{align}
+\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
+\epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} +  \sqrt{(z + \tilde{\Gamma}_{\bs{k}})^2-\abs{\gamma_{\bs{k}}}^2} \right)
+\end{align}

### 2019-04-04 Chapters/Chap3/ModelsNNN.tex
Minor changes

@@
 \label{MKMH}
-\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
+\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
 	\text{U}\hat{D}
@@
 
-This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, i \nu_{ij} \Delta)$ in \ref{BigHam}.
+This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, -i\nu_{ij} \Delta)$ in \ref{BigHam}.
 The Hamiltonian parameters are sketched in Figure \ref{fig:MKMH}.
@@
 \label{MKMHeff}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
 \end{equation}
@@
 J_{2,ij} &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-\bs{D}_{2,ij} &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+\bs{D}_{2,ij} &= 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
 \bs{\Gamma}_{2,ij} &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
@@
 
-Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
+Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\cdot\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}.
 In the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.

### 2019-04-04 Chapters/Chapter3.tex
Minor changes

@@
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
-The original Hubbard model, was developed to describe the single-band magnetism \cite{Hubbard1963}, it also describes the transition between conducting and insulating systems, predicting the existence of Mott insulators, materials which should be conducting according to band theory, but they are insulating due to electron-electron interactions.
-
 We will consider a half filled system in the strong coupling limit.
@@
 We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace.
-This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\cdot\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
+This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\cdot\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\cdot\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.
+We will start by finding a suitable basis to write the second quantized version of \ref{Ham1}.
 
@@
 
-First we will define a suitable basis for the single particle wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
+First we will define the basis of Bloch wavefunctions. To do so, we will consider the single particle Hamiltonian without the spin orbit interaction term:
 
@@
 The Bloch function is extended over the whole crystal volume $V$.
-We would like to work with a localized basis.
-An alternative orthonormal basis are the Wannier functions $\ket{\psi_{in}}$, defined in terms of the Bloch functions as:
+However, we would like to work with a localized basis.
+Such a localized basis built by a set of functions known as Wannier functions $\ket{\psi_{in}}$, which defined in terms of the Bloch functions as:
 
@@
 We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant.
-Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
+Fock states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
+With these definitions we are ready for write down the second quantized form of \ref{Ham1}, and show some approximations that lead to the Hubbard model.
 
@@
 \begin{align*}
-\Delta_{ij,x} &= -\bra{i} \lambda (\partial_y V(\bs{r}) p_z - \partial_z V(\bs{r}) p_y) \ket{j} = i \hbar \lambda \int d \bs{r} \phi_i(\bs{r})^* (\partial_y V(\bs{r}) \partial_z - \partial_z V(\bs{r}) \partial_y) \phi_j(\bs{r}) = \\
+\Delta_{ij,x} &= -\bra{i} \lambda (\partial_y V(\bs{r}) p_z - \partial_z V(\bs{r}) p_y) \ket{j} = \\
+&= i \hbar \lambda \int d \bs{r} \phi_i(\bs{r})^* (\partial_y V(\bs{r}) \partial_z - \partial_z V(\bs{r}) \partial_y) \phi_j(\bs{r}) = \\
 &= -i\hbar\lambda \int d\bs{r} \left[ \partial_z(\phi_i(\bs{r})^*\partial_y V(\bs{r}) - \partial_y(\phi_i(\bs{r})^*\partial_z V(\bs{r}) \right] \phi_j(\bs{r}) = \\
@@
 
-Therefore $\bs{\Delta}_{ii} = 0$. Notice also that $\bs{\Delta}_{ij}$ is purely imaginary.
-We can impose that $t_{ii} = t(0) = 0$. For a system of strongly correlated electrons we can assume that:
+Therefore it follows that $\bs{\Delta}_{ii} = 0$ and that $\bs{\Delta}_{ij}$ is purely imaginary.
+We can impose that $t_{ii} = t(0) = 0$ since adding a constant term to all the hopping amplitudes would only lead to a lifting in the zero point energy.
+Additionally, for a system of strongly correlated electrons we can assume that:
 
 \begin{itemize}
-\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\boldsymbol{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
+\item A property of the Wannier functions $\Phi_j$ is that they have exponentially decreasing overlaps, therefore $t_{ij}$ and $\bs{\Delta}_{ij}$ will decay rapidly with the distance $|\textbf{r}_i-\textbf{r}_j|$.
 In an isotropic system we can approximate:
@@
 This Hamiltonian is identical to the Hubbard Hamiltonian \ref{HH} adding a spin dependent hopping, which arises from the SOI.
+In the next section we will show that this Hamiltonian leads to an effective spin Hamiltonian in the appropriate limit.
 
@@
 
-At half filling and in the $t << \text{U}$ limit, which correspond to the strong coupling limit, we can apply perturbation theory to obtain the Heisenberg model from the Hubbard Hamiltonian \ref{Hubbard}.
+At half filling and in the $t, \bs{\Delta}_{ij} << \text{U}$ limit, which corresponds to the strong coupling limit, we can apply perturbation theory to obtain an effective spin Hamiltonian from the Hubbard model \ref{Hubbard}.
 First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
@@
 &\bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi} = \nonumber \\
-&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'} \bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} = \nonumber \\
+&= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2} \sum_{\langle i',j' \rangle, 					\sigma_3, \sigma_4} \left\{ \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t + \bs{\Delta}_{i'j'}\cdot \bs{\sigma}_{\sigma_3, \sigma_4} \right) \right.
+\nonumber \\
+& \left. \hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{i' \sigma_3}^\dagger \hat{c}_{j'\sigma_4} \ket{\phi} \right\} = \nonumber \\
 &= -\frac{1}{\text{U}} \bra{\phi'}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \delta_{\sigma_1, \sigma_2} t + \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2} \right) \left( \delta_{\sigma_3, \sigma_4} t - \bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3, \sigma_4} \right)\hat{c}_{i\sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i\sigma_4} \ket{\phi} = \nonumber \\
-&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) ) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} = \nonumber \\
+&-\frac{1}{\text{U}} \bra{\phi'} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left\{ \left[ t^2 						\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4} + t\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}			\bs{\sigma}_{\sigma_1 \sigma_2} \right.
+\right.
+\nonumber \\
+& \left.
+\left.
+- \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \right] \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j 		\sigma_2} \hat{c}_{j \sigma_3}^\dagger \ket{\phi} \right\} = \nonumber \\
 & \bra{\phi'} \hat{H}_J + \hat{H}_D + \hat{H}_P \ket{\phi}
@@
 
-In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish.
-We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$.
-We defined:
+In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish (remember that $\ket{\phi}$ and $\ket{\phi'}$ belong in the subspace of zero double occupied states).
+We also used $\bs{\Delta}_{ij} = - \bs{\Delta}_{ji}$ and we defined:
 
 \begin{align}
-\hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \\
-\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \\
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger
+\hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \label{C3HJ} \\
+\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HD}\\
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HP}
 \end{align}
@@
 \hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
-\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \cdot\bs{S}_i\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
+\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \bs{S}_i\cdot\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
 \end{align}
@@
 
-Also:
+The third important relation is:
 
@@
 &= -4i \bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j \label{SpinRel2} \\
-& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \nonumber \\
+& \sum_{\sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4})\bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\left(-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) = \nonumber \\
 &= \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \label{SpinRel3}
@@
 
-Now introducing the spin operators into  $\hat{H}_J$ with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
+Now introducing the spin operators into  $\hat{H}_J$ in \ref{C3HJ}, with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
 
@@
 
-Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$, using \ref{SpinRel2}:
+Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$ in \ref{C3HD}, using \ref{SpinRel2}:
 
@@
 Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$, notice that being $\bs{\Delta}_{ij}$ purely imaginary, $\bs{D}_{ij}^0$ is a real vector. 
-Lastly, using \ref{SpinRel3}, the term proportional to $\bs{\Delta}_{ij}^2$ leads to:
+Lastly, using \ref{SpinRel3}, the term proportional to \ref{C3HP} leads to:
 
@@
 
-The $J_{ij}^0\bs{S}_i\cdot\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
+The $J_{ij}^0\bs{S}_i\cdot\bs{S}_j$ term is known as exchange interaction.
+Setting $\bs{\Delta}_{ij} = 0$ (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model.
 Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material.
 However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach.
-$\bs{D}_{ij}^0 \cdot\bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
+The term $\bs{D}_{ij}^0 \cdot\bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
 interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}.
@@
 Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
+
+Notice that the exchange interaction $J_{ij}^0\bs{S}_i\cdot\bs{S}_j$ effectively models the kinetic-kinetic second order processes $i \rightarrow j \rightarrow i$, where $i$ and $j$ are nearest neighbors.
+In the same fashion the DMI models kinetic-SOI hopping processes and the anisotropic interaction models SOI hopping-SOI hopping processes.
+In the next chapter we will introduce next nearest neighbor (NNN) hopping (both kinetic and SOI), this will lead to NNN spin interactions.
+As an introduction to this, in the next subsection we show the effect of introducing NNN kinetic hopping in the Heisenberg model.
 

### 2019-04-10 Chapters/Chapter5.tex
SWT readable

@@
 \label{SpinWave}
+
+In this Chapter we will study the magnon dispersion for the effective spin Hamiltonian obtained in the last two Chapters.
+The standard way of doing this is to use the Holstein-Primakoff transformation, which maps S-spin operators on a lattice to bosonic creation/annihilation operators.
+The linear approximation of this transformation leads to a bosonic Hamiltonian which can be diagonalized to obtain the magnon dispersion relation.
+Keeping higher order terms in this transformation is also useful to study scattering effects between magnons.
+
+We will start studying the simplest model of spin interaction, the Heisenberg model. In the following sections we will add terms such as the DMI and the anisotropic NNN term derived in \ref{MKMHeff}.
 
@@
 
-Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i{\bs{k}-\bs{k}'}\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ we find:
+Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ we find:
 
@@
 
-At this point it is common to define $\gamma_{\bs{k}} = \sum_\delta e^{i \bs{k} \cdot \bs{\delta}}$, then denoting $z = \sum_\delta$ we get:
+At this point it is common to define $\gamma_{\bs{k}} = \sum_\delta e^{i \bs{k} \cdot \bs{\delta}}$.
+Using $\bs{\delta}_1=\frac{a_0}{2}(1,\sqrt{3})$, $\bs{\delta}_2=\frac{a_0}{2}(1,-\sqrt{3})$, $\bs{\delta}_3=a_0(-1,0)$ and taking $a_0=1$, we can write this as:
+\begin{equation}
+\gamma_{\bs{k}} = 2e^{\frac{i}{2}k_x}\cos(\frac{\sqrt{3}}{2}k_y)+e^{-ik_x}
+\end{equation}
+Then denoting $z = \sum_\delta$ we get:
 
@@
 
-Where $\bs{\delta}^{NNN}$ are the NNN vectors. Following the same procedure as before we get and additional magnonic term:
+Where $\bs{\delta}^{NNN}$ are the NNN vectors:
+\begin{align*}
+\bs{\delta}^{NNN}_1 &= \delta_1-\delta_3 = \frac{1}{2}(3, \sqrt{3}) \\
+\bs{\delta}^{NNN}_2 &= \delta_2-\delta_1 = (0, -\sqrt{3}) \\
+\bs{\delta}^{NNN}_3 &= \delta_3-\delta_2 = \frac{1}{2}(-3, \sqrt{3}) \\
+\bs{\delta}^{NNN}_4 &= -\bs{\delta}^{NNN}_1 = -\frac{1}{2}(3, \sqrt{3}) \\
+\bs{\delta}^{NNN}_5 &= -\bs{\delta}^{NNN}_2 = (0, \sqrt{3}) \\
+\bs{\delta}^{NNN}_6 &= -\bs{\delta}^{NNN}_3 = \frac{1}{2}(3, -\sqrt{3}) \\
+\end{align*}
+Notice that with these definitions, if $i$ is a site on the $A$ sublattice, $\nu_{i,i+\bs{\delta}^{NNN}_a}=+1$ for $a=1,2,3$ and $\nu_{i,i+\bs{\delta}^{NNN}_a}=-1$ for $a=4,5,6$.
+The opposite relations hold for $i$ in the $B$ sublattice.
+
+ Following the same procedure as before we get and additional magnonic term:
 
@@
 
-Where $\Delta_{\bs{k}} = \frac{D}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$. The full magnonic Hamiltonian now is:
+Where $\Delta_{\bs{k}} = \frac{Di}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$, for $i$ in the $A$ sublattice. This can be rewritten as:
+\begin{equation}
+\Delta_{\bs{k}} = -\frac{2D}{J}\left\{ \sin(\bs{\delta}^{NNN}_1 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_2 \cdot \bs{k}) + \sin(\bs{\delta}^{NNN}_3 \cdot \bs{k})\right\}
+\end{equation}
+The full magnonic Hamiltonian now is:
 
@@
 \end{equation}
+Notice that taking $\Gamma_{xy} = -\abs{J_2}-\abs{\Gamma_2}$ and $\Gamma_z = -\abs{J_2}+\abs{\Gamma_2}$ describes the NNN exchange interaction and the NNN anisotropic interaction in \ref{MKMHeff}.
 In terms of bosonic operators we have:

### 2019-04-11 Code/magnon_disp.R
add plot

@@ -1,0 +1,69 @@
+library(plotly)
+setwd("~/Desktop/MT/Code")
+library(latex2exp)
+library(tikzDevice)
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+                               "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+                               "\\usepackage{amssymb}"))
+gamma <- function(k) {
+  delta1=0.5*c(1,sqrt(3))
+  delta2=0.5*c(1,-sqrt(3))
+  delta3=c(-1,0)
+  result <- exp(complex(real = 0, imaginary = 1)*(k%*%delta1))+
+    exp(complex(real = 0, imaginary = 1)*(k%*%delta2))+
+    exp(complex(real = 0, imaginary = 1)*(k%*%delta3))
+  return(result)
+}
+
+delta <- function(k) {
+  delta1=0.5*c(3,sqrt(3))
+  delta2=c(0,-sqrt(3))
+  delta3=0.5*c(-3,sqrt(3))
+  result <- -2*D/J*
+    (sin(k%*%delta1)+sin(k%*%delta2)+sin(k%*%delta3))
+  return(result)
+}
+
+energy_p <- function(k) {
+  return(2*(delta(k)+sqrt(9-abs(gamma(k)^2))))
+}
+
+energy_m <- function(k) {
+  return(2*(-delta(k)+sqrt(9-abs(gamma(k)^2))))
+}
+
+kmax = 3
+res = 0.01
+J=1
+D=0.1
+S=2.5
+kx_vec<-seq(from=-kmax, to=kmax, by=res)
+samples=length(kx_vec)
+energyp <- matrix(0, length(kx_vec), length(kx_vec))
+energym <- matrix(0, length(kx_vec), length(kx_vec))
+
+for(kx in 1:samples){
+  for(ky in 1:samples){
+    energyp[kx,ky]<-energy_p(c(kx_vec[kx],kx_vec[ky]))[1][1]
+    energym[kx,ky]<-energy_m(c(kx_vec[kx],kx_vec[ky]))[1][1]
+  }
+}
+
+
+
+p <- plot_ly(z = ~energyp, x=kx_vec,y=kx_vec) %>% 
+  layout(
+    title = "",
+    scene = list(
+      xaxis = list(title = ""),
+      yaxis = list(title = ""),
+      zaxis = list(title = "")
[…]

### 2019-04-11 Code/magnon_disp.R
code changes

@@ -48,8 +48,19 @@ for(kx in 1:samples){
     energym[kx,ky]<-energy_m(c(kx_vec[kx],kx_vec[ky]))[1][1]
   }
 }
+ky=0
 
-
+plot_for_ky <- function(ky) {
+  energyp<-sapply(kx_vec, function(x) energy_p(c(x,ky))[1][1])
+  energym<-sapply(kx_vec, function(x) energy_m(c(x,ky))[1][1])
+  p<-plot_ly(x= ~kx_vec, y=~energyp,type='scatter',mode='lines',name=paste0("e+, ky=",ky)) %>%
+    add_trace(x=~kx_vec, y=~energym, name=paste0("e-, ky=",ky),type='scatter',mode='lines')
+  return(p)
+}
+p<-plot_for_ky(0)
+plot_for_ky(-1)
+subplot(plot_for_ky(-1),plot_for_ky(0),plot_for_ky(1), nrows = 3)
+?subplot
 
 p <- plot_ly(z = ~energyp, x=kx_vec,y=kx_vec) %>% 
   layout(
@@ -60,7 +71,9 @@ p <- plot_ly(z = ~energyp, x=kx_vec,y=kx_vec) %>%
       zaxis = list(title = "")
     )) %>% add_surface() %>% add_surface(z = ~energym)
 p
-p <- plot_ly(z = energyp, x=kx_vec,y=kx_vec, type = "heatmap")
+p <- plot_ly(z = energyp, x=kx_vec,y=kx_vec, type = "heatmap") %>% layout(scene=list(      xaxis = list(title = "x"),
+                                                                                           yaxis = list(title = "y"),
+                                                                                           zaxis = list(title = "")))
 m <- plot_ly(z = energym, x=kx_vec,y=kx_vec, type = "heatmap")
 p <- subplot(p, m)
 p

### 2019-04-13 Chapters/Chap3/TDHeff.tex
Few more minor changes

@@
 
-First we will start we a general Hamiltonian of the type:
+In this section we will derive a general effective Hamiltonian starting with any Hamiltonian that can be written as:
 
@@
 Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\hat{T}$ is any hopping operator.
-The only assumption we will make about $\hat{T}$ is that it is proportional to any power of $\hat{p}$ in which case we can apply the Peierls substitution (\ref{AP3A}) to introduce to take into account the effect of the electromagnetic perturbation in the lattice.
+In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
 The strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
 
-In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-In the simplest case, for example, the sum would be restricted to nearest neighbors and the hopping amplitude would be diagonal in the spin state.
+The effect of the electromagnetic perturbation in the lattice can be introduced via the Peierls substitution (\ref{AP3A}).
 With this notation, in presence of a vector potential $\vec{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:
@@
 \begin{align*}
-t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
+t_{ij}^{\sigma \sigma'}(t) &= t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = \\
+&= t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
 \end{align*}
@@
 Where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
+Since the hopping term is of second order in the creation and annihilation operators, it can change the double occupancy of the states only by $\pm1$.
 
-In order to derive the form of the effective Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$. The transformed Hamiltonian is:
+In order to derive the form of the effective spin Hamiltonian let us introduce a time dependent unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$. The transformed Hamiltonian is:
 
@@
 We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
-In order for the new Hamiltonian to be periodic we impose the unitary transformation to have the periodicity of the Hamiltonian, so that we can expand $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
-Additionally we can impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
-With these conditions the unitary transformation can be uniquely determined if we impose that $\hat{S}(t)$ does not contain block-diagonal terms, i.e.
-we can write:
+We require the transformed Hamiltonian to be block diagonal in the doublon number operator $\hat{d}$.
+To fulfill this requirement, the unitary transformation $\hat{S}(t)$ must have the same periodicity as $\hat{T}(t)$; consequently, the transformed Hamiltonian $\hat{H}'(t)$ will have the same periodicity as the original Hamiltonian $\hat{H}(t)$.
+Thus we can write $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+With the further requirement that $\hat{S}(t)$ does not contain block-diagonal terms, we can uniquely determine the unitary transformation:
 
@@
 
-We obtain:
+By choosing $i\hat{S}^{(2)}_{dm}$ such that the transformed Hamiltonian is block-diagonal, we obtain:
 
@@
 
-Now the effective Hamiltonian acts on the subspace of $\hat{P}_0$, therefore we are only interested on $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$).
+Now the effective Hamiltonian acts on the subspace of $d=0$ (zero double occupancies), therefore we are only interested on the block $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$).
 In this subspace we can write:
@@
 &\hat{H}_{\text{eff}}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} \frac{t_{ij,m-n}^{\sigma_1 \sigma_2} t_{ji,n}^{\sigma_3 \sigma_4} + t_{ij,-n}^{\sigma_1 \sigma_2} t_{ji,m+n}^{\sigma_3 \sigma_4}}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
-&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} \frac{ \mathcal{J}_{m-n}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ji}) + \mathcal{J}_{-n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ji})}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
-&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} (-1)^m \frac{ \mathcal{J}_{n-m}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} e^{im\omega t} \nonumber \\
+&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left\{ \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} \right.
+\nonumber \\
+& \left. \frac{ \mathcal{J}_{m-n}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ji}) + \mathcal{J}_{-n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ji})}{\text{U}+n\omega} e^{im\omega t} \right\} \nonumber \\
+&= - \frac{1}{2}\sum_{mn} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left\{ \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} e^{i(\frac{\pi}{2}-\theta_{ij})m} (-1)^m \right.
+\nonumber \\
+&\left. \frac{ \mathcal{J}_{n-m}(\alpha_{ij}) \mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij}) \mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} e^{im\omega t} \right\} \nonumber \\
 &= - \frac{1}{2} \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffSimplified}
@@
 
-In the following sections we will apply what we have derived here for different models of the hopping operator.
+In the following sections we will use this effective Hamiltonian for different models of the hopping operator.
+In each case we will introduce the spin relations \ref{SpinOperatorInv1} and \ref{SpinOperatorInv2} together with \ref{SpinRel1}, \ref{SpinRel2} and \ref{SpinRel3} to obtain the corresponding effective spin Hamiltonian.
 
@@
 
-We would like to investigate the case in which the electric field is time independent.
-In that case we can restrict the analysis to the one dimensional case, since in second order the electric field will only affect the bonds parallel to the field.
+Before we start using \ref{HeffSimplified} for different models we would like to investigate the case in which the electric field is time independent.
+In that case we can restrict the analysis to the one dimensional lattice, since in second order the electric field will only affect the bonds parallel to the field.
 Let us denote $\vec{\bs{E}} = E_0 \hat{e}_x$, then the Peiels transformed hopping amplitudes can be written as:

### 2019-04-13 Chapters/Chapter4.tex
Add more references and short summary in the intro
Few more minor changes

@@
 \chapter{Perturbing the lattice}
+\label{ChapPerturbing}
 
@@
 The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.
-This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}) where the starting Hamiltonian is the Hubbard model:
+For the exchange interaction coupling $J$ alone, this has already been done (\cite{Mentink2015}, \cite{Kitamura2017}) starting with the Hamiltonian of the Hubbard model:
 

### 2019-04-13 Chapters/Chapter5.tex
add plot
Few more minor changes

@@
 At this point it is common to define $\gamma_{\bs{k}} = \sum_\delta e^{i \bs{k} \cdot \bs{\delta}}$.
-Using $\bs{\delta}_1=\frac{a_0}{2}(1,\sqrt{3})$, $\bs{\delta}_2=\frac{a_0}{2}(1,-\sqrt{3})$, $\bs{\delta}_3=a_0(-1,0)$ and taking $a_0=1$, we can write this as:
+Using $\bs{\delta}_1=\frac{a_0}{2}(1,\sqrt{3})$, $\bs{\delta}_2=\frac{a_0}{2}(1,-\sqrt{3})$, $\bs{\delta}_3=a_0(-1,0)$ (see Fig \ref{Fig.Magnon.Vecs}) and taking $a_0=1$, we can write this as:
 \begin{equation}
@@
 
-Where $\bs{\delta}^{NNN}$ are the NNN vectors:
+Where $\bs{\delta}^{NNN}$ are the NNN vectors (as depicted in Fig \ref{Fig.Magnon.Vecs}):
 \begin{align*}
@@
 \end{align*}
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/NNNvec.png}
+  \caption{NN vectors $\bs{\delta}_a$ and NNN vectors $\bs{\delta}^{NNN}_a$. Red and blue denote sites of sublattices $A$ and $B$ respectively.}
+\label{Fig.Magnon.Vecs}
+\end{figure}
 Notice that with these definitions, if $i$ is a site on the $A$ sublattice, $\nu_{i,i+\bs{\delta}^{NNN}_a}=+1$ for $a=1,2,3$ and $\nu_{i,i+\bs{\delta}^{NNN}_a}=-1$ for $a=4,5,6$.
@@
 
+The new term $\pm \Delta_{\bs{k}}$ breaks the degeneracy between the $\alpha$ modes and the $\beta$ modes. In Figure \ref{Fig.Magnon.Disp} we plot the resulting energy dispersion of \ref{DispWithDMI}.
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.7\linewidth]{../Figures/magnon_disp_2.png}
+  \caption{The energy $\frac{\epsilon_{\bs{k}}^\pm}{JS}$ obtained for $D=0.1J$ }
+\label{Fig.Magnon.Disp}
+\end{figure}
+
 \section{NNN exchange}
@@
 
-Where $\Delta'_{\bs{k}} = \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right)$ and $\tilde{\Gamma}_{\bs{k}} = \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)$.
+Where $\Delta'_{\bs{k}} = \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right) = 4\left\{ \cos(\delta^{NNN}_1\cdot\bs{k}) + \cos(\delta^{NNN}_2\cdot\bs{k}) + \cos(\delta^{NNN}_3\cdot\bs{k})\right\}$ and $\tilde{\Gamma}_{\bs{k}} = \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)$.
 Therefore, now:

### 2019-04-13 Code/magnon_disp.R

@@ -35,7 +35,7 @@ energy_m <- function(k) {
 kmax = 3
 res = 0.01
 J=1
-D=0.1
+D=0
 S=2.5
 kx_vec<-seq(from=-kmax, to=kmax, by=res)
 samples=length(kx_vec)

### 2019-04-23 Appendices/AppendixE.tex
add ground state energy

@@
 
-An orthonormal basis for the extended Hilbert space can be obtained as the direct product an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$.
-A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, therefore, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$.
+An orthonormal basis for the extended Hilbert space can be obtained as the direct product of an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$.
+A convenient orthonormal basis for $\mathcal{L}_T$ is given by the functions $e^{im\omega t}$, where $m$ is usually referred to as the photon number.
+Then, if $\ket{\alpha}$ labels an orthonormal basis of $\mathcal{H}$, then the set of functions $\ket{\alpha m (t)} = \ket{\alpha}e^{im\omega t}$ is a basis of the extended Floquet space, and it is denoted as $\ket{\alpha m}\rangle$.
 In this basis, the quasienergy operator has matrix elements:
@@
 \end{equation}
+
+\section{Diagonalization}
+
+We introduce a unitary transformation $\hat{U}(t)=\sum_m e^{im\omega t}\hat{U}_m$, $\hat{Q} \rightarrow \hat{Q}'=\hat{U}^{\dagger}(t)\hat{Q}\hat{U}(t)$ or:
+
+\begin{align}
+\hat{H}(t) \rightarrow \hat{H}'(t) &= \hat{U}^{\dagger}(t)\hat{H}(t)\hat{U}(t) - i\hat{U}^{\dagger}(t)\text{d}_t\hat{U}(t) \\
+\ket{\psi(t)} \rightarrow \ket{\psi'(t)} &= \hat{U}^{\dagger}(t)\ket{\psi(t)}
+\end{align}
+
+The goal is to find $\hat{U}(t)$ such that the transformed quasienergy operator $\hat{Q}'$ is block diagonal in the photon number.
+Using \ref{QOmatelem} we notice that this requirement is equivalent to the requirement that the transformed Hamiltonian $\hat{H}'(t)$ is time independent.

### 2019-04-23 Chapters/Chapter5.tex
add ground state energy

@@
 \begin{equation}
+\label{Heisenberg}
 \hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j
@@
 
-Where the sum is over $\bs{k}$ in the first Brillouin zone. Using these relations, together with $\sum{i} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ we find:
+Where the sum is over $\bs{k}$ in the first Brillouin zone.
+Using these relations, together with $\sum{i} e^{i(\bs{k}-\bs{k}')\cdot\bs{r}_i} = \delta_{\bs{k}, \bs{k}'}$ and denoting the number of sites by $N$ and the number of nearest neighbors by $z$, we find:
 
 \begin{equation}
-\hat{H} = 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
+\hat{H} = -S^2JNz + 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
 \end{equation}
@@
 \label{MagnonicH}
-\hat{H} = 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
+\hat{H} = -S^2JNz + 2JS \sum_{\bs{k}} \left\{ z \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
 \end{equation}
@@
 Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{-\bs{k}}^\dagger \right)^T$.
-That is, $\hat{H} = \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$.
+That is, $\hat{H} = -S^2JNz + \sum_{\bs{k}} \Psi_{\bs{k}} \hat{H}_{\bs{k}} \Psi^\dagger_{\bs{k}}$.
 In order to diagonalize this Hamiltonian we introduce the Bogoliubov transformation:
@@
 \begin{align}
-\hat{H} &= 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(\abs{u_{\bs{k}}}^2+\abs{v_{\bs{k}}}^2) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right.
+\hat{H} &= -S^2JNz + 2JS \sum_{\bs{k}} \left\{ \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \left( z(\abs{u_{\bs{k}}}^2+\abs{v_{\bs{k}}}^2) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right.
 \nonumber \\
-&+ \left.
-\hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}_{\bs{k}} \left( -2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\beta}_{\bs{k}}^\dagger\hat{\alpha}_{\bs{k}} \left( -2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) \right\} \label{BeforeBogo}
+&+ \hat{\alpha}^\dagger_{\bs{k}} \hat{\beta}^\dagger_{\bs{k}} \left( -2zu_{\bs{k}}v_{\bs{k}}^* + \gamma_{\bs{k}}(v_{\bs{k}}^*)^2+\gamma_{-\bs{k}}u_{\bs{k}}^2 \right) + \hat{\alpha}_{\bs{k}}\hat{\beta}_{\bs{k}} \left( -2zu_{\bs{k}}^*v_{\bs{k}} + \gamma_{\bs{k}}(u_{\bs{k}}^*)^2+\gamma_{-\bs{k}}v_{\bs{k}}^2 \right) + \nonumber \\
+&\left. + \left( 2z\abs{v_{\bs{k}}}^2 - \gamma_{\bs{k}}u_{\bs{k}}^* v_{\bs{k}}^* - \gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) \right\} \label{AfterBogo}
 \end{align}
@@
 
-\begin{align*}
-u_{\bs{k}} &= \cosh(\frac{\theta_{\bs{k}}}{2})e^{i \xi_{\bs{k}}} \\
-v_{\bs{k}} &= \sinh(\frac{\theta_{\bs{k}}}{2})
-\end{align*}
+\begin{align}
+u_{\bs{k}} &= \cosh(\frac{\theta_{\bs{k}}}{2})e^{i \xi_{\bs{k}}} \label{Bogou} \\
+v_{\bs{k}} &= \sinh(\frac{\theta_{\bs{k}}}{2}) \label{Bogov}
+\end{align}
 
@@
 
-This erases the non diagonal terms in \ref{BeforeBogo} leading to a diagonal term:
+This erases the non diagonal terms in \ref{AfterBogo} leading to a diagonal term:
 \begin{equation}
@@
 
-Then, the dispersion relation is:
+With this, we can rewrite \ref{AfterBogo} as:
 
 \begin{align}
-\hat{H} &= \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right) \epsilon_{\bs{k}} \\
-\epsilon_{\bs{k}} &= 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}
+\hat{H} &= -S^2JNz + 2JS \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}+1 \right)\epsilon_{\bs{k}}+2JS \sum_{\bs{k}}z(\abs{v_{\bs{k}}}^2-\abs{u_{\bs{k}}}^2) = \nonumber \\
+&= E_0 + \sum_{\bs{k}}\left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \right)
 \end{align}
+
+Where we used $\sum_{\bs{k}}=\frac{N}{2}$ and where $\epsilon_{\bs{k}} = 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}$. The ground state energy of this magnon Hamiltonian is:
+\begin{equation}
+E_0 = -JNz(S^2+S)+\sum_{\bs{k}}\epsilon_{\bs{k}} \label{HeisenbergMagnonGS}
+\end{equation}
+Note that the classical ground energy of \ref{Heisenberg} is $E_{cl}=-JNzS^2$, whereas the ground state that we obtained is lowered by:
+\begin{equation}
+\Delta E=-JNzS+\sum_{\bs{k}}\epsilon_{\bs{k}} = 2JS\sum_{\bs{k}}\left( \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} - z\right)
+\end{equation}
+Which is indeed negative since the terms in the sum are always negative.
+This term represents quantum corrections to the classical ground energy $E_{cl}$.
+Note that the fact that the quantum corrections lower the energy of the classical ground state means that the classical ground state (N\'eel order) is not an eigenstate of the Heisenberg Hamiltonian.
 
@@
 \begin{equation}
-D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} - \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
+D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
 \end{equation}
@@
 \end{equation}
-The full magnonic Hamiltonian now is:
+
+Note that $\Delta_{\bs{k}}=-\Delta_{-\bs{k}}$ .The full magnonic Hamiltonian now is:
 
@@
 \label{MagnonicH2}
-\hat{H} = 2JS \sum_{\bs{k}} \left\{ \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}(z+\Delta_{\bs{k}}) + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}(z-\Delta_{-\bs{k}}) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
+\hat{H} = -S^2JNz + 2JS \sum_{\bs{k}} \left\{ \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}}(z+\Delta_{\bs{k}}) + \hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}}(z-\Delta_{\bs{k}}) + \gamma_{\bs{k}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + \gamma_{-\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right\}
 \end{equation}
@@
 z + \Delta_{\bs{k}}& \gamma_{\bs{k}} \\
-\gamma_{-\bs{k}} & z - \Delta_{-\bs{k}}
-\end{pmatrix}
+\gamma_{-\bs{k}} & z - \Delta_{\bs{k}}
+\end{pmatrix} \label{MatrixMagnonDMI}
 \end{equation}
 
-In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, whereas the energy gets lifted:
+In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, leading to:
+
+\begin{align*}
+\hat{H} &= -S^2JNz  + 2JS\sum_{\bs{k}} \left\{ \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \left( \abs{u_{\bs{k}}}^2(z+\Delta_{\bs{k}}) + \abs{v_{\bs{k}}}^2(z-\Delta_{\bs{k}}) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right.
+\\
+&\left.
++ \hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}} \left( \abs{u_{\bs{k}}}^2(z-\Delta_{\bs{k}}) + \abs{v_{\bs{k}}}^2(z+\Delta_{\bs{k}}) -\gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}} \right) + \right.
+\\
+&\left. + \left( 2\abs{v_{\bs{k}}}^2 - \gamma_{\bs{k}}u_{\bs{k}}^*v_{\bs{k}}^*-\gamma_{-\bs{k}}u_{\bs{k}}v_{\bs{k}}\right) \right\}
+\end{align*}
+
+Where we already took \ref{Bogou} and \ref{Bogov}.
+The ground state energy $E_0$ remains the same as in the base Heisenberg model while the excitation modes $\hat{\alpha}_{\bs{k}}^\dagger$ and $\hat{\beta}_{\bs{k}}^\dagger$ change in the following way:
 
 \begin{align}
-\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
+\hat{H} &= E_0 + \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
 \epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} + \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2} \right)
@@
   \includegraphics[width=0.7\linewidth]{../Figures/magnon_disp_2.png}
-  \caption{The energy $\frac{\epsilon_{\bs{k}}^\pm}{JS}$ obtained for $D=0.1J$ }
+  \caption{The energy $\frac{\epsilon_{\bs{k}}^\pm}{JS}$ obtained for $D=0.1J$. For simplicity we take $E_0 = 0$. }
 \label{Fig.Magnon.Disp}
@@
 
-Let's now introduce a term:
+We would like to see how the anisotropic spin interaction derived in \ref{MKMHeff} enters in the magnon Hamiltonian. To this end, we introduce now a term:
 
@@
 
-Where $\Delta'_{\bs{k}} = \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right) = 4\left\{ \cos(\delta^{NNN}_1\cdot\bs{k}) + \cos(\delta^{NNN}_2\cdot\bs{k}) + \cos(\delta^{NNN}_3\cdot\bs{k})\right\}$ and $\tilde{\Gamma}_{\bs{k}} = \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)$.
+Where we defined:
+\begin{align*}
+\Delta'_{\bs{k}} &= \sum_{\delta^{NNN}} \left( e^{i\bs{k}\cdot \bs{\delta}^{NNN}} +  e^{-i\bs{k}\cdot \bs{\delta}^{NNN}}\right) = 4\left\{ \cos(\delta^{NNN}_1\cdot\bs{k}) + \cos(\delta^{NNN}_2\cdot\bs{k}) + \cos(\delta^{NNN}_3\cdot\bs{k})\right\} \\
+\tilde{\Gamma}_{\bs{k}} &= \frac{1}{2J}\left( \Gamma_{xy}\Delta'_{\bs{k}}-4z\Gamma_z \right)
+\end{align*}
 Therefore, now:
@@
 
-We obtain the dispersion relation by changing $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$ in \ref{DispWithDMI}:
+This is the same as \ref{MatrixMagnonDMI} if we replace $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$, therefore the magnon Hamiltonian is:
 
 \begin{align}
-\hat{H} &= \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \label{DispWithDMI} \\
+\hat{H} &= E_0 + \sum_{\bs{k}} \left( \hat{\alpha}_{\bs{k}}^\dagger \hat{\alpha}_{\bs{k}} \epsilon_{\bs{k}}^+ +\hat{\beta}_{\bs{k}}^\dagger \hat{\beta}_{\bs{k}}  \epsilon_{\bs{k}}^- \right) \\
 \epsilon_{\bs{k}}^\pm &= 2JS \left( \pm \Delta_{\bs{k}} +  \sqrt{(z + \tilde{\Gamma}_{\bs{k}})^2-\abs{\gamma_{\bs{k}}}^2} \right)
 \end{align}
+
+This concludes our discussion of the magnons in the models derived in the last Chapter.
+The main difference of the magnonic Hamiltonian of a Kane-Mele system with a simple Heisenberg interaction is that the $\hat{\alpha}_{\bs{k}}^\dagger$ and $\hat{\beta}_{\bs{k}}^\dagger$ modes have non degenerate spectrum.
+This is arising from the addition of DMI in the model which breaks the symmetry of the system.

### 2019-04-24 Appendices/AppendixB.tex
cdots and spaces

@@
 \begin{align}
-\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
-\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
+\psi'_{\bs{R}}(\bs{r}) &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) \\
+\phi'_{\bs{k}}(\textbf{r}) &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\cdot\bs{R}}\psi'_{\bs{R}}(\bs{r}) = \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{-i\bs{k}\cdot\bs{R}} e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r})
 \end{align}
@@
 \begin{align*}
-\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
-&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
-&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
+\hat{H}'(\bs{r}) \psi'_{\bs{R}} (\bs{r}) &= \left[ \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) \right] e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \psi_{\bs{R}}(\bs{r}) = \\
+&=e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \left[ \frac{(\bs{p} - i\hbar \bs{\nabla_r}(i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)) -e\bs{A})^2}{2m} +U(\bs{r}) \right] = \\
+&= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \left[ \frac{\bs{p}^2}{2m} + U(\bs{r}) \right] \psi_{\bs{R}}(\bs{r}) = e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \hat{H}(\bs{r}) \psi_{\bs{R}}(\bs{r})
 \end{align*}
@@
 \label{PeierlsMtxElem}
-t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
+t_{ij}(t) = \bra{\psi'_{\bs{R_i}}} \hat{H}'(\bs{r}) \ket{\psi'_{\bs{R_j}}} = e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \bra{\psi_{\bs{R_i}}} \hat{H}(\bs{r}) \ket{\psi_{\bs{R_j}}}
 \end{equation}
 
-When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j) \bs{A}(t)}$.
+When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j)\cdot \bs{A}(t)}$.
 
-Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
+Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{e}_z\cdot(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then
 
 \begin{align*}
-  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
-  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\bs{A}(\bs{r}',t)} \alpha_R \hat{z}\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
+  \alpha_R \hat{e}_z\cdot(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} &= \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \psi_{\bs{R}} = \\
+  &= e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}d\bs{r}'\cdot\bs{A}(\bs{r}',t)} \alpha_R \hat{e}_z\cdot\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}}
 \end{align*}

### 2019-04-24 Appendices/AppendixD.tex
cdots and spaces

@@
 h(\bs{K}+\bs{q}) \approx \begin{pmatrix}
-    0 & \frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} \\
-    \frac{\partial f^*(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} & 0
+    0 & \frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\cdot\bs{q} \\
+    \frac{\partial f^*(\bs{k})}{\partial \bs{k}}(\bs{K})\cdot\bs{q} & 0
 \end{pmatrix}
@@
 \begin{equation}
-\frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\bs{q} = -ie^{\frac{2\pi i}{3}} \frac{3a}{2}(q_x+iq_y)
+\frac{\partial f(\bs{k})}{\partial \bs{k}}(\bs{K})\cdot\bs{q} = -ie^{\frac{2\pi i}{3}} \frac{3a}{2}(q_x+iq_y)
 \end{equation}
@@
 
-We can write this more compactly as $h(\bs{K}+\bs{q}) = v_F \left(\bs{q}\bs{\sigma}\right)^*$.
-Analogously for the $\bs{K}'$ point we obtain $h(\bs{K}'+\bs{q}) = v_F\bs{q}\bs{\sigma}$.
+We can write this more compactly as $h(\bs{K}+\bs{q}) = v_F \left(\bs{q}\cdot\bs{\sigma}\right)^*$.
+Analogously for the $\bs{K}'$ point we obtain $h(\bs{K}'+\bs{q}) = v_F\bs{q}\cdot\bs{\sigma}$.
 This result is identical to the massless Dirac Hamiltonian for relativistic electrons where the speed of light is changed to $v_F$.

### 2019-04-24 Chapters/Chap3/HWithSoi.tex
cdots and spaces

@@
 t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
+	(\delta_{\sigma \sigma'}t_0+\bs{\Delta}_{ij} \cdot \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
 	0 & \text{ otherwise}
@@
 \hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \nonumber \\
-&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
+&= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{HeffHubbSOI1}
 \end{align}
@@
 \begin{align*}
-&(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji} \bs{\sigma}_{\sigma_3, \sigma_4}) = \\ 
-&\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3, \sigma_4})
+&(\delta_{\sigma_1 \sigma_2}t_0+\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_1, \sigma_2}) (\delta_{\sigma_3 \sigma_4}t_0+\bs{\Delta}_{ji}\cdot \bs{\sigma}_{\sigma_3, \sigma_4}) = \\ 
+&\delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})
 \end{align*}
@@
 \begin{align*}
-\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3, \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
-&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
-&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
-&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) + \\
-&+\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \\
-&(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3, \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
-&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
-&= \sum_{\langle i,j \rangle} \left\{ J_{ij}\bs{S}_i\bs{S}_j +\bs{D}_{ij}\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j \right\}
+\hat{H}_{\text{eff}}(t) &= - \frac{1}{2} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left( \frac{\delta_{\sigma_1 \sigma_4}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1} \right) \left( \frac{\delta_{\sigma_2 \sigma_3}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3} \right) \nonumber \\ &\left[ \delta_{\sigma_1 \sigma_2}\delta_{\sigma_3 \sigma_4}t_0^2 + t_0\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4} \bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 \sigma_4}) - (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ji}\cdot\bs{\sigma}_{\sigma_3, \sigma_4}) \right] \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
+&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
+&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
+&\bs{\Delta}_{ij}\cdot(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) + \\
+&+\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\cdot\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\cdot\bs{\sigma}_{\sigma_2 \sigma_3}\right) \\
+&(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1, \sigma_2})(\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_3, \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
+&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\cdot\bs{S}_j + 2it_0\bs{\Delta}_{ij}\cdot \bs{S}_i \times \bs{S}_j + \sum_{\alpha, \beta} S_i^\alpha (\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta ) S_j^\beta \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
+&= \sum_{\langle i,j \rangle} \left\{ J_{ij}\bs{S}_i\cdot\bs{S}_j +\bs{D}_{ij}\cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j \right\}
 \end{align*}

### 2019-04-24 Chapters/Chap3/ModelsNNN.tex
cdots and spaces

@@
 \label{BigHam}
-\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} - 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_2 + \bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
+\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_1 + \bs{\Delta}_{1,ij}\cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} - 
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_2 + \bs{\Delta}_{2,ij}\cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + 
 	\text{U}\hat{D}
@@
 t_{ij}^{\sigma \sigma'} = \begin{cases}
-	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
-	(\delta_{\sigma \sigma'}t_2+\bs{\Delta}_{2,ij} \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
+	(\delta_{\sigma \sigma'}t_1+\bs{\Delta}_{1,ij}\cdot \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ nearest neighbors} \\
+	(\delta_{\sigma \sigma'}t_2+\bs{\Delta}_{2,ij}\cdot \bs{\sigma}_{\sigma, \sigma'}) & \text{for } i, j \text{ next nearest neighbors} \\
 	0 & \text{ otherwise}
@@
 \begin{align}
-\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}\bs{S}_i\bs{S}_j + \bs{D}_{1,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
-&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
+\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle} \left\{ J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{1,ij} \cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
+&\sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
 \end{align}
@@
 In section \ref{Numerics} we will investigate this numerically.
-The reason for this is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ (assuming flat field approximation).
+The reason for this is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\cdot\bs{A}(t)}$ (assuming flat field approximation).
 This phase will be larger for NNN hopping than for NN hopping and this will therefore translate in the corresponding spin interactions.
@@
 \label{KMHeff}
-\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
+\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
 \end{equation}
@@
 \begin{align}
-\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle ^*} \left\{ J_{1,ij}\bs{S}_i\bs{S}_j + \bs{D}_{1,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
-&\sum_{\langle \langle i,j \rangle \rangle^*} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
+\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle ^*} \left\{ J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{1,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
+&\sum_{\langle \langle i,j \rangle \rangle^*} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij} \cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
 \end{align}
@@
 \begin{equation}
-\frac{1}{U^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\bs{\vec{E}}_0} \right)
+\frac{1}{U^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} \right)
 \end{equation}

### 2019-04-24 Chapters/Chap3/TDHeff.tex
cdots and spaces

@@
 \begin{equation}
-t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)}
+t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\cdot\bs{A}(t)}
 \end{equation}
@@
 \begin{align*}
-t_{ij}^{\sigma \sigma'}(t) &= t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = \\
+t_{ij}^{\sigma \sigma'}(t) &= t_{ij}^{\sigma \sigma'}e^{ie\bs{R}_{ij}\cdot\bs{A}(t)} = t_{ij}^{\sigma \sigma'}e^{i\alpha_{ij} \cos(\omega t - \theta_{ij})} = \\
 &= t_{ij}^{\sigma \sigma'}\sum_m e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij}) e^{im\omega t} = \sum t_{ij,m}^{\sigma \sigma'} e^{im\omega t}
@@
 \label{TimeIndepHoppingAmpl}
-t_{ij}^{\sigma \sigma'} (t) = t_{ij}^{\sigma \sigma'} e^{ie \vec{\bs{R}}_{ij} \vec{\bs{E}} t}
+t_{ij}^{\sigma \sigma'} (t) = t_{ij}^{\sigma \sigma'} e^{ie \vec{\bs{R}}_{ij} \cdot \vec{\bs{E}} t}
 \end{equation}
 
-Therefore, there will be only two Fourier modes with frequency $\omega_0 = e \vec{\bs{R}}_{ij} \vec{\bs{E}} = \pm eaE_0$, where the sign $+(-)$ corresponds to the case $\vec{\bs{R}}_{ij} = \pm a \hat{e}_x$.
+Therefore, there will be only two Fourier modes with frequency $\omega_0 = e \vec{\bs{R}}_{ij} \cdot \vec{\bs{E}} = \pm eaE_0$, where the sign $+(-)$ corresponds to the case $\vec{\bs{R}}_{ij} = \pm a \hat{e}_x$.
 Notice that this frequency $\omega_0$ does not correspond to a field frequency ($\vec{\bs{E}}$ is time independent), but to the Fourier mode in the hopping amplitudes (which is induced by the time independent field).
@@
 \end{equation}
-
 Now, the first fraction represents a hopping process $i\rightarrow j \rightarrow i$ where $j$ lies left to $i$, whereas in the second fraction $j$ lies right to $i$:
@@
 \end{align*}
-
 We can rewrite this in the more compact form:
@@
 \end{equation}
-
 This is the same effective Hamiltonian obtained in the previous section without an electric field but with a shift in the intermediate state energy by $\pm \omega_0 = \pm eaE_0$.

### 2019-04-24 Chapters/Chapter2.tex
cdots and spaces

@@
 
-Let $\phi_i(\bs{r})$ be the i-\textit{th} eigenstate of the atomic Hamiltonian $\hat{H}_a(\bs{r}) = -\frac{\hbar^2p^2}{2m} + V_a(\bs{r}-bs{r}_n)$ with energy $E_i$ and where $V_a(\bs{r})$ is the atomic potential.
+Let the atomic Hamiltonian be $\hat{H}_a(\bs{r}) = -\frac{\hbar^2\hat{p}^2}{2m} + V_a(\bs{r}-\bs{r}_n)$, where $\hbar$ is the reduced Planck constant, $m$ is the electron mass, $\hat{p}$ is the momentum operator and $V_a(\bs{r})$ is the atomic potential.
+Let $\phi_i(\bs{r})$ be the i-\textit{th} eigenstate of the atomic Hamiltonian with energy $E_i$.
 The crystal Hamiltonian is:
@@
 \end{equation}
-
 An electron localized around the atom at $\bs{r}_n$ will mainly feel the potential of that atom, and the potential of the rest of the atoms will be a perturbation to the free atom problem.
@@
 \end{equation}
-
 Now, the Bloch theorem states that an eigenfunction of the crystal Hamiltonian should only change by a phase from site to site, that is $\psi_i(\bs{r}+\bs{r}_m)=e^{i \bs{k} \cdot \bs{r}_m}\psi_i(\bs{r})$, where $\bs{k}$ is the crystal momentum of the Bloch wave.
@@
 \end{equation}
-
 The energy of this state is $E_i(\bs{k}) = \bra{\psi_{i\bs{k}}} \hat{H} \ket{\psi_{i\bs{k}}}$, using \ref{SplitCrystalHam} this can be written as:
@@
 \end{equation}
-
 Assuming that $\phi_i$ is spherically symmetric, and neglecting the perturbation $v(\bs{r}-\bs{r}_n)$ further away than nearest neighbors, we can simplify this expression to:
@@
 \end{equation}
-
-Where $A = -\bra{\phi_i(\bs{r}-\bs{r}_n)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)}$ and $B = -\bra{\phi_i(\bs{r}-\bs{r}_m)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)}$ and where $\bs{\delta}$ are the NN vectors.
+Where $\bs{\delta}$ are the NN vectors and:
+\begin{align*}
+A &= -\bra{\phi_i(\bs{r}-\bs{r}_n)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)} \\
+B &= -\bra{\phi_i(\bs{r}-\bs{r}_m)}v(\bs{r}-\bs{r}_n) \ket{\phi_i(\bs{r}-\bs{r}_n)}
+\end{align*}
 $A$ measures the amount of energy reduced when the atom forms a crystal, $B$ is a measure of the width of the band. 
@@
 \end{equation}
-
 Where $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron in site $i$ and spin state $\sigma$.
@@
 In strongly correlated electron systems, the effect of electron-electron Coulomb interactions is important, and this effect is neglected in \ref{TBModel}.
-The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$:
+The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$, where $\text{U}$ is a constant accounting for the onsite electron-electron interaction:
 \begin{equation}
@@
 \end{equation}
-
 This is known as the Hubbard model, which was first proposed by Hubbard \cite{Hubbard1963} to describe electron correlations in $d$ or $f$ bands in transition metals.
@@
 \end{figure}
-
 Notice that if we set $\text{U}=0$ in \ref{HH} we recover the tight binding Hamiltonian, therefore we can say that the Hubbard model is an expansion of the tight binding model.

### 2019-04-24 Chapters/Chapter3.tex
cdots and spaces

@@
 \end{equation}
-
 where $v$ is the electron-electron interaction and where $\hat{H}^{(1)}$ is the single particle Hamiltonian:
@@
 \end{equation}
-
 Where $\lambda = \frac{\hbar^2}{4m^2c^2}$ is the spin orbit coupling constant and $\text{U}(\bs{r})$ is a periodic potential.
+$\hbar$ is the reduced Planck constant, $m$ is the electron mass, $c$ is the speed of light and $\bs{\sigma}$ is a vector of Pauli matrices $\bs{\sigma} = (\sigma_1, \sigma_2, \sigma_3)$.
 The second quantized form of this Hamiltonian can be approximated by a version of the Hubbard model.
@@
 \end{equation}
-
 Which is the well-known Bloch function form.
@@
 \end{align}
-
 Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
@@
 \end{equation}
-
 Where we assumed $\hat{v}$ to be spin independent. This can be rewritten as:
@@
 \end{equation}
-
 Where $t_{ij} = -\bra{i} -\frac{\hbar^2}{2m}\nabla^2_{\textbf{r}} + \text{U}(\textbf{r}) \ket{j}$ and $\boldsymbol{\Delta}_{ij} = -\bra{i} \lambda \boldsymbol{\nabla}V(\textbf{r}) \times \textbf{p} \ket{j}$.
@@
 \end{align*}
-
 Therefore it follows that $\bs{\Delta}_{ii} = 0$ and that $\bs{\Delta}_{ij}$ is purely imaginary.
@@
 \end{equation}
-
 Hubbard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.
@@
 \end{equation}
-
 Where we defined:
@@
 \end{align}
-
 Where $\phi(\bs{r})$ is the Wannier function centered at the origin and $\bs{R}_1$ is a nearest neighbour lattice vector.
@@
 \end{equation}
-
 Now, in a half filling system this Hamiltonian can be well approximated by an effective Hamiltonian without non local Coulomb interactions:
@@
 \end{equation}
-
 Where $\text{U}^* = \text{U} - \text{V}$.
@@
 \end{equation}
-
 This Hamiltonian is identical to the Hubbard Hamiltonian \ref{HH} adding a spin dependent hopping, which arises from the SOI.
@@
 \end{equation}
-
 The sum being over all excited states.
@@
 \end{align}
-
 In the second line we imposed $i=j'$ and $j=i'$ since that's the only way $\hat{H_t^2}\ket{\phi}$ has no double occupied sites and so the matrix element does not vanish (remember that $\ket{\phi}$ and $\ket{\phi'}$ belong in the subspace of zero double occupied states).
@@
 \end{align}
-
 Let us now introduce the on-site spin operators:
@@
 \end{equation}
-
 Which satisfy:
@@
 \end{align}
-
 In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:
@@
 \end{align*}
-
 Where we have neglected the term $\sum_{\sigma \sigma'} \frac{1}{2}\delta_{\sigma,\sigma'}(\bs{S}_i\cdot\bs{\sigma}_{\sigma',\sigma} - \bs{S}_j\cdot\bs{\sigma}_{\sigma,\sigma'})$ because eventually we will sum over all $\langle i, j \rangle$ and it will cancel out.
@@
 \end{align*}
-
 Where in the second line we expand the sum in the spin states (overbrace indicates the spin state $\sigma_1$, $\sigma_2$, $\sigma_3$, $\sigma_4$ respectively).
@@
 \end{align*}
-
 These three relations are important and will be used in the next chapter:
@@
 \end{align}
-
 Now introducing the spin operators into  $\hat{H}_J$ in \ref{C3HJ}, with $n_{i \uparrow} + n_{i \downarrow} = 1$ and using \ref{SpinRel1} we obtain:
@@
 \end{align*}
-
 The constant term can be neglected leaving:
@@
 \end{equation}
-
 Which is the Heisenberg model for antiferromagnets with $J_{ij}^0 = \frac{2t^2}{\text{U}} > 0$. Likewise, for $\hat{H}_D$ in \ref{C3HD}, using \ref{SpinRel2}:
@@
 \end{align*}
-
 Where $\bs{D}_{ij}^0 = \frac{4it}{\text{U}}\bs{\Delta}_{ij}$, notice that being $\bs{\Delta}_{ij}$ purely imaginary, $\bs{D}_{ij}^0$ is a real vector. 
@@
 \end{align*}
-
 With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
@@
 \end{equation}
-
 With:
@@
 \end{align}
-
 The $J_{ij}^0\bs{S}_i\cdot\bs{S}_j$ term is known as exchange interaction.
@@
 \end{equation}
-
-Where $\langle \langle i,j \rangle \rangle$ denotes sum over NNN. If we follow the procedure as before we will obtain an effective spin Hamiltonian:
+Where $\langle \langle i,j \rangle \rangle$ denotes sum over NNN and $t_1$ and $t_2$ denote the NN and NNN hopping amplitudes respectively.
+If we follow the procedure as before we will obtain an effective spin Hamiltonian:
 
@@
 \end{equation}
-
 Where $J_1 = \frac{t_1^2}{\text{U}}$ and $J_2 = \frac{t_2^2}{\text{U}}$.
@@
 \end{equation}
-
 Where $\epsilon_i$ are random variable $\epsilon_i \in [-W,W]$.
@@
 \end{equation}
-
 Where in the second step we added the contributions of $\langle i,j \rangle$ and $\langle j,i \rangle$ and where $J_{ij} = \frac{2t^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}$.
@@
 \end{align}
-
 Where $S$ is the spin angular momentum in units of $\hbar$. Inverting these relations, introducing them into the Hamiltonian and neglecting edge terms we obtain:
@@
 \begin{align}
-\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
+\hat{H} &= JS^2 \sum_i^{N-1} (\bs{m}_i-\bs{l}_i)\cdot(\bs{m}_i+\bs{l}_i+\bs{m}_{i+1}+\bs{l}_{i+1}) - KS^2\sum_i^N \left[(\bs{m}_{iz}+\bs{l}_{iz})^2 + (\bs{m}_{iz}-\bs{l}_{iz})^2 \right] \nonumber = \\
 & 2JS^2\sum_i^{N} (\bs{m}_i^2-\bs{l}_i^2)+\frac{JS^2}{2}\sum_i^{N-1}\left[(\bs{l}_{i+1}-\bs{l}_i)^2-(\bs{m}_{i+1}-\bs{m}_i)^2 \right] \nonumber \\
-& + JS^2\sum_i^{N-1} \left[ \bs{m}_i(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
+& + JS^2\sum_i^{N-1} \left[ \bs{m}_i\cdot(\bs{l}_{i+1}-\bs{l}_i) - \bs{l}_i\cdot(\bs{m}_{i+1}-\bs{m}_i) \right] - 2KS^2\sum_i^N(m_{iz}^2+l_{iz}^2)
 \end{align}
-
 Now we can take the continuum limit with:
@@
 \end{align*}
-
 This, together with $\bs{m}_i-\bs{l}_i = 2\bs{m}_i-1$ and $\bs{m}_{i+1} \rightarrow \bs{m}(x) + 2d \partial_x\bs{m}(x)$ gives:
 
-\begin{equation}
-\mathcal{H}(\bs{l},\bs{m}) = JS^2\left\{ 4|\bs{m}|^2 + |\partial_x\bs{l}'|^2 -  |\partial_x\bs{m}'|^2 +(\bs{m}\partial_x\bs{l} -\bs{l}\partial_x\bs{m}) \right\} -KS^2\left\{ (\bs{l}\hat{z})^2 + (\bs{m}\hat{z})^2 \right\}
-\end{equation}
+\begin{align}
+\mathcal{H}(\bs{l},\bs{m}) &= JS^2\left\{ 4|\bs{m}|^2 + |\partial_x\bs{l}'|^2 -  |\partial_x\bs{m}'|^2 +(\bs{m}\partial_x\bs{l} -\bs{l}\partial_x\bs{m}) \right\} \nonumber \\
+&-KS^2\left\{ (\bs{l}\hat{z})^2 + (\bs{m}\hat{z})^2 \right\}
+\end{align}
+This Hamiltonian is used as a starting point for the study of spin dynamics in antiferromagnets.
+Antiferromagnetic domain wall motion can be described within this framework \cite{AlirezaSW, Alireza2014}.
+Manipulation of AFM domain walls is of great interest in spintronics since it can lead to high frequency switching of magnetic textures \cite{Jungwirth2016}.
 

### 2019-04-25 Appendices/AppendixA.tex
more spaces

@@
 \end{equation}
-
 Where $m_\mu$ are integers.
@@
 \end{equation}
-
 Where $\kappa_\mu = \frac{\nu_\mu}{L_\mu}, -\frac{L_\mu}{2}+1 \leq \nu_\mu \leq \frac{L_\mu}{2}$ so that, $-\frac{1}{2} < \kappa_\mu \leq \frac{1}{2}$.
@@
 \end{align}
-
 Where $a_0$ is the atom-atom distance (in the case of graphene $a_0 = 1.42 \r{A}$).
@@
 \end{align}
-
 These two vectors also span an hexagonal structure. The vectors connecting an atom in the A sublattice to its B sublattice nearest neighbors are:
@@
 \end{align}
-
 The vectors connecting an atom in the B sublattice to its A sublattice nearest neighbors are just $\bs{R}^B_i = -\bs{R}^A_i$

### 2019-04-25 Appendices/AppendixB.tex
more spaces

@@
 \end{equation}
-
 Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian.
@@
 \end{align}
-
 Where we omitted the band number. The action of the new Hamiltonian is greatly simplified:
@@
 \end{align*}
-
 And so, the matrix elements as in the case without field except for a phase:
@@
 \end{equation}
-
 When the field can be approximated as constant along the lattice we have: $e^{i\frac{e}{\hbar}\int_{\bs{R}_j}^{\bs{R}_i} d\bs{r}'\cdot\bs{A}(\bs{r}',t)} = e^{i\frac{e}{\hbar} (\bs{R}_i-\bs{R}_j)\cdot \bs{A}(t)}$.
@@
 \end{align*}
-
 Therefore relation \ref{PeierlsMtxElem} still holds.

### 2019-04-25 Appendices/AppendixD.tex
more spaces

@@
 \end{equation}
-
 Where $i$ labels sites in sublattice A and $\bs{\delta}$ are the NN vectors, we make an abuse of notation by summing $i+\bs{\delta}$ referring, of course, to the site at position $\bs{R}_i+\bs{\delta}$.
@@
 \end{align}
-
 Then \ref{TBHex} reads:
@@
 \end{align*}
-
 Where $\psi(\bs{k}) = \left( \hat{a}_{\bs{k}}, \hat{b}_{\bs{k}} \right)^T$ and:
@@
 \end{equation}
-
 being $f(\bs{k}) = -t\sum_{\bs{\delta}} e^{i\bs{k}\cdot\bs{\delta}}$.
@@
 \end{equation}
-
 The bands will cross, or equivalently the band gap will vanish if $f(\bs{k})=0$ has a solution, which it does at the corners of the first Brillouin zone, i.e. the points:
@@
 \end{align*}
-
 Where $a$ is the lattice constant. The other corner points are equivalent to either one of these (that is, they can be obtained by a translation of a reciprocal lattice vector).
@@
 \end{equation}
-
 Now,
@@
 \end{equation}
-
 We can ignore the phase and write:
@@
 \end{equation}
-
 Where $v_F = \frac{3at}{2}$. This result is usually written in terms of Pauli matrices as:
@@
 \end{equation}
-
 We can write this more compactly as $h(\bs{K}+\bs{q}) = v_F \left(\bs{q}\cdot\bs{\sigma}\right)^*$.

### 2019-04-25 Appendices/AppendixE.tex
more spaces

@@
 \end{equation}
-
 The Floquet theorem states that the eigenstates for the time evolution operator for one period, $\hat{U}(t+T,t)$ can be written as:
@@
 \end{equation}
-
 Where $\ket{u_n(t+T)} = \ket{u_n(t)}$ is a periodic function, called Floquet mode, and $\epsilon_n$ is a real number known as the quasienergy.
@@
 \end{align*}
-
 Which means that $a_n(t') = a_n(t)$, so the eigenvalue does not depend on time, and since it is an eigenvalue of an unitary operator it can be written as $a_n = a_n(t) = e^{-i\epsilon_nT}$ for certain real number $\epsilon_n$.
@@
 \end{align*}
-
 For $\ket{u_n(t)} = e^{i\epsilon_nt} \ket{\psi_n(t)} = \ket{u_n(t+T)}$, and this proves the theorem.
@@
 \end{equation}
-
 Therefore the time evolution of a superposition of Floquet states will be determined by two different contributions:
@@
 \end{itemize} 
-
 It is interesting to study these two time dependencies separately. With his purpose we define the micromotion operator and the Floquet Hamiltnian. The micromotion operator is defined as:
@@
 \end{equation}
-
 This can be regarded as an eigenvalue problem in the space $\mathcal{F}=\mathcal{H}\otimes\mathcal{L}_T$, where $\mathcal{L}_T$ is the space of square integrable T-periodic functions.
@@
 \end{equation}
-
 An orthonormal basis for the extended Hilbert space can be obtained as the direct product of an orthonormal basis of $\mathcal{H}$ and $\mathcal{L}_T$.
@@
 \end{align}
-
 Where
@@
 \end{align}
-
 The goal is to find $\hat{U}(t)$ such that the transformed quasienergy operator $\hat{Q}'$ is block diagonal in the photon number.

### 2019-04-25 Chapters/Chap3/HWithSoi.tex
more spaces

@@
 \end{equation}
-
 The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI.
@@
 \end{align}
-
 Using $\bs{\Delta}_{ji} = - \bs{\Delta}_{ij}$:
@@
 \end{align*}
-
 The term proportional to $t_0^2$ will lead to the modified exchange interaction, as in the previous section.
@@
 \end{align*}
-
 Where we used relations \ref{SpinRel1}, \ref{SpinRel2} and \ref{SpinRel3}. We have:
@@
 \end{align}
-
 We can see that since we only considered NN hopping processes, all the terms in the spin Hamiltonian are renormalized in the same way by the laser field (as in \cite{Stepanov2017}).

### 2019-04-25 Chapters/Chap3/ModelsNNN.tex
more spaces

@@
 \end{align}
-
 Where $\Delta$ is the intrinsic spin orbit coupling constant.
@@
 \end{equation}
-
 With and:
@@
 \end{align*}
-
 according to \ref{JGeneral} and \ref{GammaGeneral}. Notice that:
@@
 \end{equation*}
-
 This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors.
@@
 \end{equation}
-
 \begin{figure}
@@
 \end{equation}
-
 Where:
@@
 \end{align*}
-
 Such a Hamiltonian was first proposed by S.
@@
 \end{align}
-
 $\langle i,j \rangle ^*$ denotes sum over NN avoiding repeating the same two sites. The coupling factors are:
@@
 \begin{align}
-J_{n,ij} &= 4\frac{t_n^2}{U^*_{ij}} \\
-\bs{D}_{n,ij} &= 8\frac{t_n i\bs{\Delta}_{n,ij}}{U^*_{ij}} \\
-\Gamma_{n,ij}^{\alpha \beta} &= \frac{4}{U^*_{ij}}(\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )
+J_{n,ij} &= 4\frac{t_n^2}{\text{U}^*_{ij}} \\
+\bs{D}_{n,ij} &= 8\frac{t_n i\bs{\Delta}_{n,ij}}{\text{U}^*_{ij}} \\
+\Gamma_{n,ij}^{\alpha \beta} &= \frac{4}{\text{U}^*_{ij}}(\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )
 \end{align}
-
 Where:
@@
 \begin{equation}
-\frac{1}{U^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} \right)
+\frac{1}{\text{U}^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} \right)
 \end{equation}
-
+We thus see that, again, the effect of a static electric field can be taken into consideration by a renormalization of the onsite interaction $\text{U}_{ij}^*$.
 \end{subsection}

### 2019-04-25 Chapters/Chap3/Numerics.tex
Figure2 changes
cdots and spaces
more spaces

@@
 \label{Numerics}
+
+In this section we will make a short numerical study of the analytic results obtained in the previous sections.
+Additionally, for the one dimensional spin chain we will show the tilting angle between spins in presence of DMI, $\theta$ can be controlled with the laser field.
 
@@
 \end{equation}
-
 and the energy is minimized for $\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})$, i.e.
@@
 \end{align}
-
 Where $\bs{D}_{2,ij} = \hat{e}_z D_{2,ij}$ and where $J_{1,ij}^0 = J_{1}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = -\frac{4t_2\Delta\nu_{ij}}{\text{U}}$.
@@
 \end{align}
-
 In each case the absolute vale is independent of $i,j$.
@@
   %\centering
-  \includegraphics[width=1\linewidth]{Figures/NNvsNNN.pdf}
+  \includegraphics[width=1\linewidth]{Figures/NNvsNNN1.pdf}
   \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$.
@@
 \begin{align}
-\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{r}), \sin(\bs{Q}\bs{r}), 0 \right) \\
-\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{r} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
+\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\cdot\bs{r}), \sin(\bs{Q}\cdot\bs{r}), 0 \right) \\
+\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\cdot\bs{r} + \theta), \sin(\bs{Q}\cdot\bs{r} + \theta), 0 \right)
 \end{align}
-
 The $1, 2$ subindex stands for the sublattice.
@@
 \end{align}
-
 Notice that when the spins are constrained in the $\hat{e}_x, \hat{e}_y$ plane, the anisotropic interaction $\bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j$ becomes a ferromagnetic interaction.

### 2019-04-25 Chapters/Chap3/TDHeff.tex
more spaces

@@
 \end{equation}
-
 Where $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\hat{T}$ is any hopping operator.
@@
 \end{equation}
-
 Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$.
@@
 \end{equation}
-
 With $\alpha_{ij} = \pm|e\bs{R}_{ij}\vec{A}|$ in such a way that:
@@
 \end{align}
-
 and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
@@
 \end{align*}
-
 Where we defined
@@
 \end{equation}
-
 Which is the \textit{m}th Fourier mode of the hopping term and $\mathcal{J}_m(x)$ is the \textit{m}th Bessel function \cite{Kitamura2017}.
@@
 \end{equation}
-
 Where $\hat{T}_{dm}(t)$ changes the doublon number by $d$, for example, if $\hat{P}_d$ is the projection operator into the subspace with doublon number $d$, then $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
@@
 \end{equation} 
-
 We perform the unitary transformation perturbatively in the hopping operator, we can formally write $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ will play the role of a bookkeeping parameter in the perturbative expansion.
@@
 \end{equation}
-
 where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
@@
 \end{equation}
-
 Derived in appendix \ref{AP3B}, where $\text{ad}_A(B) = [A,B]$ to rewrite the transformed Hamiltonian as:
@@
 \end{equation}
-
 Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:
@@
 \end{equation}
-
 Now, in this expression we have to expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
@@
 \end{equation}
-
 Which is indeed diagonal in the doublon number, and therefore we can take $i\hat{S}^{(0)}(t)=0$.
@@
 \end{align}
-
 This equation holds up to order $\eta^2$. In first order we obtain:
@@
 \end{equation}
-
 Now we expanding in $m,d$ and use $\left[ \hat{D}, \hat{S}^{(\nu)}_{dm} \right] = d\hat{S}^{(\nu)}_{dm}$ because $\hat{S}^{(\nu)}_{dm}$ changes the doublon number by $d$:
@@
 \end{equation}
-
 Therefore:
@@
 \end{align}
-
 To second order we find:
@@
 \end{align}
-
 Using \ref{1stO} and using $\left[ i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t)\right] = 0$ due to different Fourier modes of the hopping operator being equal up to a constant (explain better), we can rewrite:
@@
 \end{equation}
-
 Using \ref{1stOSpin} and \ref{1stOH}, the middle term is:
@@
 \end{align*}
-
 Altogether:
@@
 \end{align*}
-
 By choosing $i\hat{S}^{(2)}_{dm}$ such that the transformed Hamiltonian is block-diagonal, we obtain:
@@
 \end{align}
-
 Now the effective Hamiltonian acts on the subspace of $d=0$ (zero double occupancies), therefore we are only interested on the block $\hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0$ (notice that $\hat{P}_0 \hat{H}'^{(1)}(t) \hat{P}_0 = 0$).
@@
 \end{align}
-
 Now, since the hopping operators act on the subspace $d=0$ and must remain within that subspace, therefore $\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0$ will be a sum of all possible hoppings between two different sites:
@@
 \end{align*}
-
 Where $a$ and $b$ are any two Fourier modes.
@@
 \end{align}
-
 Where we defined:
@@
 \end{equation}
-
 In the following sections we will use this effective Hamiltonian for different models of the hopping operator.
@@
 \end{equation}
-
 Therefore, there will be only two Fourier modes with frequency $\omega_0 = e \vec{\bs{R}}_{ij} \cdot \vec{\bs{E}} = \pm eaE_0$, where the sign $+(-)$ corresponds to the case $\vec{\bs{R}}_{ij} = \pm a \hat{e}_x$.
@@
 \end{itemize}
-
 Taking this into consideration we see that only $m=0$ terms will remain, which is consistent with the fact that the two phases cancel out in the process $i \rightarrow j \rightarrow i$.

### 2019-04-25 Chapters/Chapter4.tex
more spaces

@@
-\chapter{Perturbing the lattice}
+\chapter{Laser illumination}
 \label{ChapPerturbing}
@@
 \end{equation*} 
-
 In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role.
@@
 \end{equation*}
-
 Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.

### 2019-04-25 Chapters/Chapter5.tex
cdots and spaces
more spaces

@@
 \label{Heisenberg}
-\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j
+\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i\cdot \bs{S}_j
 \end{equation}
-
 In order to obtain the magnon Hamiltonian for this model we introduce the antiferromagnet Holstein-Primakoff transformation:
@@
 \end{align}
-
 Where $A$ and $B$ denote two Ne\'{e}l sublattices and $\hat{a}_i$, $\hat{b}_i$ are bosonic annihilation operators.
@@
 \begin{align*}
-\bs{S}_i\bs{S}_j = S_i^zS_j^z + \frac{1}{2}\left(S_i^+S_j^- + S_i^-S_j^+ \right) = S \left( \hat{a}^\dagger_i \hat{a}_i + \hat{b}^\dagger_j \hat{b}_j + \hat{a}_i\hat{b}_j + \hat{a}^\dagger_i\hat{b}^\dagger_j \right) - \hat{a}^\dagger_i \hat{a}_i\hat{b}^\dagger_j \hat{b}_j - S^2
+\bs{S}_i\cdot\bs{S}_j = S_i^zS_j^z + \frac{1}{2}\left(S_i^+S_j^- + S_i^-S_j^+ \right) = S \left( \hat{a}^\dagger_i \hat{a}_i + \hat{b}^\dagger_j \hat{b}_j + \hat{a}_i\hat{b}_j + \hat{a}^\dagger_i\hat{b}^\dagger_j \right) - \hat{a}^\dagger_i \hat{a}_i\hat{b}^\dagger_j \hat{b}_j - S^2
 \end{align*}
-
 Now the $S^2$ term is a constant that lowers the energy of the antiferromagnet, therefore is shall not be taken into account to compute the magnon dispersion.
@@
 \end{equation}
-
 Where $\delta$ are the NN vectors. Using this, and the Fourier relations:
@@
 \end{align}
-
 Where the sum is over $\bs{k}$ in the first Brillouin zone.
@@
 \begin{equation}
-\hat{H} = -S^2JNz + 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
+\hat{H} = -S^2JNz + 2JS \sum_{\bs{k} \bs{\delta}} \left( \hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \hat{b}^\dagger_{\bs{k}}\hat{b}_{\bs{k}} + e^{i\bs{k}\cdot\bs{\delta}}\hat{a}_{\bs{k}}\hat{b}_{\bs{-k}} + e^{-i \bs{k}\cdot\bs{\delta}}  \hat{a}^\dagger_{\bs{k}}\hat{b}^\dagger_{-\bs{k}} \right)
 \end{equation}
-
 At this point it is common to define $\gamma_{\bs{k}} = \sum_\delta e^{i \bs{k} \cdot \bs{\delta}}$.
@@
 \end{equation}
-
 Which can be written in matrix form as:
@@
 \end{equation}
-
 Acting on the spinor $\Psi_{\bs{k}} = \left(\hat{a}_{\bs{k}},\hat{b}_{-\bs{k}}^\dagger \right)^T$.
@@
 \end{equation}
-
 Where $u_{\bs{k}}$ and $v_{\bs{k}}$ are complex functions satisfying $\abs{u_{\bs{k}}}^2-\abs{v_{\bs{k}}}^2 = 1$ in order to perserve the bosonic commutation relations.
@@
 \end{equation}
-
 Inserting this in \ref{MagnonicH} and ignoring constant terms we get:
@@
 \end{align}
-
 Therefore, in order to erase the non diagonal terms we impose:
@@
 \end{align}
-
 Where $\theta_{\bs{k}}$ and $\xi_{\bs{k}}$ are real functions to be determined. Introducing these relations in \ref{condition}:
@@
 \end{equation}
-
 By taking $\xi_{\bs{k}}$ to be the phase of $\gamma_{\bs{k}}$, i.e. $\gamma_{\bs{k}} = \abs{\gamma_{\bs{k}}} e^{i\xi_{\bs{k}}}$ we get a real equation on $\theta_{\bs{k}}$. Altogether we find:
@@
 \end{align}
-
 This erases the non diagonal terms in \ref{AfterBogo} leading to a diagonal term:
@@
 \end{equation}
-
 With this, we can rewrite \ref{AfterBogo} as:
@@
 \end{align}
-
 Where we used $\sum_{\bs{k}}=\frac{N}{2}$ and where $\epsilon_{\bs{k}} = 2JS \sqrt{z^2-\abs{\gamma_{\bs{k}}}^2}$. The ground state energy of this magnon Hamiltonian is:
@@
 \begin{equation}
-\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i \bs{S}_j + D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j
+\hat{H} = J \sum_{\langle i j \rangle} \bs{S}_i\cdot \bs{S}_j + D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z\cdot \bs{S}_i \times \bs{S}_j
 \end{equation}
-
 The NNN DMI term will couple spins within the same sublattice. Using the HP transformation:
@@
 \end{equation}
-
 Now we will make the sum over NNN in the following way:
@@
 \end{equation}
-
 Where $\bs{\delta}^{NNN}$ are the NNN vectors (as depicted in Fig \ref{Fig.Magnon.Vecs}):
@@
 \begin{equation}
-D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
+D \sum_{\langle \langle i j \rangle \rangle} \nu_{ij}\hat{e}_z \cdot\bs{S}_i \times \bs{S}_j = 2JS\sum_{\bs{k}} \left\{ \Delta_{\bs{k}}\hat{a}^\dagger_{\bs{k}}\hat{a}_{\bs{k}} + \Delta_{-\bs{k}}\hat{b}^\dagger_{-\bs{k}}\hat{b}_{-\bs{k}} \right\}
 \end{equation}
-
 Where $\Delta_{\bs{k}} = \frac{Di}{2J}\sum_{\bs{\delta}^{NNN}} \nu_{i,i+\delta} (e^{i\bs{k}\cdot\bs{\delta}} -e^{-i\bs{k}\cdot\bs{\delta}})$, for $i$ in the $A$ sublattice. This can be rewritten as:
@@
 \end{equation}
-
 Note that $\Delta_{\bs{k}}=-\Delta_{-\bs{k}}$ .The full magnonic Hamiltonian now is:
@@
 \end{equation}
-
 Or:
@@
 \end{equation}
-
 In this case, applying the transformation \ref{Bogoliubov} leads to the same condition for the coefficients  $u_{\bs{k}}$ and $v_{\bs{k}}$, leading to:
@@
 \end{align*}
-
 Where we already took \ref{Bogou} and \ref{Bogov}.
@@
 \end{align}
-
 The new term $\pm \Delta_{\bs{k}}$ breaks the degeneracy between the $\alpha$ modes and the $\beta$ modes. In Figure \ref{Fig.Magnon.Disp} we plot the resulting energy dispersion of \ref{DispWithDMI}.
@@
 \end{align*}
-
 Where we defined:
@@
 \end{equation}
-
 This is the same as \ref{MatrixMagnonDMI} if we replace $z \rightarrow z + \tilde{\Gamma}_{\bs{k}}$, therefore the magnon Hamiltonian is:
@@
 \end{align}
-
 This concludes our discussion of the magnons in the models derived in the last Chapter.

### 2019-04-27 Appendices/AppendixE.tex
reading over 1-3

@@
 
-We introduce a unitary transformation $\hat{U}(t)=\sum_m e^{im\omega t}\hat{U}_m$, $\hat{Q} \rightarrow \hat{Q}'=\hat{U}^{\dagger}(t)\hat{Q}\hat{U}(t)$ or:
+We introduce a unitary transformation $\hat{U}(t)=\sum_m e^{im\omega t}\hat{U}_m$, that transforms the quasienergy operator $\hat{Q} \rightarrow \hat{Q}'=\hat{U}^{\dagger}(t)\hat{Q}\hat{U}(t)$ or:
 
@@
 Using \ref{QOmatelem} we notice that this requirement is equivalent to the requirement that the transformed Hamiltonian $\hat{H}'(t)$ is time independent.
+Different techniques can be employed for determining the transformation $\hat{U}(t)$.
+In \cite{Eckardt2015} degenerate perturbation theory is used for this end.

### 2019-04-27 Chapters/Chap3/TDHeff.tex
reading over 1-3

@@
 \begin{equation}
+\label{TimeDepHopping}
 t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\cdot\bs{A}(t)}
 \end{equation}
-Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$.
+Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$ and we take $\hbar=1$.
 We write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, where $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
 The vector potential takes the form $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.
+With the hopping amplitudes in \ref{TimeDepHopping} the Hamiltonian becomes time dependent. We will use Floquet theory \ref{APE} to derive an effective Hamiltonian including the laser perturbation.
 

### 2019-04-27 Chapters/Chapter1.tex
reading over 1-3

@@
 N\'eel who introduced a thermodynamic theory following the Weiss's model of a local molecular field.
-This made it possible to explain the antiferromagnetic order and it predicted the existence of a temperature above which this order vanishes.
+This made it possible to describe the antiferromagnetic order and it predicted the existence of a temperature above which this order vanishes.
 This temperature is known as N\'eel temperature.
-Later N\'eel proposed the picture of a magnetic order where two sublattices were magnetised in opposite directions.
+Later N\'eel proposed the picture of a magnetic order where two sublattices were magnetized in opposite directions.
 During the same period, Lev Landau developed a phenomenological model using a combination of two antiferromagnetically coupled ferromagnetic layers.
 
-The discovery of the giant magnetoresistance effect by P.
+In the 80s, the discovery of the giant magnetoresistance effect by P.
 Grünberg \cite{Binasch1989} and A.
-Fert \cite{Baibich1988} in the 80s opened the gate for a new field of study known as spinotronics, in which electron spin is exploited in improved electronic devices.
+Fert \cite{Baibich1988} opened the gate for a new field of study known as spinotronics, in which electron spin is exploited in improved electronic devices.
 Magnetoresistive random-access memory (MRAM) is an example of a new type of memory in which data is stored in magnetic elements \citep{Akerman2005}.
@@
 
-However, so far, in most current spinotronic devices antiferromagnets play only a minor role.
-During several decades after the discovery of antiferromagnetics, these materials were percived as useless from a practical point of view.
+However, so far, in most spinotronic devices antiferromagnets play only a minor role.
+During several decades after the discovery of antiferromagnetics, these materials were perceived as useless from a practical point of view.
 On contrast, ferromagnets have been widely studied historically for its technical applications.
@@
 We apply this technique to some more specific, well-known models, such as the Kane-Mele-Hubbard model.
+Lastly, in Chapter \ref{SpinWave} we use spin wave theory to study the magnon dispersion of the Hamiltonians we derived in the previous Chapters.

### 2019-04-27 Chapters/Chapter2.tex
reading over 1-3

@@
 In the opposite limit, we can consider systems in which the ion potential is so large that the electrons are bound in the cores with occasional jumps from site to site.
-This is known as tight binding model and it can be used to study a wide variety of solids.
+This is known as tight binding model and it can be used to study a wide variety of solids \cite{Ashcroft}.
 It is typically used for calculations of the electronic band structure.
@@
 An electron localized around the atom at $\bs{r}_n$ will mainly feel the potential of that atom, and the potential of the rest of the atoms will be a perturbation to the free atom problem.
-That is, we can spit \ref{CrystalHam} into:
+That is, we can split \ref{CrystalHam} into:
 \begin{equation}
@@
 \end{equation}
-Now, the Bloch theorem states that an eigenfunction of the crystal Hamiltonian should only change by a phase from site to site, that is $\psi_i(\bs{r}+\bs{r}_m)=e^{i \bs{k} \cdot \bs{r}_m}\psi_i(\bs{r})$, where $\bs{k}$ is the crystal momentum of the Bloch wave.
+Now, the Bloch theorem (we shall provide a short proof of this theorem in the next Chapter) states that an eigenfunction of the crystal Hamiltonian should only change by a phase from site to site, that is $\psi_i(\bs{r}+\bs{r}_m)=e^{i \bs{k} \cdot \bs{r}_m}\psi_i(\bs{r})$, where $\bs{k}$ is the crystal momentum of the Bloch wave.
 We can see that see implies $b_i(\bs{r}_m) = e^{i \bs{k} \cdot \bs{r}_m}b_i(0)$, by normalizing $\psi_i(\bs{r})$ we find $b_i(0) = \frac{1}{\sqrt{N}}$, where $N$ is the number of atoms in the crystal.
@@
 However, it exhibits much richer phenomena.
-It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e.
-they should be conductors according to band theory, but electron-electron interactions keep away from).
+It can be considered an impoved tight binding model.
+For example, it describes Mott insulators, materials which should be conductors according to band theory, but electron-electron interactions keep away from.
+Transitions from the Mott insulator phase to a metallic phase can also be understood in this framework \cite{Katsnelson1984}.
 Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
-Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it.
+Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it \cite{Vitali2019,Giuliani2007}.
 
  Figure \ref{fig:Hubbard} shows a graphical representation of the parameters in \ref{HH}.
-The new term $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
-The half-filled case is most commonly studied, this is the situation where the system has one electron per site (or it has half the maximum allowed number).
+The new term $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, when $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$.
+The half-filled case is most commonly studied, this is the situation where the system has one electron per site (so that the system contains half the maximum allowed number of electrons).
 This situation is simpler in many ways and it exhibits a lot of interesting phenomena (Mott insulating behavior, antiferromagnetic order, etc.).
-However, other cases have also been widely studied.
+However, other cases have also been widely studied \cite{Spalek2007}.
 
@@
 Notice that if we set $\text{U}=0$ in \ref{HH} we recover the tight binding Hamiltonian, therefore we can say that the Hubbard model is an expansion of the tight binding model.
-The opposite limit $t=0$ is more interesting.
+The opposite limit $t=0$ is also interesting.
 In the half-filling case, for $\text{U}>0$ the ground state will be any state with exactly one electron per site.
@@
 The subspace spanned by these states is referred to as low energy subspace, and in this case is has energy $E_0 = 0$.
-If we switch $0 \neq t \ll \text{U}$ this hopping term will allow an even further decrease in energy by allowing virtual processes $i \rightarrow j \rightarrow i$ that localized the electrons withing their neighbor sites.
-For $t \ll \text{U}$ the dynamics of the system can be described withing the low energy subspace only, by doing so we can obtain an effective spin Hamiltonian $\hat{H}_{\text{eff}} = \sum{\langle i,j \rangle} J \bs{S}_i\cdot\bs{S}_j$ where $J>0$ describing an antiferromagnetic system.
+If we switch $0 \neq t \ll \text{U}$ this hopping term will allow a further decrease in energy by allowing virtual processes $i \rightarrow j \rightarrow i$ that delocalize the electrons withing their neighbor sites.
+For $t \ll \text{U}$ the dynamics of the system can be described withing the low energy subspace only, by doing so we can obtain an effective spin Hamiltonian $\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J \bs{S}_i\cdot\bs{S}_j$ where $J>0$ describing an antiferromagnetic system.
 A rigorous derivation of this will be offered in the next Chapter, however we can intuitively understand this result in the following way: the virtual processes $i \rightarrow j \rightarrow i$ will be allowed when the electrons at sites $i$ and $j$ have opposite spin (otherwise it would contradict the Pauli principle), therefore states where neighbor sites have opposite spins will have a lower energy due to the delocalization mechanism.

### 2019-04-27 Chapters/Chapter3.tex
reading over 1-3

@@
 
-In this chapter we will start with a Hamiltonian
+In this chapter we will derive an effective spin Hamiltonian for the low energy subspace of a strongly correlated system described by a Hamiltonian:
 
@@
 If $\Gamma^{\bs{k}}$ is a one dimensional representation and $\ket{\phi_n, \bs{k}}$ is a wavefunction in the energy level $n$ belonging to that representation then $T_{\bs{R}}\ket{\phi_{n, \bs{k}}} = \Gamma^{\bs{k}}(\bs{R}) \ket{\phi_{n, \bs{k}}}$.
-Now, imposing periodic boundary conditions, $\Gamma^{\bs{k}}(\bs{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in \ref{AP1A}.
+Now, imposing periodic boundary conditions, $\Gamma^{\bs{k}}(\bs{a}_\mu)^{L_\mu} = 1$, where $\bs{a}_\mu$ are the primitive translations and $L_\mu$ is the number of lattice sites in the $\mu$ direction as defined in Appendix \ref{AP1A}.
 This can be accomplished if we label the representation with a vector of the first Brillouin zone and have $\Gamma^{\bs{k}}(R) = e^{i \bs{k} \cdot \bs{R}}$.
@@
 However, we would like to work with a localized basis.
-Such a localized basis built by a set of functions known as Wannier functions $\ket{\psi_{in}}$, which defined in terms of the Bloch functions as:
+Such a localized basis can be built by a set of functions known as Wannier functions $\ket{\psi_{in}}$, which are defined in terms of the Bloch functions as:
 
 \begin{align}
-\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\cdot\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
-\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\bs{k}\cdot\bs{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
+\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{N}}\sum_{\bs{R}} e^{i\bs{k}\cdot\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
+\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{N}} \sum_{\bs{k}\in BZ} e^{-i\bs{k}\cdot\bs{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
 \end{align}
-Where $M$ is the number of lattice sites as defined in \ref{AP1A}.
-Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations.
+Where $N$ is the number of lattice sites as defined in Appendix \ref{AP1A}.
+Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$.
+Therefore, we only need to define one Wannier function for each band and the others are obtained by translations.
 From now on we will restrict ourselves to a fixed band, so we will drop the band index.
@@
 Fock states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.
-With these definitions we are ready for write down the second quantized form of \ref{Ham1}, and show some approximations that lead to the Hubbard model.
+With these definitions we are ready to write down the second quantized form of \ref{Ham1}, and show some approximations that eventually lead to the Hubbard model.
 
@@
 
-In this section we will derive the second quantized form of \ref{Ham1} using the Wannier function basis.
+In this section we will derive the second quantized form of \ref{Ham1} using the Wannier functions as a basis.
 Let $\hat{c}_{j \sigma}^\dagger$ and $\hat{c}_{j \sigma}$ create and annihilate a particle in the state $\ket{j\sigma}$.
@@
 We can impose that $t_{ii} = t(0) = 0$ since adding a constant term to all the hopping amplitudes would only lead to a lifting in the zero point energy.
-Additionally, for a system of strongly correlated electrons we can assume that:
+Additionally, for a system of strongly correlated electrons we can make the following approximations:
 
@@
 \item Taking into account the locality of the Wannier functions and the Coulomb interaction, the dominant contribution of $\bra{ij} \hat{v} \ket{kl}$ will come from $i=j=k=l$.
-Terms with $i=k$ and $j=l$ also contribute when $i, j$ are nearest neighbours.
+Terms with $i=k$ and $j=l$ also contribute when $i, j$ are nearest neighbors.
 Therefore we approximate:
@@
 This is illustred in Figure \ref{Fig2.1}.
-A more rigouros derivation of this effective model can be found in \cite{Schuler2013}.
+A more rigouros derivation of this effective approximation can be found in \cite{Schuler2013}.
 Altough $\text{V} < \text{U}$, they can be comparable in magnitude, and $\text{U}^*$ can be reduced by a factor of $0.5$ or more.
@@
 \centering
-  \includegraphics[width=0.5\linewidth]{../Figures/non_local_coulomb.png}
+  \includegraphics[width=0.8\linewidth]{../Figures/non_local_coulomb.png}
   \caption{Image from \cite{Schuler2013}.
@@
 At half filling and in the $t, \bs{\Delta}_{ij} << \text{U}$ limit, which corresponds to the strong coupling limit, we can apply perturbation theory to obtain an effective spin Hamiltonian from the Hubbard model \ref{Hubbard}.
-First notice that in the case $t = 0$ the ground state corresponds to having all sites single-occupied.
-There are two possible spin orientations for each sites, so there is a $2^M$ degeneracy.
-The ground state energy is $0$.
+First notice that in the case $t = 0$ the ground state corresponds to a state where all sites are single-occupied.
+There are two possible spin orientations for each sites, so there is a $2^N$ degeneracy.
+The ground state energy is $E_0=0$.
 The first exited states are obtained by moving one electron from one site to another, thus leaving one empty site and one double-occupied site.
-The energy of one of these states is $\text{U}$.
-Now, if we turn the kinetic term on as a perturbation, having two neighbors electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas while being parallel this hopping is not allowed and there is no energy reduction.
-Therefore, we can see that when turning the kinetic term on antiparallel alignment will be favored.
+The energy of one of these states is $E_1=\text{U}$.
+Now, if we turn the kinetic term on as a perturbation, having two neighbor electrons with antiparallel spin will allow them to hop and reduce the kinetic energy, whereas if the two neighbor electrons have parallel spins, this hopping is not allowed and there is not such an energy reduction.
+Therefore, we can see that when turning the kinetic term on, antiparallel alignment will be favored.
 
+Now we will apply perturbation theory to find an effective Hamiltonian for the low energy subspace.
 Let us write $\hat{H} = \hat{H}_0 + \hat{H}_t$, where $\hat{H}_0$ is the Hamiltonian for $t=0$ i.e.
 $\hat{H}_0 = \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and $\hat{H_t} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t + \bs{\Delta}_{ij}\cdot \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and in first order in $t$ $\bra{\phi'} \hat{H} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
+Let $\ket{\phi}$ and $\ket{\phi'}$ be states from the ground state of $\hat{H}_0$, then we know that $\bra{\phi'} \hat{H_0} \ket{\phi} = 0$ and the first order correction to this energy vanishes $\bra{\phi'} \hat{H}^{(1)} \ket{\phi} = \bra{\phi'} \hat{H_t} \ket{\phi} = 0$ since $\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma}$ moves an electron from site $j$ to $i$ thus leaving $i$ doubly occupied, therefore $\hat{H_t} \ket{\phi}$ has no superposition with $\phi'$.
 In second order we have:
@@
 \begin{equation}
-\bra{\phi'} \hat{H} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
+\bra{\phi'} \hat{H}^{(2)} \ket{\phi} = \sum_s \frac{\bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi}}{E_0-E_s}
 \end{equation}
@@
 Since $\hat{H_t}\ket{\phi}$ is a superposition of states with exactly one double occupied site and one empty site, we see that only excited states with one double occupied site will contribute.
-These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
+These states have energy $E_s = \text{U}$ therefore we have $\bra{\phi'} \hat{H}^{(2)} \ket{\phi} = -\frac{1}{\text{U}}\sum_s \bra{\phi'} \hat{H_t} \ket{s}\bra{s} \hat{H_t} \ket{\phi} = \bra{\phi'} -\frac{\hat{H_t^2}}{\text{U}} \ket{\phi}$.
 This means that within the subspace generated by the ground states of $\hat{H_0}$, $\hat{H}$ acts as an effective Hamiltonian $\hat{H}_{\text{eff}} = -\frac{\hat{H_t^2}}{\text{U}}$.
@@
 \hat{H}_J &= -\frac{t^2}{\text{U}} \sum_{\langle i,j \rangle, \sigma, \sigma'} \hat{c}_{i\sigma}^\dagger \hat{c}_{i\sigma'} \hat{c}_{j\sigma} \hat{c}_{j \sigma'}^\dagger \label{C3HJ} \\
-\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HD}\\
-\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HP}
+\hat{H}_D &= -\frac{t}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} \bs{\Delta}_{ij}\cdot(\delta_{\sigma_3 \sigma_4}	\bs{\sigma}_{\sigma_1 \sigma_2} - \delta_{\sigma_1 \sigma_2} \bs{\sigma}_{\sigma_3 	\sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HD}\\
+\hat{H}_P &= \frac{1}{\text{U}}\sum_{\langle i,j \rangle, \sigma_1, \sigma_2, \sigma_3, \sigma_4} (\bs{\Delta}_{ij}\cdot\bs{\sigma}_{\sigma_1 \sigma_2})(\bs{\Delta}_{ij} \cdot\bs{\sigma}_{\sigma_3 \sigma_4}) \hat{c}_{i\sigma_1}^\dagger \hat{c}_{i\sigma_4} \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \label{C3HP}
 \end{align}
@@
 \end{align}
-In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show two important relations. First:
+In the half-filling case we have $n_{i \uparrow} + n_{i \downarrow} = 1$ and we can show three important relations. First:
 
@@
 \end{align*}
-With $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
+Where $ \bs{\Gamma}_{ij}$ is a tensor with components $\bs{\Gamma_{ij}}^{\alpha \beta} = \frac{1}{\text{U}}(\delta_{\alpha \beta} 2\bs{\Delta}_{ij}^2 - 4\Delta_{ij}^\alpha\Delta_{ij}^\beta)$.
 The total effective Hamiltonian is:
@@
 In the next chapter we will introduce next nearest neighbor (NNN) hopping (both kinetic and SOI), this will lead to NNN spin interactions.
-As an introduction to this, in the next subsection we show the effect of introducing NNN kinetic hopping in the Heisenberg model.
+As an introduction to this, in the next subsection we show the effect of introducing NNN kinetic hopping in the Hubbard model without SOI.
 
@@
 \end{equation}
-Where $J_1 = \frac{t_1^2}{\text{U}}$ and $J_2 = \frac{t_2^2}{\text{U}}$.
+Where $J_1 = \frac{2t_1^2}{\text{U}}$ and $J_2 = \frac{2t_2^2}{\text{U}}$.
 This Hamiltonian is known as $J_1-J_2$ Heisenberg model.
@@
 Notice that we can also obtain a $J_1-J_2$ Heisenberg model starting simply from a NN hamiltonian $\hat{H} = -\sum_{\langle i,j \rangle, \sigma}t_{1}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$.
-This is because the NNN exchange interaction comes from the possibility of the process $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ being $i,j$ NNN.
+This is because the NNN exchange interaction comes from the possibility of the process $i\sigma \rightarrow j\sigma \rightarrow i\sigma$ where $i,j$ are next nearest neighbours.
 This process is available when sites $i, j$ have opposite spins (otherwise it would violate the Pauli principle).
@@
 \end{equation}
-Where $\epsilon_i$ are random variable $\epsilon_i \in [-W,W]$.
+Where $\epsilon_i$ are random variables $\epsilon_i \in [-W,W]$.
 At half filling we can derive an effective Hamiltonian using the same procedure as before.

### 2019-04-27 Chapters/Chap3/HNoSoi.tex
cdots and spaces
til hnosoi

@@
 \label{Section3Hubbard}
-We start by considering the simplest hopping operator, as in the Hubbard model:
+We start by considering the simplest hopping operator, excluding SOI terms \ref{HnoSOI}:
 
@@
 
-Which is the Hamiltonian \ref{Hubbard} without DMI interaction.
-We see that the hopping amplitudes introduced in the previous section take the form $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'} t_0$ for $i,j$ being nearest neighbors, and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
+We see that the hopping amplitudes introduced in the previous section can be written as $t_{ij}^{\sigma \sigma'} = \delta_{\sigma \sigma'} t_0$ for $i,j$ being nearest neighbors, and $t_{ij}^{\sigma \sigma'} = 0$ otherwise.
 With this we can directly apply \ref{HeffSimplified} to obtain:
@@
 \begin{align*}
-\sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} = \sum_{\sigma, \sigma'} \left( \frac{\delta_{\sigma \sigma'}}{2} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma} \right) \left( \frac{\delta_{\sigma \sigma'}}{2} - \bs{S}_j\bs{\sigma}_{\sigma \sigma'} \right) = -2\bs{S}_i \bs{S}_j
+\sum_{\sigma, \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \hat{c}_{j \sigma'}^\dagger \hat{c}_{i \sigma'} = \sum_{\sigma, \sigma'} \left( \frac{\delta_{\sigma \sigma'}}{2} + \bs{S}_i\cdot\bs{\sigma}_{\sigma' \sigma} \right) \left( \frac{\delta_{\sigma \sigma'}}{2} - \bs{S}_j\cdot\bs{\sigma}_{\sigma \sigma'} \right) = -2\bs{S}_i\cdot \bs{S}_j
 \end{align*}
@@
 \begin{equation}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j
+\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \cdot \bs{S}_j
 \end{equation}
@@
 \label{MFactorApprox0}
-\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
 \end{equation}
@@
 \label{MFactorApprox}
-\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx 2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right)
+\mathcal{M}(\alpha_{ij}, \text{U}, \omega) \approx 2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right)
 \end{equation}
@@
 
+Notice that this result is independent of the helicity of the applied field, this is true even if we do not make the approximation \ref{MFactorApprox}.
+
 \begin{subsection}{Honeycomb lattice}
@@
 \begin{align}
-\Phi &= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j = \nonumber \\
-&= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i \bs{S}_j + |\vec{E}_0|^2 \frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \bs{S}_j
+\Phi &= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \cdot \bs{S}_j = \nonumber \\
+&= \Phi_0 + \sum_{\langle i,j \rangle} J_{ij}^0 \bs{S}_i \cdot \bs{S}_j + |\vec{E}_0|^2 \frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \cdot \bs{S}_j
 \end{align}
@@
 \begin{equation}
-\epsilon = \epsilon^0 + 2\frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \bs{S}_j
+\epsilon = \epsilon^0 + 2\frac{t_0^2 e^2 a^2}{\omega}\left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)\sum_{\langle i,j \rangle} \bs{S}_i \cdot \bs{S}_j
 \end{equation}

### 2019-04-27 Chapters/Chap3/TDHeff.tex
til hnosoi

@@
 In terms of on-site creation and annihilation operators we can write the hopping operator as $\hat{T} = \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}$.
-The strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
+For a strongly correlated system, the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitude, therefore, in a half filling system the zero double occupancies subspace $d=0$ can be taken as the low energy subspace in which the effective Hamiltonian will act.
+
+The doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$, has eigenvalues positive integers $d$, corresponding to states with exactly $d$ double occupancies (doublons).
+For later use, we define $\hat{P}_d$ as the projection operator onto the subspace spanned by states with eigenvalue $d$, i.e., states with exactly $d$ doublons.
+At site $i$, we can define the projection operator to the double occupied state as $\hat{P}_{i,1} = \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and the projection operator to the complementary space as $\hat{P}_{i,0} = 1 - \hat{P}_{i,1}$ \cite{Fazekas}.
+We can then define the projection operator $\hat{P}_{d}$ for the whole system as follows.
+Let $\mathcal{O}$ and $\mathcal{P}^d(\mathcal{O})$ denote the set of sites on the lattice and the set of subsets of $\mathcal{O}$ with exactly $d$ elements, respectively.
+Then, in compact form, the projection operator reads $\hat{P}_d = \sum_{A \in \mathcal{P}^d(\mathcal{O})} \left\{\prod_{i \in A} \hat{P}_{i,1} \prod_{i \notin A} \hat{P}_{i,0} \right\}$.
 
 The effect of the electromagnetic perturbation in the lattice can be introduced via the Peierls substitution (\ref{AP3A}).
-With this notation, in presence of a vector potential $\vec{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:
+With this notation, in presence of a vector potential $\bs{A}(t)$ (which we assume to not vary noticeably in the scale of the lattice) the Peierls substitution leads to an extra time dependent phase in the hopping amplitude:
 
@@
 \end{equation}
-Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$ and we take $\hbar=1$.
+Where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $e$ is the electronic charge and we take $\hbar=1$.
 We write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, where $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively.
@@
 
-Let us define:
+First, let us define:
 
@@
 \end{align}
-and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion:
+and $\theta_{ij} \in \left[0,\pi\right)$. Then we can apply the Jacobi–Anger expansion \cite{Korsch2006}:
 
@@
 This is the same effective Hamiltonian obtained in the previous section without an electric field but with a shift in the intermediate state energy by $\pm \omega_0 = \pm eaE_0$.
+This can be easily interpreted physically, the processes with intermediate energy $\text{U}+\omega_0$ correspond to processes in which an electron 'climbs up' the electric potential and then 'falls down' so that the intermediate energy is raised by the potential energy gained in the process; processes with intermediate energy $\text{U}-\omega_0$ correspond to the opposite process.
 We will analyze the corresponding spin Hamiltonian of this effective Hamiltonian when we consider the Kane-Mele-Hubbard model in Section \ref{section3NNN}.

### 2019-04-27 Chapters/Chapter4.tex
til hnosoi

@@
 
-\begin{equation*}
+\begin{equation}
+\label{HnoSOI}
 \hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
-\end{equation*} 
+\end{equation} 
 In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role.
@@
 In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions.
-The simplest model with spin orbit interaction is \ref{Hubbard}:
+The simplest model with spin orbit interaction is the one we derived in the previous Chapter, \ref{Hubbard}:
 
@@
 \end{equation*}
-Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.
+Which is the same as \ref{HnoSOI} plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$.
 In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
 
-In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure describing a topological insulator.
+In the case of graphene or other coplanar honeycomb lattice structures, nearest neighbor Rashba terms are not allowed by symmetry, and only next nearest neighbor (NNN) spin conserving terms contribute \cite{Kane2005}, this term opens a gap in the band structure thus describing a topological insulator.
 For this case we examine the Kane-Mele-Hubbard model.
 The effective spin model of this Hamiltonian contains the usual exchange interaction and DMI and, in addition, it exhibits anisotropic exchange interaction arising from the intrinsic SOI term.
-This new term has already been obtained in \cite{Rachel2010} without taking into account any electromagnetic field.
+This new term has already been obtained in \cite{Rachel2010} without taking into account any external electromagnetic field.
 
-Non-coplanar honeycomb lattice may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
+Non-coplanar honeycomb lattices may exhibit intrinsic Rashba interactions between NNN \cite{Liu2011}, this, together with a NNN hopping (which would arise from direct overlapping of the next nearest neighbor Wannier functions or from second order processes) will lead to NNN DMI.
 

### 2019-04-29 Appendices/AppendixA.tex
reading over 1-3
minor changes

@@
 
-Here we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
+In this appendix we will introduce some notation. The Bravais lattice in a crystal is the lattice generated by the primitive translations $\bs{a}_\mu$:
 
@@
 The volume of the unit cell is $v = \textbf{a}_1 \cdot (\textbf{a}_2 \times \textbf{a}_3)$.
-The crystal volume is $V = Mv$ where $M = L_1 L_2 L_3$ is the number of lattice sites.
+The crystal volume is $V = Nv$ where $N = L_1 L_2 L_3$ is the number of lattice sites.
 The primitive translations in the reciprocal lattice are defined as $\textbf{b}_1 = \frac{2 \pi}{v}\textbf{a}_2 \times \textbf{a}_3$, etc.
@@
 
-In the next chapters we will also consider the two dimensional honecomb lattice. For this lattice we can choose the primitive translations to be:
+In the next chapters we will also consider the two dimensional honeycomb lattice. For this lattice we can choose the primitive translations to be:
 
@@
 In Fig.
-(b) the reciprocal lattice is shown, toghether with the high symmetry points $K$, $M$ and $K'$.}
+(b) the reciprocal lattice is shown, together with the high symmetry points $K$, $M$ and $K'$.}
 \label{Fig2.2}

### 2019-04-29 Chapters/Chap3/ModelsNNN.tex
minor changes

@@
 In section \ref{Numerics} we will investigate this numerically.
-The reason for this is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\cdot\bs{A}(t)}$ (assuming flat field approximation).
+The reason why the renormalization differs for NN and NNN spin interactions is that in a hopping process, the electron picks up a phase $e^{ie\bs{R}_{ij}\cdot\bs{A}(t)}$ (assuming flat field approximation).
 This phase will be larger for NNN hopping than for NN hopping and this will therefore translate in the corresponding spin interactions.
@@
 \end{figure}
-
 This corresponds to the case $\bs{\Delta}_{1,ij} = 0$ and $\bs{\Delta}_{2,ij} = (0, 0, -i\nu_{ij} \Delta)$ in \ref{BigHam}.
@@
 A.
-Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}.
+Owerre to model honeycomb topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}.
 Experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}.

### 2019-04-29 Chapters/Chap3/Numerics.tex
minor changes

@@
 
-We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\bs{S}_j - \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\bs{S}_i \times \bs{S}_j$.
-This approximated Hamiltonian with no NNN exchange interaction is very simple, but in some systems where it has even been observed that $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018} it can be a good approximation.
+We will start with a one dimensional chain with hamiltonian $\hat{H} = \sum_{\langle i,j \rangle} |J_1| \bs{S}_i\cdot\bs{S}_j - \sum_{\langle \langle i,j \rangle \rangle} \nu_{ij}|D_2|\hat{e}_z\cdot\bs{S}_i \times \bs{S}_j$.
+This approximated Hamiltonian with no NNN exchange interaction is very simple, but in some systems where it has even been observed that $|\bs{D}_{2,ij}| > |J_{2,ij}|$ \cite{Chen2018}, therefore it can be a good approximation to disregard  $|J_{2,ij}|$ with respect to $|\bs{D}_{2,ij}|$.
 We write the absolute values in $|J_1|$ and $|D_2|$ to limit the analysis to the range in which the field does not change the sign of these factors.
@@
 \end{equation}
-and the energy is minimized for $\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})$, i.e.
+and the energy is minimized for 
+\begin{equation}
+\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})
+\end{equation}
+i.e.
 $\theta^* = \theta^*(\frac{J_1}{D_2})$.
@@
 \centering
-\begin{subfigure}{.45\textwidth}
+\begin{subfigure}{.5\textwidth}
   %\centering
@@
 \hspace*{\fill}
-\begin{subfigure}{.45\textwidth}
+\begin{subfigure}{.5\textwidth}
   %\centering

### 2019-04-29 Chapters/Chapter5.tex
minor changes

@@
 In this Chapter we will study the magnon dispersion for the effective spin Hamiltonian obtained in the last two Chapters.
-The standard way of doing this is to use the Holstein-Primakoff transformation, which maps S-spin operators on a lattice to bosonic creation/annihilation operators.
+The standard way of doing this is to use the Holstein-Primakoff transformation \cite{Auerbach,Nolting2009}, which maps S-spin operators on a lattice to bosonic creation/annihilation operators.
 The linear approximation of this transformation leads to a bosonic Hamiltonian which can be diagonalized to obtain the magnon dispersion relation.
@@
 \end{align*}
-Now the $S^2$ term is a constant that lowers the energy of the antiferromagnet, therefore is shall not be taken into account to compute the magnon dispersion.
+Now the $S^2$ term is a constant that lowers the energy of the antiferromagnet.
 The term $\hat{a}^\dagger_i \hat{a}_i\hat{b}^\dagger_j \hat{b}_j$ is zeroth order in $S$ and therefore neglected.
@@
 \end{align}
-The new term $\pm \Delta_{\bs{k}}$ breaks the degeneracy between the $\alpha$ modes and the $\beta$ modes. In Figure \ref{Fig.Magnon.Disp} we plot the resulting energy dispersion of \ref{DispWithDMI}.
+The new term $\pm \Delta_{\bs{k}}$ breaks the degeneracy between the $\alpha$ modes and the $\beta$ modes.
+In Figure \ref{Fig.Magnon.Disp} we plot the resulting energy dispersion of \ref{DispWithDMI}.
+This dispersion relation has already been studied in \cite{Zyuzin2016,Cheng2016}.
 

### 2019-05-02 Paper/paper.tex
paper update

--- 2019-03-10 Paper/paper.tex
@@
 \usepackage{epstopdf}
+\usepackage{braket}
 %\usepackage{caption}
@@
 \begin{document}
-\title{Ultrafast Control of Spin-Spin Interactions in Two-Dimensional Magnets}
+\title{Ultrafast Control of Spin Interactions in  Honeycomb Antiferromagnetic Insulators}
 
@@
 \author{Alireza Qaiumzadeh}
-%\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
+\thanks{Corresponding author: alireza.qaiumzadeh@ntnu.no}
 \affiliation{Center for Quantum Spintronics, Department of Physics, Norwegian University of Science and Technology, NO-7491 Trondheim, Norway}
@@
 \begin{abstract}
-Light provides ultrafast control of exchange and Dzyaloshinskii-Moriya interactions, we consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half-filling and in the strongly correlated limit, i.e., the Mott insulator regime of a canted antiferromagnet.
-Based on the Floquet theory, we demonstrate that changing the amplitude and frequency of circularly polarized laser pulses, tunes the amplitude, the sign and even the ratio between these two spin interactions.
-Furthermore, the renormalizations of the spin interactions are helicity independent.
-Our results pave the way for ultrafast optical manipulation of spins in recently discovered two-dimensional magnetic materials.
+Light enables ultrafast, direct and nonthermal control of the exchange and Dzyaloshinskii-Moriya interactions.
+We consider two-dimensional honeycomb lattices described by the Kane-Mele-Hubbard model at half filling and in the strongly correlated limit, i.e., the Mott insulator phase of a canted antiferromagnet.
+Based on Floquet theory, we demonstrate that by changing the amplitude and frequency of polarized laser pulses, one can tune the amplitudes and signs of and even the ratio between the exchange and Dzyaloshinskii-Moriya spin interactions.
+Furthermore, the renormalizations of the spin interactions are independent of helicity.
+Our results pave the way for ultrafast optical spin manipulation in recently discovered two-dimensional magnetic materials.
 \end{abstract}
@@
 
-\textit{Introduction}.--- The discovery of all-optical control of the order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by ultrashort, intense and high-frequency laser pulses has transformed spintronics to a new era of ultrafast magnetism \cite{kimel2005ultrafast,Rasing}.
-Although the underlying microscopic mechanism remains unclear, there have been many attempts to uncover its origins.
-Recently, it has been theoretically proposed that laser pulses can modify and even reverse the sign of the exchange interaction \cite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018}, the strongest spin interaction in magnetic systems.
-This finding has been supported by recent experiments \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
-Another important spin interaction is the Dzyaloshinskii-Moriya interaction (DMI), an antisymmetric exchange interaction in inversion symmetry broken systems, where the chiral symmetry of the system is broken \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
-While this interaction is much weaker than the exchange interaction, its presence has important consequences in magnetic materials and causes weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, topological objects like chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phase of topological magnon insulators \cite{Owerre2016, Elyasi2018, Chen2018, Owerre1, Owerre2}.
-The ratio between these two interactions controls the tilting angle of the canted spins.
-Finding a mechanism to tune this ratio enables new phenomena in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
+\textit{Introduction}.--- The discovery of all-optical control of the order parameters in antiferromagnetic (AFM) and ferromagnetic (FM) materials by means of ultrashort intense high-frequency laser pulses has propelled spintronics into a new era of ultrafast magnetism \cite{kimel2005ultrafast,2009NatPh...5..727K,Rasing}.
+Despite many attempts to uncover its origin, the detailed underlying microscopic mechanism remains unclear.
+The process triggering ultrafast magnetization dynamics phenomena may rely on either thermal or nonthermal mechanisms \cite{heat-light,Rasing}.
+Thus far, it has been believed that ultrafast {\it{nonthermal}} manipulation of spins is possible only through either a direct coupling between the magnetic field component of the laser pulses and the spins or an indirect coupling between the electric field component of the light and the spins via spin-orbit coupling \cite{Rasing,Mikhaylovskiy2015,AlirezaQ1,AlirezaQ2}.
+Recent experiments have demonstrated that laser pulses can directly modify the amplitude and sign of the exchange interaction, which is the strongest spin interaction in magnetically ordered systems \cite{2018Natur.553..481G,Mikhaylovskiy2015,Perakis,PhysRevLett.93.197403}.
+Refs.
+\onlinecite{PhysRevLett.113.057201,PhysRevLett.115.075301,Mentink2015,PhysRevLett.118.097701,Stepanov2017,Kitamura,MentinkReview,Barbeau2018} have theoretically proposed that a direct coupling between the electric field of the light and the spins facilitates nonthermal optical modification of the exchange interaction, in agreement with recent experiments \cite{2018Natur.553..481G,Mikhaylovskiy2015}.
 
-Another recent important breakthrough in spintronics is the discovery of two-dimensional (2D) van der Waals AFM and FM materials with metallic, semiconducting and insulating band structures \cite{2D1,2D2}.
-The advantage of low dimensionality and magnetic order in the same material enables novel spintronics devices with exceptional performances.
+In magnetic systems with broken inversion symmetry, there is also an antisymmetric exchange interaction between spins that breaks the chiral symmetry, namely, the Dzyaloshinskii-Moriya interaction (DMI) \cite{dzyaloshinsky1958, moriya1960,Alireza-DMI1, Alireza-DMI2}.
+Although this interaction is considerably weaker than the exchange interaction, it is essential in magnetic materials for enabling weak ferromagnetism in AFM materials \cite{dzyaloshinsky1958, moriya1960}, topological objects such as chiral skyrmions \cite{2009Sci...323..915M,2017NatRM...217031F,AlirezaSk1, AlirezaSk2} and chiral domain walls \cite{Thiaville_2012,Parkin,AlirezaSW}, and exotic phases of topological magnon insulators \cite{Owerre2016,PhysRevLett.117.227201, Elyasi2018, Chen2018, Owerre1, Owerre2}.
+The ratio between the exchange interaction and the DMI controls the tilt angle of the canted spins.
+Finding a mechanism for tuning this ratio can enable new phenomena in ultrafast spin dynamics and switching \cite{Mikhaylovskiy2015,Mentink2015,Stepanov2017,Kitamura}.
 
-In this Letter, we show that intense and high-frequency laser pulses can change the spin-spin interactions and the ratio between the exchange interaction and the DMI dramatically in a wide class of 2D magnetic materials described by the Kane-Mele-Hubbard model.
+Another far-reaching recent breakthrough in spintronics is the discovery of two-dimensional (2D) Van der Waals AFM and FM materials with metallic, semiconducting and insulating band structures \cite{2D1,2D2}.
+The advantages presented by the existence of low dimensionality and magnetic order in the same material enable the development of new spintronics devices with exceptional performance.
+
+In this Letter, we show that intense high-frequency laser pulses can dramatically affect the spin-spin interactions and the ratio between the exchange interaction and the DMI in a broad class of 2D magnetic materials described by the Kane-Mele-Hubbard model.
+We find that light can be used to tune both the sign and magnitude of the AFM exchange interaction, in agreement with the dynamical mean-field theory \cite{Mentink2015}.
+Importantly, we demonstrate that laser pulses can also be used to independently change the sign and magnitude of the DMI, thus enabling rapid control of magnetism.
+The ability to independently control the signs and magnitudes of the exchange interaction and the DMI enables superior control of magnetic textures in 2D magnets.
 
 \textit{Model Hamiltonian}.---
-Electrons in a 2D planar honeycomb lattice in the presence of electron-electron interactions can be described by the Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}.
-The Hamiltonian in the absence of external perturbations is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic SOI $\hat{\mathcal{H}}_{\text{SOI}}$ and the Coulomb interaction between the electrons modelled by the extended Hubbard interaction $\hat{\mathcal{H}}_{\text{int}}$,
+The electron dynamics in 2D planar honeycomb lattices can be described by the Kane-Mele-Hubbard model \cite{Kane2005,PhysRevLett.107.010401,PhysRevLett.106.100403,PhysRevB.82.075106,PhysRevB.84.235149,Griset2012,Auerbach}; see Fig.
+\ref{fig1}.
+In the absence of external perturbations, the Hamiltonian is the sum of the kinetic term $\hat{\mathcal{H}}_t$, the intrinsic spin-orbit interaction (SOI) $\hat{\mathcal{H}}_{\text{SOI}}$, and the repulsive Coulomb interaction between the electrons as modeled in the form of the extended Hubbard interaction $\hat{\mathcal{H}}_{\text{int}}$:
 \begin{equation}
@@
 \end{align}
-Here $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote, respectively, nearest neighbors (NN) and next-nearest neighbours (NNN), $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) are fermionic creation (annihilation) operators for an electron on site $i$ and spin state $\tau=\{\uparrow,\downarrow\}$, $t_1$ and $t_2$ are NN and NNN hopping amplitudes, $\Delta$ is the intrinsic SOI parameter, $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$), $\sigma^{z}$ is the $z$-component of Pauli matrices $\bm{\sigma}$, $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions.
-The presence of the intrinsic NNN SOI, Eq.
+Here, $\langle\cdot\rangle$ and $\langle\langle\cdot\rangle\rangle$ denote nearest neighbors (NN) and next-nearest neighbors (NNN), respectively; $\hat{c}_{i \tau}^\dagger$ and $ \hat{c}_{i \tau}$ are the fermionic creation and annihilation operators, respectively, for an electron at site $i$ and in spin state $\tau=\{\uparrow,\downarrow\}$;
+$t_1$ and $t_2$ are the NN and NNN hopping amplitudes, respectively; $\Delta$ is the intrinsic SOI parameter, and $\nu_{ij}=\pm 1$ depending the hoping orientation from $j$ to $i$ (see Fig.
+\ref{fig1}); $\sigma^{z}$ is the $z$-component of the Pauli matrices $\bm{\sigma}$; and $U_{00}$ and $V_{ij}$ are the on-site and NN Coulomb interactions, respectively.
+The intrinsic NNN SOI, Eq.
 (\ref{Hsoi}), reduces the $\mathrm{SU}(2)$ symmetry of the original Hubbard model to the $\mathrm{U}(1)$ spin group.
-In buckled noncoplanar honeycomb lattices and systems with structural inversion asymmetry, the presence of, respectively, NNN and NN Rashba SOIs, further reduces the symmetry to $Z_2$.
+In buckled non-coplanar honeycomb lattices or systems with structural inversion asymmetry, the presence of NNN or NN Rashba SOIs, respectively, further reduces the symmetry to $Z_2$.
 
@@
 \includegraphics[width=0.6\columnwidth]{kmh.png}
-\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counterclockwise hoping.}
+\caption{A honeycomb cell with NN hopping $t_1$, NNN hopping $t_2$, intrinsic SOI $\Delta$, and $\nu_{ij} = \pm 1$ for clockwise and counterclockwise hopping.}
 \label{fig1}
@@
 
-Using the variational principle, it has been shown that the NN Coulomb interaction can be approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013,Stepanov2017}.
-Thus, we only take into account the local Coulomb interaction in our total Hamiltonian and express the interaction part of the Hamiltonian in Eq.
+Using the variational principle, it has been shown that the NN Coulomb interaction can be approximated by a renormalized local interaction $U =U_{00} - \bar{V}$, where $\bar{V}$ is a weighted average of the NN Coulomb interaction \cite{Schuler2013}.
+Thus, we consider only the local Coulomb interaction in our total Hamiltonian and express the interaction part of the Hamiltonian in Eq.
 (\ref{Hint}) as
@@
 \end{equation}
-where we define the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ with eigenvalues $d$.
-We denote the projection operator to the subspace of states with eigenvalue $d$ (i.e.
-states with exactly $d$ double occupancies) by $\hat{P}_d$.
-We are interested in the strongly correlated regime $U\gg t_{1(2)}$.
-In such a strong-coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) has a much larger energy than those with no double occupancies ($d=0$).
-We obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second-order perturbation theory in the hopping terms.
-Using the following relations,
+where we introduce the doublon number operator $\hat{d} = \sum_{i=1} \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$, which has an eigenvalue of $d$.
+For later use, we define $\hat{P}_d$ as the projection operator onto the subspace spanned by states with eigenvalue $d$, i.e., states with exactly $d$ doublons.
+At site $i$, we can define the projection operator related to double occupancy as $\hat{P}_{i,1} = \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ and the projection operator related to the absence of double occupancy as $\hat{P}_{i,0} = 1 - \hat{P}_{i,1}$ \cite{Fazekas}.
+We can then define the projection operator $\hat{P}_{d}$ for the whole system as follows.
+Let $\mathcal{O}$ and $\mathcal{P}^d(\mathcal{O})$ denote the set of sites on the lattice and the set of subsets of $\mathcal{O}$ with exactly $d$ elements, respectively.
+Then, in compact form, the projection operator reads $\hat{P}_d = \sum_{A \in \mathcal{P}^d(\mathcal{O})} \left\{\prod_{i \in A} \hat{P}_{i,1} \prod_{i \notin A} \hat{P}_{i,0} \right\}$.
+
+We are interested in the strongly correlated regime $U\gg t_{1(2)}$ at half filling.
+In the limit of such strong coupling, any state with a nonzero number of double occupancies ($d \neq 0$) has a much larger energy than a state with no double occupancy ($d=0$).
+We obtain an effective Hamiltonian acting on the $d=0$ subspace by means of second-order perturbation theory in the hopping terms.
+Using the relations
+\begin{subequations}
+\label{SpinOperatorInv1}
 \begin{align}
-&\hat{c}_{i \tau}^\dagger \hat{c}_{i \tau'} = \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow})\delta_{\tau \tau'}  + \bs{S}_i\cdot\bs{\tau}_{\tau', \tau}, \label{SpinOperatorInv1}\\
-&\hat{c}_{i \tau} \hat{c}_{i \tau'}^\dagger = \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) \delta_{\tau \tau'} - \bs{S}_i\cdot\bs{\tau}_{\tau, \tau'}, \label{SpinOperatorInv2}
+&\hat{c}_{i \tau}^\dagger \hat{c}_{i \tau'} = \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow})\delta_{\tau \tau'}  + \bs{S}_i\cdot\bs{\tau}_{\tau', \tau}, \\
+&\hat{c}_{i \tau} \hat{c}_{i \tau'}^\dagger = \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) \delta_{\tau \tau'} - \bs{S}_i\cdot\bs{\tau}_{\tau, \tau'},
 \end{align}
+\end{subequations}
 we find the spin Hamiltonian for 2D AFM Mott insulators,
@@
 H_{\text{S}} =& J_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + J_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j,  \n \\
-&+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \bs{D}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
+&+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \bs{D}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
 \end{align}
-with the following spin-spin interactions,
+with the following spin-spin interactions:
 \begin{subequations}
@@
 &J_{1(2)} = \frac{2t_{1(2)}^2}{U}, \\
-&\bs{\Gamma}_{ij} =\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
+&\bs{\Gamma} =\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
 &\bs{D}_{ij} = \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
@@
 \end{subequations}
-The first and second terms in the spin Hamiltonian, Eq.
-(\ref{MKMHeff0}), are the NN and NNN symmetric Heisenberg AFM exchange interactions, $J_{1(2)}>0$, respectively; the third term is the NNN anisotropic Heisenberg exchange interaction (XXZ-like term) arising from the intrinsic SOI, and finally, the last term is the intrinsic NNN DMI.
-The intrinsic SOI in Eq.
-(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, perpendicular to the honeycomb plane.
+In the spin Hamiltonian given in Eq.
+(\ref{MKMHeff0}), the first and second terms are the NN and NNN symmetric Heisenberg AFM exchange interactions ($J_{1(2)}>0$), respectively; the third term is the NNN anisotropic Heisenberg exchange interaction (an XXZ-like term) arising from the intrinsic SOI; and the last term is the intrinsic NNN DMI.
+The intrinsic SOI in the Kane-Mele-Hubbard model, Eq.
+(\ref{Hsoi}), leads to a DMI vector, $\bs{D}_{ij}$, that is perpendicular to the honeycomb plane.
 It can also be shown that the Rashba SOI results in an in-plane DMI vector that is perpendicular to the lattice bonds.
-For the sake of completeness, we explain shortly the effect of disorder by adding an on-site disorder potential $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ in the Kane-Mele-Hubbard Hamiltonian Eq.
+
+Although the microscopic derivation of anisotropic exchange interaction in the spin Hamiltonian of Eq.
+(\ref{MKMHeff0}) has been reported before \cite{PhysRevB.82.075106,Vaezi,2017TDM.....4c5002L}, we are not aware of any other microscopic calculation of intrinsic NNN DMI in honeycomb lattices \cite{Owerre2016,PhysRevLett.117.227201,Chen2018}.
+The spin Hamiltonian of Eq.
+(\ref{MKMHeff0}) gives rise to several interesting features and exotic phases, such as the existence of the magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, a topological magnon insulator phase \cite{Owerre2016, PhysRevLett.117.227201, Elyasi2018, Chen2018}, spin Hall effects for Weyl magnons \cite{Zyuzin2018, Sekine2016}, magnonic Floquet topological insulators, spin density waves \cite{Mulder2010}, and chiral and topological gapped spin liquid phases \cite{Vaezi}.
+Ultrafast control of the DMI and the exchange interaction by means of laser pulses can enable engineering of all of these phenomena.
+
+For completeness, let us briefly illustrate the effect of disorder by adding an on-site disorder potential $\sum_{i \tau} \varepsilon_i \hat{c}_{i \tau}^\dagger \hat{c}_{i \tau}$ to the Kane-Mele-Hubbard Hamiltonian given in Eq.
 (\ref{MKMH}), where $\varepsilon_i$ is an uncorrelated random variable.
-Following the above procedure, it can be shown that the spin interaction parameters are renormalized as $U^{-1} \rightarrow U/\left(U^2-(\epsilon_j-\epsilon_i)^2\right)$ \cite{Protopopov2018}.
-In the large $U$ limit, the effect of disorder is negligible and we thus ignore it in the rest of this Letter.
+Following the above procedure, it can be shown that the spin interaction parameters are renormalized as $1/U \rightarrow 1/\left(U-(\epsilon_j-\epsilon_i)^2/U\right)$ \cite{Protopopov2018}.
+In the large $U$ limit and in the presence of very high frequency oscillations, the effect of disorder is negligible; thus, we do not include it in the following.
 
-The terms in the spin Hamiltonian derived in Eq.
-(\ref{MKMHeff0}) have already been obtained phenomenologically \cite{Owerre2016} and confirmed experimentally \cite{Chen2018}.
-To the best of our knowledge, this is the first microscopic derivation of the complete spin Hamiltonian $\hat{H}_{\text{S}}$ from the microscopic Kane-Mele-Hubbard model.
-This Hamiltonian has interesting features and exotic phases like, the existence of magnon spin Nernst effect in collinear AFM layers \cite{Cheng2016, PhysRevLett.117.217203}, topological magnon insulator phase \cite{Owerre2016, Elyasi2018, Chen2018}, spin Hall effects of Weyl magnons \cite{Zyuzin2018, Sekine2016} magnonic Floquet topological insulators, spin density wave \cite{Mulder2010}, chiral and topological gapped spin liquid phases \cite{Vaezi}.
-Ultrafast control of DMI and exchange interaction by laser pulses enables engineering all these phenomena.
+\textit{Laser illumination}.---
+We introduce the effects of laser irradiation in the Kane-Mele-Hubbard Hamiltonian of Eq.
+(\ref{MKMH}) via the Peierls substitution \cite{Peierls1933}.
+The electric field of a polarized laser pulse is  $\bs{E}(t) = E_0( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})/2$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the unit vector representing the laser polarization, with $\lambda= 0$ for linear polarization, and $\lambda= \pm 1$ for right- and left-handed polarizations.
 
-\textit{Laser illumination}.
-The effect of laser irradiation is introduced in the Kane-Mele-Hubbard Hamiltonian, Eq.
-(\ref{MKMH}), via the Peierls substitution method \cite{Peierls1933}.
-The electric-field component of a polarized laser pulse is given by $\bs{E}(t) = \frac{E_0}{2}( e^{-i\omega t}\hat{\epsilon}+\mathrm{c.c.})$, where $E_0$ is the electric field amplitude, $\omega$ is the laser pulse frequency, and $\hat{\epsilon} = (\hat{\mathrm{e}}_x+i\lambda\hat{\mathrm{e}}_y)/\sqrt{1+\lambda^2}$ is the polarization unit vector with $\lambda= 0$ for linear polarization and $\lambda= \pm 1$ for right- and left handed polarizations.
-
-It is more convenient to rewrite the noninteracting part of the Kane-Mele-Hubbard Hamiltonian, Eq.
-(\ref{MKMH}), as $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
-t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i,j$ being NN and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i,j$ being NNN.
-According to the Peierls substitution method, the hopping part of the Hamiltonian gain an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the electronic charge, and $\bs{A}$ is the vector potential of the laser pulse $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
-The Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A} \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|$, in a such way that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
-Now, we use the Jacobi–-Anger expansion to rewrite the Peierls phase in the basis of its harmonics,
+It is convenient to rewrite the noninteracting part of the Kane-Mele-Hubbard Hamiltonian in Eq.
+(\ref{MKMH}) as an effective hopping term $\hat{T}_0=\hat{\mathcal{H}}_{\text{K}}+\hat{\mathcal{H}}_{\text{SOI}} = - \sum_{i,j , \tau, \tau'}
+t_{ij}^{\tau\tau'} \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau'}$, where the hopping amplitude is $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_1$ for $i$ and $j$ that satisfy the NN condition and $t_{ij}^{\tau\tau'} = \delta_{\tau,\tau'}t_2 - i\Delta\nu_{ij}\sigma^z_{\tau, \tau'}$ for $i$ and $j$ that satisfy the NNN condition.
+With the Peierls substitution, the hopping part of the Hamiltonian gains an extra phase $t_{ij}^{\tau\tau'}\rightarrow t_{ij}^{\tau\tau'} e^{{i e \bs{R}_{ij} \cdot \bs{A}(t)}}$, where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$, $e$ is the charge of an electron, and $\bs{A}$ is the vector potential of the laser pulse; $\bs{A}(t) = \frac{1}{2}(\bs{A} e^{-i\omega t} + \mathrm{c.c.})$, with $\bs{A} = \frac{iE_0}{\omega}\hat{\epsilon}$.
+The Peierls phase can be rewritten as $e\bs{R}_{ij}\cdot\bs{A} \equiv \alpha_{ij} e^{i \theta_{ij}}$, with $\alpha_{ij} = \pm|e\bs{R}_{ij}\cdot \bs{A}|$, such that $\alpha_{ij}= -\alpha_{ji}$, $\theta_{ij}= \theta_{ji}$, and $\theta_{ij} \in \left[0,\pi\right)$.
+Now, we can use the Jacobi–-Anger expansion to rewrite the Peierls phase in the basis of its harmonics:
 \begin{equation}
@@
 
-The total Hamiltonian in the presence of the laser field is time dependent through its hopping part, $\hat{H}(t) = \hat{T}(t) +  U\hat{d}$.
-Using Eq.
-(\ref{JacobiAnger}), we find $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$, where $\hat{T}_m$ is the sum of all the \textit{m}-th Fourier mode of the hopping terms.
-We can additionally decompose $\hat{T}_m = \hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m}$, where $\hat{T}_{dm}(t)$ changes the doublon number by adding $d$ double occupancies, $\hat{T}_{dm}(t) = \sum_i \hat{P}_{i+d}\hat{T}_{m}(t)\hat{P}_i$.
-With this, we can write the hopping operator as
+In the presence of the laser field, the hopping term in the Hamiltonian depends on time, $\hat{H}(t) = \hat{T}(t) +  U\hat{d}$.
+From Eq.
+(\ref{JacobiAnger}), we find that $\hat{T}(t) = \sum_m \hat{T}_m e^{im \omega t}$, where $\hat{T}_m$ is the sum of all \textit{m}-th Fourier modes of the hopping terms.
+We can additionally adopt the decomposition $\hat{T}_m = \hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m}$, where $\hat{T}_{dm}(t)$ changes the doublon number by adding $d$ double occupancies and is expressed as $\hat{T}_{dm}(t) = \sum_n \hat{P}_{n+d}\hat{T}_{m}(t)\hat{P}_n$.
+Since the hopping term is of second order in the creation and annihilation operators, it can change the double occupancy of the states only by $\pm1$.
+Thus, we can express the hopping operator as
 \begin{equation}
-\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t},
+\hat{T}(t) = \sum_m (\hat{T}_{-1,m}+\hat{T}_{0,m}+\hat{T}_{1,m})e^{im\omega t}.
 \end{equation}
 
-To find the renormalized spin Hamiltonian, we first derive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,2018NJPh...20i3022R,Floquet2}.
-To this end, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, by using a unitary transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$,
+To find the renormalized spin Hamiltonian in the strongly correlated regime, we first derive an effective static Hamiltonian using the Floquet formalism \cite{Floquet1,2018NJPh...20i3022R,Floquet2}.
+To this end, we transform the original time-dependent Hamiltonian, $\hat{H}(t)$, by using the canonical transformation $\hat{U}(t) = e^{-i\hat{S}(t)}$ \cite{PhysRevLett.116.125301,Kitamura2017}:
 \begin{equation}
@@
 \end{equation}
-We perform the unitary transformation perturbatively in the hopping parameter.
 We can formally express $\hat{T}(t) = \eta \hat{T}(t)$, where $\eta$ plays the role of a bookkeeping parameter in the perturbation expansion.
 We expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$.
-We require that the transformed Hamiltonian must have the same periodicity as the original time-dependent Hamiltonian.
-Thus the unitary transformation must have the same periodicity as the driven laser field so that $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
-Additionally, we impose the transformed Hamiltonian to be block diagonal in the doublon number $d$.
-With the further requirement that $\hat{S}(t)$ does not contain block-diagonal terms we can uniquely determine the unitary transformation.
-Following the same procedure we used for the hopping operator, we write
+We require the transformed Hamiltonian to be  block diagonal in the doublon number operator $\hat{d}$.
+To fulfill this requirement, the unitary transformation $\hat{S}(t)$ must have the same periodicity as $\hat{T}(t)$; consequently, the transformed Hamiltonian $\hat{H}'(t)$ will have the same periodicity as the original Hamiltonian $\hat{H}(t)$.
+Thus, we can write $\hat{S}^{(\nu)}(t) = \sum_m e^{im\omega t}\hat{S}^{(\nu)}_m$.
+With the further requirement that $\hat{S}(t)$ does not contain block-diagonal terms, we can uniquely determine the unitary transformation:
 \begin{equation}
@@
 where $\hat{S}^{(\nu)}_{d,m}$ changes the double occupancy number by $d$.
-We expand the transformed Hamiltonian Eq.
-(\ref{Htransformed}) in power series of $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
-After tedious, but straightforward calculations, the transformed Hamiltonian up to the second order in the hopping parameter is obtained $\hat{H}'(t)= \hat{T}'(t)+\text{U}\hat{d}$, where
+We expand the transformed Hamiltonian of Eq.
+(\ref{Htransformed}) into a power series in $\eta$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ such that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number.
+After tedious but straightforward calculations, we obtain the transformed Hamiltonian up to the second order in the hopping parameter, $\hat{H}'(t)= \hat{T}'(t)+U\hat{d}$, where
 \begin{align}
@@
 &\hat{T}'(t) \approx  - \sum_m \hat{T}_{0,m}(t)e^{im\omega t} + \n \\
-&+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1,n}, \hat{T}_{-1,m-n} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1,n}, \hat{T}_{1,m-n} \right]}{\text{U}-n\omega} \right) e^{im\omega t}.
+&+ \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1,n}, \hat{T}_{-1,m-n} \right]}{U+n\omega} - \frac{\left[\hat{T}_{-1,n}, \hat{T}_{1,m-n} \right]}{U-n\omega} \right) e^{im\omega t}.
 \end{align}
-Now, we are in the situation that we can calculate the effective static Hamiltonian by time averaging of the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the projection operator to the $d=0$ subspace.
-After some algebra, the effective static Hamiltonian in terms of creation and annihilation operators is obtained,
+Now, we calculate the effective static Hamiltonian by time averaging the transformed Hamiltonian $\hat{H}_{\text{eff}}=\hat{P}_0\hat{H}'(t)\hat{P}_0$, where $\hat{P}_0$ is the Gutzwiller projection onto the subspace containing no doubly occupied sites at all, i.e., the $d=0$ subspace \cite{Fazekas}.
+After some algebra, the effective static Hamiltonian is obtained in terms of the creation and annihilation operators:
 \begin{align}
-\hat{H}_{\text{eff}} &= - \sum_{i,j, \tau, \tau'} \left(t_{ij}^{\tau} t_{ji}^{\tau'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \right)  \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \hat{c}_{j \tau'}^\dagger \hat{c}_{i \tau'}.
+\hat{H}_{\text{eff}} &= - \sum_{i,j, \tau, \tau'} \left(t_{ij}^{\tau} t_{ji}^{\tau'} \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega} \right)  \hat{c}_{i \tau}^\dagger \hat{c}_{j \tau} \hat{c}_{j \tau'}^\dagger \hat{c}_{i \tau'}.
 \label{GeneralHeff}
@@
 
-Finally, the spin Hamiltonian at half-filling is obtained using the relations Eqs. (\ref{SpinOperatorInv1}) and (\ref{SpinOperatorInv2}):
+Finally, using the relations in Eq. (\ref{SpinOperatorInv1}), we obtain the spin Hamiltonian at half filling,
 \begin{align}
 \label{MKMHeffw}
-\tilde{H}_{\text{S}}(\omega) =& \tilde{J}_{1}\sum_{\langle i,j \rangle} \bs{S}_i\cdot\bs{S}_j + \tilde{J}_{2}\sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i\cdot\bs{S}_j, \n \\
+\tilde{H}_{\text{S}}(\omega) =& \sum_{\langle i,j \rangle} \tilde{J}_{1,ij} \bs{S}_i\cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \tilde{J}_{2,ij}\bs{S}_i\cdot\bs{S}_j \n \\
 &+ \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \tilde{\bs{\Gamma}}_{ij} \bs{S}_j +\sum_{\langle \langle i,j \rangle \rangle} \tilde{\bs{D}}_{ij}\cdot \bs{S}_i \times \bs{S}_j,
 \end{align}
-with the following renormalized spin interactions,
+with the following renormalized spin interactions:
 \begin{subequations}
@@
 \begin{align}
-&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}, \\
-&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega},\\
-&\tilde{\bs{D}}_{ij} = 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
+&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega}, \\
+&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega},\\
+&\tilde{\bs{D}}_{ij} = 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
 \end{align}
 \end{subequations}
-All spin interaction parameters are renormalized by the same function, but $\alpha_{ij}$ differs for NN and NNN parameters.
-Thus, the ratios between the NN and NNN renormalized parameters are different than those of non-perturbed parameters.
-The renormalized spin interactions presented in Eq.
-(\ref{Renor-para}) are helicity independent.
+All spin interaction parameters are renormalized by the same function, but $\alpha_{ij}$ differs between the NN and NNN parameters.
+Thus, the ratios between the renormalized NN and NNN parameters are different from those for the unperturbed parameters.
+Therefore, in a honeycomb lattice described by the Kane-Mele-Hubbard model, the ratio between the AFM exchange interaction and the intrinsic DMI is different before and after light irradiation, while in a square lattice with the NN Rashba SOI, it is not possible to control this ratio.
+The renormalized spin interactions presented in Eq. (\ref{Renor-para}) do not depend on the helicity in this model.
 
@@
 \vspace{-1cm}
-\caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as a function of the Floquet parameter $\mathcal{E} = \frac{eaE_0}{\omega}$, for two laser frequencies $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
+\caption{Dimensionless exchange interaction (green lines) and DMI (red lines) as functions of the Floquet parameter $\mathcal{E} = \frac{eaE_0}{\omega}$ for two laser frequencies, $\omega = 4$ (solid lines) and $\omega = 14$ (dashed lines).}
 \label{fig2}
@@
 
-Figure \ref{fig2}, shows the dependence of dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
+Figure \ref{fig2} shows the dependence of the dimensionless NN exchange interaction $\tilde{J}_{1,ij}/J_{1,ij}$ and the dimensionless NNN DMI $\tilde{D}_{ij}/D_{ij}$ on the Floquet parameter $\mathcal{E} = \frac{e a E_0}{\omega}$, where $a$ is the lattice constant.
 We show this dependence for two different laser pulse frequencies.
 We set $\hbar = 1$ and $t_1=1$ and measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$.
-The results are obtained for material parameters $t_2=0.1$ and $\text{U} = 10$.
-Figure \ref{fig2}, shows that it is possible not only to change the sign and amplitude of the exchange interaction as already reported in Ref.
-\cite{Mentink2015} but it is possible to change the sign and amplitude of the intrinsic DMI.
-More importantly, the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$ can be tuned by laser excitations which is responsible for ultrafast photoinduced spin dynamics and magnon scattering phenomena.
+The presented results correspond to material parameters of $t_2=0.1$ and $U = 10$.
+Figure \ref{fig2} shows that it is possible not only to change the sign and amplitude of the exchange interaction, as reported in Ref.
+\cite{Mentink2015}, but also to change the sign and amplitude of the intrinsic DMI.
+Figure \ref{fig2} shows that the ratio $\tilde{J}_{1,ij}/\tilde{D}_{ij}\neq J_{1,ij}/D_{ij}$, which is responsible for ultrafast photoinduced spin dynamics phenomena, can be tuned by means of laser excitations in systems with specific symmetries.
 
-Eqs.
-(\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ represent the spatial component of vectors, $i$ and $j$ refer to the lattice site, and $g$ is the opto-magnetic coupling tensor which can be read from Eqs.
+Eqs.\ (\ref{MKMHeffw}) and (\ref{Renor-para}) explicitly show that the spin Hamiltonian in the presence of a time-dependent external field can be effectively written as $\tilde{H}_{\text{S}}=H_{\text{S}}+g_{\alpha \beta i j} S^\alpha_i S^\beta_j E^{\alpha} E^{*\beta} $, where $\alpha$ and $\beta$ represent the spatial components of vectors, $i$ and $j$ refer to lattice sites, and $g$ is the optomagnetic coupling tensor, which can be read off from Eq.
 (\ref{Renor-para}).
-Thus, the dielectric permittivity tensor which determines the optical properties of the medium, is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$.
-This opto-magnetic effect described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the scattered light $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
+Thus, the dielectric permittivity tensor, which determines the optical properties of the medium, is given by $\varepsilon_{\alpha \beta}=\partial^2 \tilde{H}_{\text{S}}/\partial E^{\alpha}\partial E^{*\beta}$.
+The optomagnetic effect, which is described by the dielectric permittivity $\varepsilon$, can be detected by measuring the intensity of the light scattered by magnons, $I_{\mathrm{sc}} \propto (\varepsilon_{\alpha \beta} E_0)^2$ \cite{Demokritov1985}.
 
-In ultrafast spin dynamics experiments, very intense laser pulses are used and one might think on how heating might affect the validity of our approach.
-Recent theoretical \cite{Rudner2019,PhysRevB.97.014311} and experimental \cite{PhysRevA.96.053602} works show that the energy absorption rate is suppressed exponentially for high frequency laser pulses $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, which is the case in ultrafast experiments with optical laser pulses.
-Thus, rapidly driven systems have a very long prethermalization period and this implies that the evolution of these systems in the presence of short laser pulses can be described by our formalism safely.
+In ultrafast spin dynamics experiments, very intense laser pulses are used, and thus, it might be relevant to consider how heating might affect the validity of our approach.
+Recent theoretical \cite{2016AnPhy.367...96K,Rudner2019,PhysRevB.97.014311} and experimental \cite{PhysRevA.96.053602} works have shown that the energy absorption rate is exponentially suppressed for high-frequency laser pulses, i.e., for $\omega/W\gg 1$, where $W\propto t_1$ is the fermionic bandwidth, and this condition holds in ultrafast experiments with optical laser pulses.
+Thus, rapidly driven systems have a very long prethermalization period, implying that the evolution of these systems in the presence of short laser pulses can be safely described by our formalism.
 
-The possibility of ultrafast optical modification of the exchange interactions in the bulk of iron oxides has been recently reported \cite{Mikhaylovskiy2015}.
-We hope that our work will stimulate new experiments on measuring both exchange interaction and DMI in novel 2D magnetic systems.
+The possibility of ultrafast optical modification of the exchange interaction in the bulk of iron oxides has recently been reported \cite{Mikhaylovskiy2015}.
+We hope that our work will motivate new experiments on measuring both the exchange interaction and the DMI in novel 2D magnetic systems.
 
-In summary, we have investigated the effect of polarized and intense high-frequency laser pulses on 2D canted antiferromagnetic Mott insulators using Floquet theory.
-We have found that both sign and amplitude of the ratio between the exchange interaction and DMI is changed in honeycomb lattices irrespective to the helicity of laser pulses.
-Our calculations open a new way to ultrafast and energy-efficient control of spins and engineering of topological objects and topological properties of 2D van der Waals magnetic materials.
+In summary, we have investigated the effect of intense high-frequency polarized laser pulses on 2D canted AFM Mott insulators using Floquet theory.
+We have found that both the sign and the amplitude of the ratio between the exchange interaction and the DMI in a honeycomb lattice can be modified, regardless of the helicity of the laser pulses.
+Our calculations offer a new way to achieve ultrafast and energy-efficient control of spins and, thus, the engineering of topological objects and topological properties for 2D van der Waals magnetic materials.
 

### 2019-05-02 Presentation/presentation.tex
asdf
wrap on
paper update

@@
 \usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
+\usepackage[backend=bibtex,natbib=true,sorting=none,style=nature]{biblatex}
+\bibliography{../MT.bib}
 
@@
 
+%\begin{figure}
+%\includegraphics[width=0.5\linewidth]{../Figures/fm_device.png}
+%\caption{Source: Wikipedia}
+%\end{figure}
+
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{../Figures/fm_device.png}
+  \begin{minipage}[c]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{../Figures/fm_device.png}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.2\textwidth}
+    \caption{Source: Wikipedia} \label{fig:1}
+  \end{minipage}
 \end{figure}
@@
 \frametitle{Antiferromagnetic Spintronics}
+
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{../Figures/afm_device.png}
+  \begin{minipage}[c]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{../Figures/afm_device.png}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.2\textwidth}
+    \caption{Source: Nature, Spin transport and spin torque in antiferromagnetic devices} \label{fig:2}
+  \end{minipage}
 \end{figure}
+
 \end{frame}
@@
 \end{equation}
-In antiferromagnets $J > 0$. Mentink, J. H. et al. showed that it is possible to manipulate the exchange constant by applying a laser field. $J = J_0 + \Delta J$.
+In antiferromagnets $J > 0$ ($J < 0$ for ferromagnets). Mentink, J. H. et al. showed that it is possible to manipulate the exchange constant by applying a laser field. $J = J_0 + \Delta J$.
 \end{block}
@@
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{../Figures/dmi_canting.png}
+  \begin{minipage}[c]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{../Figures/dmi_canting.png}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.2\textwidth}
+    \caption{Source: Nanoscale} \label{fig:3}
+  \end{minipage}
 \end{figure}
+
 \end{block}
@@
 \includegraphics[width=1\linewidth]{../Figures/canted_afm.png}
+\caption{Source: Kimmel presentation}
 \end{figure}
@@
 \begin{frame}
+\begin{figure}
+  \begin{minipage}[c]{0.5\textwidth}
+    \includegraphics[width=\textwidth]{../Figures/NNvsNNN1.pdf}
+  \end{minipage}\hfill
+  \begin{minipage}[c]{0.5\textwidth}
+    \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$.
+Similar results are obtained in \cite{Mentink2015} for $J_{1}$.
+Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
+  \end{minipage}
+\end{figure}
+\footfullcite{Mentink2015}
+\end{frame}
+
+\begin{frame}
 \Huge{\centerline{The End}}

### 2019-05-02 Presentation/presentation.tex
presentation updates

@@
 %\author[author1]{author1\inst{1}\\[1ex]  {\small supervisor1\inst{1,2}}}
-\author[Juan Manuel Losada Sosnovsky]{Juan Manuel Losada Sosnovsky\\[10mm]{\small Supervisor: Alireza Qaiumzadeh}}
+\author[Juan Manuel Losada Sosnovsky]{Juan Manuel Losada Sosnovsky\\[5mm]{\small Supervisors: Arne Brataas and Alireza Qaiumzadeh}}
 \institute[NTNU] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
@@
 \begin{frame}
-\frametitle{Manipulation of the spin state}
+\frametitle{Spin models}
 \begin{block}{Heisenberg model}
 \begin{equation} 
-\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j \nonumber
+\hat{H} = \sum_{\langle i,j \rangle} J \bs{S}_i \bs{S}_j \nonumber
 \end{equation}
@@
 \begin{frame}
-\frametitle{Manipulation of the spin state}
+\frametitle{Spin models}
+The Dzyaloshinskii-Moriya interaction (DMI):
+\begin{equation*}
+\bs{D}_{ij}\bs{S}_i\times\bs{S}_j
+\end{equation*}
+\begin{itemize}
+\item Arises from the spin orbit coupling.
+\item It favours canted order, i.e. weak ferromagnetism in AFM.
+\item Enables topological objects such as chiral skyrmions and chiral domain walls.
+\end{itemize}
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Spin models}
 \begin{block}{Heisenberg model with DMI}
 \begin{equation} 
-\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j + \sum_{\langle i,j \rangle} \vec{D}_{ij}\boldsymbol{S}_i \times \boldsymbol{S}_j\nonumber
+\hat{H} = \sum_{\langle i,j \rangle} J \bs{S}_i \bs{S}_j + \sum_{\langle i,j \rangle} \vec{D}_{ij}\bs{S}_i \times \bs{S}_j\nonumber
 \end{equation}
 
-Under some circumstances this Hamiltonian describes a canted antiferromagnet.
+The ratio between the exchange interaction and the DMI controls the tilt angle of the canted spins.
 
@@
 
+%------------------------------------------------
+
 \begin{frame}
-\frametitle{Manipulation of the spin state}
+\frametitle{Spin models}
 If we can manipulate $J$ and $D$ we can control the canting angle.
@@
 
-\begin{frame}
-\frametitle{Manipulation of the spin state}
-We need $\frac{J}{D} \neq \frac{J+\Delta J}{D+\Delta D}$.
-\\[10mm]
-However, $\frac{J}{D} = \frac{J+\Delta J}{D+\Delta D}$.
-\end{frame}
+%------------------------------------------------
+
+%\begin{frame}
+%\frametitle{Manipulation of the spin state}
+%We need $\frac{J}{D} \neq \frac{J+\Delta J}{D+\Delta D}$.
+%\\[10mm]
+%However, $\frac{J}{D} = \frac{J+\Delta J}{D+\Delta D}$.
+%\end{frame}
+
+%------------------------------------------------
 
 \begin{frame}
-\frametitle{Manipulation of the spin state}
+\frametitle{Model}
+Strongly correlated electrons in a planar honeycomb lattice can be described by:
 \begin{block}{Kane-Mele-Hubbard model}
 \begin{equation}
-\hat{H}_{\text{KMH}} = -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}\nonumber
-\end{equation}
-
-It leads to a spin Hamiltonian:
-
-\begin{equation}
-\hat{H}_{\text{KMH}}^{\text{eff}} = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \nonumber
+\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -
+	\sum_{\langle \langle i,j \rangle \rangle, \sigma, \sigma'}(\delta_{\sigma,\sigma'}t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U}\hat{D}\nonumber
 \end{equation}
@@
 
+%------------------------------------------------
+
 \begin{frame}
-\frametitle{Manipulation of the spin state}
-\begin{block}{Modified Kane-Mele-Hubbard model}
+\frametitle{Model}
+The effective spin Hamiltonian in the strongly correlated regime takes the form:
 \begin{equation}
-\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 + i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
-	\text{U}\hat{D}\nonumber
+\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1}\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma} \bs{S}_j \right\} \nonumber
 \end{equation}
+With:
+\begin{align*}
+&J_{1(2)} = \frac{2t_{1(2)}^2}{U}, \\
+&\bs{\Gamma} =\frac{2\Delta^2}{U} \text{diag}(-1,-1,1),\\
+&\bs{D}_{ij} = \frac{4 t_2 \Delta}{U}\nu_{ij}  \hat{\mathrm{e}}_z.
+\end{align*}
 
-It leads to a spin Hamiltonian:
+\end{frame}
 
-\begin{equation}
-\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\bs{S}_j + \bs{D}_{2,ij} \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\} \nonumber
-\end{equation}
+%------------------------------------------------
 
-What we wanted, in this case if we apply light $\frac{J}{D} \neq \frac{J+\Delta J}{D + \Delta D}$.
+\begin{frame}
+\frametitle{Method}
+\begin{equation*}
+\hat{H} = -\hat{T} + \text{U}\hat{D}
+\end{equation*}
+$\hat{T}$ is a hopping operator, and $\hat{D}$ is the doublon number operator.
+\begin{align*}
+\hat{D} &= \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} \\
+\hat{T} &= \sum_{i,j, \sigma, \sigma'} t_{ij}^{\sigma \sigma'} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'}
+\end{align*}
+$\text{U} \gg t_{ij}^{\sigma \sigma'}$, strongly correlated regime.
+\end{frame}
 
-\end{block}
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Method}
+To account for the laser illumination we use several techniques:
+\begin{itemize}
+\item Peierls substitution.
+\item Apply time dependent unitary transformation.
+\item Expand unitary transformation and transformed Hamiltonian.
+\item Determine unitary transformation.
+\end{itemize}
 \end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Peierls substitution}
+In the presence of a vector potential $\bs{A}(t)$ the hopping amplitudes acquire a time dependent phase:
+\begin{equation*}
+\label{TimeDepHopping}
+t_{ij}^{\sigma \sigma'}(t) = t_{ij}^{\sigma \sigma'} e^{ie\bs{R}_{ij}\bs{A}(t)}
+\end{equation*}
+The Hamiltonian is time dependent.
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Unitary transformation}
+Apply $\hat{U}(t) = e^{-i\hat{S}(t)}$,
+
+\begin{equation*}
+\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
+\end{equation*}
+The goal is $\hat{H}'(t)$ to be block diagonal in $\hat{D}$ up to certain order in the hopping amplitudes.
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Expand transformed Hamiltonian}
+Formally $\hat{T}(t) = \eta\hat{T}(t)$, where $\eta$ plays the role of a bookkeeping parameter in the perturbative expansion.
+\begin{align*}
+\hat{S}(t) &= \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t) \\
+\hat{H}'(t) &= \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)
+\end{align*}
+
+The transformed Hamiltonian can be written:
+
+\begin{equation*} 
+\hat{H}'(t) = \sum_m \frac{1}{m!} \text{ad}_{i\hat{S}(t)}^m \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right)
+\end{equation*}
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Determine unitary transformation}
+We decompose the hopping operator as $\hat{T}(t) = \sum_{d,m} \hat{T}_{d,m}e^{im\omega t}$, where $\hat{T}_{d,m}$ changes the doublon number by $d$.
+\begin{align*}
+\hat{H}'^{(0)}(t) &= \text{U}\hat{D} \\
+\hat{H}'^{(1)}(t) &= -\sum_m \hat{T}_{0,m}(t)e^{im\omega t} \\
+\hat{H}'^{(2)}(t) &= \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
+\end{align*}
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Projecting onto the low energy subspace}
+In the strongly correlated limit we can assume that the Hamiltonian acts only within the $d=0$ subspace, i.e. $\hat{H}_{\text{eff}}=\langle \hat{P}_0\hat{H}'(t)\hat{P}_0 \rangle$. Obtaining:
+\begin{equation*}
+\hat{H}_{\text{eff}} = - \sum_{i,j, \sigma_1, \sigma_2, \sigma_3, \sigma_4}\hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_2} \hat{c}_{j \sigma_3}^\dagger \hat{c}_{i \sigma_4} t_{ij}^{\sigma_1 \sigma_2} t_{ji}^{\sigma_3 \sigma_4} \left\{ \sum_{n} \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \right\}
+\end{equation*}
+Where $\alpha_{ij} = e\bs{R}_{ij}\bs{A}$.
+\end{frame}
+
+%------------------------------------------------
+
+\begin{frame}
+\frametitle{Results}
+If we apply this procedure to the Kane Mele Hubbard model, we get:
+\begin{align*}
+\tilde{H}_{\text{S}}(\omega) =& \sum_{\langle i,j \rangle} \tilde{J}_{1,ij} \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ \tilde{J}_{2,ij}\bs{S}_i\bs{S}_j + \bs{S}_i \tilde{\bs{\Gamma}}_{ij} \bs{S}_j + \tilde{\bs{D}}_{ij} \bs{S}_i \times \bs{S}_j \right\}
+\end{align*}
+with the following renormalized spin interactions:
+\begin{align*}
+&\tilde{J}_{1(2),ij} = 2t_{1(2)}^2\sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega}, \\
+&\tilde{\bs{\Gamma}}_{ij} = 2\Delta^2 \text{diag}(-1,-1,1) \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega},\\
+&\tilde{\bs{D}}_{ij} = 4 t_2 \Delta \sum_n\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{U+n\omega} \nu_{ij} \hat{\mathrm{e}}_z.
+\end{align*}
+\end{frame}
+
+%------------------------------------------------
 
@@
 
+%------------------------------------------------
+
 \begin{frame}
